### 2021-09-27 finalReportPres.tex
Initial commit

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

% \UseRawInputEncoding
\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}

% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=red!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=red!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=red!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

\setbeamertemplate{navigation symbols}{} % Remove navigation symbols
\setbeamertemplate{bibliography item}{\insertbiblabel}  % insert bibliography numbers instead of symbol
\setbeamertemplate{caption}[numbered] % adds the figure or table number to the caption.

% Set up footer manually
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.45\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor\hspace*{1em}(\insertshortinstitute)
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.4\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertframenumber{} / \inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
}

%==============================================================================
%     TITLE
%==============================================================================
\title[Smart Robotic Cart]{Smart Robotic Cart: A Prototype}

\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and Jason~Braker
Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[April~20,~2021]{Tuesday, April~27,~2021}

% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

\subject{Mobile Robot Localization}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

%==============================================================================
%==============================================================================
%     START OF SLIDES
%==============================================================================
%==============================================================================

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline} 
  \tableofcontents%[pausesections]
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\begin{frame}{Introduction}{}
 % \begin{center}
 %    \href{videos/smartRoboticCartIntroVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/finalPresVideoTitle.png}}
 %  \end{center}
\end{frame}

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}
      Design a robotic cart that follows the user without line of sight (LoS) sensors
    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}
      Utilize wireless radio frequency (RF) signal strength to locate and then follow the user
    \end{LARGE}
  \end{block}
\end{frame}

%----------------------------------

%----------------------------------

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
    %     \caption{Shopping Support Robot}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

%----------------------------------

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{Conclusions and Future Work}

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item The algorithm we implemented works the majority of the time
      \item Through tests and gathering data we were able iterate on our approach and tune the algorithms to function more reliably
      \item Our design is cost effective in comparison to other robotic carts
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item Improve the localization algorithm for better angle estimation
      \item Test more reflector designs to see if the XBee signals can be more refined
      \item Implement obstacle detection and avoidance
      \item Multi-frequency radio modules to try to improve distance estimation
    \end{itemize}
  \end{block}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{References}

\begin{frame}{References}
  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
\end{frame}

%==============================================================================
%==============================================================================
%     END OF SLIDES
%==============================================================================
%==============================================================================

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-27 parts/10-introduction.tex
Initial commit

%======================================================================
\chapter{Introduction}
\label{ch:intro}
%======================================================================

%----------------------------------------------------------------------
\section{Motivation and Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are more costly than they are worth.

\vspace*{12pt}
\noindent
In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store. The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field.

\vspace*{12pt}
\noindent
Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}. Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.

\vspace*{12pt}
\noindent
One such method, shown in Fig. \ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
\begin{figure}[H]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob Robot}
   \label{fig:CompaRob}
\end{figure}

In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user. The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves radio reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
% \begin{itemize}
%     \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
%     \item Chapter \ref{ch: sysDesign} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
%     \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
%     \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
%     \item Appendix \ref{ch: coppSimModeling} goes through the steps to model and simulate the Budget Bot chassis in CoppeliaSim
%     \item Appendix \ref{ch: assemblyInstructions} gives the step-by-step procedure for assembling the robot
% \end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-09-27 poster.tex
Initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usepackage{tikz}
\usepackage{todonotes}
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{hyperref}
\usepackage{subfigure}  % Written by Steven Douglas Cochran
\usepackage{amssymb,amsmath,bm}    % From the American Mathematical Society
\usepackage{siunitx} % for units like degree, ...
\sisetup{unitsep=\cdot,binary-units=true}
\usepackage{mathtools}
\usepackage{xcolor,soul}
\usepackage{geometry}
\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=BUred,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=BUred,bg=gray!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=gray!10} % Colors of the body of highlighted blocks

% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.022\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.25in} % Reduce the top margin size
\setlength{\leftmargin}{-0.25in}
\setlength{\rightmargin}{-0.25in}

%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables
%\usepackage{subfigure}

%-----------------------------------------------------------
% TITLE SECTION
%-----------------------------------------------------------

\title{Smart Control of 2 Degree of Freedom Helicopters} % Poster title

\author{Glenn Janiak, Ken Vonckx, Advisor: Dr. Suruz Miah} % Author(s)

\institute{Department of Electrical and Computer Engineering, Bradley University, Peoria IL} %Institution(s)
\vskip -.5cm

%-----------------------------------------------------------
% POSTER CONTENT
%-----------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{1ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
%\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t]

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%-----------------------------------------------------------
% OBJECTIVE AND CONTRIBUTION
%-----------------------------------------------------------

\begin{alertblock}{Objective and Contribution}
%
\textbf{Objective}
\vskip -0.75cm
\begin{itemize}
    \item Develop a platform allowing mobile devices to control the motion of a group of helicopters
\end{itemize}
%\begin{itemize}
%    \item Develop a platform that allows mobile devices to control helicopters with the least amount of error via an embedded system 
%\end{itemize}
%
\vskip -1cm
\textbf{Contribution}
\vskip -0.75cm
\begin{itemize}
    \item Determine trade-offs between traditional control techniques and machine learning
    %\item Embedded System Implementation
    %\item Mobile Device Control 
    \item Multi-Helicopter Application
\end{itemize}
\vskip -0.75cm
\textbf{Applications}
\vskip -0.75cm
\begin{itemize}
    \item Teleoperation approach to search and rescue 
    \item Aerial turbulence resistance 
\end{itemize}

%

\end{alertblock}

%-----------------------------------------------------------
% PROBLEM SETUP
%-----------------------------------------------------------
\vskip -1cm
\begin{block}{Problem Setup}
\vskip -1cm
%\begin{enumerate}
%    \item Develop and linearize system model
%    \item Simulate algorithms in MATLAB
%    \item Test algorithms on desktop computer using USB connection 
%    \item Test algorithms on Raspberry Pi microcontroller
%    \item Test algorithms on mobile device
%\end{enumerate}

\begin{figure}
    \centering
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ProblemStatementImage_Gray2}}
    % \fcolorbox{gray!20}{gray!20}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ipe/highLevel_gry_grn.eps}
    % }
    \caption{High level architecture of the proposed system.}
    \label{fig:highLevelDiagram}
\end{figure}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    % \fcolorbox{gray!10}{gray!10}{
    % \includegraphics[height=.2\textheight,width=.92\textwidth,keepaspectratio=true]{figs/img/quanserAero.png}
    % }
    \caption{2-DOF helicopter (Quanser Aero).}
    %\caption{DC motors are attached to main and tail rotors which allow the helicopter to change its pitch and yaw respectively.}
    \label{fig:helicoterModel}
\end{figure}
\vskip -1cm
$\bullet$ State-space representation of 2-DOF helicopter
\begin{align*}
\begin{bmatrix}
    \dot\theta\\
    \dot\psi\\
    \ddot{\theta}\\
    \ddot{\psi}
\end{bmatrix}&=
%\label{eq:matrixA}
\begin{bmatrix}
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1 \\
    0 & -K_{sp}/J_p & -D_p/J_p & 0 \\
    0 & 0 & 1 & -D_y/J_y 
\end{bmatrix} 
%\label{eq:stateMatrix} 
\begin{bmatrix}
    \theta\\
    \psi\\
    \dot{\theta}\\
    \dot{\psi}
\end{bmatrix}
\\&+
%\label{eq:matrixB}
\begin{bmatrix}
    0 & 0 \\
    0 & 0 \\
    K_{pp}/J_p & K_{py}/J_p \\
    K_{yp}/J_y & K_{yy}/J_y 
\end{bmatrix}
%\label{eq:inputMatrix}
\begin{bmatrix}
    V_p \\
    V_y 
\end{bmatrix}
\end{align*}

\vskip -1cm
\end{block}

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The second column

%-----------------------------------------------------------
% LQR
%-----------------------------------------------------------

\begin{block}{Motion (Trajectory) Control Algorithm}
\vskip -1cm
%\begin{itemize}
%    \item Determines optimal control gain for dynamic systems
%%    \begin{subequations}
%%        \small
%%        \begin{align}
%%            & \dot{x} = Ax + Bu\\
%%            & u = -Kx\\
%%            & J(u) = \int_{0}^{\infty} (x^TQx + u^TRu + 2x^TNu)dt\\
%%            & A^TS+SA-(SB+N)R^{-1}(B^TS+N^T)+Q=0\\
%%            & K=R^{-1}(B^TS+N^T)
%%        \end{align}
%%    \label{eq:LQR_EQ}
%%    \end{subequations}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.92\textwidth,keepaspectratio=true]{figs/ipe/algorithmFramework}}
    \caption{A desired orientation is given by a user.  The difference between this input and the actual position is calculated.  The controller the calculates the proper amount of voltage to apply to the DC motors.}
    \label{fig:algorithmFramework}
\end{figure}
%\end{itemize} 
\vskip -1cm
\begin{enumerate}
    \item Employ state-space representation of 2-DOF helicopter:
    \begin{align*}
        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
    \end{align*}
    \item Use state feedback law
    \begin{center}
        \vskip -1cm
        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
    \end{center}
    \vskip -1cm
    to minimize the quadratic cost function:
    \begin{align*}
        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
    \end{align*}
    \item Find the solution $\mathbf{S}$ to the Riccati equation
    \begin{align*}
        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
    \end{align*}    
    \item Calculate gain, $\mathbf{K}$
    \begin{center}
        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
    \end{center}
\end{enumerate}

%\vskip -2.5cm
\end{block}

%-----------------------------------------------------------
% LQG
%-----------------------------------------------------------

\begin{block}{Optimal Noise Resistant Control Algorithm}
\vskip -1cm
\begin{itemize}
    \item Utilizes gain calculated in LQR
    \item Added Kalman filter to reduce external disturbances to the system
%    \begin{subequations}
%        \small
%        \begin{align}
%            & some eq = x\\
%            & some eq = y\\
%            & some eq = z
%        \end{align}
%    \label{eq:LQG_EQ}
%    \end{subequations}
\end{itemize} 
%\todo[inline]{Insert Dr. Miah's LQG image from his slides here}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[width=1.05\textwidth,keepaspectratio=true]{figs/img/LQG_SimulinkResize.png}}
    \caption{Noise resistant 2-DOF helicopter model.}
    \label{fig:LQGModel}
\end{figure}

%\vskip -2.5cm
\end{block}

\end{column} % End of second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column
%-----------------------------------------------------------
% ADP
%-----------------------------------------------------------

\begin{block}{Reinforcement Learning Algorithm}
\vskip -1cm
\begin{itemize}
    %\item Reinforcement learning based approach
    \item Uses neural network based on difference between desired and actual orientation to determine optimal gain
    %\item Unlike LQR, ADP operates only in discrete-time and calculates new gains as the system is running
%    \begin{subequations}
%        \small
%        \begin{align}
%            & some eq = x\\
%            & some eq = y\\
%            & some eq = z
%        \end{align}
%    \label{eq:ADP_EQ}
%    \end{subequations}
\end{itemize} 
%\begin{enumerate}
%    \item Apply input to the system and calculate error e(k) at time k
%    \item Use Euler's method to convert the error model into discrete-time and record data every $\tau \sec$
%    \begin{center}
%        $e_{k+1}=f(e_k)+G(e_k)u_k$
%    \end{center}
%    \item 
%    %\item Minimize the cost function
%    %\begin{center}
%        $J(u)=\sum_{k=0}^{\infty} e_k^TQe_k+u_k^TRu_k$
%    %\end{center}
%    %\item Define value function
%    %\begin{center}
%        $V(e_k)=$
%    %\end{center}    
%    \item Solve for gain, K
%    \begin{center}
%        $K=0.5R^{-1}B^TP$
%    \end{center}
%\end{enumerate}

\begin{figure}
    \centering
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[width=.9\textwidth,keepaspectratio=true]{figs/ipe/ADP_Neural_Network.eps}}
    \caption{ADP Neural Network}
    \label{fig:NeuralNetwork}
\end{figure}

\vskip 1.5cm
%(1) t = kτ where τ is given
%(2)Advance the system by applying determined inputs to the system and measure system states
%(3)Calculate state error as e[k] = xref[k] − x[k], save state error
%(4) If t 6= T, increment k and start at (1)
%(5) If t = T, update K using collected error data
%(5a)Use error states since last update of K as inputs to the neural network
%(5b)Recursively determine wc values for each of the instances
%(5c)Approximate new wc value using regression analysis of the individually calculated wc values
%(6)Calculate new K using wc values
%(7) Increment k and start at (1)

\vskip -2.5cm
\end{block}
%-----------------------------------------------------------
% Subsystem Block Diagram
%-----------------------------------------------------------
%\begin{block}{Subsystem Block Diagram}
%\begin{figure}
%    \centering
%        \missingfigure{Insert figure.}
%    % \boxed{\includegraphics[width=.92\textwidth,keepaspectratio=true]{figs/ipe/subsystemBlockDiagramAlternate2}}
%    \label{fig:subsystem}
%\end{figure}
%\end{block}

%-----------------------------------------------------------
% SIMULATION RESULTS
%-----------------------------------------------------------

\begin{block}{Simulation Results}
\vskip -1cm
%\begin{itemize}
%    \item \todo[inline]{add LQR and LQG simulation results}
%\end{itemize}

%Before implementing the algorithm, it was simulated using the industry standard robot simulator V-REP. With numerous robot models available, V-REP is able to accurately and consistently produce like those expected in real--world scenarios. Preliminary simulation results can be seen in Fig.~\ref{fig:vrepResults}.

\begin{figure}
    \centering
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch}
    \label{fig:simStepPitch}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw}
    \label{fig:simStepYaw}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch_Volt}
    \label{fig:simPitchVolt}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw_Volt}
    \label{fig:simYawVolt}
    }
    \caption{A comparison between LQG and LQR control for a step input is shown for \subref{fig:simStepPitch}~the~main~rotor and \subref{fig:simStepYaw}~the~tail~rotor and the corresponding voltages in \subref{fig:simPitchVolt}~and~\subref{fig:simYawVolt}}
    \label{fig:simResults}
\end{figure}
\vskip -2cm
\end{block}

\end{column} % End of third column

\begin{column}{\sepwid}\end{column}

\begin{column}{\onecolwid} % The fourth column

%-----------------------------------------------------------
% EXPERIMENTAL RESULTS
%-----------------------------------------------------------

\begin{block}{Experimental Results}
\vskip -1cm
%\begin{itemize}
%    \item ADP Algorithm
%\end{itemize}
\begin{figure}
    \centering
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/ipe/setup.eps}}
    \caption{Experimental Setup}
    \label{fig:Setup}
\end{figure}

\begin{figure}
    \centering
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Pitch_ADP_LQR}
    \label{fig:stepPitchADP}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Yaw_ADP_LQR}
    \label{fig:stepYawADP}
    }
    \caption{ADP experimental results for \subref{fig:stepPitchADP}~the~main~rotor and \subref{fig:stepYawADP}~the~tail~rotor given a step input}
    \label{fig:ADP_Results}
\end{figure}
%\begin{itemize}
%    \item Comparison between different controller architectures (proportional controller and proportional controller with integral term)
%\end{itemize}
\vskip -.5cm

\begin{figure}
    \centering
    \subfigure[][]{
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Pitch_LQR_RMSE}
    \label{fig:stepPitch}
    }
    \subfigure[][]{
    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Yaw_LQR_RMSE}
    \label{fig:stepYaw}
    }
    \caption{Comparison between P and PI control for a step input is shown for \subref{fig:stepPitch}~the~main~rotor and \subref{fig:stepYaw}~the~tail~rotor}
    \label{fig:expResults}
\end{figure}
\vskip -2cm
\end{block}

\begin{figure}
  \centering
  \subfigure[][]{
  \label{fig:time0}
  % \includegraphics[width=0.4\textwidth]{figs/img/timeEquals0.jpg}
  }
  \subfigure[][]{
  \label{fig:time10}
  % \includegraphics[width=0.4\textwidth,height=0.057\textheight]{figs/img/timeEquals10_2}
  }  
  \caption{\subref{fig:time0} Time = 0~and~\subref{fig:time10} Time = 10}
  \label{fig:posistionAtTime}
\end{figure}

%\begin{block}{Conclusion}

%As seen in the experimental results, this system brings moderate accuracy considering its implementation. With a total cost of around \$140 for the system mounted on the mobile robot and around \$23 for the beacons, this system is much more attainable for those conducting research in mapping and localization algorithms and inexpensive to scale to commercial applications.

%\end{block}

%-----------------------------------------------------------
% Conclusion and Future Work
%-----------------------------------------------------------

\begin{alertblock}{Conclusion and Future Work}
\begin{itemize}
    \item Model-based reinforcement learning technique (ADP)  is useful when system model is unknown
   % \item PI controller greatly reduces steady-state error, however increases overshoot and settling time
    \vskip .75cm
    \item Implement PI controller for ADP algorithm
    \item Use digital compass to increase accuracy of orientation and help identify initial position
\end{itemize}

\end{alertblock}

\end{column} % End of the fourth column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-27 proposal.tex
Initial commit

\documentclass[letterpaper,12pt]{article}   %%% Can be report

%% set paper margins
\oddsidemargin=0.1in
\evensidemargin=0.1in
\textwidth=6.0in
\topmargin=-0.7in
\textheight=9.0in
\parindent=0.2in

\usepackage{amsmath,amssymb,bm}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{subfigure}
\graphicspath{%
  {figs/ipe/}
  {figs/dia/}
  {figs/matlab/}
  {figs/imag/}
} 
\usepackage[width=11cm,font=footnotesize,labelfont=bf, %
format=default,justification=centerlast]{caption} % Figure caption text customization

\usepackage{pgfgantt}

\usepackage{booktabs,array} % Packages for tables

\usepackage{hyperref}
\usepackage{soul}
\usepackage{easyReview}
\usepackage{setspace}
\usepackage{multirow}

\usepackage[ruled, vlined, linesnumbered]{algorithm2e} % For algorithms

\usepackage{tikz}
\usetikzlibrary{positioning,fit}

\usepackage{siunitx}
\sisetup{unitsep=\cdot}

\title{ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\
\vspace{0.5in}
Project Title: Robotic Cart
\vspace{1.0in}
\author{Kallistah Allen, Darrah Beebe, and Jason Braker\\ Advisors: Dr.~Suruz Miah and Dr.~Prasad Shastry}
}
%\date{February 6, 2003}  No need to write, Date will be automatically on the title page
\date{}  % Do not show date on the title page

%%%%%%%%%%%%%%%%% Set document line spacing %%%%%%%%%%%%%%%%%%%%%
\singlespacing
%\onehalfspacing
%\doublespacing
% all packages are in the following tex file.
%\input{paper-preamble.tex}
\begin{document}

%%% Make title page 
\begin{titlepage}
 \maketitle

\vspace*{4.0cm}
\begin{center}
\normalsize
Electrical and Computer Engineering Department\\
Caterpillar College of Engineering and Technology\\
\href{http://www.bradley.edu/}{Bradley University}\\

\vspace*{6.0cm}
\copyright~K.~Allen,~D.~Beebe~and~J.~Braker, Peoria, IL, USA, 2020\\

\end{center}
\thispagestyle{empty}

\end{titlepage} 
%%%%%%%%%%%%
%\thispagestyle{empty}
%\maketitle
\newpage
\renewcommand{\contentsname}{Table of Contents}
\tableofcontents
\newpage

\section{Introduction}
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are more costly than they are worth. In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store. The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field. Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.

% \section{Literature Review}
% Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores. See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.

% \vspace*{12pt}
% \noindent
% One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

% \vspace*{12pt}
% \noindent
% In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user. The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.

% \vspace*{12pt}
% \noindent
% The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals. The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals. This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user. Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays. The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment. Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.

% \vspace*{12pt}
% \noindent
% All of the solutions that were found required direct line-of-sight between the robot and the user. In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing. The major challenge of this implementation will be estimating the distance between the robot and the remote in varying environments.

% \section{System Requirements}
% There are three primary requirements for our proposed mobile robotic cart. These requirements are stated as follows:

% \begin{enumerate}
%   \item The mobile cart to follow the remote attached to the user while maintaining a safe distance of $1~[\si{\meter}]$ to $1.5~[\si{\meter}]$. This requirement stems from the intended usage of the project, which is a cart that follows the user. The cart must be able to follow the remote, but it also must be able to keep an appropriate distance so it does not run into the user or fall too far behind.

%   \item The second requirement for the system is that the cart should be able to travel at $1~[\si{\meter\per\second}]$. If the cart can only travel slowly, it will not be as useful since the user will have to walk very slowly to allow the cart to keep up.

%   \item The proposed cart is not to rely on line-of-sight communication between the remote (user) and the cart. In the case that an obstacle gets between the cart and the remote, the communication should be able to be maintained so that the cart still knows where the user is located.
% \end{enumerate}

% \section{System Architecture}
% The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target (user or customer, for example) as shown in \autoref{fig:sys_block_diag}. The proposed mobile cart is a wheeled robot that sends and receives radio signals to follow the remote target. The remote acts as the target for the mobile cart system by sending radio signals back and forth with the cart.

% \subsection{System Block Diagram}
% The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}. There are four inputs to the proposed cart system. Obviously, the robotic cart is powered on through a source of power (input), which is simply a battery, for instance. There will be an on/off switch to allow the system to be powered down when not in use. The motion of the cart will be controlled by the motion of the remote. A stretch goal is to have mode selection buttons to allow the user to put the system into different operating modes which will be explained later on.

% \vspace*{12pt}
% \noindent
% The main output of the system is the trajectory of the cart on the ground. As the user moves with the remote, the cart is supposed to follow the user. The other output of the robotic cart system is status indication in the form of LED lights. These lights will be used to notify the user of the status of the system.

% \begin{figure}[!h]
%     \centering
%     % \includegraphics[scale=0.9]{figs/system_block_diagram_2}
%     \caption{System level block diagram detailing inputs and outputs to the
%       mobile cart system.}
% 	\label{fig:sys_block_diag}
% \end{figure}

% \subsection{Subsystem Block Diagrams}
% Both of the subsystems of the mobile cart system, being the Mobile Cart and Remote Target, act as their own enclosed systems. The two subsystems communicate with one another by relaying radio messages between them. The block diagram of the Remote Target subsystem is shown in \autoref{fig:remote_block_diag}. Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 9 volt battery with a voltage regulation circuit.

% \vspace*{12pt}
% \noindent
% The Mobile Cart subsystem block diagram is shown in
% \autoref{fig:mobile_block_diag}. The Mobile Cart has four inputs. The cart
% requires a power source, which will be a Li-Po battery. The power to the
% subsystem will be toggled by an on/off switch. The buttons for changing the
% operating mode of the cart will be on the cart if we have time to implement
% them. The final input to the mobile cart subsystem is the XBee network messages
% received from the remote target.

% \vspace*{12pt}
% \noindent

% There are three outputs of the mobile cart subsystem. The first is the wheel
% velocities that move the cart. There will also be LEDs to indicate the status of
% the system to the user. Also, the cart will send radio messages to the remote
% target by means of an array of XBee radio modules. %
% %
% \begin{figure}[h!]
%   \centering
%   \missingfigure
%   % \includegraphics[scale=0.9]{figs/remote_target_block_diagram}
%   \caption{Remote Target block diagram}
%   \label{fig:remote_block_diag}
% \end{figure}

% \begin{figure}[h!]
%   \centering
%   % \includegraphics[scale=0.82]{figs/mobile_cart_block_diagram}
%   \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
%   \label{fig:mobile_block_diag}
% \end{figure}

% \subsection{System Components}
% There are several components that are required for the mobile cart system. Although some of these parts are available in the Bradley University laboratory, other parts must be purchased. The parts that exist in the lab are shown in \autoref{tab:Partslablist}. Also, \autoref{tab:Partslist} shows the list of parts that we must purchase. The parts lists shown are the parts needed to build two mobile cart systems.

% \begin{table}[h!]
%   \centering
%   \begin{tabular}{c|c}
%       \toprule
%       \textbf{Quantity} & \textbf{Parts}\\
%       \toprule
%       2 & Budget Bot Chassis\\
%       4 & 10 uF Ceramic Capacitor\\
%       4 & LM1117 Regulator\\
%       2 & Battery Packs for Budget Bot\\
%       8 & 9V Batteries\\
%       4 & Solderable PCB Boards\\
%       3 & XBee USB Adapter\\
%       \bottomrule
%       %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
%       %\bottomrule
%   \end{tabular}
%   \caption{Parts Available in Laboratory}
%   \label{tab:Partslablist}
% \end{table}

% \begin{table}[h!]
%   \centering
%   \begin{tabular}{c|c|c}
%     \toprule
%     \textbf{Quantity} & \textbf{Parts} & \textbf{Price}\\
%     \toprule
%     4 & Pololu 37D Metal Gear motor 4751 & \$ 39.95\\
%     12 & XBee S2C Module & \$ 23.10\\
%     10 & XBee Adapter Board & \$ 4.99\\
%     2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99\\
%     1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99\\
%     1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99\\
%     1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
%     \bottomrule
%     \multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
%     \bottomrule
%   \end{tabular}
%   \caption{Purchased parts for the Robotic Cart Project}
%   \label{tab:Partslist}
% \end{table}

% \vspace*{12pt}
% \noindent
% The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}). Another major component is the reflector array that
% will be used to directionalize the RF signals received from the remote target that is with the user.

% \begin{figure}
%   \centering
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
%     \captionsetup{width=\textwidth}
%     \caption{Budget Bot Chassis}
%     \label{fig:budgetBotChassis}
%   \end{minipage}%
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
%     \captionsetup{width=\textwidth}
%     \caption{BeagleBone Blue}
%     \label{fig:beagleboneBlue}
%   \end{minipage}
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
%     \captionsetup{width=\textwidth}
%     \caption{XBee S2C Module}
%     \label{fig:XBeeModule}
%   \end{minipage}
% \end{figure}

% \vspace*{12pt}
% \noindent
% The reflector array will be mounted on top of the cart where it will be attached with a stepper motor. There are two reflector designs that we will be evaluating in this project. The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly. Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array. The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this. To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}. The lower half of this reflector is paraboloidal in shape to limit the signals coming from below. The upper part of the reflector is strictly parabolic. This shape focuses the signals in the horizontal plane, but allows signals from above to still be received. We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape. Both models will then be tested to determine which design works better.

% \begin{figure}[h!]
%   \centering
%   \begin{minipage}[t]{0.5\textwidth}
%     \centering
%     % \includegraphics[height=2in]{figs/img/paraboloidalReflector}
%     \captionsetup{width=\textwidth, justification=raggedright}
%     \caption{Paraboloidal Reflector Model}
%     \label{fig:parabolodialReflector}
%   \end{minipage}
%   \begin{minipage}[t]{0.4\textwidth}
%     \centering
%     % \includegraphics[height=2in]{figs/img/parabolicReflector}
%     \captionsetup{width=\textwidth, justification=raggedright}
%     \caption{Combined Parabolic/Paraboloidal Reflector}
%     \label{fig:parabolicReflector}
%   \end{minipage}
% \end{figure}

% \subsection{Operation of Mobile Cart System}
% The Mobile Cart will controlled by a central embedded computer which we are using the BeagleBone Blue for. Two DC motors will be used to drive wheels to move the cart. Five XBee modules will be used to allow communication with the remote target. One of these radio sensors will be mounted on top of the cart to broadcast in all directions. The other four sensors will be placed inside parabolic reflectors at right angles to each other. This sensor array will be mounted on a stepper motor to allow rotation.

% \vspace*{12pt}
% \noindent

% There are two main steps in the operation of the robotic cart system. The first step is localization of the remote in the robot's local coordinate frame. Once the location of the remote is known, the navigation step handles the control of the wheel velocities to move the cart to the desired location. A flowchart of the system operation is shown in \autoref{fig:sysOpFlowchart}.

% \begin{figure}
%   \centering
%   \input{figs/dia/systemOperationFlowchart.tex}
%   \caption{Flowchart of System Operation}
%   \label{fig:sysOpFlowchart}
% \end{figure}

% \subsection{Algorithms}
% As mentioned previously, there are two steps in the operation of the system. These steps are the localization of the remote and the navigation of the robot. This section describes the algorithms used for these tasks.

% \subsubsection{Localization Algorithm}
% The strength of the radio signals between the cart and remote will be used to estimate the position of the remote relative to the cart. By rotating the sensor array 90 degrees and measuring the signal strength of messages from the remote at several steps in the rotation, the bearing of the remote can be estimated as the direction in which the maximum signal strength is received. To estimate the distance between the cart and the remote, the signal strength will be measured and used to calculate the distance. The omnidirectional radio module on top will be responsible for coordinating the messages from the remote by sending the remote commands that tell the remote when to send signals. A flowchart of the localization algorithm is shown in \autoref{fig:locAlgoFlowchart}. Also, a pseudo-code version of the algorithm is shown in \autoref{alg:locAlgo}

% \begin{figure}
%   \centering
%   \input{figs/dia/localizationAlgoFlowchart.tex}
%   \caption{Flowchart of Localization Algorithm}
%   \label{fig:locAlgoFlowchart}
% \end{figure}

% \begin{algorithm}[h!]
%   \SetAlgoLined
%   \KwOut{Range $d_{ref}$ and Bearing $\theta_{ref}$ of remote}
%   Constants: step angle $\theta_{step}$\\
%   Static direction variable $dir = 1$
%   \Begin
%   {
%     \uIf{Reflectors not rotated 90\textdegree}
%     {
%       Send signal strength request to remote\\
%       Get signal strengths from receivers\\
%       Rotate reflectors through an angle of $dir*\theta_{step}$\\
%     }
%     \Else
%     {
%       $\theta_{ref} =$ direction of max signal strength\\
%       Compute $d_{ref}$ using signal strength\\
%       $dir = -dir$\\
%     }
%   }
%   \caption{Localization Algorithm}
%   \label{alg:locAlgo}
% \end{algorithm}

% \subsubsection{Navigation Algorithm}
% Once the bearing and distance of the remote are estimated, the cart must move to follow the remote. We will use a modified Point Navigation algorithm to navigate the robot to follow the remote. The robot will estimate the coordinates of the remote with respect to the robot's local reference frame. The robot will then apply actuation to move to the point that is a set following distance from the remote. A flowchart of the navigation algorithm is shown in \autoref{fig:navAlgoFlowchart}. Also, a pseudo-code version of the algorithm is shown in \autoref{alg:navAlgo}.

% \begin{figure}
%   \centering
%   \input{figs/dia/navigationAlgoFlowchart.tex}
%   \caption{Flowchart of Navigation Algorithm}
%   \label{fig:navAlgoFlowchart}
% \end{figure}

% \begin{algorithm}[h!]
%   \SetAlgoLined
%   \KwIn{Range $d_{ref}$ and Bearing $\theta_{ref}$ of Remote}
%   \KwOut{Mobile Robot Trajectory}
%   Constants: following distance $d_f$ and proportional gains $K_p$ and $K_\omega$\\
%   \Begin
%   {
%     Compute target point with respect to robot's local frame as $x_{ref} = (d_{ref} - d_f)\cos \theta_{ref}$, $y_{ref} = (d_{ref} - d_f)\sin \theta_{ref}$\\
%     Compute linear speed $v(t) = sign(x_{ref})K_p\sqrt{x_{ref}^2 + y_{ref}^2}$\\
%     Compute $\omega(t) = K_\omega \theta_{ref}$\\
%     Apply wheel speeds to robot\\
%   }
%   \caption{Navigation Algorithm}
%   \label{alg:navAlgo}
% \end{algorithm}

% % \subsection{Specifications}

% % \section{Preliminary Work}

% % \subsection{Modelling} \label{sec:model}

% % \subsection{Simulation Results} \label{sec:simresults}

% % \subsection{Design} \label{sec:design}

% % \subsection{Experimental Activities} \label{sec:expresults}

% % \section{Parts List}

% \section{Timeline and Milestones} \label{sec:timeline}

% \begin{figure}
%   \centering
%   \begin{ganttchart}[
%     hgrid,
%     vgrid,
%     x unit=.6cm,
%     y unit title=.8cm,
%     y unit chart=.6cm,
%     milestone label font=\tiny,
%     milestone progress label font = \tiny,
%     milestone progress label anchor = east,
%     bar label font=\tiny,
%     group label font=\small,
%     bar/.append style={fill=green},
%     bar incomplete/.append style={fill=red},
%     group progress label font = \tiny,
%     progress label text={$\displaystyle#1\%$},
%     group progress label anchor = east,
%     bar progress label font = \tiny,
%     bar progress label anchor = east,
%     ]{1}{17}

%     \gantttitle{2020}{17}\\
%     \gantttitle{Sep}{4}
%     \gantttitle{Oct}{4}
%     \gantttitle{Nov}{4}
%     \gantttitle{Dec}{4}
%     \gantttitle{}{1}\\

%     \ganttgroup[progress = 100]{Research}{3}{12} \\
%     \ganttbar[progress = 100]{Research Multipath}{3}{12}\\
%     \ganttbar[progress = 100]{Research Reflector}{3}{12}\\

%     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
%     \ganttbar[progress = 80]{CoppeliaSim simulation}{8}{10}\\
%     \ganttmilestone[progress = 0]{Simulation Complete}{10}\\

%     \ganttgroup[progress = 100]{Project Proposal}{11}{12}\\
%     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
%     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\

%     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
%     \ganttbar[progress = 90]{Voltage Regulator Circuit}{13}{13}\\
%     \ganttbar[progress = 80]{Configuration with X-CTU}{14}{14}\\
%     \ganttbar[progress = 90]{Sensing RSSI}{14}{14}\\
%     \ganttbar[progress = 70]{Serial Communication}{14}{14}\\
%   \end{ganttchart}
% \caption{Gantt chart for Fall 2020}
% \label{fig:gantt1}
% \end{figure}

% \begin{figure}
%   \centering
%   \begin{ganttchart}[
%     hgrid,
%     vgrid,
%     x unit=.6cm,
%     y unit title=.8cm,
%     y unit chart=.6cm,
%     milestone label font=\tiny,
%     milestone progress label font = \tiny,
%     milestone progress label anchor = east,
%     bar label font=\tiny,
%     group label font=\small,
%     bar/.append style={fill=green},
%     bar incomplete/.append style={fill=red},
%     group progress label font = \tiny,
%     progress label text={$\displaystyle#1\%$},
%     group progress label anchor = east,
%     bar progress label font = \tiny,
%     bar progress label anchor = east,
%     ]{1}{18}
%     \gantttitle{2021}{18}\\
%     \gantttitle{Jan}{2}
%     \gantttitle{Feb}{4}
%     \gantttitle{Mar}{4}
%     \gantttitle{Apr}{4}
%     \gantttitle{May}{4}\\

%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
%     \ganttbar[progress = 0]{Replace Motors}{3}{3}\\
%     \ganttbar[progress = 0]{Design and Construct Reflector}{3}{4}\\
%     \ganttbar[progress = 0]{Mount Reflector}{4}{4}\\
%     \ganttmilestone[progress = 0]{Assembly Complete}{4}\\

%     \ganttgroup[progress = 10]{Software}{5}{6}\\
%     \ganttbar[progress = 20]{XBee Library}{5}{5}\\
%     \ganttbar[progress = 0]{Control Library}{6}{6}\\

%     \ganttgroup[progress = 0]{Angle Estimation}{7}{8}\\
%     \ganttbar[progress = 0]{Rotate XBee on Stepper Motor}{7}{7}\\
%     \ganttbar[progress = 0]{Determine Angle}{8}{8}\\

%     \ganttgroup[progress = 0]{Distance Estimation}{9}{10}\\
%     \ganttbar[progress = 0]{Calibrate Distance Calculation}{9}{10}\\

%     \ganttgroup[progress = 0]{Subsystem Integration}{11}{15}\\
%     \ganttbar[progress = 0]{Angle Estimation Testing}{11}{11}\\
%     \ganttbar[progress = 0]{Distance Estimation Testing}{12}{13}\\
%     \ganttbar[progress = 0]{System Testing}{14}{15}\\
%     \ganttmilestone[progress = 0]{Integration Complete}{15}\\

%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
%     \ganttbar[progress = 0]{Final Report}{16}{16}\\
%     \ganttbar[progress = 0]{Final Presentation}{17}{17}\\
%     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
%     \ganttbar[progress = 0]{Project Demo}{17}{17}\\

%     \ganttmilestone[progress = 0]{Project Complete}{17}
%   \end{ganttchart}
%   \caption{Gantt Chart for Spring 2020}
%   \label{fig:gantt2}
% \end{figure}

% The Gantt charts in Figures \ref{fig:gantt1} and \ref{fig:gantt2} show our planned schedule to complete this project. In these charts, there are four sections in each month represented by the dotted grid. This is to approximate a weekly schedule. Our first milestone is to complete the simulation of the system in MATLAB and CoppeliaSim. This includes simulating a remote as well as the robotic cart. The simulation of the RSSI detection will be handled in Matlab based on the positions of the cart and remote. We will add noise to the simulated RSSI in order to simulate the multipath effect. The expected functionality is that the cart will follow the remote.

% The second milestone is to complete the assembly of both the cart and the remote. The cart assembly involves replacing the existing motors with the purchased motors, as well as mounting the stepper motor, reflector, and XBee on top of the robot. The assembly of the remote involves constructing the voltage regulator circuit.

% The third milestone is to integrate the subsystems into one system. This will involve testing the angle and distance estimation from the cart to the remote. It will also include testing the following capabilities of the overall system. We expect that this will require a large amount of debugging and tuning. Therefore, we have allotted several weeks for this purpose.

% The fourth and final milestone is to complete the final report and presentation. This involves documenting our findings in a report and presenting our work. At this point, the project will be complete.

\section{Concluding Remarks}
A robotic cart that follows the user is a useful application of mobile robotics. Although some methods of performing this task have been developed, the existing methods require line-of-sight sensing between the robot and the cart. Our proposed robotic cart system does not require line-of-sight since it uses analog wireless signal strength as opposed to ultrasonic or photographic sensing. In this way, we plan to develop a robotic cart that can detect the user even in the presence of obstacles.

\pagebreak
\bibliographystyle{IEEEtran}
\bibliography{bib/references.bib}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-27 proposalPres.tex
Initial commit

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

% \UseRawInputEncoding
\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{fontawesome5}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}

\usepackage[ruled, vlined, linesnumbered]{algorithm2e} % For algorithms

\usepackage{amsmath} % For typesetting math

% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=red!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=red!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=red!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

\setbeamertemplate{bibliography item}{\insertbiblabel}  % insert bibliography numbers instead of symbol
\setbeamertemplate{caption}[numbered] % adds the figure or table number to the caption.

\title[Robotic Cart System (Proposal)]{Robotic Cart System}

% % A subtitle is optional and this may be deleted
\subtitle{Product Proposal}

\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and
Jason~Braker
Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[December~3,~2020]{Thursday, December~3,~2020}

% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

% \subject{Mobile Robot Localization}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each section:
\AtBeginSection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline} 
  \tableofcontents%[pausesections]
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\begin{frame}{Introduction}
  % \begin{center}
  %   % \href{videos/proposalVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/proposalVideoTitle}}
  % \end{center}
  % \begin{center}
  %   \includemedia[
  %     width=\textwidth,
  %     height=0.7\textheight,
  %     label=proposalVideo,
  %     % activate=onclick,
  %     % playbutton=fancy,
  %     addresource=videos/proposalVideo.mp4,
  %     flashvars={source=videos/proposalVideo.mp4}]
  %     {}{VPlayer.swf}
  %     \\
  %     % \mediabutton[
  %     %   mediacommand=proposalVideo:playPause,
  %     %   overface=\color{blue}{\fbox{\strut \faPause\ \faPlay}},
  %     %   downface=\color{red}{\fbox{\strut \faPause\ \faPlay}}
  %     % ]{}
  %     % \mediabutton[
  %     %   mediacommand=proposalVideo:setSource
  %     %   [(videos/proposalVideo.mp4)]]{\fbox{Introduction Video}}
  % \end{center}
\end{frame}

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}
      Design a robotic cart that follows the user.
    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}
      Utilize wireless signal strength to locate and then follow the user.
    \end{LARGE}
  \end{block}
\end{frame}

% \begin{frame}{Introduction}{}
% %\documentclass{beamer}
%   % applications of mobile robot navigation and problem description
%   \begin{block}{Applications of Mobile Carts}
%     \begin{itemize}
%       %\item Mail delivery
%       %\item Transferring files in offices
%       \item Carrying medical supplies in hospitals (Fig.\ref{fig:medCart})
%       \item Carrying materials and tools in factories (Fig. \ref{fig:factCart})
%       \item Shopping carts for ease of use and people with disabilities
%     \end{itemize}
%   \end{block}
%       \begin{figure}
%       \centering
%       \begin{minipage}[t]{0.5\textwidth}
%         \centering
%         \includegraphics[height=3.0cm]{figs/img/MedicalRoboticCart}
%         \caption{Medical Mobile Robotic Cart\textsuperscript{a}}
%         \label{fig:medCart}
%       \end{minipage}
%       \begin{minipage}[t]{0.4\textwidth}
%         \centering
%         \includegraphics[height=2.0cm]{figs/img/FactoryRoboticCart}
%         \caption{Factory Mobile Robotic Cart\textsuperscript{b}}
%         \label{fig:factCart}
%       \end{minipage}
%       \end{figure}
%     \begin{tiny}
%       \textsuperscript{a}https://www.cnet.com/news/robots-give-a-helping-hand-in-san-franciscos-newest-hospital/\\\textsuperscript{b}https://www.greencarcongress.com/2020/05/20200515-nvidia.html
%     \end{tiny}
% \end{frame}

%----------------------------------

\section{Literature Review}

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
        Mobile platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

%----------------------------------

% \begin{frame}{Literature Review}
%   \begin{block}{Existing Solution}
%         Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
%   \end{block}
%     \begin{figure}[b]
%         \centering
%         \includegraphics[width=0.40\textwidth]{figs/img/ShoppingSuportRobot}
%         \caption{Shopping Support Robot}
%         %\label{fig:sysBlockDiag}
%     \end{figure}
% \end{frame}

% %----------------------------------

% \begin{frame}{Literature Review}
%   \begin{block}{Existing Solution}
%     Arduino MEGA 2560, six ultrasonic sensors, two DC motors with Pulse Width Modulation (PWM), an Android Studio IDE device, and Bluetooth~\cite{Rawashdeh2017-Person}
%   \end{block}
%     \begin{figure}[b]
%         \centering
%         \includegraphics[width=0.50\textwidth]{figs/img/SmartCart}
%         \caption{Smart Cart Robot}
%         %\label{fig:sysBlockDiag}
%     \end{figure}
% \end{frame}

%----------------------------------

\begin{frame}{Existing Solutions}
  \begin{block}{Problems}
    \begin{itemize}
      \item Require line-of-sight between robot and user
      \item Some require costly dedicated image processing hardware
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Benefits of Proposed Solution}
    \begin{itemize}
      \item Line-of-sight is not required since analog RF signals will be used
      \item RF components are cost-effective
    \end{itemize}
  \end{block}
\end{frame}

%----------------------------------

% \begin{frame}{Literature Review}
%   \begin{block}{Multipath Interference}
%     \begin{itemize}
%       \item Proposed solutions to multipath interference
%       \begin{itemize}
%         \item Course estimation calculations such as recieved signal strength indicator (RSSI) and time difference of arrival (TDoA)
%         \item IEEE 802.11b wireless Ethernet device to measure RF signals
%         \item Sampling radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position
%       \end{itemize}
%     \end{itemize}
%   \end{block}
%       \begin{figure}[b]
%         \centering
%         \includegraphics[width=0.40\textwidth]{figs/img/MultipathFading}
%         \caption{Multipath Fading}
%         %\label{fig:sysBlockDiag}
%     \end{figure}
% \end{frame}

% %----------------------------------

% \begin{frame}{Literature Review}
%   \begin{block}{Challenges}
%     \begin{itemize}
%       \item Communication between the robot and the remote
%       \item Buffer distance between the robotic cart and the customer without using line of sight sensing
%     \end{itemize}
%   \end{block}
% \end{frame}

%----------------------------------

\section{System Requirements}
\begin{frame}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      \item Cart should be able to follow the remote target
      \item Cart should maintain a distance of 1~[\si{\meter}] to 1.5~[\si{\meter}] from the remote target.
      \item Cart should be able to attain a speed of at least 1~[\si{\meter\per\second}]
      \item Cart should not require line-of-sight to follow remote
     \end{itemize}
  \end{block}
\end{frame}

%----------------------------------

%----------------------------------

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    \begin{LARGE}
      \begin{itemize}
        \item Develop a robotic cart system utilizing wireless signal strength to locate and follow the user.
        \begin{itemize}
          \item Does not require line-of-sight
          \item Low-cost design
        \end{itemize}
      \end{itemize}
    \end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Inaccurate distance measurements due to multipath effect from environment
      \item Achieving full 360\textdegree measurement in short enough time
    \end{itemize}
  \end{block}
\end{frame}

%----------------------------------

\section{References}

% \begin{frame}{References}
%   \bibliographystyle{IEEEtran}
%   \begin{itemize}
%     \item N. Rawashdeh, R. Haddad, O. Jadallah, and A. To’ma, “A person-following
% robotic cart controlled via a smartphone application: design and evaluation,”
% 09 2017, pp. 1–5.
%     \item M. M. Islam, A. Lam, H. Fukuda, Y. Kobayashi, and Y. Kuno, “An intelligent
% shopping support robot: understanding shopping behavior from 2d skeleton data using gru network,” ROBOMECH Journal, vol. 6, no. 1, 2019.
%     \item J. Sales, J. Marti, R. Marin Prades, E. Cervera, and P. Sanz, “Comparob: The
% shopping cart assistance robot,” International Journal of Distributed Sensor Networks, vol. 2016, pp. 1–15, 02 2016.
%     \item M. S. Miah, J. Knoll, and K. Hevrdejs, “Intelligent range-only mapping and navigation for mobile robots,” IEEE Transactions on Industrial Informatics, vol. 14, no. 3, pp. 1164–1174, 2018.
%     \item D. Li and S. Lane, “A novel and versatile parabolic reflector that significantly
% improves wi-fi reception at different distances and angles,” 2013.

%   \end{itemize}

% \end{frame}

%----------------------------------

\begin{frame}{References}

  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
% 	\begin{itemize}
% 		\item T. Xie, H. Jiang, X. Zhao, and C. Zhang, “A wi-fi-based wireless indoor position sensing system with multipath interference mitigation,” Sep 2019. [Online].
% Available: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6767237/
% 		\item A. M. Ladd, K. E. Bekris, A. Rudys, L. E. Kavraki, and D. S. Wallach, “Robotics-
% based location sensing using wireless ethernet,” Wireless Networks, vol. 11, no. 1-2, p. 189–204, 2005.
% 		\item M. Lindhe, K. Johansson, and A. Bicchi, “An experimental study of exploiting multipath fading for robot communications,” Robotics: Science and Systems III, 2007.
% 		\item M. Lindhe and K. Johansson, “Using robot mobility to exploit multipath fading,”Wireless Communications, IEEE, vol. 16, pp. 30 – 37, 03 2009.
% 	\end{itemize}

\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-27 systemLevelFunctionalRequirements.tex
Initial commit

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%%%\usepackage[document]{ragged2e}

%%% Examples of Article customizations
% These packages are optional, depending on whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{letterpaper} % or letterpaper (US) or a5paper or....
\geometry{margin=1in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options
\graphicspath{
{figs/ipe/}
}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{siunitx}
\sisetup{inter-unit-product = \cdot}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

\usepackage{caption}        %Allows modification of captions
% \usepackage{indentfirst}    %Allows for indenting first paragraphs

\usepackage{hyperref}
\usepackage{todonotes}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customize the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\usepackage{tikz}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{enumerate}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Command to make the lines in the title page

%%% END Article customizations

%%% The "real" document content comes below...

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisors}: Dr. Suruz Miah and Dr. Prasad Shastry}

%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

% \setlength{\parindent}{4em} % this should indent paragraphs

\setlength{\marginparwidth}{2cm}

\begin{document}
\maketitle

% \newpage
% \tableofcontents % Table of contents
\newpage % Start lab look on a new page

\section{Project Description}
Robotic carts are of paramount importance to conduct many indoor or outdoor tasks. There are many applications of autonomous robotic carts. For example, in a grocery store, a customer (especially a person with disability) may need more than one cart but is incapable of pushing two carts simultaneously. Therefore, a second cart that is capable of identifying the customer to follow and is able to track and follow the customer through the store would be very useful. In an indoor office environment, such an autonomous robotic cart may be used to carry items such as files from one office to another. In an outdoor environment, such a cart may be used to carry sheets of glass.

There are many solutions available in the market for such robotic carts. However, all of them require line of sight communication. In this project, we are proposing a robotic cart using mainly analog signals using cost-effective wireless communication. Implementation of a fully functional robotic cart will be out of the scope of this project but is an ultimate goal for this project in the coming years. However, this project is expected to encourage further research in this area as well as provide a foundation for that research.

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. The system, as a whole, will take into consideration the world around it and avoid obstacles while trying to follow the remote target.  The system will also be trying to follow the remote pointer even if it loses the line of sight detection.  If the robot loses track or falls too far behind the remote, the remote will indicate this to the user.

% A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
% \begin{figure}[b]
%     \centering
%     \captionsetup{justification=centering, margin=3cm}
%     \includegraphics[width=6.5in]{figs/system_block_diagram}
%     \caption{Block Diagram of the Robotic Cart System}
%     \label{fig:sysBlockDiag}
% \end{figure}

\subsection{System Inputs and Outputs}
\subsubsection{Inputs}
There are four inputs to the robotic cart system.
\begin{itemize}
    \item Power - Both the mobile cart and the remote will require power from a battery.
    \item On/Off Switch - The user must be able to turn both the cart and the remote off to save power when the robotic cart system is not in use.
    \item Movement of the Remote - The user will control the mobile cart by moving with the remote.
    \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
\end{itemize}

\subsubsection{Outputs}
There are two outputs from the robotic cart system.
\begin{itemize}
    \item Movement of the Cart - The cart will move to follow the remote.
    \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
\end{itemize}

%------------------------------------------------
\section{Requirements and Specifications}
\subsection{Requirements}
The robotic cart system will meet the following requirements:
\begin{itemize}
    \item Cart should follow remote at a reasonable distance
    \item Cart should be able to travel at a speed reasonable for walking
    \item User should be alerted if cart falls too far behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should avoid obstacles
\end{itemize}

\subsection{Specifications}
Based on the requirements, the robotic cart system must meet the following specifications:
\begin{itemize}
    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
    \item Cart should be able to travel at speeds up to 2 m/s
    \item User should be alerted if the cart falls more than 2 meters behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should not collide with obstacles while following remote
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-10-04 systemLevelFunctionalRequirements.tex
Updated labnotebook and systemLevelFunctionalRequirements.tex

@@
         \HRule \\[0.4cm]
-        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
+        {\Huge \bfseries HIL Plant Modeling \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
         \HRule \\[0.4cm]
@@
     }
-\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisors}: Dr. Suruz Miah and Dr. Prasad Shastry}
+\author{Hannah Grady and Nicholas Nauman \\ \underline{Advisors}: Dr. Suruz Miah}
 
@@
 \section{Project Description}
-Robotic carts are of paramount importance to conduct many indoor or outdoor tasks.
-There are many applications of autonomous robotic carts.
-For example, in a grocery store, a customer (especially a person with disability) may need more than one cart but is incapable of pushing two carts simultaneously.
-Therefore, a second cart that is capable of identifying the customer to follow and is able to track and follow the customer through the store would be very useful.
-In an indoor office environment, such an autonomous robotic cart may be used to carry items such as files from one office to another.
-In an outdoor environment, such a cart may be used to carry sheets of glass.
+Autonomous vehicles are being developed by many companies with the goal of being able to use these vehicles in both commercial and residential settings.
+These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
+Also, autonomous vehicles have the ability to increase safety for other drivers and pedestrians alike.
+To control autonomous vehicles, accurate models of six main subsystems must be created so controllers can be developed to reliably control the system.
 
-There are many solutions available in the market for such robotic carts.
-However, all of them require line of sight communication.
-In this project, we are proposing a robotic cart using mainly analog signals using cost-effective wireless communication.
-Implementation of a fully functional robotic cart will be out of the scope of this project but is an ultimate goal for this project in the coming years.
-However, this project is expected to encourage further research in this area as well as provide a foundation for that research.
+There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
+There are controllers in place to control the Lexus vehicle platform, but the reliability of these controllers are lower than what is expected.
+The scope of this project includes developing models for each subsystem so AutonomouStuff can implement controls that improve the reliability of the vehicle platform.
 
 %------------------------------------------------
+
+\section{Literature}
+\label{sec:Literature}
+
+Authors in~\cite{Adnan2010} shows how a system with small non-linearities cna be modeled using Matlab's System Identification Toolbox.
+Since the researchers were able to model their system successfully, that indicates that we should be able to model our steering model with its small non-linearities caused by very small steering angles as well.
+Any concerns that modeling the vehicle components using the System Identification Toolbox will produce inaccurate results are addressed by~\cite{Donjaroennon2021}.
+Using input and output signals, they were able to come up with a model that had a best fit percentage of 95.1\%.
+Therefore we can carry out our project knowing that the models we produce will be accurate.
+
+Autonomous vehicle modeling is illustrated by authors in~\cite{Wang2021}.
+
+Mathematical model construction is conducted by authors in~\cite{Donjaroennon2021}.
+
 \section{System Architecture}
 \subsection{System Block Diagram}
-The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device.
-The system, as a whole, will take into consideration the world around it and avoid obstacles while trying to follow the remote target.
-The system will also be trying to follow the remote pointer even if it loses the line of sight detection.
-If the robot loses track or falls too far behind the remote, the remote will indicate this to the user.
+The Lexus car platform is comprised of six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model.
+The system, as a whole, will be taking into consideration obstacles around it while the vehicle traverses a predetermined route.
+For the system to be able to accomplish this reliably, the six main subsystems must be precisely modeled, especially the steering subsystem.
 
-% A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
-% \begin{figure}[b]
-%     \centering
-%     \captionsetup{justification=centering, margin=3cm}
-%     \includegraphics[width=6.5in]{figs/system_block_diagram}
-%     \caption{Block Diagram of the Robotic Cart System}
-%     \label{fig:sysBlockDiag}
-% \end{figure}
+A block diagram of the vehicle steering model is shown in \autoref{fig:sysBlockDiag}
+\begin{figure}[b]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=3.5in]{figs/inkscape/steeringModelArchitecture}
+    \caption{Block Diagram of the Vehicle Steering Model}
+    \label{fig:sysBlockDiag}
+\end{figure}
 
@@
 \subsubsection{Inputs}
-There are four inputs to the robotic cart system.
+
 \begin{itemize}
-    \item Power - Both the mobile cart and the remote will require power from a battery.
-    \item On/Off Switch - The user must be able to turn both the cart and the remote off to save power when the robotic cart system is not in use.
-    \item Movement of the Remote - The user will control the mobile cart by moving with the remote.
-    \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
+    \item Steering Model
+    \begin{itemize}
+    		\item Desired Steering Wheel Angle
+    		\item Actual Steering Wheel Angle 
+    		\item Torque Voltages
+    \end{itemize}
+    \item Acceleration Model
+    \begin{itemize}
+    		\item Acceleration Pedal Voltages
+    \end{itemize}
+    \item Brake Model
+    \begin{itemize}
+    		\item Brake Pedal Pressure Voltages
+    		\item Brake Pedal Stroke Voltages 
+    		\item Brake Pedal On/Off Switch
+    \end{itemize}
+    \item Shift Model
+    \begin{itemize}
+    		\item Desired Shift Gear
+    \end{itemize}
+    \item Speed Model
+    \begin{itemize}
+    		\item Acceleration Pedal Position
+    		\item Brake Pedal Position
+    		\item Shifter Actual Gear
+    \end{itemize}
+    \item Speed Control Model
+    \begin{itemize}
+    		\item Desired Vehicle Speed
+    \end{itemize}
 \end{itemize}
@@
 \subsubsection{Outputs}
-There are two outputs from the robotic cart system.
+
 \begin{itemize}
-    \item Movement of the Cart - The cart will move to follow the remote.
-    \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
+    \item Steering Model
+    \begin{itemize}
+    		\item Wheel Angle
+    		\item Actual Steering Wheel Angle
+    \end{itemize}
+    \item Acceleration Model
+    \begin{itemize}
+    		\item Acceleration Pedal Position
+    \end{itemize}
+    \item Brake Model
+    \begin{itemize}
+    		\item Brake Pedal Position
+    		\item Brake Pressed
+    \end{itemize}
+    \item Shift Model
+    \begin{itemize}
+    		\item Shifter Actual Gear
+    \end{itemize}
+    \item Speed Model
+    \begin{itemize}
+    		\item Vehicle Speed
+    \end{itemize}
+    \item Speed Control Model
+    \begin{itemize}
+    		\item Vehicle Speed
+    \end{itemize}
 \end{itemize}
@@
 \subsection{Requirements}
-The robotic cart system will meet the following requirements:
+The vehicle platform plant model will meet the following requirements:
 \begin{itemize}
-    \item Cart should follow remote at a reasonable distance
-    \item Cart should be able to travel at a speed reasonable for walking
-    \item User should be alerted if cart falls too far behind
-    \item Cart should not require line-of-sight to follow remote
-    \item Cart should avoid obstacles
+    \item The plant model should have an accurate model of the six main subsystems
+    \item A HIL test bench can be developed from the plant models of the subsystems
+    \item The steering model can handle very small steering angles
 \end{itemize}
@@
 \subsection{Specifications}
-Based on the requirements, the robotic cart system must meet the following specifications:
+Based on the requirements, the vehicle platform plant model must meet the following specifications:
 \begin{itemize}
-    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
-    \item Cart should be able to travel at speeds up to 2 m/s
-    \item User should be alerted if the cart falls more than 2 meters behind
-    \item Cart should not require line-of-sight to follow remote
-    \item Cart should not collide with obstacles while following remote
+    \item The model of the steering subsystem should be modeled first as it is crucial to operation and has non-linearity considerations
+    \item The remaining subsystems will be modeled individually 
+    \item Our steering model will be designed to accommodate very small steering angles
 \end{itemize}
 
+\section{Other Considerations}
+As we progress with this project, it is important that we take into consideration how this will affect others and make sure that we are holding ourselves to high ethical standards. 
+\begin{itemize}
+    \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents and driving fatalities and injuries.
+As a result people will be able to live longer and healthier lives.
+By creating accurate models, we will help advance the development of autonomous vehicles and make this a reality.
+    \item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle.
+We will address this by creating a rigorous test plan for our models.
+    \item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use.
+How we will help ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
+    \item Global Factors: This is irrelevant to this project.
+While our work will help with the development of autonomous vehicles, we do not have any control or impact over how they will be introduced to the world and used in society.
+    \item Cultural Factors: 
+    \item Social Factors: Advancing autonomous vehicle research could lead to them replacing those who drive for a living, such as taxi or Uber drivers.
+This is an important issue that needs to be addressed as autonomous vehicles become more widespread, but it is outside of the scope of our project.
+    \item Environmental Factors: By modeling the vehicle components using software, that means the vehicle will not have to be used as often for testing.
+Less vehicle use could potentially have a positive impact on the environment.
+    \item Business Factors: We must keep in mind the maintenance of developed software to control the vehicle based on updates to the control models. 
+    \item Economic Factors: There is an increased cost associated with the specialized hardware which allows for the autonomy of the vehicle.
+However, this cost is justified to the consumer as it reduces the stress and time involved with driving a vehicle.
+
+\end{itemize}
+
+\pagebreak
+\bibliographystyle{IEEEtran}
+\bibliography{bib/references.bib}
 \end{document}

### 2021-10-05 proposalPres.tex
Updated references.bib, proposal, and system level document

@@
 
-\title[Robotic Cart System (Proposal)]{Robotic Cart System}
+\title[HIL Plant Modeling (Proposal)]{HIL Plant Modeling}
 
@@
 
-\date[December~3,~2020]{Thursday, December~3,~2020}
+\date[October~7,~2021]{Thursday, October~7,~2021}
 
@@
     \begin{LARGE}
-      Design a robotic cart that follows the user.
+      Model vehicle subsystems for a Lexus platform. 
     \end{LARGE}
@@
     \begin{LARGE}
-      Utilize wireless signal strength to locate and then follow the user.
+      Use the System Identification Toolbox in Matlab to develop a model for each subsystem. 
     \end{LARGE}

### 2021-10-05 systemLevelFunctionalRequirements.tex
Updated references.bib, proposal, and system level document

@@
 \section{Project Description}
-Autonomous vehicles are being developed by many companies with the goal of being able to use these vehicles in both commercial and residential settings.
+Autonomous vehicles are being developed by many companies for commercial and personal use.
 These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
-Also, autonomous vehicles have the ability to increase safety for other drivers and pedestrians alike.
-To control autonomous vehicles, accurate models of six main subsystems must be created so controllers can be developed to reliably control the system.
+Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
+To control autonomous vehicles, accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage the system.
 
 There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
-There are controllers in place to control the Lexus vehicle platform, but the reliability of these controllers are lower than what is expected.
-The scope of this project includes developing models for each subsystem so AutonomouStuff can implement controls that improve the reliability of the vehicle platform.
+We will be modeling these six subsystems for a Lexus platform using the System Identification Toolbox from Matlab.
+The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
+There are controllers in place to control the Lexus vehicle platform, but the reliability of these controllers is lower than expected.
+The scope of this project includes developing models for each subsystem so Autonomous Stuff can implement controls that improve the reliability of the vehicle platform.
+These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
 
@@
 
-Authors in~\cite{Adnan2010} shows how a system with small non-linearities cna be modeled using Matlab's System Identification Toolbox.
+Researchers in ~\cite{Adnan2010} show how a system with small non-linearities can be modeled using Matlab's System Identification Toolbox.
 Since the researchers were able to model their system successfully, that indicates that we should be able to model our steering model with its small non-linearities caused by very small steering angles as well.
-Any concerns that modeling the vehicle components using the System Identification Toolbox will produce inaccurate results are addressed by~\cite{Donjaroennon2021}.
+Another method for modeling small non-linearities is introduced by the authors in ~\cite{Saruchi2015} using a Steer-By-Wire method as the model for the steering system.
+With this model a composite nonlinear feedback (CNF) PID controller can be implemented to control the steering system even for small turning angles.
+Another option for modeling the steering system is using a third order ARMAX model as proposed by ~\cite{Li1999}.
+Using this model, traditional analysis methods can be used to develop a model and controller.
+Any concerns that modeling the vehicle components using the System Identification Toolbox will produce inaccurate results are addressed by ~\cite{Donjaroennon2021}.
 Using input and output signals, they were able to come up with a model that had a best fit percentage of 95.1\%.
-Therefore we can carry out our project knowing that the models we produce will be accurate.
+With these options for modeling automotive systems, we can carry out our project knowing that the models we produce will be accurate.
 
-Autonomous vehicle modeling is illustrated by authors in~\cite{Wang2021}.
-
-Mathematical model construction is conducted by authors in~\cite{Donjaroennon2021}.
-
+%------------------------------------------------
 \section{System Architecture}
@@
 For the system to be able to accomplish this reliably, the six main subsystems must be precisely modeled, especially the steering subsystem.
-
 A block diagram of the vehicle steering model is shown in \autoref{fig:sysBlockDiag}
-\begin{figure}[b]
+\begin{figure}[h]
     \centering
@@
     \begin{itemize}
+    		\item Torque Voltages
+    		\begin{itemize}
     			\item Desired Steering Wheel Angle
     			\item Actual Steering Wheel Angle
-    		\item Torque Voltages
+    		\end{itemize}
     \end{itemize}
@@
 
+%------------------------------------------------
 \section{Other Considerations}
@@
     \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents and driving fatalities and injuries.
-As a result people will be able to live longer and healthier lives.
+As a result, people will be able to live longer and healthier lives.
 By creating accurate models, we will help advance the development of autonomous vehicles and make this a reality.
@@
 How we will help ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
-    \item Global Factors: This is irrelevant to this project.
-While our work will help with the development of autonomous vehicles, we do not have any control or impact over how they will be introduced to the world and used in society.
-    \item Cultural Factors: 
+    \item Global Factors: Our work will be used to help advance the technology behind autonomous vehicles, but we will not have any control over how they will be used in society.
+Therefore, this factor is irrelevant the project.
+    \item Cultural Factors: This is irrelevant to this project.
+While our work will help with the development of autonomous vehicles, we do not have any control or impact over how they will be introduced within cultural boundaries.
     \item Social Factors: Advancing autonomous vehicle research could lead to them replacing those who drive for a living, such as taxi or Uber drivers.
@@
 However, this cost is justified to the consumer as it reduces the stress and time involved with driving a vehicle.
-
 \end{itemize}
 
+%------------------------------------------------
 \pagebreak

### 2021-10-07 proposalPres.tex
Updated presentation slides, system level requirement document

@@
 
-\title[HIL Plant Modeling (Proposal)]{HIL Plant Modeling}
+\title[HIL Plant Modeling]{Hardware-in-Loop Plant Modeling for Autonomous
+  Vehicle}
 
 % % A subtitle is optional and this may be deleted
-\subtitle{Product Proposal}
+\subtitle{Modeling, Simulation, and Testing}
 
-\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and
-Jason~Braker
-Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
+\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
+\linebreak Advisors:~Dr.~Suruz~Miah}
 % - Give the names in the same order as the appear in the paper.
@@
 
-\begin{frame}{Introduction}
-  % \begin{center}
-  %   % \href{videos/proposalVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/proposalVideoTitle}}
-  % \end{center}
-  % \begin{center}
-  %   \includemedia[
-  %     width=\textwidth,
-  %     height=0.7\textheight,
-  %     label=proposalVideo,
-  %     % activate=onclick,
-  %     % playbutton=fancy,
-  %     addresource=videos/proposalVideo.mp4,
-  %     flashvars={source=videos/proposalVideo.mp4}]
-  %     {}{VPlayer.swf}
-  %     \\
-  %     % \mediabutton[
-  %     %   mediacommand=proposalVideo:playPause,
-  %     %   overface=\color{blue}{\fbox{\strut \faPause\ \faPlay}},
-  %     %   downface=\color{red}{\fbox{\strut \faPause\ \faPlay}}
-  %     % ]{}
-  %     % \mediabutton[
-  %     %   mediacommand=proposalVideo:setSource
-  %     %   [(videos/proposalVideo.mp4)]]{\fbox{Introduction Video}}
-  % \end{center}
+\begin{frame}{Introduction}{}
+    \begin{block}{Applications of Autonomous Vehicles}
+    	\begin{itemize}
+    		\item Autonomous vehicles are being developed by many companies for commercial and personal use
+    		\item Modeling the steering system for autonomous vehicles is a challenging task
+     		\item Models for autonomous vehicle subsystems must be very accurate due to safety factors
+		\end{itemize}
+    \end{block}
+        \begin{figure}
+			\centering
+			\begin{minipage}[t]{0.4\textwidth}
+				\centering
+				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesAStuff}
+				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
+				\label{fig:fleet}
+			\end{minipage}
+			\begin{minipage}[t]{0.4\textwidth}
+				\centering
+				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesSteering}
+				\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
+				\label{fig:steerSystem}
+			\end{minipage}
+        \end{figure}
+    \begin{tiny}
+		\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+    \end{tiny}
 \end{frame}
@@
   \begin{block}{Problem Statement}
-    \begin{LARGE}
+    \begin{large}
       Model vehicle subsystems for a Lexus platform.
-    \end{LARGE}
+ \begin{itemize}
+          \item Steering Model
+          \item Acceleration Model
+          \item Brake Model
+          \item Shift Model
+          \item Speed Model
+          \item Speed Control Model
+        \end{itemize} 
+    \end{large}
   \end{block}
@@
   \begin{block}{Proposed Solution}
-    \begin{LARGE}
-      Use the System Identification Toolbox in Matlab to develop a model for each subsystem. 
-    \end{LARGE}
+    \begin{large}
+      Use conventional System Identification techniques for modeling subsystems based on available raw data.  
+    \end{large}
   \end{block}
 \end{frame}
-
-% \begin{frame}{Introduction}{}
-% %\documentclass{beamer}
-%   % applications of mobile robot navigation and problem description
-%   \begin{block}{Applications of Mobile Carts}
-%     \begin{itemize}
-%       %\item Mail delivery
-%       %\item Transferring files in offices
-%       \item Carrying medical supplies in hospitals (Fig.\ref{fig:medCart})
-%       \item Carrying materials and tools in factories (Fig. \ref{fig:factCart})
-%       \item Shopping carts for ease of use and people with disabilities
-%     \end{itemize}
-%   \end{block}
-%       \begin{figure}
-%       \centering
-%       \begin{minipage}[t]{0.5\textwidth}
-%         \centering
-%         \includegraphics[height=3.0cm]{figs/img/MedicalRoboticCart}
-%         \caption{Medical Mobile Robotic Cart\textsuperscript{a}}
-%         \label{fig:medCart}
-%       \end{minipage}
-%       \begin{minipage}[t]{0.4\textwidth}
-%         \centering
-%         \includegraphics[height=2.0cm]{figs/img/FactoryRoboticCart}
-%         \caption{Factory Mobile Robotic Cart\textsuperscript{b}}
-%         \label{fig:factCart}
-%       \end{minipage}
-%       \end{figure}
-%     \begin{tiny}
-%       \textsuperscript{a}https://www.cnet.com/news/robots-give-a-helping-hand-in-san-franciscos-newest-hospital/\\\textsuperscript{b}https://www.greencarcongress.com/2020/05/20200515-nvidia.html
-%     \end{tiny}
-% \end{frame}
 
@@
   \begin{block}{Existing Solution}
-        Mobile platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
+        Use of System Identification Toolbox in Matlab to create models from data~\cite{Donjaroennon2021}
+  \end{block}
+  \begin{block}{Existing Solution}
+        Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
+  \end{block}
+  \begin{block}{Existing Solution}
+        Steer-By-Wire method as a system model~\cite{Saruchi2015}
   \end{block}
@@
     \begin{itemize}
-      \item Line-of-sight is not required since analog RF signals will be used
-      \item RF components are cost-effective
+      \item High level of accuracy 
     \end{itemize}
@@
     \begin{itemize}
-      \item Cart should be able to follow the remote target
-      \item Cart should maintain a distance of 1~[\si{\meter}] to 1.5~[\si{\meter}] from the remote target.
-      \item Cart should be able to attain a speed of at least 1~[\si{\meter\per\second}]
-      \item Cart should not require line-of-sight to follow remote
+      	\item The plant model should have an accurate model of the six main subsystems
+    		\item A hardware-in-loop (HIL) test bench can be developed from the plant models of the subsystems
+    		\item The steering model can handle very small steering angles
     \end{itemize}
@@
       \begin{itemize}
-        \item Develop a robotic cart system utilizing wireless signal strength to locate and follow the user.
+        \item Develop models of an autonomous vehicle's subsystems
         \begin{itemize}
-          \item Does not require line-of-sight
-          \item Low-cost design
+          \item Steering Model
+          \item Acceleration Model
+          \item Brake Model
+          \item Shift Model
+          \item Speed Model
+          \item Speed Control Model
         \end{itemize}
@@
     \begin{itemize}
-      \item Inaccurate distance measurements due to multipath effect from environment
-      \item Achieving full 360\textdegree measurement in short enough time
+      \item Achieving an acceptable accuracy and reliability for each model due to its nonlinearities over small changes
     \end{itemize}
@@
 
-% \begin{frame}{References}
+%\begin{frame}{References}
 %  \bibliographystyle{IEEEtran}
@@
   \bibliography{bib/references.bib}
+
+%\begin{itemize}
+%\item
+%@INPROCEEDINGS{Donjaroennon2021,
+%  author={Donjaroennon, Natthapon and Nuchkum, Suphatchakan and Leeton, Uthen},
+%  booktitle={2021 9th International Electrical Engineering Congress (iEECON)}, 
+%  title={Mathematical model construction of DC Motor by closed-loop system Identification technique Using Matlab/Simulink}, 
+%  year={2021},
+%  volume={},
+%  number={},
+%  pages={289-292},
+%  doi={10.1109/iEECON51072.2021.9440305}}
+%\end{itemize}
 % 	\begin{itemize}

### 2021-10-10 proposalPres.tex
Updated presentation slides, system level requirement document, lab notebook, and figures folder

@@
 
-\title[HIL Plant Modeling]{Hardware-in-Loop Plant Modeling for Autonomous
+\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous
   Vehicle}
@@
 \author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
-\linebreak Advisors:~Dr.~Suruz~Miah}
+\linebreak Advisor:~Dr.~Suruz~Miah}
 % - Give the names in the same order as the appear in the paper.
@@
     \begin{large}
-      Use conventional System Identification techniques for modeling subsystems based on available raw data.  
+      A potential solution is to develop conventional System Identification techniques for modeling subsystems using available raw data.  
     \end{large}
@@
   \begin{block}{Existing Solution}
-        Use of System Identification Toolbox in Matlab to create models from data~\cite{Donjaroennon2021}
-  \end{block}
-  \begin{block}{Existing Solution}
-        Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
-  \end{block}
-  \begin{block}{Existing Solution}
-        Steer-By-Wire method as a system model~\cite{Saruchi2015}
+ \begin{itemize}
+        \item Use of System Identification Toolbox in Matlab to create models from data~\cite{Adnan2010}
+	 \begin{itemize}
+		    \tiny
+		    		\item Offers a variety of model choices
+				\item Needs a large amount of raw data to produce an accurate model
+	\end{itemize}
+	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
+	 \begin{itemize}
+		    \tiny
+		    		\item Allows the use of traditional analysis methods to create a model 
+				\item More room for error during calculations
+	\end{itemize}
+	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
+	 \begin{itemize}
+		    \tiny
+		    		\item Can model systems with small non-linearities 
+				\item Mechanical components replaced by electrical components 
+	\end{itemize}
+\end{itemize}
   \end{block}
@@
 
-\begin{frame}{Existing Solutions}
-  \begin{block}{Problems}
-    \begin{itemize}
-      \item Require line-of-sight between robot and user
-      \item Some require costly dedicated image processing hardware
-    \end{itemize}
-  \end{block}
-  \pause
-  \begin{block}{Benefits of Proposed Solution}
-    \begin{itemize}
-      \item High level of accuracy 
-    \end{itemize}
-  \end{block}
-\end{frame}
+%\begin{frame}{Existing Solutions}
+%  \begin{block}{Problems}
+%    \begin{itemize}
+%      \item Require line-of-sight between robot and user
+%      \item Some require costly dedicated image processing hardware
+%    \end{itemize}
+%  \end{block}
+%  \pause
+%  \begin{block}{Benefits of Proposed Solution}
+%    \begin{itemize}
+%      \item High level of accuracy 
+%    \end{itemize}
+%  \end{block}
+%\end{frame}
 
@@
 \section{System Requirements}
+\begin{frame}
+\tiny
+	\begin{block}{System Inputs and Outputs}
+		\begin{itemize}
+			\tiny
+		    \item Steering Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Torque Voltages
+		    		\begin{itemize}
+		    		\tiny
+		    			\item Desired Steering Wheel Angle
+		    			\item Actual Steering Wheel Angle
+		    		\end{itemize}
+		    \end{itemize}
+		    \item Acceleration Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Acceleration Pedal Voltages
+		    \end{itemize}
+		    \item Brake Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Brake Pedal Pressure Voltages
+		    		\item Brake Pedal Stroke Voltages 
+		    		\item Brake Pedal On/Off Switch
+		    \end{itemize}
+		    \item Shift Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Desired Shift Gear
+		    \end{itemize}
+		    \item Speed Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Acceleration Pedal Position
+		    		\item Brake Pedal Position
+		    		\item Shifter Actual Gear
+		    \end{itemize}
+		    \item Speed Control Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Desired Vehicle Speed
+		    \end{itemize}
+		\end{itemize}
+	\end{block}
+\end{frame}
+\begin{frame}			
+	\begin{figure}
+		\includegraphics[width=10cm]{figs/inkscape/steeringModelArchitecture}
+		\caption{Block Diagram of Steering Subsystem}
+		\label{fig:steeringModel}
+	\end{figure}
+\end{frame}
+
 \begin{frame}{System Requirements}

### 2021-10-10 systemLevelFunctionalRequirements.tex
Updated presentation slides, system level requirement document, lab notebook, and figures folder

@@
 \usepackage{hyperref}
-\usepackage{todonotes}
+
+% \usepackage{easyReview}
 
@@
 \usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
+
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage{soul}
+
 \renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
@@
         \HRule \\[0.4cm]
-        {\Huge \bfseries HIL Plant Modeling \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
+        {\Huge \bfseries Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
         \HRule \\[0.4cm]
@@
     }
-\author{Hannah Grady and Nicholas Nauman \\ \underline{Advisors}: Dr. Suruz Miah}
+\author{Hannah Grady and Nicholas Nauman \\ \underline{Advisor}: Dr. Suruz Miah}
 
@@
 \section{Project Description}
-Autonomous vehicles are being developed by many companies for commercial and personal use.
+Autonomous vehicles are being developed by many companies for commercial and/or personal use.
 These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
@@
 
-There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
-We will be modeling these six subsystems for a Lexus platform using the System Identification Toolbox from Matlab.
+There are six main subsystems - a steering model, an acceleration model, a brake
+model, a shifting model, a speed model, and a cruise model - that must be
+modeled to get an accurate representation of how the vehicle should be
+controlled. We will be modeling these six subsystems for a Lexus platform using
+the System Identification Toolbox from Matlab.
 The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
@@
 
-Researchers in ~\cite{Adnan2010} show how a system with small non-linearities can be modeled using Matlab's System Identification Toolbox.
-Since the researchers were able to model their system successfully, that indicates that we should be able to model our steering model with its small non-linearities caused by very small steering angles as well.
-Another method for modeling small non-linearities is introduced by the authors in ~\cite{Saruchi2015} using a Steer-By-Wire method as the model for the steering system.
-With this model a composite nonlinear feedback (CNF) PID controller can be implemented to control the steering system even for small turning angles.
-Another option for modeling the steering system is using a third order ARMAX model as proposed by ~\cite{Li1999}.
-Using this model, traditional analysis methods can be used to develop a model and controller.
-Any concerns that modeling the vehicle components using the System Identification Toolbox will produce inaccurate results are addressed by ~\cite{Donjaroennon2021}.
-Using input and output signals, they were able to come up with a model that had a best fit percentage of 95.1\%.
-With these options for modeling automotive systems, we can carry out our project knowing that the models we produce will be accurate.
+Researchers in~\cite{Adnan2010} show how a system with small non-linearities can
+be modeled using Matlab's System Identification Toolbox. Since the researchers
+were able to model their system successfully, that indicates that we should be
+able to model our steering model with its small non-linearities caused by very
+small steering angles as well. Another method for modeling small non-linearities
+is introduced by the authors in~\cite{Saruchi2015} using a Steer-By-Wire method
+as the model for the steering system. With this model, a composite nonlinear
+feedback (CNF) PID controller can be implemented to control the steering system
+even for small turning angles. Another option for modeling the steering system
+is using a third order ARMAX model as proposed by~\cite{Li1999}. Using this
+model, traditional analysis methods can be used to develop a model and
+controller. Any concerns that modeling the vehicle components using the System
+Identification Toolbox will produce inaccurate results are addressed by
+~\cite{Donjaroennon2021}. Using input and output signals, they were able to come
+up with a model that had a best fit percentage of 95.1\%. With these options for
+modeling automotive systems, we can carry out our project knowing that the
+models we produce will be accurate.
 
@@
 \subsection{System Block Diagram}
-The Lexus car platform is comprised of six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model.
-The system, as a whole, will be taking into consideration obstacles around it while the vehicle traverses a predetermined route.
-For the system to be able to accomplish this reliably, the six main subsystems must be precisely modeled, especially the steering subsystem.
-A block diagram of the vehicle steering model is shown in \autoref{fig:sysBlockDiag}
+The Lexus car platform is comprised of six main subsystems - a steering model,
+an acceleration model, a brake model, a shifting model, a speed model, and a
+cruise model. The system, as a whole, will be taking into consideration
+obstacles around it while the vehicle traverses a predetermined route. For the
+system to be able to accomplish this reliably, the six main subsystems must be
+precisely modeled, especially the steering subsystem. A block diagram of the
+vehicle steering model is shown in \autoref{fig:sysBlockDiag}. %
+%
 \begin{figure}[h]
@@
     \includegraphics[width=3.5in]{figs/inkscape/steeringModelArchitecture}
-    \caption{Block Diagram of the Vehicle Steering Model}
+    \caption{Block Diagram of the Vehicle Steering Model.}
     \label{fig:sysBlockDiag}
 \end{figure}
+%
 
@@
 
+\todo[inline]{For the steering model, is it a single input (torque voltage) and multiple output system?}
 \begin{itemize}

### 2021-10-21 systemLevelFunctionalRequirements.tex
ECE 497 deliverables source files

@@
 Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
-To control autonomous vehicles, accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage the system.
+Accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage these vehicles.
 
@@
 The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
-There are controllers in place to control the Lexus vehicle platform, but the reliability of these controllers is lower than expected.
-The scope of this project includes developing models for each subsystem so Autonomous Stuff can implement controls that improve the reliability of the vehicle platform.
+There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected.
+The scope of this project includes developing mathematical models for each subsystem so Autonomous Stuff can implement controls that improve the reliability of the autonomous vehicle platform.
 These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
@@
 an acceleration model, a brake model, a shifting model, a speed model, and a
-cruise model. The system, as a whole, will be taking into consideration
-obstacles around it while the vehicle traverses a predetermined route. For the
+cruise model. As a whole, the system will be taking nearby obstacles into consideration as the vehicle traverses a predetermined route. For the
 system to be able to accomplish this reliably, the six main subsystems must be
-precisely modeled, especially the steering subsystem. A block diagram of the
-vehicle steering model is shown in \autoref{fig:sysBlockDiag}. %
+precisely modeled, especially the steering subsystem. The block diagrams of each system is shown below.
 %
-\begin{figure}[h]
+\begin{figure}
     \centering
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=3.5in]{figs/inkscape/steeringModelArchitecture}
+    \includegraphics[width=3in]{figs/inkscape/steeringModelArchitecture}
     \caption{Block Diagram of the Vehicle Steering Model.}
-    \label{fig:sysBlockDiag}
+    \label{fig:steerBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Block Diagram of the Vehicle Brake Model.}
+    \label{fig:brakeBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+    \caption{Block Diagram of the Vehicle Acceleration Model.}
+    \label{fig:accelBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
+    \caption{Block Diagram of the Vehicle Shift Model.}
+    \label{fig:shiftBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
+    \caption{Block Diagram of the Vehicle Speed Control Model.}
+    \label{fig:cruiseBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
+    \caption{Block Diagram of the Vehicle Speed Model.}
+    \label{fig:speedBlockDiag}
 \end{figure}
@@
 
-\todo[inline]{For the steering model, is it a single input (torque voltage) and multiple output system?}
 \begin{itemize}
@@
     \begin{itemize}
-    		\item Torque Voltages
+    		\item Two Torque Voltage Signals
     		\begin{itemize}
@@
     \begin{itemize}
-    		\item Desired Shift Gear
+    		\item Desired Shifter Gear
     \end{itemize}
@@
     \begin{itemize}
-    		\item Shifter Actual Gear
+    		\item Actual Shifter Gear
     \end{itemize}
@@
 %------------------------------------------------
+\section{Hardware Implementation}
+
+Each subsystem that we will be testing has a similar hardware setup. The hardware used for each system is as follows:
+\begin{itemize}
+	\item System-specific components
+	\item PACMod
+	\item CAN Case
+	\item Laptop
+\end{itemize}
+CAN data is collected on the laptop.
+The data is collected from the system-specific components by the PACMod, which is connected to the CAN case.
+This case is then connected to the laptop via a CAN bus.
+In \autoref{fig:hardwareSetup1} and \autoref{fig:hardwareSetup2} below, the CAN case and laptop are visible, but the PACMod and other internal components are not.
+%
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=3.25in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    \caption{Depiction of Hardware Setup for Autonomous Vehicle Platform.}
+    \label{fig:hardwareSetup1}
+\end{figure}\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[angle=180,width=3.25in]{figs/img/picturesVisitToAStuff/dataColletionSetup2-20211007}
+    \caption{Depiction of Hardware Setup for Autonomous Vehicle Platform.}
+    \label{fig:hardwareSetup2}
+\end{figure}
+%
+
+%------------------------------------------------
 \section{Requirements and Specifications}
@@
     \item The plant model should have an accurate model of the six main subsystems
-    \item A HIL test bench can be developed from the plant models of the subsystems
+    \item A HIL test bench can be developed from the plant model of the subsystems
     \item The steering model can handle very small steering angles
@@
     \item The model of the steering subsystem should be modeled first as it is crucial to operation and has non-linearity considerations
-    \item The remaining subsystems will be modeled individually 
+    \item All subsystems will be modeled individually 
     \item Our steering model will be designed to accommodate very small steering angles
@@
 \begin{itemize}
-    \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents and driving fatalities and injuries.
+    \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents along with driving fatalities and injuries.
 As a result, people will be able to live longer and healthier lives.
@@
 Less vehicle use could potentially have a positive impact on the environment.
-    \item Business Factors: We must keep in mind the maintenance of developed software to control the vehicle based on updates to the control models. 
+    \item Business Factors: This is relevant to our project.
+From a business standpoint, using software to develop these mathematical models and using HIL testing can be less expensive than constantly using a vehicle for testing.
+By completing this project we can help AutonomouStuff save money.
     \item Economic Factors: There is an increased cost associated with the specialized hardware which allows for the autonomy of the vehicle.

### 2021-10-22 proposalPres.tex

@@
 %----------------------------------
+\begin{frame}{Other Considerations}
+  \begin{block}{Factors}
+  	\begin{small}
+      \begin{itemize}
+        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
+and driving fatalities and injuries. As a result, people will be able to live longer and
+healthier lives. By creating accurate models, we will help advance the development of
+autonomous vehicles and make this a reality.
+		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle.
+We will address this by creating a rigorous test plan for our models.
+		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
+ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
+		\item Global Factors: 
+		\item Cultural Factors: 
+		\item Social Factors: 
+		\item Environmental Factors: 
+		\item Business Factors: 
+		\item Economic Factors: 
+      \end{itemize}
+     \end{small}
+  \end{block}
+\end{frame}
 

### 2021-10-25 proposal.tex
Update proposal.tex
I updated the project title and authors of the project proposal document
Updated lab notebook and proposal document

@@
 \vspace{0.5in}
-Project Title: Robotic Cart
+Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle 
 \vspace{1.0in}
-\author{Kallistah Allen, Darrah Beebe, and Jason Braker\\ Advisors: Dr.~Suruz Miah and Dr.~Prasad Shastry}
+\author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}
 }
@@
 \vspace*{6.0cm}
-\copyright~K.~Allen,~D.~Beebe~and~J.~Braker, Peoria, IL, USA, 2020\\
+\copyright~H.~Grady~and~N.~Nauman, Peoria, IL, USA, 2021\\
 
@@
 \section{Introduction}
-Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks.
-There are robotic systems currently available in the market that perform these tasks in a variety of ways.
-For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously.
-One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items.
-Moreover, robots used for this purpose are more costly than they are worth.
-In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store.
-The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field.
-Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.
+Autonomous vehicles are being developed by many companies for commercial and/or personal use.
+These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
+Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
+Accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage these vehicles.
+
+There are six main subsystems - a steering model, an acceleration model, a brake
+model, a shifting model, a speed model, and a cruise model - that must be
+modeled to get an accurate representation of how the vehicle should be
+controlled. We will be modeling these six subsystems for a Lexus platform using
+the System Identification Toolbox from Matlab.
+The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
+There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected.
+The scope of this project includes developing mathematical models for each subsystem so Autonomous Stuff can implement controls that improve the reliability of the autonomous vehicle platform.
+These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
 
@@
 
-% \section{System Requirements}
-% There are three primary requirements for our proposed mobile robotic cart. These requirements are stated as follows:
-
-% \begin{enumerate}
-%   \item The mobile cart to follow the remote attached to the user while maintaining a safe distance of $1~[\si{\meter}]$ to $1.5~[\si{\meter}]$.
-This requirement stems from the intended usage of the project, which is a cart that follows the user.
-The cart must be able to follow the remote, but it also must be able to keep an appropriate distance so it does not run into the user or fall too far behind.
-
-%   \item The second requirement for the system is that the cart should be able to travel at $1~[\si{\meter\per\second}]$.
-If the cart can only travel slowly, it will not be as useful since the user will have to walk very slowly to allow the cart to keep up.
-
-%   \item The proposed cart is not to rely on line-of-sight communication between the remote (user) and the cart.
-In the case that an obstacle gets between the cart and the remote, the communication should be able to be maintained so that the cart still knows where the user is located.
-% \end{enumerate}
+\section{System Requirements}
+The vehicle platform plant model will meet the following requirements:
+\begin{itemize}
+    \item The plant model should have an accurate model of the six main subsystems
+    \item A HIL test bench can be developed from the plant model of the subsystems
+    \item The steering model can handle very small steering angles
+\end{itemize}
 
@@
 
-% % \subsection{Specifications}
+ \subsection{Specifications}
+ Based on the requirements, the vehicle platform plant model must meet the following specifications:
+ \begin{itemize}
+    \item The model of the steering subsystem should be modeled first as it is crucial to operation and has non-linearity considerations
+    \item All subsystems will be modeled individually 
+    \item Our steering model will be designed to accommodate very small steering angles
+ \end{itemize}
 
@@
 \section{Concluding Remarks}
-A robotic cart that follows the user is a useful application of mobile robotics.
-Although some methods of performing this task have been developed, the existing methods require line-of-sight sensing between the robot and the cart.
-Our proposed robotic cart system does not require line-of-sight since it uses analog wireless signal strength as opposed to ultrasonic or photographic sensing.
-In this way, we plan to develop a robotic cart that can detect the user even in the presence of obstacles.
+Autonomous vehicles have a numerous amount of useful applications in today's society. ...
 

### 2021-10-28 proposal.tex
Updated Proposal Doc
I updated the proposal document by changing the names on the title page. There is an error involving line 40 and I tried to fix it but wasn't able to.

@@
 
-% \section{Literature Review}
-% Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores.
-See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example.
-Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.
+ \section{Literature Review}
+In the paper “Identification of Multiple Input-Single Output (MISO) Model for MPPT of Photovoltaic System”, the researchers wanted to model a system where the two inputs were Solar irradiance and Cell temperature and the output was DC current.
+In order to model this system Matlab’s System Identification Toolbox was used.
+In order to create different models, they collected and used data from an energy center in Malaysia.
+After generating different models, the researchers ended up going with a fourth order ARX (also known as ARXQS) model because it was the most accurate, with a best fit percentage of 93.42\%.
+The polynomial model equation for ARX is shown below.
+
+y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)
+
+y(t) is the output of the equation at a certain time t, while u(t) is the input at a certain time t.
+The noise disturbance of the system is represented by e(t).
+The variables na, nb, and nk are the system’s number of poles, amount of b parameters, and the samples before the inputs begin to affect the system’s output.
 

### 2021-10-28 proposal.tex
Updated proposal.tex with system ID section

@@
 
-y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)
+$y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)$
 
-y(t) is the output of the equation at a certain time t, while u(t) is the input at a certain time t.
+$y(t)$ is the output of the equation at a certain time t, while u(t) is the input at a certain time t.
 The noise disturbance of the system is represented by e(t).
 The variables na, nb, and nk are the system’s number of poles, amount of b parameters, and the samples before the inputs begin to affect the system’s output.
+
+\section{System Identification}
+
+Introduction to system identification...., Mathworks' MATLAB has the system
+identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+
+\subsection{Example 1: ..........}
+\label{sec:sysID-Example1}
+
+\subsection{Example 2: ..........}
+\label{sec:sysID-Example2}
+
+\subsection{Example 3: ..........}
+\label{sec:sysID-Example3}
 

### 2021-10-30 proposal.tex
Updated Proposal Preliminary Work
I updated the Preliminary Work section of the Project Proposal.

@@
 
-% % \section{Preliminary Work}
+\section{Preliminary Work}
+To start this project, we first read documentation outlining the uses of Matlab's System Identification Toolbox.
+From there we worked on Matlab tutorials on how to model systems from data using System Identification and then find the most accurate model.
+We specifically tried to find examples with Multiple-Input Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since most of the vehicle subsystems we will model fall into one of these categories.
+A literature review was also conducted to see how systems with small non-linearities like our steering subsystem were modeled using System Identification.
+On October 7th we traveled to AutonomouStuff in order to collect data from the steering, acceleration, and braking subsystems in an autonomous vehicle.
+The data we collected will be used to generate and then verify our models.
 

### 2021-10-31 proposal.tex
Updated Proposal.tex file
I added my summary of a MATLAB tutorial and also started working on the parts list and timeline sections.

@@
 
-\subsection{Example 1: ..........}
+\subsection{Example 1: Dealing with Multi-Variable Systems: Identification and Analysis}
 \label{sec:sysID-Example1}
+During this example I learned how to create an iddata object from a dataset in order to get the inputs and the outputs.
+The next step was to look at the impulse and step responses in order to learn more about how the inputs and outputs act.
+From there the state space model was estimated using the first part of the given data.
+This model was compared to the step responses that were found earlier and with the second part of the data to see if it was a good fit.
+The model had a best fit percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\% for the speed data.
+The frequency response of the model was estimated with spectral analysis and bode plots were also created.
+The tutorial explained that if the data doesn’t give nice models, then it is best to try out submodels for the different channels.
+Two single-input single-output (SISO) models were created and compared with the existing multiple-input multiple-output (MIMO) model and the actual data.
+The Nyquist plots were also compared.
+Both SISO models performed well during these comparisons.
+The next step in the tutorial was to create a multiple-input single-output (MISO) model in order to get a model that more accurately reflected the generated voltage data.
+By creating this model and comparing it to the validation data and previous models, we saw a best fit percentage of 90.18\%.
+The last thing the example showed was how to merge the two SISO models we created earlier.
 
@@
 
-% % \section{Parts List}
+\section{Parts List}
+	\subsection{Software}
+	\begin{itemize}
+    \item MATLAB's System Identification Toolbox 
+    \item  
+ \end{itemize}
 
-% \section{Timeline and Milestones} \label{sec:timeline}
+	\subsection{Hardware} 
+	\begin{itemize}
+    \item Laptop
+    \item PAC Mod 
+    \item CAN Case 
+    \item CAN Bus 
+ \end{itemize}
 
-% \begin{figure}
-%   \centering
-%   \begin{ganttchart}[
-%     hgrid,
-%     vgrid,
-%     x unit=.6cm,
-%     y unit title=.8cm,
-%     y unit chart=.6cm,
-%     milestone label font=\tiny,
-%     milestone progress label font = \tiny,
-%     milestone progress label anchor = east,
-%     bar label font=\tiny,
-%     group label font=\small,
-%     bar/.append style={fill=green},
-%     bar incomplete/.append style={fill=red},
-%     group progress label font = \tiny,
-%     progress label text={$\displaystyle#1\%$},
-%     group progress label anchor = east,
-%     bar progress label font = \tiny,
-%     bar progress label anchor = east,
-%     ]{1}{17}
+\section{Timeline and Milestones} \label{sec:timeline}
+
+ \begin{figure}
+   \centering
+   \begin{ganttchart}[
+     hgrid,
+     vgrid,
+     x unit=.6cm,
+     y unit title=.8cm,
+     y unit chart=.6cm,
+     milestone label font=\tiny,
+     milestone progress label font = \tiny,
+     milestone progress label anchor = east,
+     bar label font=\tiny,
+     group label font=\small,
+     bar/.append style={fill=green},
+     bar incomplete/.append style={fill=red},
+     group progress label font = \tiny,
+     progress label text={$\displaystyle#1\%$},
+     group progress label anchor = east,
+     bar progress label font = \tiny,
+     bar progress label anchor = east,
+     ]{1}{17}
 
 %     \gantttitle{2020}{17}\\
-%     \gantttitle{Sep}{4}
-%     \gantttitle{Oct}{4}
-%     \gantttitle{Nov}{4}
-%     \gantttitle{Dec}{4}
-%     \gantttitle{}{1}\\
+     \gantttitle{Sep}{4}
+     \gantttitle{Oct}{4}
+     \gantttitle{Nov}{4}
+     \gantttitle{Dec}{4}
+     \gantttitle{}{1}\\
 
 %     \ganttgroup[progress = 100]{Research}{3}{12} \\
-%     \ganttbar[progress = 100]{Research Multipath}{3}{12}\\
-%     \ganttbar[progress = 100]{Research Reflector}{3}{12}\\
+     \ganttbar[progress = 100]{Read System Identification Documentation}{3}{12}\\
+     \ganttbar[progress = 100]{Collect Steering, Acceleration, and Braking Data}{3}{12}\\
 
 %     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
-%     \ganttbar[progress = 80]{CoppeliaSim simulation}{8}{10}\\
-%     \ganttmilestone[progress = 0]{Simulation Complete}{10}\\
+     \ganttbar[progress = 80]{System Identification Tutorials}{8}{10}\\
+     \ganttbar[progress = 100]{System Functional Requirements Document}{8}{10}\\
+          \ganttbar[progress = 100]{System Functional Requirements Presentation}{8}{10}\\
 
-%     \ganttgroup[progress = 100]{Project Proposal}{11}{12}\\
-%     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
-%     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\
+     \ganttbar[progress = 100]{Parts Order Request}{8}{12}\\
+     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
+     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\
 
 %     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
-%     \ganttbar[progress = 90]{Voltage Regulator Circuit}{13}{13}\\
-%     \ganttbar[progress = 80]{Configuration with X-CTU}{14}{14}\\
-%     \ganttbar[progress = 90]{Sensing RSSI}{14}{14}\\
-%     \ganttbar[progress = 70]{Serial Communication}{14}{14}\\
-%   \end{ganttchart}
-% \caption{Gantt chart for Fall 2020}
-% \label{fig:gantt1}
-% \end{figure}
+     \ganttmilestone[progress = 90]{Model Steering System}{13}{13}\\
+     \ganttbar[progress = 80]{Model Acceleration System}{14}{14}\\
+     \ganttbar[progress = 90]{Model Braking System}{14}{14}\\
 
-% \begin{figure}
-%   \centering
-%   \begin{ganttchart}[
-%     hgrid,
-%     vgrid,
-%     x unit=.6cm,
-%     y unit title=.8cm,
-%     y unit chart=.6cm,
-%     milestone label font=\tiny,
-%     milestone progress label font = \tiny,
-%     milestone progress label anchor = east,
-%     bar label font=\tiny,
-%     group label font=\small,
-%     bar/.append style={fill=green},
-%     bar incomplete/.append style={fill=red},
-%     group progress label font = \tiny,
-%     progress label text={$\displaystyle#1\%$},
-%     group progress label anchor = east,
-%     bar progress label font = \tiny,
-%     bar progress label anchor = east,
-%     ]{1}{18}
-%     \gantttitle{2021}{18}\\
-%     \gantttitle{Jan}{2}
-%     \gantttitle{Feb}{4}
-%     \gantttitle{Mar}{4}
-%     \gantttitle{Apr}{4}
-%     \gantttitle{May}{4}\\
+   \end{ganttchart}
+ \caption{Gantt chart for Fall 2021}
+ \label{fig:gantt1}
+ \end{figure}
+
+ \begin{figure}
+   \centering
+   \begin{ganttchart}[
+     hgrid,
+     vgrid,
+     x unit=.6cm,
+     y unit title=.8cm,
+     y unit chart=.6cm,
+     milestone label font=\tiny,
+     milestone progress label font = \tiny,
+     milestone progress label anchor = east,
+     bar label font=\tiny,
+     group label font=\small,
+     bar/.append style={fill=green},
+     bar incomplete/.append style={fill=red},
+     group progress label font = \tiny,
+     progress label text={$\displaystyle#1\%$},
+     group progress label anchor = east,
+     bar progress label font = \tiny,
+     bar progress label anchor = east,
+     ]{1}{18}
+     %\gantttitle{2021}{18}\\
+     \gantttitle{Jan}{2}
+     \gantttitle{Feb}{4}
+     \gantttitle{Mar}{4}
+     \gantttitle{Apr}{4}
+     \gantttitle{May}{4}\\
 
 %     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
-%     \ganttbar[progress = 0]{Replace Motors}{3}{3}\\
-%     \ganttbar[progress = 0]{Design and Construct Reflector}{3}{4}\\
-%     \ganttbar[progress = 0]{Mount Reflector}{4}{4}\\
-%     \ganttmilestone[progress = 0]{Assembly Complete}{4}\\
+     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{3}{3}\\
+     \ganttbar[progress = 0]{Model Shift System}{3}{4}\\
+     \ganttbar[progress = 0]{Model Speed Control System}{4}{4}\\
+     \ganttbar[progress = 0]{Model Speed System}{4}{10}\\
 
 %     \ganttgroup[progress = 10]{Software}{5}{6}\\
-%     \ganttbar[progress = 20]{XBee Library}{5}{5}\\
-%     \ganttbar[progress = 0]{Control Library}{6}{6}\\
-
-%     \ganttgroup[progress = 0]{Angle Estimation}{7}{8}\\
-%     \ganttbar[progress = 0]{Rotate XBee on Stepper Motor}{7}{7}\\
-%     \ganttbar[progress = 0]{Determine Angle}{8}{8}\\
-
-%     \ganttgroup[progress = 0]{Distance Estimation}{9}{10}\\
-%     \ganttbar[progress = 0]{Calibrate Distance Calculation}{9}{10}\\
-
-%     \ganttgroup[progress = 0]{Subsystem Integration}{11}{15}\\
-%     \ganttbar[progress = 0]{Angle Estimation Testing}{11}{11}\\
-%     \ganttbar[progress = 0]{Distance Estimation Testing}{12}{13}\\
-%     \ganttbar[progress = 0]{System Testing}{14}{15}\\
-%     \ganttmilestone[progress = 0]{Integration Complete}{15}\\
+     \ganttbar[progress = 20]{Test Subsystems}{5}{5}\\
+     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{6}{6}\\
 
 %     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
-%     \ganttbar[progress = 0]{Final Report}{16}{16}\\
-%     \ganttbar[progress = 0]{Final Presentation}{17}{17}\\
-%     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
-%     \ganttbar[progress = 0]{Project Demo}{17}{17}\\
+     \ganttmilestone[progress = 0]{Final Report}{16}{16}\\
+     \ganttmilestone[progress = 0]{Final Presentation}{17}{17}\\
+     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
+     \ganttbar[progress = 0]{Project Demo}{17}{17}\\
 
 %     \ganttmilestone[progress = 0]{Project Complete}{17}
-%   \end{ganttchart}
-%   \caption{Gantt Chart for Spring 2020}
-%   \label{fig:gantt2}
-% \end{figure}
+   \end{ganttchart}
+   \caption{Gantt Chart for Spring 2022}
+   \label{fig:gantt2}
+ \end{figure}
 

### 2021-10-31 proposal.tex
Updated proposal.tex

--- 2021-10-28 proposal.tex
@@
 Accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage these vehicles.
-
-There are six main subsystems - a steering model, an acceleration model, a brake
-model, a shifting model, a speed model, and a cruise model - that must be
-modeled to get an accurate representation of how the vehicle should be
-controlled. We will be modeling these six subsystems for a Lexus platform using
-the System Identification Toolbox from Matlab.
+\vspace*{12pt}
+\noindent
+There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
+We will be modeling these six subsystems for a Lexus vehicle platform using the System Identification Toolbox from Matlab.
 The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
-There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected.
-The scope of this project includes developing mathematical models for each subsystem so Autonomous Stuff can implement controls that improve the reliability of the autonomous vehicle platform.
+There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected due to non-linear behaviors of the torques voltages required to control each subsystem.
+The scope of this project includes developing mathematical models for each subsystem so AutonomouStuff can implement controls that improve the reliability of the autonomous vehicle platform.
 These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
@@
     \item A HIL test bench can be developed from the plant model of the subsystems
-    \item The steering model can handle very small steering angles
+    \item The steering model can handle very small changes in steering angles
+    \begin{itemize}
+    		\item The steering model should have a very smooth, continuous output as a choppy, discontinuous output would translate into difficulty tracking the vehicle in a straight line for instances such as keeping the vehicle in its lane.
+For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle
+    \end{itemize}
 \end{itemize}
@@
  \subsection{Specifications}
- Based on the requirements, the vehicle platform plant model must meet the following specifications:
+ Based on the system requirements, the vehicle platform plant model must meet the following specifications:
  \begin{itemize}

### 2021-11-01 proposal.tex
Updated labNotebook.tex and proposal.tex

@@
 
-Introduction to system identification...., Mathworks' MATLAB has the system
-identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
+There are many components or systems that engineers use to accomplish a task that they are assigned without knowing the exact behavior of this system for a given input.
+Without knowing the response of this black-box, there could be unexpected consequences from a system.
+The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
+Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
 
@@
 
-\subsection{Example 2: ..........}
+\subsection{Example 2: Selecting Model Structures for Multivariable Systems}
 \label{sec:sysID-Example2}
+This example discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
+Therefore, the process for developing a model for a MISO system is importing the data as an iddata object, removing the mean from the data, and estimating the solution using any model structure available in the toolbox.
+The command line can be used by using the function associated with the model structure name and then using the compare function to get the best fit percentage.
+For MIMO systems, there are not model structures built into the System Identification Toolbox and they must be imported instead.
+Otherwise the process is very similar to that of a MISO system.
+For a MIMO system, using the compare function can be crucial.
+The compare function will tell which output channel is the most difficult to develop a model for, if it is possible at all.
+With this information, the output channel that is hardest to model should first be modeled individually because there will be less freedom in what model structures are available.
+The other channels should be able to closely relate to the model for the output channel you selected.
 
@@
 \label{sec:sysID-Example3}
-
-% \vspace*{12pt}
-% \noindent
-% One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
-Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
-Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
-
-% \vspace*{12pt}
-% \noindent
-% In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user.
-The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}.
-In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.
-
-% \vspace*{12pt}
-% \noindent
-% The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems.
-Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals.
-The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals.
-This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user.
-Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays.
-The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment.
-Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.
-
-% \vspace*{12pt}
-% \noindent
-% All of the solutions that were found required direct line-of-sight between the robot and the user.
-In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing.
-The major challenge of this implementation will be estimating the distance between the robot and the remote in varying environments.
 
@@
 
-% \section{System Architecture}
-% The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target (user or customer, for example) as shown in \autoref{fig:sys_block_diag}.
-The proposed mobile cart is a wheeled robot that sends and receives radio signals to follow the remote target.
-The remote acts as the target for the mobile cart system by sending radio signals back and forth with the cart.
+\section{System Architecture}
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:sys_block_diag}.
 
@@
 
-% \subsection{System Components}
-% There are several components that are required for the mobile cart system.
-Although some of these parts are available in the Bradley University laboratory, other parts must be purchased.
-The parts that exist in the lab are shown in \autoref{tab:Partslablist}.
-Also, \autoref{tab:Partslist} shows the list of parts that we must purchase.
-The parts lists shown are the parts needed to build two mobile cart systems.
-
-% \begin{table}[h!]
-%   \centering
-%   \begin{tabular}{c|c}
-%       \toprule
-%       \textbf{Quantity} & \textbf{Parts}\\
-%       \toprule
-%       2 & Budget Bot Chassis\\
-%       4 & 10 uF Ceramic Capacitor\\
-%       4 & LM1117 Regulator\\
-%       2 & Battery Packs for Budget Bot\\
-%       8 & 9V Batteries\\
-%       4 & Solderable PCB Boards\\
-%       3 & XBee USB Adapter\\
-%       \bottomrule
-%       %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
-%       %\bottomrule
-%   \end{tabular}
-%   \caption{Parts Available in Laboratory}
-%   \label{tab:Partslablist}
-% \end{table}
-
-% \begin{table}[h!]
-%   \centering
-%   \begin{tabular}{c|c|c}
-%     \toprule
-%     \textbf{Quantity} & \textbf{Parts} & \textbf{Price}\\
-%     \toprule
-%     4 & Pololu 37D Metal Gear motor 4751 & \$ 39.95\\
-%     12 & XBee S2C Module & \$ 23.10\\
-%     10 & XBee Adapter Board & \$ 4.99\\
-%     2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99\\
-%     1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99\\
-%     1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99\\
-%     1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
-%     \bottomrule
-%     \multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
-%     \bottomrule
-%   \end{tabular}
-%   \caption{Purchased parts for the Robotic Cart Project}
-%   \label{tab:Partslist}
-% \end{table}
-
-% \vspace*{12pt}
-% \noindent
-% The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}).
-Another major component is the reflector array that
-% will be used to directionalize the RF signals received from the remote target that is with the user.
-
-% \begin{figure}
-%   \centering
-%   \begin{minipage}[t]{0.32\textwidth}
-%     % \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
-%     \captionsetup{width=\textwidth}
-%     \caption{Budget Bot Chassis}
-%     \label{fig:budgetBotChassis}
-%   \end{minipage}%
-%   \begin{minipage}[t]{0.32\textwidth}
-%     % \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
-%     \captionsetup{width=\textwidth}
-%     \caption{BeagleBone Blue}
-%     \label{fig:beagleboneBlue}
-%   \end{minipage}
-%   \begin{minipage}[t]{0.32\textwidth}
-%     % \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
-%     \captionsetup{width=\textwidth}
-%     \caption{XBee S2C Module}
-%     \label{fig:XBeeModule}
-%   \end{minipage}
-% \end{figure}
-
-% \vspace*{12pt}
-% \noindent
-% The reflector array will be mounted on top of the cart where it will be attached with a stepper motor.
-There are two reflector designs that we will be evaluating in this project.
-The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly.
-Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array.
-The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this.
-To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}.
-The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.
-The upper part of the reflector is strictly parabolic.
-This shape focuses the signals in the horizontal plane, but allows signals from above to still be received.
-We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape.
-Both models will then be tested to determine which design works better.
-
-% \begin{figure}[h!]
-%   \centering
-%   \begin{minipage}[t]{0.5\textwidth}
-%     \centering
-%     % \includegraphics[height=2in]{figs/img/paraboloidalReflector}
-%     \captionsetup{width=\textwidth, justification=raggedright}
-%     \caption{Paraboloidal Reflector Model}
-%     \label{fig:parabolodialReflector}
-%   \end{minipage}
-%   \begin{minipage}[t]{0.4\textwidth}
-%     \centering
-%     % \includegraphics[height=2in]{figs/img/parabolicReflector}
-%     \captionsetup{width=\textwidth, justification=raggedright}
-%     \caption{Combined Parabolic/Paraboloidal Reflector}
-%     \label{fig:parabolicReflector}
-%   \end{minipage}
-% \end{figure}
-
 % \subsection{Operation of Mobile Cart System}
@@
 % \end{figure}
-
-% \subsection{Algorithms}
-% As mentioned previously, there are two steps in the operation of the system.
-These steps are the localization of the remote and the navigation of the robot.
-This section describes the algorithms used for these tasks.
-
-% \subsubsection{Localization Algorithm}
-% The strength of the radio signals between the cart and remote will be used to estimate the position of the remote relative to the cart.
-By rotating the sensor array 90 degrees and measuring the signal strength of messages from the remote at several steps in the rotation, the bearing of the remote can be estimated as the direction in which the maximum signal strength is received.
-To estimate the distance between the cart and the remote, the signal strength will be measured and used to calculate the distance.
-The omnidirectional radio module on top will be responsible for coordinating the messages from the remote by sending the remote commands that tell the remote when to send signals.
-A flowchart of the localization algorithm is shown in \autoref{fig:locAlgoFlowchart}.
-Also, a pseudo-code version of the algorithm is shown in \autoref{alg:locAlgo}
-
-% \begin{figure}
-%   \centering
-%   \input{figs/dia/localizationAlgoFlowchart.tex}
-%   \caption{Flowchart of Localization Algorithm}
-%   \label{fig:locAlgoFlowchart}
-% \end{figure}
-
-% \begin{algorithm}[h!]
-%   \SetAlgoLined
-%   \KwOut{Range $d_{ref}$ and Bearing $\theta_{ref}$ of remote}
-%   Constants: step angle $\theta_{step}$\\
-%   Static direction variable $dir = 1$
-%   \Begin
-%   {
-%     \uIf{Reflectors not rotated 90\textdegree}
-%     {
-%       Send signal strength request to remote\\
-%       Get signal strengths from receivers\\
-%       Rotate reflectors through an angle of $dir*\theta_{step}$\\
-%     }
-%     \Else
-%     {
-%       $\theta_{ref} =$ direction of max signal strength\\
-%       Compute $d_{ref}$ using signal strength\\
-%       $dir = -dir$\\
-%     }
-%   }
-%   \caption{Localization Algorithm}
-%   \label{alg:locAlgo}
-% \end{algorithm}
-
-% \subsubsection{Navigation Algorithm}
-% Once the bearing and distance of the remote are estimated, the cart must move to follow the remote.
-We will use a modified Point Navigation algorithm to navigate the robot to follow the remote.
-The robot will estimate the coordinates of the remote with respect to the robot's local reference frame.
-The robot will then apply actuation to move to the point that is a set following distance from the remote.
-A flowchart of the navigation algorithm is shown in \autoref{fig:navAlgoFlowchart}.
-Also, a pseudo-code version of the algorithm is shown in \autoref{alg:navAlgo}.
-
-% \begin{figure}
-%   \centering
-%   \input{figs/dia/navigationAlgoFlowchart.tex}
-%   \caption{Flowchart of Navigation Algorithm}
-%   \label{fig:navAlgoFlowchart}
-% \end{figure}
-
-% \begin{algorithm}[h!]
-%   \SetAlgoLined
-%   \KwIn{Range $d_{ref}$ and Bearing $\theta_{ref}$ of Remote}
-%   \KwOut{Mobile Robot Trajectory}
-%   Constants: following distance $d_f$ and proportional gains $K_p$ and $K_\omega$\\
-%   \Begin
-%   {
-%     Compute target point with respect to robot's local frame as $x_{ref} = (d_{ref} - d_f)\cos \theta_{ref}$, $y_{ref} = (d_{ref} - d_f)\sin \theta_{ref}$\\
-%     Compute linear speed $v(t) = sign(x_{ref})K_p\sqrt{x_{ref}^2 + y_{ref}^2}$\\
-%     Compute $\omega(t) = K_\omega \theta_{ref}$\\
-%     Apply wheel speeds to robot\\
-%   }
-%   \caption{Navigation Algorithm}
-%   \label{alg:navAlgo}
-% \end{algorithm}
 
@@
 \section{Concluding Remarks}
-Autonomous vehicles have a numerous amount of useful applications in today's society. ...
+Autonomous vehicles have a numerous amount of useful applications in today's society.
+From being used for delivering packages to allowing drivers to rest while traveling, as the technology for autonomous vehicles is enhanced, they will become an enticing product that many consumers will purchase and use.
+One of the biggest concerns with autonomous vehicles today is the risk associated with public safety.
+One solution to reducing the safety risk is ensuring that accurate controllers are developed to reliably control each subsystem involved with the controlling the movement of the autonomous vehicle.
+Due to non-linear behaviors, there is no simple solution for developing reliable controllers.
+This project will focus on deriving models of some main subsystems so that these non-linear behaviors are removed and smooth controllers can be developed.
 

### 2021-11-01 proposal.tex
Updated Timeline
Updated the Timeline/Milestone Section, and started on the example summary.

@@
 
-\subsection{Example 3: ..........}
+\subsection{Example 3: Identify Linear Models Using the Command Line}
 \label{sec:sysID-Example3}
@@
 %     \ganttgroup[progress = 100]{Research}{3}{12} \\
-     \ganttbar[progress = 100]{Read System Identification Documentation}{3}{12}\\
-     \ganttbar[progress = 100]{Collect Steering, Acceleration, and Braking Data}{3}{12}\\
+     \ganttbar[progress = 100]{Read System Identification Documentation}{3}{6}\\
+     \ganttbar[progress = 100]{Collect Steering, Acceleration, and Braking Data}{6}{7}\\
 
 %     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
-     \ganttbar[progress = 80]{System Identification Tutorials}{8}{10}\\
-     \ganttbar[progress = 100]{System Functional Requirements Document}{8}{10}\\
-          \ganttbar[progress = 100]{System Functional Requirements Presentation}{8}{10}\\
+     \ganttbar[progress = 100]{System Identification Tutorials}{4}{7}\\
+     \ganttbar[progress = 100]{System Functional Requirements Document}{4}{9}\\
+          \ganttbar[progress = 100]{System Functional Requirements Presentation}{4}{9}\\
 
      \ganttbar[progress = 100]{Parts Order Request}{8}{12}\\
-     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
-     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\
+     \ganttbar[progress = 50]{Proposal Document}{9}{15}\\
+     \ganttbar[progress = 30]{Proposal Presentation}{9}{15}\\
 
 %     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
-     \ganttmilestone[progress = 90]{Model Steering System}{13}{13}\\
-     \ganttbar[progress = 80]{Model Acceleration System}{14}{14}\\
-     \ganttbar[progress = 90]{Model Braking System}{14}{14}\\
+     \ganttmilestone[progress = 30]{Model Steering System}{13}{14}\\
+     \ganttbar[progress = 0]{Model Acceleration System}{14}{15}\\
+     \ganttbar[progress = 0]{Model Braking System}{15}{16}\\
 
@@
      \ganttbar[progress = 0]{Model Shift System}{3}{4}\\
-     \ganttbar[progress = 0]{Model Speed Control System}{4}{4}\\
-     \ganttbar[progress = 0]{Model Speed System}{4}{10}\\
+     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
+     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\
 
 %     \ganttgroup[progress = 10]{Software}{5}{6}\\
-     \ganttbar[progress = 20]{Test Subsystems}{5}{5}\\
-     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{6}{6}\\
+     \ganttbar[progress = 0]{Test Subsystems}{9}{12}\\
+     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{12}{15}\\
 
 %     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
-     \ganttmilestone[progress = 0]{Final Report}{16}{16}\\
-     \ganttmilestone[progress = 0]{Final Presentation}{17}{17}\\
+     \ganttmilestone[progress = 0]{Final Report}{15}{15}\\
+     \ganttmilestone[progress = 0]{Final Presentation}{16}{16}\\
      \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
@@
  \end{figure}
+
+	Our Gantt charts shown in Figures \ref{fig:gantt1} and \ref{fig:gantt2} outline our project work and milestones for the year.
+While we are still working on the details, we plan on splitting the work equally to make sure that we each get a chance to learn from this project and to keep it fair for all team members.
+
+The first milestone on our list will be to model the steering system.
+This will be a challenge due to its small non-linearities around very small steering angle changes.
+The next milestone will be to test our subsystem models on AutonomouStuff's HIL system.
+This is one of the most important milestones because the company sponsors our project and we are working to help solve one of their problems.
+Our last two milestones will be to present our work in the form of a final report and presentation.
+This is where all of our work will come together and we will get a chance to explain how we solved the problem.
+
+We plan on demonstrating our project for AutonomouStuff along with including a full report on how we modeled the vehicle subsystems.
+As for the final report and presentation, we plan on working on it as soon as possible next semester.
+This presentation will also be shown to the Industrial Advisory Board.
 

### 2021-11-02 proposal.tex
Updated Proposal Document
I paraphrased the System Requirements and System Specification sections. I also added to the Matlab examples, along with the Modeling section

@@
 \label{sec:sysID-Example3}
+This example shows how to create models for MISO systems using the command line.
+Before starting the model estimation process, the equilibrium values of the inputs and outputs had to be taken out.
+The data from each experiment also had to be separated into different iddata objects.
+The example showed how to estimate and compare non-parametric impulse response, transfer function, ARMA, state-space, and Box-Jenkins models with the measured experimental data.
+The state-space model with the five-step response prediction was the most accurate, with a best fit percentage of 85.83\%.
 
 \section{System Requirements}
-The vehicle platform plant model will meet the following requirements:
+The vehicle plant model will fulfill the requirements listed below:
 \begin{itemize}
-    \item The plant model should have an accurate model of the six main subsystems
-    \item A HIL test bench can be developed from the plant model of the subsystems
+    \item The resulting plant model will consist of accurate subsystem models
+    \item The subsystems can be used to create an HIL testbench
     \item The steering model can handle very small changes in steering angles
@@
  \subsection{Specifications}
- Based on the system requirements, the vehicle platform plant model must meet the following specifications:
+ Based on the system requirements listed above, the plant model will meet the following specifications:
  \begin{itemize}
-    \item The model of the steering subsystem should be modeled first as it is crucial to operation and has non-linearity considerations
-    \item All subsystems will be modeled individually 
-    \item Our steering model will be designed to accommodate very small steering angles
+    \item The steering subsystem will be modeled first due to its non-linearities and the fact that it is important to the operation of the vehicle
+    \item Each vehicle subsystem will be modeled separately 
+    \item The steering subsystem will be able to handle small steering angles
  \end{itemize}
@@
 
-% % \subsection{Modelling} \label{sec:model}
+ \subsection{Modeling} \label{sec:model}
+ All modeling of vehicle subsystems will be done using Matlab's System Identification Toolbox feature.
+The subsystems can be grouped into four different categories: Single-Input-Single-Output, Multiple-Input-Multiple-Output, Single-Input-Multiple-Output, and Multiple-Input-Single-Output.
 

### 2021-11-02 proposal.tex
Updated proposal and bibliography file

@@
  \section{Literature Review}
+
+Authors in~\cite{Hussain2011} illustrates identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.
+
 In the paper “Identification of Multiple Input-Single Output (MISO) Model for MPPT of Photovoltaic System”, the researchers wanted to model a system where the two inputs were Solar irradiance and Cell temperature and the output was DC current.
@@
 \label{sec:sysID-Example1}
+
 During this example I learned how to create an iddata object from a dataset in order to get the inputs and the outputs.
@@
 
+The Gantt chart highlighting the progress and potential schedule of the project in Fall 2021 is shown in Figure~\ref{fig:gantt1}.
+
  \begin{figure}
@@
  \end{figure}
+
+The potential schedule for our project in Spring 2022 is highlighted in the gantt chart shown in Figure~\ref{fig:gantt2}.
 

### 2021-11-03 proposal.tex
Updated Proposal.tex
I added the software used by AutonomouStuff to the parts list
Adding inkscape fig, Updating proposal.tex

@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:sys_block_diag}.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:steerBlockDiag}, \autoref{fig:brakeBlockDiag}, \autoref{fig:accelBlockDiag}, \autoref{fig:shiftBlockDiag}, \autoref{fig:cruiseBlockDiag}, and \autoref{fig:speedBlockDiag}.
 
-% \subsection{System Block Diagram}
-% The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}.
-There are four inputs to the proposed cart system.
-Obviously, the robotic cart is powered on through a source of power (input), which is simply a battery, for instance.
-There will be an on/off switch to allow the system to be powered down when not in use.
-The motion of the cart will be controlled by the motion of the remote.
-A stretch goal is to have mode selection buttons to allow the user to put the system into different operating modes which will be explained later on.
-
-% \vspace*{12pt}
-% \noindent
-% The main output of the system is the trajectory of the cart on the ground.
-As the user moves with the remote, the cart is supposed to follow the user.
-The other output of the robotic cart system is status indication in the form of LED lights.
-These lights will be used to notify the user of the status of the system.
-
-% \begin{figure}[!h]
-%     \centering
-%     % \includegraphics[scale=0.9]{figs/system_block_diagram_2}
-%     \caption{System level block diagram detailing inputs and outputs to the
-%       mobile cart system.}
-% 	\label{fig:sys_block_diag}
-% \end{figure}
-
-% \subsection{Subsystem Block Diagrams}
-% Both of the subsystems of the mobile cart system, being the Mobile Cart and Remote Target, act as their own enclosed systems.
-The two subsystems communicate with one another by relaying radio messages between them.
-The block diagram of the Remote Target subsystem is shown in \autoref{fig:remote_block_diag}.
-Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 9 volt battery with a voltage regulation circuit.
-
-% \vspace*{12pt}
-% \noindent
-% The Mobile Cart subsystem block diagram is shown in
-% \autoref{fig:mobile_block_diag}. The Mobile Cart has four inputs. The cart
-% requires a power source, which will be a Li-Po battery. The power to the
-% subsystem will be toggled by an on/off switch. The buttons for changing the
-% operating mode of the cart will be on the cart if we have time to implement
-% them. The final input to the mobile cart subsystem is the XBee network messages
-% received from the remote target.
-
-% \vspace*{12pt}
-% \noindent
-
-% There are three outputs of the mobile cart subsystem. The first is the wheel
-% velocities that move the cart. There will also be LEDs to indicate the status of
-% the system to the user. Also, the cart will send radio messages to the remote
-% target by means of an array of XBee radio modules. %
-% %
-% \begin{figure}[h!]
-%   \centering
-%   \missingfigure
-%   % \includegraphics[scale=0.9]{figs/remote_target_block_diagram}
-%   \caption{Remote Target block diagram}
-%   \label{fig:remote_block_diag}
-% \end{figure}
-
-% \begin{figure}[h!]
-%   \centering
-%   % \includegraphics[scale=0.82]{figs/mobile_cart_block_diagram}
-%   \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
-%   \label{fig:mobile_block_diag}
-% \end{figure}
-
-% \subsection{Operation of Mobile Cart System}
-% The Mobile Cart will controlled by a central embedded computer which we are using the BeagleBone Blue for.
-Two DC motors will be used to drive wheels to move the cart.
-Five XBee modules will be used to allow communication with the remote target.
-One of these radio sensors will be mounted on top of the cart to broadcast in all directions.
-The other four sensors will be placed inside parabolic reflectors at right angles to each other.
-This sensor array will be mounted on a stepper motor to allow rotation.
-
-% \vspace*{12pt}
-% \noindent
-
-% There are two main steps in the operation of the robotic cart system.
-The first step is localization of the remote in the robot's local coordinate frame.
-Once the location of the remote is known, the navigation step handles the control of the wheel velocities to move the cart to the desired location.
-A flowchart of the system operation is shown in \autoref{fig:sysOpFlowchart}.
-
-% \begin{figure}
-%   \centering
-%   \input{figs/dia/systemOperationFlowchart.tex}
-%   \caption{Flowchart of System Operation}
-%   \label{fig:sysOpFlowchart}
-% \end{figure}
+\begin{minipage}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=3in]{figs/inkscape/steeringModelArchitecture}
+    \caption{Block Diagram of the Vehicle Steering Model.}
+    \label{fig:steerBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Block Diagram of the Vehicle Brake Model.}
+    \label{fig:brakeBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+    \caption{Block Diagram of the Vehicle Acceleration Model.}
+    \label{fig:accelBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
+    \caption{Block Diagram of the Vehicle Shift Model.}
+    \label{fig:shiftBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
+    \caption{Block Diagram of the Vehicle Speed Control Model.}
+    \label{fig:cruiseBlockDiag}
+\end{figure}
+%
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
+    \caption{Block Diagram of the Vehicle Speed Model.}
+    \label{fig:speedBlockDiag}
+\end{minipage}
 

### 2021-11-03 proposal.tex
Updated references.bib and proposal.tex

@@
 \label{sec:sysID-Example2}
-This example discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example, \~cite{Matlab2} discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
     		\item The steering model should have a very smooth, continuous output as a choppy, discontinuous output would translate into difficulty tracking the vehicle in a straight line for instances such as keeping the vehicle in its lane.
-For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle
+For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle.
+The non-linear behavior is depicted in \autoref{fig:nonlinGraph}.
     \end{itemize}
 \end{itemize}
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=3in]{figs/inkscape/nonlinearBehavior}
+    \caption{Steering Non-linear Behavior}
+    \label{fig:nonlinGraph}
+\end{figure}
 
@@
  \begin{itemize}
-    \item The steering subsystem will be modeled first due to its non-linearities and the fact that it is important to the operation of the vehicle
+    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and the fact that it is important to the operation of the vehicle
     \item Each vehicle subsystem will be modeled separately 
@@
     \item MATLAB's System Identification Toolbox 
-    \item  
+    \item Vector CANAlyzer 
  \end{itemize}

### 2021-11-03 proposal.tex
Updated proposal.tex

@@
 \label{sec:sysID-Example2}
-This example, \~cite{Matlab2} discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example, \~cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.

### 2021-11-03 proposal.tex
Update proposal.tex
I have added the new citations for both matlab examples

@@
 
-During this example I learned how to create an iddata object from a dataset in order to get the inputs and the outputs.
+During this example in~\cite{example1} I learned how to create an iddata object from a dataset in order to get the inputs and the outputs.
 The next step was to look at the impulse and step responses in order to learn more about how the inputs and outputs act.
@@
 \label{sec:sysID-Example3}
-This example shows how to create models for MISO systems using the command line.
+This example in~\cite{example3} shows how to create models for MISO systems using the command line.
 Before starting the model estimation process, the equilibrium values of the inputs and outputs had to be taken out.

### 2021-11-06 proposalPres.tex
Update ProposalPres.tex
I added some slides to our presentation to reflect the different sections of our proposal document.

@@
 
+\section{System Identification}
+
+\begin{frame}{System Identification}
+  \begin{block}{System Identification}
+ \begin{itemize}
+        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
+The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
+Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+	\item 
+	\item 
+\end{itemize}
+  \end{block}
+\end{frame}
+
 % \begin{frame}{Literature Review}
@@
 %\end{frame}
-
-%----------------------------------
-
-% \begin{frame}{Literature Review}
-%   \begin{block}{Multipath Interference}
-%     \begin{itemize}
-%       \item Proposed solutions to multipath interference
-%       \begin{itemize}
-%         \item Course estimation calculations such as recieved signal strength indicator (RSSI) and time difference of arrival (TDoA)
-%         \item IEEE 802.11b wireless Ethernet device to measure RF signals
-%         \item Sampling radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position
-%       \end{itemize}
-%     \end{itemize}
-%   \end{block}
-%       \begin{figure}[b]
-%         \centering
-%         \includegraphics[width=0.40\textwidth]{figs/img/MultipathFading}
-%         \caption{Multipath Fading}
-%         %\label{fig:sysBlockDiag}
-%     \end{figure}
-% \end{frame}
-
-% %----------------------------------
 
@@
 
+%--------------------------------
+
+\section{System Architecture}
+
+\begin{frame}{System Architecture}
+  \begin{block}{}
+ \begin{itemize}
+        \item 
+	\item 
+	\item 
+\end{itemize}
+  \end{block}
+\end{frame}
+
 %----------------------------------
+
+\section{Preliminary Work}
+
+\begin{frame}{Preliminary Work}
+  \begin{block}{Preliminary Work}
+ \begin{itemize}
+        \item Documentation on MATLAB's System Identification Toolbox and tutorials
+        \item Literature Review 
+        \item Data Collection for steering, braking and acceleration subsystems
+\end{itemize}
+  \end{block}
+  \begin {block}{Modeling}
+  \begin{itemize}
+  	\item All modeling of vehicle subsystems will be done using MATLAB's System Identification Toolbox feature.
+The subsystems can be grouped into four different categories: Single-Input-Single-Output, Multiple-Input-Multiple-Output, Single-Input-Multiple-Output, and Multiple-Input-Single-Output.
+  	\end{itemize}
+  	\end{block}
+\end{frame}
+
+%----------------------------------
+\section{Simulation Results}
+
+\begin{frame}{Simulation Results}
+  \begin{block}{}
+ \begin{itemize}
+        \item 
+	\item 
+	\item 
+\end{itemize}
+  \end{block}
+\end{frame}
+
+%----------------------------------
+\section{Parts List}
+
+\begin{frame}{Parts List}
+  \begin{block}{Software and Hardware}
+ \begin{itemize}
+        \item Software
+        \begin{itemize}
+        \small
+        \item MATLAB's System Identification Toolbox
+        \item Vector CANAlyzer
+        \end{itemize}
+	\item Hardware
+	\begin{itemize}
+	\small
+	\item Laptop
+	\item PAC Mod
+	\item CAN Case 
+	\item CAN Bus
+	\end{itemize}
+\end{itemize}
+  \end{block}
+\end{frame}
+
+%----------------------------------
+\section{Timeline and Milestones}
+
+\begin{frame}{Timeline and Milestones}
+  \begin{block}{Milestones}
+ \begin{itemize}
+        \item Model steering subsystem 
+	\item Test subsystem models with HIL system 
+	\item Final report and presentation 
+\end{itemize}
+  \end{block}
+\end{frame}
+
+%----------------------------------
+\section{Timeline and Milestones}
+
+\begin{frame}{Timeline and Milestones}
+
+\end{frame}
+
+%----------------------------------
+
 \begin{frame}{Other Considerations}

### 2021-11-07 proposalPres.tex
Update proposalPres.tex
I added to the literature review and System Architecture slides, and changed some things in the System Identification slide.

@@
 \begin{frame}{Literature Review}
-  \begin{block}{Existing Solution}
+  \begin{block}{Existing Solutions}
  \begin{itemize}
@@
 				\item Mechanical components replaced by electrical components 
+	\end{itemize}
+	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
+	\begin{itemize}
+	\tiny
+		\item Fourth order ARX model ended up giving the best fit
 	\end{itemize}
@@
 Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
-	\item 
-	\item 
 \end{itemize}
@@
 \begin{frame}{System Architecture}
-  \begin{block}{}
+  \begin{block}{System Architecture}
  \begin{itemize}
-        \item 
-	\item 
-	\item 
+        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems
 \end{itemize}

### 2021-11-07 proposal.tex
Updated labNotebook.tex and proposal.tex
Added entries for 11/2 and 11/4 and created blank entry for 11/9

Added subsections Design and Simulation Results
Updated proposal.tex
Added figures for the estimated transfer function models of the steering system
Updated proposal.tex

@@
 \usepackage{siunitx}
-\sisetup{unitsep=\cdot}
 
@@
 
-\begin{minipage}
-%
 \begin{figure}
@@
     \label{fig:speedBlockDiag}
-\end{minipage}
+\end{figure}
 
@@
 
-% % \subsection{Simulation Results} \label{sec:simresults}
+\subsection{Design} \label{sec:design}
+Each subsystem that we are modeling are set up in a similar manner.
+In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU).
+In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode.
+In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem.
+Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
 
-% % \subsection{Design} \label{sec:design}
+\subsection{Simulation Results} \label{sec:simresults}
+In \autoref{fig:byWireSteerModel}, the output steering angle is plotted versus time when the vehicle is in by-wire mode.
+The figure shows the output steering angle from some data collected to depict the steering system behavior plotted with the behavior of the estimated model.
+The best fit percentage for this model is 85.54.
+Likewise, \autoref{fig:manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode.
+The best fit percentage for this model is 90.27.
 
-% % \subsection{Experimental Activities} \label{sec:expresults}
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
+    \caption{Output of Estimated By-Wire System Model}
+    \label{fig:byWireSteerModel}
+\end{figure}
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
+    \caption{Output of Estimated Manual System Model}
+    \label{fig:manualSteerModel}
+\end{figure}
 

### 2021-11-07 proposalPres.tex
Update proposalPres.tex file
I tried to add gantt charts to the timeline and milestones slide, but was unable to do so.
Updated proposalPres.tex
Added Design slide, Simulation Results

@@
 %----------------------------------
+\section{Design}
+
+\begin{frame}{Design}
+	\begin{block}
+		Each subsystem that we are modeling are set up in a similar manner.
+In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU).
+In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode.
+In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem.
+Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
+	\end{block}
+\end{frame}
+
+%----------------------------------
 \section{Simulation Results}
@@
  \begin{itemize}
-        \item 
-	\item 
-	\item 
+	\item The best fit percentage of the by-wire steering estimated model is 85.54
+	\item The best fit percentage of the manual steering estimated model is 90.27
  \end{itemize}
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
+    \caption{Output of Estimated By-Wire System Model}
+    \label{fig:byWireSteerModel}
+\end{figure}
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
+    \caption{Output of Estimated Manual System Model}
+    \label{fig:manualSteerModel}
+\end{figure}
   \end{block}

### 2021-11-09 proposalPres.tex
Updated proposalPres.tex
Added two image files to figs/img

@@
 
-% \begin{frame}{Literature Review}
-%   \begin{block}{Existing Solution}
-%         Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
-%   \end{block}
-%     \begin{figure}[b]
-%         \centering
-%         \includegraphics[width=0.40\textwidth]{figs/img/ShoppingSuportRobot}
-%         \caption{Shopping Support Robot}
-%         %\label{fig:sysBlockDiag}
-%     \end{figure}
-% \end{frame}
-
-% %----------------------------------
-
-% \begin{frame}{Literature Review}
-%   \begin{block}{Existing Solution}
-%     Arduino MEGA 2560, six ultrasonic sensors, two DC motors with Pulse Width Modulation (PWM), an Android Studio IDE device, and Bluetooth~\cite{Rawashdeh2017-Person}
-%   \end{block}
-%     \begin{figure}[b]
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{figs/img/SmartCart}
-%         \caption{Smart Cart Robot}
-%         %\label{fig:sysBlockDiag}
-%     \end{figure}
-% \end{frame}
-
-%----------------------------------
-
-%\begin{frame}{Existing Solutions}
-%  \begin{block}{Problems}
-%    \begin{itemize}
-%      \item Require line-of-sight between robot and user
-%      \item Some require costly dedicated image processing hardware
-%    \end{itemize}
-%  \end{block}
-%  \pause
-%  \begin{block}{Benefits of Proposed Solution}
-%    \begin{itemize}
-%      \item High level of accuracy 
-%    \end{itemize}
-%  \end{block}
-%\end{frame}
-
-% \begin{frame}{Literature Review}
-%   \begin{block}{Challenges}
-%     \begin{itemize}
-%       \item Communication between the robot and the remote
-%       \item Buffer distance between the robotic cart and the customer without using line of sight sensing
-%     \end{itemize}
-%   \end{block}
-% \end{frame}
-
 %----------------------------------
@@
 \section{System Requirements}
+
+\begin{frame}{System Requirements}
+  \begin{block}{Specifications}
+    The vehicle plant model will fulfill the requirements listed below:
+\begin{itemize}
+    \item The resulting plant model will consist of accurate subsystem models
+    \item The subsystems can be used to create a HIL testbench
+    \item The steering model can handle very small changes in steering angles
+    \begin{itemize}
+    		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
+    \end{itemize}
+\end{itemize}
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=1in]{figs/inkscape/nonlinearBehavior}
+    \caption{Steering Non-linear Behavior}
+    \label{fig:nonlinGraph}
+\end{figure}
+  \end{block}
+\end{frame}
+
+%--------------------------------
+
+\section{System Architecture}
+
+\begin{frame}{System Architecture}
+  \begin{block}{System Architecture}
+ \begin{itemize}
+        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems
+\end{itemize}
+  \end{block}
+\end{frame}
+
 \begin{frame}
+\begin{minipage}[t]{0.48\linewidth}
 \tiny
-	\begin{block}{System Inputs and Outputs}
+	\begin{block}{System Inputs}
 		\begin{itemize}
@@
 	\end{block}
-\end{frame}
-\begin{frame}			
-	\begin{figure}
-		\includegraphics[width=10cm]{figs/inkscape/steeringModelArchitecture}
-		\caption{Block Diagram of Steering Subsystem}
-		\label{fig:steeringModel}
-	\end{figure}
+\end{minipage}%
+\hfill%
+\begin{minipage}[t]{0.48\linewidth}
+\begin{block}{System Inputs}
+		\begin{itemize}
+			\tiny
+		    \item Steering Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Wheel Angle
+		    		\item Actual Steering Angle
+		    \end{itemize}
+		    \item Acceleration Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Acceleration Pedal Position
+		    \end{itemize}
+		    \item Brake Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Brake Pedal Position
+		    		\item Brake Pressed
+		    \end{itemize}
+		    \item Shift Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Actual Shift Gear
+		    \end{itemize}
+		    \item Speed Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Vehicle Speed
+		    \end{itemize}
+		    \item Speed Control Model
+		    \begin{itemize}
+		    \tiny
+		    		\item Vehicle Speed
+		    \end{itemize}
+		\end{itemize}
+	\end{block}
+\end{minipage}
 \end{frame}
 
-\begin{frame}{System Requirements}
-  \begin{block}{Specifications}
-    \begin{itemize}
-      	\item The plant model should have an accurate model of the six main subsystems
-    		\item A hardware-in-loop (HIL) test bench can be developed from the plant models of the subsystems
-    		\item The steering model can handle very small steering angles
-    \end{itemize}
-  \end{block}
+\begin{frame}
+\centering
+\includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
+\begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System \item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
+\includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
+\includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
 \end{frame}
 
-%--------------------------------
-
-\section{System Architecture}
-
-\begin{frame}{System Architecture}
-  \begin{block}{System Architecture}
- \begin{itemize}
-        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems
-\end{itemize}
-  \end{block}
+\begin{frame}
+\centering
+\includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
+\begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
+\includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
+\includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
 \end{frame}
@@
 
-\section{Preliminary Work}
+\subsection{Preliminary Work}
 
@@
 %----------------------------------
-\section{Design}
+\subsection{Design}
 
 \begin{frame}{Design}
-	\begin{block}
+	\begin{block}{}
 		Each subsystem that we are modeling are set up in a similar manner.
@@
 %----------------------------------
-\section{Simulation Results}
-
-\begin{frame}{Simulation Results}
-  \begin{block}{}
- \begin{itemize}
-	\item The best fit percentage of the by-wire steering estimated model is 85.54
-	\item The best fit percentage of the manual steering estimated model is 90.27
- \end{itemize}
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
-    \caption{Output of Estimated By-Wire System Model}
-    \label{fig:byWireSteerModel}
-\end{figure}
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
-    \caption{Output of Estimated Manual System Model}
-    \label{fig:manualSteerModel}
-\end{figure}
-  \end{block}
-\end{frame}
-
-%----------------------------------
-\section{Parts List}
+\subsection{Parts List}
 
@@
 %----------------------------------
+\section{Simulation Results}
+
+\begin{frame}{Simulation Results}
+  \begin{block}{}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire steering estimated model is 85.54
+	\item Best fit percentage of the manual steering estimated model is 90.27
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireSteerModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualSteerModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
+\end{frame}
+
+%----------------------------------
 \section{Timeline and Milestones}
@@
 %----------------------------------
-\section{Timeline and Milestones}
 
-\begin{frame}{Timeline and Milestones}
-
-\end{frame}
-
-%----------------------------------
-
-\begin{frame}{Other Considerations}
-  \begin{block}{Factors}
-  	\begin{small}
-      \begin{itemize}
-        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
-and driving fatalities and injuries. As a result, people will be able to live longer and
-healthier lives. By creating accurate models, we will help advance the development of
-autonomous vehicles and make this a reality.
-		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle.
+%\begin{frame}{Other Considerations}
+%  \begin{block}{Factors}
+%  	\begin{small}
+%      \begin{itemize}
+%        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
+%and driving fatalities and injuries. As a result, people will be able to live longer and
+%healthier lives. By creating accurate models, we will help advance the development of
+%autonomous vehicles and make this a reality.
+%		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle.
 We will address this by creating a rigorous test plan for our models.
-		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
-ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
-		\item Global Factors: 
-		\item Cultural Factors: 
-		\item Social Factors: 
-		\item Environmental Factors: 
-		\item Business Factors: 
-		\item Economic Factors: 
-      \end{itemize}
-     \end{small}
-  \end{block}
-\end{frame}
+%		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
+%ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
+%		\item Global Factors: 
+%		\item Cultural Factors: 
+%		\item Social Factors: 
+%		\item Environmental Factors: 
+%		\item Business Factors: 
+%		\item Economic Factors: 
+%      \end{itemize}
+%     \end{small}
+%  \end{block}
+%\end{frame}
 

### 2021-11-10 proposalPres.tex
Added two figures into /figs/img folder
Updated labNotebook.tex with 11/9 entry

Updated proposalPres.tex with Acceleration System Model Estimation Results

@@
 
+\begin{frame}
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=4in]{figs/inkscape/steeringModelBlockDiagram}
+    \caption{Steering System Block Diagram}
+    \label{fig:steerBlockDiag}
+\end{figure}
+\end{frame}
+
 %----------------------------------
@@
 \begin{frame}{Simulation Results}
-  \begin{block}{}
+  \begin{block}{Steering System}
  \begin{itemize}
@@
         \label{fig:manualSteerModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
+\end{frame}
+
+\begin{frame}{Simulation Results}
+  \begin{block}{Acceleration System}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
+	\item Best fit percentage of the manual acceleration estimated model is 98.3
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireAccelModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualAccelModel}
     \end{minipage}

### 2021-11-12 proposalPres.tex
Updated simulation results figures
Updated proposalPres.tex

@@
 
-\section{System Identification}
-
-\begin{frame}{System Identification}
-  \begin{block}{System Identification}
- \begin{itemize}
-        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
-The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
-Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
-\end{itemize}
-  \end{block}
-\end{frame}
-
-%----------------------------------
-
 \section{System Requirements}
@@
 \begin{minipage}[t]{0.48\linewidth}
-\begin{block}{System Inputs}
+\begin{block}{System Outputs}
 		\begin{itemize}
@@
 
+\section{System Identification}
+
+\begin{frame}{System Identification}
+  \begin{block}{System Identification}
+ \begin{itemize}
+        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
+The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
+Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+\end{itemize}
+  \end{block}
+\end{frame}
+
 \subsection{Preliminary Work}
@@
 %----------------------------------
-\section{Simulation Results}
+\subsection{Modeling}
+
+\begin{frame}{Model Equations}
+	\begin{block}{}
+		\begin{itemize}
+			\item Transfer Function Model: 
+			\begin{equation}
+				\frac{Y(s)}{U_A(s)} = \frac{b_{n}*s^{n} + b_{n-1}*s^{n-1} + ... + b_1*s + b_0}{a_{m}*s^{m} + a_{m-1}*s^{m-1} + ... + a_1*s + a_0}
+			\end{equation}
+			where m = number of poles and n = number of zeros
+			\item ARX Model: 
+			\begin{equation}
+				A(z)*y(t) = B(z)*u(t) + e(t)
+			\end{equation}
+		\end{itemize}
+	\end{block}
+\end{frame}
+
+%----------------------------------
+\section{Validation and Testing}
 
@@
 
+\begin{frame}{By-Wire Steering System Transfer Function}
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque A}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & 3.44E-16 \\
+				b_1 & -2.203E-15 \\
+				b_2 & 1.24E-13 \\
+				b_3 & 5.975E-13 \\
+				b_4 & 3.001E-12 \\
+				b_5 & 5.23E-12 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 1.949E-16 \\
+				a_1 & 1.455E-14 \\
+				a_2 & 8.797E-13 \\
+				a_3 & 2.304E-11 \\
+				a_4 & 9.041E-10 \\
+				a_5 & 9.01E-9 \\
+				a_6 & 2.714E-7 \\
+				a_7 & 9.241E-7 \\
+				a_8 & 1.946E-5 \\
+				a_9 & 3.889E-5 \\
+				a_{10} & 0.0005721 \\
+				a_{11} & 0.0008035 \\
+				a_{12} & 0.008695 \\
+				a_{13} & 0.008922 \\
+				a_{14} & 0.07499 \\
+				a_{15} & 0.05422 \\
+				a_{16} & 0.3631 \\
+				a_{17} & 0.1693 \\
+				a_{18} & 0.9394 \\
+				a_{19} & 0.2118 \\
+				a_{20} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}%
+\hfill%
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque B}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & -6.645E-15 \\
+				b_1 & 2.161E-14 \\
+				b_2 & -2.605E-14 \\
+				b_3 & -4.744E-13 \\
+				b_4 & -1.813E-13 \\
+				b_5 & -4.858E-12 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 2.92E-15 \\
+				a_1 & 2.758E-13 \\
+				a_2 & 1.761E-11 \\
+				a_3 & 4.228E-10 \\
+				a_4 & 1.422E-8 \\
+				a_5 & 1.561E-7 \\
+				a_6 & 1.501E-6 \\
+				a_7 & 8.426E-6 \\
+				a_8 & 5.981E-5 \\
+				a_9 & 0.0002016 \\
+				a_{10} & 0.001226 \\
+				a_{11} & 0.002649 \\
+				a_{12} & 0.01456 \\
+				a_{13} & 0.02044 \\
+				a_{14} & 0.104 \\
+				a_{15} & 0.09228 \\
+				a_{16} & 0.4417 \\
+				a_{17} & 0.2257 \\
+				a_{18} & 1.025 \\
+				a_{19} & 0.2305 \\
+				a_{20} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}
+\end{frame}
+
+\begin{frame}{Manual Steering System Transfer Function}
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque A}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & 6.516E4 \\
+				b_1 & -2.944E5 \\
+				b_2 & 2.328E5 \\
+				b_3 & -2.487E5 \\
+				b_4 & 8.25E4 \\
+				b_5 & -3.038E4 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 1.224E5 \\
+				a_1 & 4.227E5 \\
+				a_2 & 2.202E6 \\
+				a_3 & 3.54E6 \\
+				a_4 & 7.98E6 \\
+				a_5 & 7.62E5 \\
+				a_6 & 1.071E7 \\
+				a_7 & 6.745E6 \\
+				a_8 & 6.85E6 \\
+				a_9 & 3.006E6 \\
+				a_{10} & 2.365E6 \\
+				a_{11} & 7.37E5 \\
+				a_{12} & 4.669E5 \\
+				a_{13} & 1.021E5 \\
+				a_{14} & 5.319E4 \\
+				a_{15} & 7752 \\
+				a_{16} & 3353 \\
+				a_{17} & 287.5 \\
+				a_{18} & 102.4 \\
+				a_{19} & 3.653 \\
+				a_{20} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}%
+\hfill%
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque B}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			20th Order Transfer Function Model			
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & 1.209E4 \\
+				b_1 & 1.855E5 \\
+				b_2 & -2.801E5 \\
+				b_3 & 4.72E5 \\
+				b_4 & -3.976E4 \\
+				b_5 & 7.693E4 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 4.687E4 \\
+				a_1 & 7.037E5 \\
+				a_2 & 2.624E6 \\
+				a_3 & 6.133E6 \\
+				a_4 & 1.197E7 \\
+				a_5 & 1.487E7 \\
+				a_6 & 1.887E7 \\
+				a_7 & 1.446E7 \\
+				a_8 & 1.314E7 \\
+				a_9 & 7.01E6 \\
+				a_{10} & 4.79E6 \\
+				a_{11} & 1.886E6 \\
+				a_{12} & 9.836E5 \\
+				a_{13} & 2.937E5 \\
+				a_{14} & 1.149E5 \\
+				a_{15} & 2.617E4 \\
+				a_{16} & 7205 \\
+				a_{17} & 1232 \\
+				a_{18} & 200 \\
+				a_{19} & 23.54 \\
+				a_{20} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}
+\end{frame}
+
 \begin{frame}{Simulation Results}
@@
   \end{block}
+\end{frame}
+
+\begin{frame}{By-Wire Acceleration System Transfer Function}
+	\begin{block}{Fourth-Order ARX Model}
+		\begin{equation}
+			A(z)*y(t) = B(z)*u(t) + e(t)
+		\end{equation}
+		%
+		where, 
+		%
+		\begin{equation}
+			A(z) = 1 - 1.018*z^{-1} - 0.002901*z^{-2} + 0.4631*z^{-3} - 0.2038*z^{-4}
+		\end{equation}
+		\begin{equation}
+			B_1(z) = -0.0207 - 0.01912*z^{-1} - 0.02159*z^{-2} - 0.03307*z^{-3}
+		\end{equation}
+		\begin{equation}
+			B_2(z) = 0.02017 + 0.01833*z^{-1} + 0.09461*z^{-2} + 0.05683*z^{-3}
+		\end{equation}
+	\end{block}
+\end{frame}
+
+\begin{frame}{Manual Acceleration System Transfer Function}
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque A}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & -5.741E6 \\
+				b_1 & -2.644E7 \\
+				b_2 & -2.797E6 \\
+				b_3 & -1.304E7 \\
+				b_4 & -3.203E6 \\
+				b_5 & -1.159E6 \\
+				b_6 & -5.519E5 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 2.307E7 \\
+				a_1 & 8.369E7 \\
+				a_2 & 9.137E8 \\
+				a_3 & 1.992E9 \\
+				a_4 & 3.753E9 \\
+				a_5 & 5.454E9 \\
+				a_6 & 5.548E9 \\
+				a_7 & 5.869E9 \\
+				a_8 & 3.453E9 \\
+				a_9 & 3.161E9 \\
+				a_{10} & 1.54E9 \\
+				a_{11} & 9.654E8 \\
+				a_{12} & 3.556E8 \\
+				a_{13} & 1.789E8 \\
+				a_{14} & 5.082E7 \\
+				a_{15} & 2.071E7 \\
+				a_{16} & 4.569E6 \\
+				a_{17} & 1.498E6 \\
+				a_{18} & 2.553E5 \\
+				a_{19} & 6.532E4 \\
+				a_{20} & 8443 \\
+				a_{21} & 1559 \\
+				a_{22} & 147.3 \\
+				a_{23} & 15.5 \\
+				a_{24} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}%
+\hfill%
+\begin{minipage}[t]{0.48\linewidth}
+	\begin{block}{Torque B}
+		\tiny
+		\begin{tabular}{ cc }   % top level tables, with 2 columns
+			% leftmost table of the top level table
+			\begin{tabular}{ |c|c| } 
+				\hline
+				b_0 & -4.159E6 \\
+				b_1 & 1.851E6 \\
+				b_2 & -4.457E6 \\
+				b_3 & 9.043E5 \\
+				b_4 & -7.45E5 \\
+				b_5 & 1.865E5 \\
+				b_6 & -1.545E4 \\
+				\hline
+			\end{tabular} &  % starting rightmost sub table
+			% table 2
+			\begin{tabular}{ |c|c| } 
+				\hline
+				a_0 & 5.224E6 \\
+				a_1 & 4.205E7 \\
+				a_2 & 1.429E8 \\
+				a_3 & 3.233E8 \\
+				a_4 & 5.444E8 \\
+				a_5 & 7.326E8 \\
+				a_6 & 8.247E8 \\
+				a_7 & 7.402E8 \\
+				a_8 & 6.301E8 \\
+				a_9 & 3.99E8 \\
+				a_{10} & 2.731E8 \\
+				a_{11} & 1.264E8 \\
+				a_{12} & 7.223E7 \\
+				a_{13} & 2.48E7 \\
+				a_{14} & 1.216E7 \\
+				a_{15} & 3.084E6 \\
+				a_{16} & 1.324E6 \\
+				a_{17} & 2.422E5 \\
+				a_{18} & 9.264E4 \\
+				a_{19} & 1.159E4 \\
+				a_{20} & 4003 \\
+				a_{21} & 307.4 \\
+				a_{22} & 96.87 \\
+				a_{23} & 3.451 \\
+				a_{24} & 1 \\
+				\hline
+			\end{tabular} \\
+		\end{tabular}
+	\end{block}
+\end{minipage}
 \end{frame}

### 2021-11-15 proposalPres.tex
Updated proposalPres.tex file
I just made some small changes to some of the sections in the proposal presentation

@@
  \begin{itemize}
-        \item Use of System Identification Toolbox in Matlab to create models from data~\cite{Adnan2010}
+        \item Use of System Identification Toolbox in MATLAB to create models from data~\cite{Adnan2010}
 	 \begin{itemize}
@@
  \begin{itemize}
-        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems
+        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems
 \end{itemize}
@@
 	\begin{block}{}
-		Each subsystem that we are modeling are set up in a similar manner.
+		Each subsystem that we are modeling is set up in a similar manner.
 In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU).
@@
     \begin{itemize}
-      \item Achieving an acceptable accuracy and reliability for each model due to its nonlinearities over small changes
+      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes
     \end{itemize}

### 2021-11-17 proposalPres.tex
Edited a figure so it takes up less empty space
Updated proposalPres.tex

@@
   \begin{block}{System Architecture}
+    \begin{large}
+      The overall system architecture of this project consists of six subsystems
       \begin{itemize}
-        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems
+          \item Steering Model
+          \item Acceleration Model
+          \item Brake Model
+          \item Shift Model
+          \item Speed Model
+          \item Speed Control Model
         \end{itemize} 
+    \end{large}
   \end{block}
@@
 
-\begin{frame}
+\begin{frame}{System Architecture}
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
+\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System \item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
+\end{frame}
+
+\begin{frame}{System Architecture}
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
+\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
+\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
+\end{frame}
+
+\begin{frame}{System Architecture}
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=4in]{figs/inkscape/steeringModelBlockDiagram}
+    \caption{Steering System Block Diagram}
+    \label{fig:steerBlockDiag}
+\end{figure}
+\end{frame}
+
+\begin{frame}{System Inputs and Outputs}
 \begin{minipage}[t]{0.48\linewidth}
@@
 
-\begin{frame}
-\centering
-\includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
-\begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System \item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
-\includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
-\includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
-\end{frame}
-
-\begin{frame}
-\centering
-\includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
-\begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
-\includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
-\includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
-\end{frame}
-
-\begin{frame}
-\begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=4in]{figs/inkscape/steeringModelBlockDiagram}
-    \caption{Steering System Block Diagram}
-    \label{fig:steerBlockDiag}
-\end{figure}
-\end{frame}
-
 %----------------------------------
@@
  \begin{itemize}
-        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
-The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
-Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+        \item Developing mathematical models for a dynamic system
+        \item Uses the measurement of the input and output signals
+        \begin{itemize}
+        		\item Single Input Single Output (SISO)
+        		\item Single Input Multiple Output (SIMO)
+        		\item Multiple Input Single Output (MISO)
+        		\item Multiple Input Multiple Output (MIMO)
+        \end{itemize}
+        \item Achieve an accurate estimation of the system response for any given input
+        \item Mathworks' MATLAB System Identification Toolbox
 \end{itemize}
@@
   \end{block}
-  \begin {block}{Modeling}
-  \begin{itemize}
-  	\item All modeling of vehicle subsystems will be done using MATLAB's System Identification Toolbox feature.
-The subsystems can be grouped into four different categories: Single-Input-Single-Output, Multiple-Input-Multiple-Output, Single-Input-Multiple-Output, and Multiple-Input-Single-Output.
-  	\end{itemize}
-  	\end{block}
 \end{frame}
@@
 %----------------------------------
-\subsection{Design}
+\subsection{Experimental Setup}
 
-\begin{frame}{Design}
-	\begin{block}{}
-		Each subsystem that we are modeling is set up in a similar manner.
-In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU).
-In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode.
-In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem.
-Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
+\begin{frame}{Experimental Setup}
+	\begin{block}{Control Method}
+		\begin{itemize}
+			\item Manual Mode
+			\begin{itemize}
+				\item Vehicle is not autonomous
+				\item Torque voltages are sent by the ECU
+			\end{itemize}
+			\item By-Wire Mode
+			\begin{itemize}
+				\item Vehicle is autonomous
+				\item Torque voltages are sent by the PACMod
+				\item Torque voltages sent from the ECU are discarded by open-circuiting the motors
+			\end{itemize}
+		\end{itemize}
+		\begin{figure}
+			\centering
+    			\captionsetup{justification=centering, margin=3cm}
+    			\includegraphics[width=1in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    			\caption{Autonomous Vehicle Data Collection Setup}
+    			\label{fig:vehicleSetup}
+		\end{figure}
 	\end{block}
@@
 			\begin{equation}
-				\frac{Y(s)}{U_A(s)} = \frac{b_{n}*s^{n} + b_{n-1}*s^{n-1} + ... + b_1*s + b_0}{a_{m}*s^{m} + a_{m-1}*s^{m-1} + ... + a_1*s + a_0}
+				\frac{Y(s)}{U_A(s)} = \frac{b_{n}s^{n} + b_{n-1}s^{n-1} + ... + b_1s + b_0}{a_{m}s^{m} + a_{m-1}s^{m-1} + ... + a_1s + a_0}
 			\end{equation}
@@
 			\begin{equation}
-				A(z)*y(t) = B(z)*u(t) + e(t)
+				A(z)y(t) = B(z)u(t) + e(t)
 			\end{equation}
@@
 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			20th Order Transfer Function Model			
 			% leftmost table of the top level table
@@
 		\begin{equation}
-			A(z)*y(t) = B(z)*u(t) + e(t)
+			A(z)y(t) = B(z)u(t) + e(t)
 		\end{equation}
@@
 		\begin{equation}
-			A(z) = 1 - 1.018*z^{-1} - 0.002901*z^{-2} + 0.4631*z^{-3} - 0.2038*z^{-4}
+			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
 		\end{equation}
 		\begin{equation}
-			B_1(z) = -0.0207 - 0.01912*z^{-1} - 0.02159*z^{-2} - 0.03307*z^{-3}
+			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
 		\end{equation}
 		\begin{equation}
-			B_2(z) = 0.02017 + 0.01833*z^{-1} + 0.09461*z^{-2} + 0.05683*z^{-3}
+			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
 		\end{equation}

### 2021-11-17 proposal.tex
Updated proposal.tex

@@
 \usepackage{siunitx}
+%\sisetup{unitsep=\cdot}
 
@@
 
-\vspace*{6.0cm}
+\vspace*{3.0cm}
 \copyright~H.~Grady~and~N.~Nauman, Peoria, IL, USA, 2021\\
@@
 Autonomous vehicles are being developed by many companies for commercial and/or personal use.
-These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
+These autonomous vehicles, like the fleet AutonomouStuff has as shown in \autoref{fig:fleet}, would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
 Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
@@
 These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
+Models for each subsystem must created for both manual drive mode and by-wire, or autonomous, mode.
+\autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle.
+Each subsystem, like the steering system in this example, sends torque voltages to a motor that will control the subsystem.
+In \autoref{fig:steerSystem}, the motor would turn the pinion arms which would change the steering angle of the vehicle.
+This principle is applied to all other subsystems.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesAStuff}
+	\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
+	\label{fig:fleet}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesSteering}
+	\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
+	\label{fig:steerSystem}
+\end{figure}
+\begin{tiny}[h]
+	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+\end{tiny}
 
@@
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=3in]{figs/inkscape/nonlinearBehavior}
+    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
     \caption{Steering Non-linear Behavior}
@@
  All modeling of vehicle subsystems will be done using Matlab's System Identification Toolbox feature.
-The subsystems can be grouped into four different categories: Single-Input-Single-Output, Multiple-Input-Multiple-Output, Single-Input-Multiple-Output, and Multiple-Input-Single-Output.
+The subsystems can be grouped into four different categories: Single-Input Single-Output (SISO), Multiple-Input Multiple-Output (MIMO), Single-Input Multiple-Output (SIMO), and Multiple-Input Single-Output (MISO).
 
-\subsection{Design} \label{sec:design}
+ \subsection{Parts List}
+	The following is the software required for this project: 
+	\begin{itemize}
+    		\item MATLAB's System Identification Toolbox 
+    		\item Vector CANAlyzer 
+ 	\end{itemize}
+
+	The following is the hardware required for this project:  
+	\begin{itemize}
+    		\item Laptop
+    		\item PAC Mod 
+    		\item CAN Case 
+    		\item CAN Bus 
+ 	\end{itemize}
+
+\subsection{Experimental Setup} \label{sec:setup}
 Each subsystem that we are modeling are set up in a similar manner.
@@
 Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
+In \autoref{fig:vehicleSetup}, the experimental setup for data collection is shown.
+The laptop is used to collect the data from the desired vehicle subsystem by the use of Vector's CANAlyzer software.
+The CAN Case collects data from the PAC Mod and ECU and sends the data using a CAN bus to the laptop which is then parsed and displayed through the use of CANAlyzer.
+The ECU and PAC Mod are not shown in \autoref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
+
+\begin{figure}
+	\centering
+    	\captionsetup{justification=centering, margin=3cm}
+    	\includegraphics[width=5in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    	\caption{Autonomous Vehicle Data Collection Setup}
+    	\label{fig:vehicleSetup}
+\end{figure}
 
@@
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
+    \includegraphics[width=5in]{figs/img/byWireSteeringTransferFunctionModel}
     \caption{Output of Estimated By-Wire System Model}
@@
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
+    \includegraphics[width=5in]{figs/img/manualSteeringTransferFunctionModel}
     \caption{Output of Estimated Manual System Model}
@@
 \end{figure}
-
-\section{Parts List}
-	\subsection{Software}
-	\begin{itemize}
-    \item MATLAB's System Identification Toolbox 
-    \item Vector CANAlyzer 
- \end{itemize}
-
-	\subsection{Hardware} 
-	\begin{itemize}
-    \item Laptop
-    \item PAC Mod 
-    \item CAN Case 
-    \item CAN Bus 
- \end{itemize}
 

### 2021-11-17 proposalPres.tex
Update proposalPres.tex
I updated the date and added an example to the presentation. I will push my other changes later.

@@
 
-\date[October~7,~2021]{Thursday, October~7,~2021}
+\date[November~18,~2021]{Thursday, November~18,~2021}
 
@@
   \end{block}
+
+   \begin {block}{MATLAB Example: Dealing with Multi-Variable Systems: Identification and Analysis}
+  \begin{itemize}
+  	\item  Learned how to create an iddata object from a given data set 
+  	\item Created a state space model and compared it to the validation data 
+  	\item Tried creating submodels for some of the channels in order to try and get a better fit 
+  	\item Then created a MISO model and learned how to merge the two SISO models that were created earlier 
+  	\end{itemize}
+  	\end{block}
+
 \end{frame}

### 2021-11-18 proposalPres.tex
Update proposalPres.tex
I added a timeline block and a frame break to the presentation, along with changing the font in the conclusion slide.
~
Added a parameter table in By-Wire Steering System

@@
 \begin{frame}{By-Wire Steering System Transfer Function}
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque A}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & 3.44E-16 \\
-				b_1 & -2.203E-15 \\
-				b_2 & 1.24E-13 \\
-				b_3 & 5.975E-13 \\
-				b_4 & 3.001E-12 \\
-				b_5 & 5.23E-12 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 1.949E-16 \\
-				a_1 & 1.455E-14 \\
-				a_2 & 8.797E-13 \\
-				a_3 & 2.304E-11 \\
-				a_4 & 9.041E-10 \\
-				a_5 & 9.01E-9 \\
-				a_6 & 2.714E-7 \\
-				a_7 & 9.241E-7 \\
-				a_8 & 1.946E-5 \\
-				a_9 & 3.889E-5 \\
-				a_{10} & 0.0005721 \\
-				a_{11} & 0.0008035 \\
-				a_{12} & 0.008695 \\
-				a_{13} & 0.008922 \\
-				a_{14} & 0.07499 \\
-				a_{15} & 0.05422 \\
-				a_{16} & 0.3631 \\
-				a_{17} & 0.1693 \\
-				a_{18} & 0.9394 \\
-				a_{19} & 0.2118 \\
-				a_{20} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}%
-\hfill%
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque B}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & -6.645E-15 \\
-				b_1 & 2.161E-14 \\
-				b_2 & -2.605E-14 \\
-				b_3 & -4.744E-13 \\
-				b_4 & -1.813E-13 \\
-				b_5 & -4.858E-12 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 2.92E-15 \\
-				a_1 & 2.758E-13 \\
-				a_2 & 1.761E-11 \\
-				a_3 & 4.228E-10 \\
-				a_4 & 1.422E-8 \\
-				a_5 & 1.561E-7 \\
-				a_6 & 1.501E-6 \\
-				a_7 & 8.426E-6 \\
-				a_8 & 5.981E-5 \\
-				a_9 & 0.0002016 \\
-				a_{10} & 0.001226 \\
-				a_{11} & 0.002649 \\
-				a_{12} & 0.01456 \\
-				a_{13} & 0.02044 \\
-				a_{14} & 0.104 \\
-				a_{15} & 0.09228 \\
-				a_{16} & 0.4417 \\
-				a_{17} & 0.2257 \\
-				a_{18} & 1.025 \\
-				a_{19} & 0.2305 \\
-				a_{20} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}
+
+  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$&$a_{19}$&$a_{20}$\\
+      \midrule
+      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
+      \bottomrule
+    \end{tabular}}
+
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque A}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & 3.44E-16 \\
+% 				b_1 & -2.203E-15 \\
+% 				b_2 & 1.24E-13 \\
+% 				b_3 & 5.975E-13 \\
+% 				b_4 & 3.001E-12 \\
+% 				b_5 & 5.23E-12 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 1.949E-16 \\
+% 				a_1 & 1.455E-14 \\
+% 				a_2 & 8.797E-13 \\
+% 				a_3 & 2.304E-11 \\
+% 				a_4 & 9.041E-10 \\
+% 				a_5 & 9.01E-9 \\
+% 				a_6 & 2.714E-7 \\
+% 				a_7 & 9.241E-7 \\
+% 				a_8 & 1.946E-5 \\
+% 				a_9 & 3.889E-5 \\
+% 				a_{10} & 0.0005721 \\
+% 				a_{11} & 0.0008035 \\
+% 				a_{12} & 0.008695 \\
+% 				a_{13} & 0.008922 \\
+% 				a_{14} & 0.07499 \\
+% 				a_{15} & 0.05422 \\
+% 				a_{16} & 0.3631 \\
+% 				a_{17} & 0.1693 \\
+% 				a_{18} & 0.9394 \\
+% 				a_{19} & 0.2118 \\
+% 				a_{20} & 1 \\
+% 				\hline
+% 			\end{tabular} 
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}%
+% \hfill%
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque B}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & -6.645E-15 \\
+% 				b_1 & 2.161E-14 \\
+% 				b_2 & -2.605E-14 \\
+% 				b_3 & -4.744E-13 \\
+% 				b_4 & -1.813E-13 \\
+% 				b_5 & -4.858E-12 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 2.92E-15 \\
+% 				a_1 & 2.758E-13 \\
+% 				a_2 & 1.761E-11 \\
+% 				a_3 & 4.228E-10 \\
+% 				a_4 & 1.422E-8 \\
+% 				a_5 & 1.561E-7 \\
+% 				a_6 & 1.501E-6 \\
+% 				a_7 & 8.426E-6 \\
+% 				a_8 & 5.981E-5 \\
+% 				a_9 & 0.0002016 \\
+% 				a_{10} & 0.001226 \\
+% 				a_{11} & 0.002649 \\
+% 				a_{12} & 0.01456 \\
+% 				a_{13} & 0.02044 \\
+% 				a_{14} & 0.104 \\
+% 				a_{15} & 0.09228 \\
+% 				a_{16} & 0.4417 \\
+% 				a_{17} & 0.2257 \\
+% 				a_{18} & 1.025 \\
+% 				a_{19} & 0.2305 \\
+% 				a_{20} & 1 \\
+% 				\hline
+% 			\end{tabular} 
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}
 \end{frame}
@@
 \begin{frame}{Manual Steering System Transfer Function}
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque A}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & 6.516E4 \\
-				b_1 & -2.944E5 \\
-				b_2 & 2.328E5 \\
-				b_3 & -2.487E5 \\
-				b_4 & 8.25E4 \\
-				b_5 & -3.038E4 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 1.224E5 \\
-				a_1 & 4.227E5 \\
-				a_2 & 2.202E6 \\
-				a_3 & 3.54E6 \\
-				a_4 & 7.98E6 \\
-				a_5 & 7.62E5 \\
-				a_6 & 1.071E7 \\
-				a_7 & 6.745E6 \\
-				a_8 & 6.85E6 \\
-				a_9 & 3.006E6 \\
-				a_{10} & 2.365E6 \\
-				a_{11} & 7.37E5 \\
-				a_{12} & 4.669E5 \\
-				a_{13} & 1.021E5 \\
-				a_{14} & 5.319E4 \\
-				a_{15} & 7752 \\
-				a_{16} & 3353 \\
-				a_{17} & 287.5 \\
-				a_{18} & 102.4 \\
-				a_{19} & 3.653 \\
-				a_{20} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}%
-\hfill%
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque B}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & 1.209E4 \\
-				b_1 & 1.855E5 \\
-				b_2 & -2.801E5 \\
-				b_3 & 4.72E5 \\
-				b_4 & -3.976E4 \\
-				b_5 & 7.693E4 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 4.687E4 \\
-				a_1 & 7.037E5 \\
-				a_2 & 2.624E6 \\
-				a_3 & 6.133E6 \\
-				a_4 & 1.197E7 \\
-				a_5 & 1.487E7 \\
-				a_6 & 1.887E7 \\
-				a_7 & 1.446E7 \\
-				a_8 & 1.314E7 \\
-				a_9 & 7.01E6 \\
-				a_{10} & 4.79E6 \\
-				a_{11} & 1.886E6 \\
-				a_{12} & 9.836E5 \\
-				a_{13} & 2.937E5 \\
-				a_{14} & 1.149E5 \\
-				a_{15} & 2.617E4 \\
-				a_{16} & 7205 \\
-				a_{17} & 1232 \\
-				a_{18} & 200 \\
-				a_{19} & 23.54 \\
-				a_{20} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque A}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & 6.516E4 \\
+% 				b_1 & -2.944E5 \\
+% 				b_2 & 2.328E5 \\
+% 				b_3 & -2.487E5 \\
+% 				b_4 & 8.25E4 \\
+% 				b_5 & -3.038E4 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 1.224E5 \\
+% 				a_1 & 4.227E5 \\
+% 				a_2 & 2.202E6 \\
+% 				a_3 & 3.54E6 \\
+% 				a_4 & 7.98E6 \\
+% 				a_5 & 7.62E5 \\
+% 				a_6 & 1.071E7 \\
+% 				a_7 & 6.745E6 \\
+% 				a_8 & 6.85E6 \\
+% 				a_9 & 3.006E6 \\
+% 				a_{10} & 2.365E6 \\
+% 				a_{11} & 7.37E5 \\
+% 				a_{12} & 4.669E5 \\
+% 				a_{13} & 1.021E5 \\
+% 				a_{14} & 5.319E4 \\
+% 				a_{15} & 7752 \\
+% 				a_{16} & 3353 \\
+% 				a_{17} & 287.5 \\
+% 				a_{18} & 102.4 \\
+% 				a_{19} & 3.653 \\
+% 				a_{20} & 1 \\
+% 				\hline
+% 			\end{tabular} \\
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}%
+% \hfill%
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque B}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & 1.209E4 \\
+% 				b_1 & 1.855E5 \\
+% 				b_2 & -2.801E5 \\
+% 				b_3 & 4.72E5 \\
+% 				b_4 & -3.976E4 \\
+% 				b_5 & 7.693E4 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 4.687E4 \\
+% 				a_1 & 7.037E5 \\
+% 				a_2 & 2.624E6 \\
+% 				a_3 & 6.133E6 \\
+% 				a_4 & 1.197E7 \\
+% 				a_5 & 1.487E7 \\
+% 				a_6 & 1.887E7 \\
+% 				a_7 & 1.446E7 \\
+% 				a_8 & 1.314E7 \\
+% 				a_9 & 7.01E6 \\
+% 				a_{10} & 4.79E6 \\
+% 				a_{11} & 1.886E6 \\
+% 				a_{12} & 9.836E5 \\
+% 				a_{13} & 2.937E5 \\
+% 				a_{14} & 1.149E5 \\
+% 				a_{15} & 2.617E4 \\
+% 				a_{16} & 7205 \\
+% 				a_{17} & 1232 \\
+% 				a_{18} & 200 \\
+% 				a_{19} & 23.54 \\
+% 				a_{20} & 1 \\
+% 				\hline
+% 			\end{tabular} \\
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}
 \end{frame}
@@
 \begin{frame}{Manual Acceleration System Transfer Function}
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque A}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & -5.741E6 \\
-				b_1 & -2.644E7 \\
-				b_2 & -2.797E6 \\
-				b_3 & -1.304E7 \\
-				b_4 & -3.203E6 \\
-				b_5 & -1.159E6 \\
-				b_6 & -5.519E5 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 2.307E7 \\
-				a_1 & 8.369E7 \\
-				a_2 & 9.137E8 \\
-				a_3 & 1.992E9 \\
-				a_4 & 3.753E9 \\
-				a_5 & 5.454E9 \\
-				a_6 & 5.548E9 \\
-				a_7 & 5.869E9 \\
-				a_8 & 3.453E9 \\
-				a_9 & 3.161E9 \\
-				a_{10} & 1.54E9 \\
-				a_{11} & 9.654E8 \\
-				a_{12} & 3.556E8 \\
-				a_{13} & 1.789E8 \\
-				a_{14} & 5.082E7 \\
-				a_{15} & 2.071E7 \\
-				a_{16} & 4.569E6 \\
-				a_{17} & 1.498E6 \\
-				a_{18} & 2.553E5 \\
-				a_{19} & 6.532E4 \\
-				a_{20} & 8443 \\
-				a_{21} & 1559 \\
-				a_{22} & 147.3 \\
-				a_{23} & 15.5 \\
-				a_{24} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}%
-\hfill%
-\begin{minipage}[t]{0.48\linewidth}
-	\begin{block}{Torque B}
-		\tiny
-		\begin{tabular}{ cc }   % top level tables, with 2 columns
-			% leftmost table of the top level table
-			\begin{tabular}{ |c|c| } 
-				\hline
-				b_0 & -4.159E6 \\
-				b_1 & 1.851E6 \\
-				b_2 & -4.457E6 \\
-				b_3 & 9.043E5 \\
-				b_4 & -7.45E5 \\
-				b_5 & 1.865E5 \\
-				b_6 & -1.545E4 \\
-				\hline
-			\end{tabular} &  % starting rightmost sub table
-			% table 2
-			\begin{tabular}{ |c|c| } 
-				\hline
-				a_0 & 5.224E6 \\
-				a_1 & 4.205E7 \\
-				a_2 & 1.429E8 \\
-				a_3 & 3.233E8 \\
-				a_4 & 5.444E8 \\
-				a_5 & 7.326E8 \\
-				a_6 & 8.247E8 \\
-				a_7 & 7.402E8 \\
-				a_8 & 6.301E8 \\
-				a_9 & 3.99E8 \\
-				a_{10} & 2.731E8 \\
-				a_{11} & 1.264E8 \\
-				a_{12} & 7.223E7 \\
-				a_{13} & 2.48E7 \\
-				a_{14} & 1.216E7 \\
-				a_{15} & 3.084E6 \\
-				a_{16} & 1.324E6 \\
-				a_{17} & 2.422E5 \\
-				a_{18} & 9.264E4 \\
-				a_{19} & 1.159E4 \\
-				a_{20} & 4003 \\
-				a_{21} & 307.4 \\
-				a_{22} & 96.87 \\
-				a_{23} & 3.451 \\
-				a_{24} & 1 \\
-				\hline
-			\end{tabular} \\
-		\end{tabular}
-	\end{block}
-\end{minipage}
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque A}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & -5.741E6 \\
+% 				b_1 & -2.644E7 \\
+% 				b_2 & -2.797E6 \\
+% 				b_3 & -1.304E7 \\
+% 				b_4 & -3.203E6 \\
+% 				b_5 & -1.159E6 \\
+% 				b_6 & -5.519E5 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 2.307E7 \\
+% 				a_1 & 8.369E7 \\
+% 				a_2 & 9.137E8 \\
+% 				a_3 & 1.992E9 \\
+% 				a_4 & 3.753E9 \\
+% 				a_5 & 5.454E9 \\
+% 				a_6 & 5.548E9 \\
+% 				a_7 & 5.869E9 \\
+% 				a_8 & 3.453E9 \\
+% 				a_9 & 3.161E9 \\
+% 				a_{10} & 1.54E9 \\
+% 				a_{11} & 9.654E8 \\
+% 				a_{12} & 3.556E8 \\
+% 				a_{13} & 1.789E8 \\
+% 				a_{14} & 5.082E7 \\
+% 				a_{15} & 2.071E7 \\
+% 				a_{16} & 4.569E6 \\
+% 				a_{17} & 1.498E6 \\
+% 				a_{18} & 2.553E5 \\
+% 				a_{19} & 6.532E4 \\
+% 				a_{20} & 8443 \\
+% 				a_{21} & 1559 \\
+% 				a_{22} & 147.3 \\
+% 				a_{23} & 15.5 \\
+% 				a_{24} & 1 \\
+% 				\hline
+% 			\end{tabular} \\
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}%
+% \hfill%
+% \begin{minipage}[t]{0.48\linewidth}
+% 	\begin{block}{Torque B}
+% 		\tiny
+% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
+% 			% leftmost table of the top level table
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				b_0 & -4.159E6 \\
+% 				b_1 & 1.851E6 \\
+% 				b_2 & -4.457E6 \\
+% 				b_3 & 9.043E5 \\
+% 				b_4 & -7.45E5 \\
+% 				b_5 & 1.865E5 \\
+% 				b_6 & -1.545E4 \\
+% 				\hline
+% 			\end{tabular} &  % starting rightmost sub table
+% 			% table 2
+% 			\begin{tabular}{ |c|c| } 
+% 				\hline
+% 				a_0 & 5.224E6 \\
+% 				a_1 & 4.205E7 \\
+% 				a_2 & 1.429E8 \\
+% 				a_3 & 3.233E8 \\
+% 				a_4 & 5.444E8 \\
+% 				a_5 & 7.326E8 \\
+% 				a_6 & 8.247E8 \\
+% 				a_7 & 7.402E8 \\
+% 				a_8 & 6.301E8 \\
+% 				a_9 & 3.99E8 \\
+% 				a_{10} & 2.731E8 \\
+% 				a_{11} & 1.264E8 \\
+% 				a_{12} & 7.223E7 \\
+% 				a_{13} & 2.48E7 \\
+% 				a_{14} & 1.216E7 \\
+% 				a_{15} & 3.084E6 \\
+% 				a_{16} & 1.324E6 \\
+% 				a_{17} & 2.422E5 \\
+% 				a_{18} & 9.264E4 \\
+% 				a_{19} & 1.159E4 \\
+% 				a_{20} & 4003 \\
+% 				a_{21} & 307.4 \\
+% 				a_{22} & 96.87 \\
+% 				a_{23} & 3.451 \\
+% 				a_{24} & 1 \\
+% 				\hline
+% 			\end{tabular} \\
+% 		\end{tabular}
+% 	\end{block}
+% \end{minipage}
 \end{frame}
@@
   \end{block}
+
+  \begin{block}{Timeline}
+  \begin{itemize}
+  \item Fall Semester
+  \begin{itemize}
+	\begin{tiny}
+	\item System Identification Documentation 
+	\item Collect Steering, Acceleration, and Brake Data 
+	\item System Identification Tutorials
+	\item System Functional Requirements Document and Presentation
+	\item Proposal Document and Presentation 
+	\item Model Steering, Acceleration, and Brake Subsystems 
+	\end{tiny}
+	\end{itemize}
+	\item Spring Semester
+	\begin{itemize}
+	\begin{tiny}
+	\item Collect Shift, Speed Control, and Speed Data  
+	\item Model Shift, Speed Control, and Speed Subsystems  
+	\item Test Subsystems
+	\item Test Subsystems with HIL
+	\item Final Report and Presentation 
+	\item IAB Presentation 
+	\item Project Demonstration  
+	\end{tiny}
+	\end{itemize}
+	\end{itemize}
+  \end{block}
+
 \end{frame}
@@
   \begin{block}{Project goals}
-    \begin{LARGE}
+    %\begin{LARGE}
       \begin{itemize}
@@
       \end{itemize}
-    \end{LARGE}
+    %\end{LARGE}
   \end{block}
@@
 
-\begin{frame}{References}
+\begin{frame}[allowframebreaks]{References}
 

### 2021-11-18 proposalPres.tex
Updated proposalPres.tex
Fixed errors in sim result tables

Added slide about ARX model representation in MATLAB

@@
 \begin{frame}{Model Equations}
-	\begin{block}{}
+	\begin{block}{Model Equations}
 		\begin{itemize}
@@
 		\end{itemize}
+	\end{block}
+\end{frame}
+
+\begin{frame}{Model Equations}
+	\tiny	
+	\begin{block}{ARX Model MATLAB Representation}
+		The polynomial equation for an ARX Model is:
+		\begin{equation}
+			y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)
+		\end{equation}
+		where na, nb, and nk are the system’s number of poles, number of zeros, and the system dead time, respectively
+		MATLAB represents the ARX Model with the following equation:
+		\begin{equation}
+			A(z)y(t) = B(z)u(t - n_k) + e(t)
+		\end{equation}
+		where z is a delay operator and 
+		\begin{equation}
+			A(z) = 1 + a_1z^{-1} + ... + a_{na}z^{-n_a}
+		\end{equation}
+		\begin{equation}
+			B(z) = b_1 + b_2z^{-1} + ... + b_{nb}z^{-n_b}
+		\end{equation}
+		For MISO systems, MATLAB uses the following equation to represent the ARX Model:
+		\begin{equation}
+			A(z)y(t) = B_1(z)u_1(t - nk_{1}) + B_2(z)u_2(t - nk_{2}) + ... + B_{nu}(z)u_{nu}(t - nk_{nu})
+		\end{equation}
+		where nu is the number of system inputs
 	\end{block}
@@
 
+\begin{block}{Torque Voltage A}
 	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
       \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$&$a_{19}$&$a_{20}$\\
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
       \midrule
@@
 
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque A}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & 3.44E-16 \\
-% 				b_1 & -2.203E-15 \\
-% 				b_2 & 1.24E-13 \\
-% 				b_3 & 5.975E-13 \\
-% 				b_4 & 3.001E-12 \\
-% 				b_5 & 5.23E-12 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 1.949E-16 \\
-% 				a_1 & 1.455E-14 \\
-% 				a_2 & 8.797E-13 \\
-% 				a_3 & 2.304E-11 \\
-% 				a_4 & 9.041E-10 \\
-% 				a_5 & 9.01E-9 \\
-% 				a_6 & 2.714E-7 \\
-% 				a_7 & 9.241E-7 \\
-% 				a_8 & 1.946E-5 \\
-% 				a_9 & 3.889E-5 \\
-% 				a_{10} & 0.0005721 \\
-% 				a_{11} & 0.0008035 \\
-% 				a_{12} & 0.008695 \\
-% 				a_{13} & 0.008922 \\
-% 				a_{14} & 0.07499 \\
-% 				a_{15} & 0.05422 \\
-% 				a_{16} & 0.3631 \\
-% 				a_{17} & 0.1693 \\
-% 				a_{18} & 0.9394 \\
-% 				a_{19} & 0.2118 \\
-% 				a_{20} & 1 \\
-% 				\hline
-% 			\end{tabular} 
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}%
-% \hfill%
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque B}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & -6.645E-15 \\
-% 				b_1 & 2.161E-14 \\
-% 				b_2 & -2.605E-14 \\
-% 				b_3 & -4.744E-13 \\
-% 				b_4 & -1.813E-13 \\
-% 				b_5 & -4.858E-12 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 2.92E-15 \\
-% 				a_1 & 2.758E-13 \\
-% 				a_2 & 1.761E-11 \\
-% 				a_3 & 4.228E-10 \\
-% 				a_4 & 1.422E-8 \\
-% 				a_5 & 1.561E-7 \\
-% 				a_6 & 1.501E-6 \\
-% 				a_7 & 8.426E-6 \\
-% 				a_8 & 5.981E-5 \\
-% 				a_9 & 0.0002016 \\
-% 				a_{10} & 0.001226 \\
-% 				a_{11} & 0.002649 \\
-% 				a_{12} & 0.01456 \\
-% 				a_{13} & 0.02044 \\
-% 				a_{14} & 0.104 \\
-% 				a_{15} & 0.09228 \\
-% 				a_{16} & 0.4417 \\
-% 				a_{17} & 0.2257 \\
-% 				a_{18} & 1.025 \\
-% 				a_{19} & 0.2305 \\
-% 				a_{20} & 1 \\
-% 				\hline
-% 			\end{tabular} 
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      3.44E-16 & -2.203E-15 & 1.24E-13 & 5.975E-13 & 3.001E-12 & 5.23E-12\\
+      \bottomrule
+    \end{tabular}}
+\end{block}
+\begin{block}{Torque Voltage B}
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      2.92E-15 & 2.758E-13 & 1.761E-11 & 4.228E-10 & 1.422E-8 & 1.561E-7 & 1.501E-6 & 8.426E-6 & 5.981E-5 & 0.0002016 & 0.001226 & 0.002649 & 0.01456 & 0.02044 & 0.104 & 0.09228 & 0.4417 & 0.2257 & 1.025 & 0.2305 & 1\\
+      \bottomrule
+    \end{tabular}}
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      -6.645E-15 & 2.161E-14 & -2.605E-14 & -4.744E-13 & -1.813E-13 & -4.858E-12\\
+      \bottomrule
+    \end{tabular}}
+\end{block}  
 \end{frame}
@@
 \begin{frame}{Manual Steering System Transfer Function}
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque A}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & 6.516E4 \\
-% 				b_1 & -2.944E5 \\
-% 				b_2 & 2.328E5 \\
-% 				b_3 & -2.487E5 \\
-% 				b_4 & 8.25E4 \\
-% 				b_5 & -3.038E4 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 1.224E5 \\
-% 				a_1 & 4.227E5 \\
-% 				a_2 & 2.202E6 \\
-% 				a_3 & 3.54E6 \\
-% 				a_4 & 7.98E6 \\
-% 				a_5 & 7.62E5 \\
-% 				a_6 & 1.071E7 \\
-% 				a_7 & 6.745E6 \\
-% 				a_8 & 6.85E6 \\
-% 				a_9 & 3.006E6 \\
-% 				a_{10} & 2.365E6 \\
-% 				a_{11} & 7.37E5 \\
-% 				a_{12} & 4.669E5 \\
-% 				a_{13} & 1.021E5 \\
-% 				a_{14} & 5.319E4 \\
-% 				a_{15} & 7752 \\
-% 				a_{16} & 3353 \\
-% 				a_{17} & 287.5 \\
-% 				a_{18} & 102.4 \\
-% 				a_{19} & 3.653 \\
-% 				a_{20} & 1 \\
-% 				\hline
-% 			\end{tabular} \\
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}%
-% \hfill%
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque B}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & 1.209E4 \\
-% 				b_1 & 1.855E5 \\
-% 				b_2 & -2.801E5 \\
-% 				b_3 & 4.72E5 \\
-% 				b_4 & -3.976E4 \\
-% 				b_5 & 7.693E4 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 4.687E4 \\
-% 				a_1 & 7.037E5 \\
-% 				a_2 & 2.624E6 \\
-% 				a_3 & 6.133E6 \\
-% 				a_4 & 1.197E7 \\
-% 				a_5 & 1.487E7 \\
-% 				a_6 & 1.887E7 \\
-% 				a_7 & 1.446E7 \\
-% 				a_8 & 1.314E7 \\
-% 				a_9 & 7.01E6 \\
-% 				a_{10} & 4.79E6 \\
-% 				a_{11} & 1.886E6 \\
-% 				a_{12} & 9.836E5 \\
-% 				a_{13} & 2.937E5 \\
-% 				a_{14} & 1.149E5 \\
-% 				a_{15} & 2.617E4 \\
-% 				a_{16} & 7205 \\
-% 				a_{17} & 1232 \\
-% 				a_{18} & 200 \\
-% 				a_{19} & 23.54 \\
-% 				a_{20} & 1 \\
-% 				\hline
-% 			\end{tabular} \\
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}
+
+\begin{block}{Torque Voltage A}
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
+      \bottomrule
+    \end{tabular}}
+
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
+      \bottomrule
+    \end{tabular}}
+\end{block}
+\begin{block}{Torque Voltage B}
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
+      \bottomrule
+    \end{tabular}}
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
+      \bottomrule
+    \end{tabular}}
+\end{block}
 \end{frame}
@@
 		\begin{equation}
-			A(z)y(t) = B(z)u(t) + e(t)
+			A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
 		\end{equation}
 		%
-		where, 
+		where na = 4, nb = 4, nk = 0, and, 
 		%
@@
 \begin{frame}{Manual Acceleration System Transfer Function}
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque A}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & -5.741E6 \\
-% 				b_1 & -2.644E7 \\
-% 				b_2 & -2.797E6 \\
-% 				b_3 & -1.304E7 \\
-% 				b_4 & -3.203E6 \\
-% 				b_5 & -1.159E6 \\
-% 				b_6 & -5.519E5 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 2.307E7 \\
-% 				a_1 & 8.369E7 \\
-% 				a_2 & 9.137E8 \\
-% 				a_3 & 1.992E9 \\
-% 				a_4 & 3.753E9 \\
-% 				a_5 & 5.454E9 \\
-% 				a_6 & 5.548E9 \\
-% 				a_7 & 5.869E9 \\
-% 				a_8 & 3.453E9 \\
-% 				a_9 & 3.161E9 \\
-% 				a_{10} & 1.54E9 \\
-% 				a_{11} & 9.654E8 \\
-% 				a_{12} & 3.556E8 \\
-% 				a_{13} & 1.789E8 \\
-% 				a_{14} & 5.082E7 \\
-% 				a_{15} & 2.071E7 \\
-% 				a_{16} & 4.569E6 \\
-% 				a_{17} & 1.498E6 \\
-% 				a_{18} & 2.553E5 \\
-% 				a_{19} & 6.532E4 \\
-% 				a_{20} & 8443 \\
-% 				a_{21} & 1559 \\
-% 				a_{22} & 147.3 \\
-% 				a_{23} & 15.5 \\
-% 				a_{24} & 1 \\
-% 				\hline
-% 			\end{tabular} \\
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}%
-% \hfill%
-% \begin{minipage}[t]{0.48\linewidth}
-% 	\begin{block}{Torque B}
-% 		\tiny
-% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
-% 			% leftmost table of the top level table
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				b_0 & -4.159E6 \\
-% 				b_1 & 1.851E6 \\
-% 				b_2 & -4.457E6 \\
-% 				b_3 & 9.043E5 \\
-% 				b_4 & -7.45E5 \\
-% 				b_5 & 1.865E5 \\
-% 				b_6 & -1.545E4 \\
-% 				\hline
-% 			\end{tabular} &  % starting rightmost sub table
-% 			% table 2
-% 			\begin{tabular}{ |c|c| } 
-% 				\hline
-% 				a_0 & 5.224E6 \\
-% 				a_1 & 4.205E7 \\
-% 				a_2 & 1.429E8 \\
-% 				a_3 & 3.233E8 \\
-% 				a_4 & 5.444E8 \\
-% 				a_5 & 7.326E8 \\
-% 				a_6 & 8.247E8 \\
-% 				a_7 & 7.402E8 \\
-% 				a_8 & 6.301E8 \\
-% 				a_9 & 3.99E8 \\
-% 				a_{10} & 2.731E8 \\
-% 				a_{11} & 1.264E8 \\
-% 				a_{12} & 7.223E7 \\
-% 				a_{13} & 2.48E7 \\
-% 				a_{14} & 1.216E7 \\
-% 				a_{15} & 3.084E6 \\
-% 				a_{16} & 1.324E6 \\
-% 				a_{17} & 2.422E5 \\
-% 				a_{18} & 9.264E4 \\
-% 				a_{19} & 1.159E4 \\
-% 				a_{20} & 4003 \\
-% 				a_{21} & 307.4 \\
-% 				a_{22} & 96.87 \\
-% 				a_{23} & 3.451 \\
-% 				a_{24} & 1 \\
-% 				\hline
-% 			\end{tabular} \\
-% 		\end{tabular}
-% 	\end{block}
-% \end{minipage}
+\begin{block}{Torque Voltage A}
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{25}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
+      \midrule
+      2.307E7 & 8.369E7 & 9.137E8 & 1.992E9 & 3.753E9 & 5.454E9 & 5.548E9 & 5.869E9 & 3.453E9 & 3.161E9 & 1.54E9 & 9.654E8 & 3.556E8 & 1.789E8 & 5.082E7 & 2.071E7 & 4.569E6 & 1.498E6 & 2.553E5 & 6.532E4 & 8443 & 1559 & 147.3 & 15.5 & 1\\
+      \bottomrule
+    \end{tabular}}
+
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{7}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
+      \midrule
+      -5.741E6 & -2.644E7 & -2.797E6 & -1.304E7 & -3.203E6 & -1.159E6 & -5.519E5\\
+      \bottomrule
+    \end{tabular}}
+\end{block}
+\begin{block}{Torque Voltage B}
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{25}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
+      \midrule
+      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
+      \bottomrule
+    \end{tabular}}
+
+    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{7}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
+      \midrule
+      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
+      \bottomrule
+    \end{tabular}}
+\end{block}
 \end{frame}

### 2021-11-18 proposalPres.tex
Minor changes to the content of proposalPres.tex

@@
     		\item Autonomous vehicles are being developed by many companies for commercial and personal use
-    		\item Modeling the steering system for autonomous vehicles is a challenging task
+    		\item Modeling different subsystems (such as, steering, brake,
+          acceleration, $\ldots$)  for autonomous vehicles is a challenging task
      		\item Models for autonomous vehicle subsystems must be very accurate due to safety factors
@@
   \begin{block}{Problem Statement}
-    \begin{large}
-      Model vehicle subsystems for a Lexus platform.
+      Model different subsystems for an autonomous vehicle (Lexus platform is considered in this project), which are
       \begin{itemize}
-          \item Steering Model
-          \item Acceleration Model
-          \item Brake Model
-          \item Shift Model
-          \item Speed Model
-          \item Speed Control Model
+          \item Steering
+          \item Acceleration
+          \item Brake
+          \item Shift
+          \item Speed
+          \item Speed control
         \end{itemize} 
-    \end{large}
+        using input-output raw data available offline
   \end{block}
@@
   \begin{block}{Specifications}
-    The vehicle plant model will fulfill the requirements listed below:
+    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
 \begin{itemize}
-    \item The resulting plant model will consist of accurate subsystem models
-    \item The subsystems can be used to create a HIL testbench
-    \item The steering model can handle very small changes in steering angles
+    \item Resulting plant model will consist of reasonably accurate subsystem models
+    \item Subsystems can be used to create a HIL testbench
+    \item Steering model can handle very small changes in steering angles
     \begin{itemize}
@@
     \begin{large}
-      The overall system architecture of this project consists of six subsystems
+      The overall system architecture of this project consists of six subsystems: 
       \begin{itemize}
-          \item Steering Model
-          \item Acceleration Model
-          \item Brake Model
-          \item Shift Model
-          \item Speed Model
-          \item Speed Control Model
+          \item Steering
+          \item Acceleration
+          \item Brake %Model
+          \item Shift %Model
+          \item Speed %Model
+          \item Speed control %Model
         \end{itemize} 
@@
       \begin{itemize}
-        \item Develop models of an autonomous vehicle's subsystems
+        \item Develop models of an autonomous vehicle's subsystems, which are 
         \begin{itemize}
-          \item Steering Model
-          \item Acceleration Model
-          \item Brake Model
-          \item Shift Model
-          \item Speed Model
-          \item Speed Control Model
+          \item Steering %  Model
+          \item Acceleration % Model
+          \item Brake % Model
+          \item Shift % Model
+          \item Speed % Model
+          \item Speed control %Model
         \end{itemize}
@@
     \begin{itemize}
-      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes
+      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle, $\ldots$
     \end{itemize}

### 2021-11-19 proposalPres.tex
Update proposalPres.tex
I added a picture to the problem statement slide, and I still need to figure out how to position it. I also made edits to the Parts List and Concluding Remarks slides.

@@
   \begin{block}{Problem Statement}
-      Model different subsystems for an autonomous vehicle (Lexus platform is considered in this project), which are
+      Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
       \begin{itemize}
@@
         using input-output raw data available offline
+
+          \begin{figure}
+			\centering
+			\begin{minipage}[t]{0.4\textwidth}
+				%\centering
+				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
+
+			\end{minipage}
+			\end{figure}
   \end{block}
+
   \pause
@@
 	\item Laptop
-	\item PAC Mod
-	\item CAN Case 
-	\item CAN Bus
+	\item PACMod ECU
+	\item CANCase 
+	\item CAN bus
 	\end{itemize}
@@
       \begin{itemize}
-        \item Develop models of an autonomous vehicle's subsystems, which are 
-        \begin{itemize}
-          \item Steering %  Model
-          \item Acceleration % Model
-          \item Brake % Model
-          \item Shift % Model
-          \item Speed % Model
-          \item Speed control %Model
-        \end{itemize}
+        \item Develop reliable and accurate models of an autonomous vehicle's subsystems 
+        \item Help further the work on autonomous vehicle development
+%        \begin{itemize}
+%          \item Steering %  Model
+%          \item Acceleration % Model
+%          \item Brake % Model
+%          \item Shift % Model
+%          \item Speed % Model
+%          \item Speed control %Model
+%        \end{itemize}
       \end{itemize}
@@
     \begin{itemize}
-      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle, $\ldots$
+      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle
     \end{itemize}

### 2021-11-19 proposalPres.tex
Update proposalPres.tex
Updated proposalPres.tex
Updated sim result figures

--- 2021-11-18 proposalPres.tex
@@
 \begin{frame}{System Requirements}
+	\tiny  
   \begin{block}{Specifications}
@@
     \begin{itemize}
+		\tiny    		
     		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
@@
 \begin{figure}[h]
+	\tiny    
     \centering
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
         \caption{Output of Estimated By-Wire System Model}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
         \caption{Output of Estimated Manual System Model}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
         \caption{Output of Estimated By-Wire System Model}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
+        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
         \caption{Output of Estimated Manual System Model}

### 2021-11-19 proposalPres.tex

--- 2021-11-19 proposalPres.tex
@@
 				%\centering
+
 				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}

### 2021-11-22 proposal.tex
Updated proposalPres.tex, proposal.tex, and labNotebook.tex

@@
 \usepackage{rotating}
-\usepackage{subfigure}
+%\usepackage{subfigure}
+\usepackage{subcaption}
 \graphicspath{%
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesAStuff}
-	\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
-	\label{fig:fleet}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesSteering}
-	\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
-	\label{fig:steerSystem}
-\end{figure}
-\begin{tiny}[h]
-	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
-\end{tiny}
+%\begin{figure}[h]
+%	\centering
+%	\subcaptionbox{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
+%		[2.5cm]{\includegraphics{figs/img/autonomousVehiclesAStuff}}
+%	\subcaptionbox{Autonomous Vehicle Steering System\textsuperscript{b}}
+%		[2.5cm]{\includegraphics{figs/img/autonomousVehiclesSteering}}
+%\end{figure}
+%\begin{tiny}[h]
+%	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+%\end{tiny}
 
@@
  \begin{itemize}
-    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and the fact that it is important to the operation of the vehicle
+    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and it is important to the operation of the vehicle
     \item Each vehicle subsystem will be modeled separately 
@@
     		\item Laptop
-    		\item PAC Mod 
-    		\item CAN Case 
-    		\item CAN Bus 
+    		\item PACMod 
+    		\item CANCase 
+    		\item CAN bus 
  	\end{itemize}

### 2021-11-22 proposalPres.tex
Updated proposalPres.tex
Merged changes; Updated Experimental Setup slide
Updated proposalPres.tex, proposal.tex, and labNotebook.tex

@@
 				\item Vehicle is not autonomous
-				\item Torque voltages are sent by the ECU
+				\item Torque voltages are sent by the vehicle ECU
 			\end{itemize}
@@
 				\item Vehicle is autonomous
-				\item Torque voltages are sent by the PACMod
-				\item Torque voltages sent from the ECU are discarded by open-circuiting the motors
+				\item Torque voltages are sent by the PACMod ECU
+				\item Torque voltages sent from the vehicle ECU are discarded by open-circuiting the motors
 			\end{itemize}
@@
 
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+	\begin{center}
+		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     		\begin{tabular}{*{21}{c}}
@@
     		\end{tabular}}
+	\end{center}
+
 \end{block}
@@
     \end{tabular}}
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+	\begin{center}
+		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     		\begin{tabular}{*{21}{c}}
@@
     \end{tabular}}
+	\end{center}	    	 
 \end{block}  
@@
     \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{center}
+    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     \begin{tabular}{*{21}{c}}
@@
     \end{tabular}}
+    \end{center}
 \end{block}
@@
     \end{tabular}}
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+	\begin{center}
+	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     \begin{tabular}{*{21}{c}}
@@
     \end{tabular}}
+	\end{center}	    	  
 \end{block}
@@
     \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{center}
+    		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     \begin{tabular}{*{7}{c}}
@@
     \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{center}
+    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
     \begin{tabular}{*{7}{c}}

### 2021-11-23 proposal.tex
Updated proposal.tex
Major updates to validation and testing section, design setup section, introduction section, and system architecture section

Updated nonlinearBehavior figure

--- 2021-11-17 proposal.tex
@@
 Autonomous vehicles are being developed by many companies for commercial and/or personal use.
-These autonomous vehicles, like the fleet AutonomouStuff has as shown in \autoref{fig:fleet}, would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
+These autonomous vehicles, like the fleet AutonomouStuff has as shown in \autoref{fleet}, would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
 Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
 Accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage these vehicles.
+
 \vspace*{12pt}
-\noindent
-There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
+
+\noindent There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
 We will be modeling these six subsystems for a Lexus vehicle platform using the System Identification Toolbox from Matlab.
@@
 Models for each subsystem must created for both manual drive mode and by-wire, or autonomous, mode.
-\autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle.
+\autoref{steerSystem} depicts how the by-wire mode controls the vehicle.
 Each subsystem, like the steering system in this example, sends torque voltages to a motor that will control the subsystem.
-In \autoref{fig:steerSystem}, the motor would turn the pinion arms which would change the steering angle of the vehicle.
+In \autoref{steerSystem}, the motor would turn the pinion arms which would change the steering angle of the vehicle.
 This principle is applied to all other subsystems.
+
+\vspace*{12pt}
 
@@
 	\centering
-	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesAStuff}
-	\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
-	\label{fig:fleet}
+	\subcaptionbox{AutonomouStuff Vehicle Fleet\textsuperscript{a} \label{fleet}}
+		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/autonomousVehiclesAStuff}}
+	\subcaptionbox{Autonomous Vehicle Steering System\textsuperscript{b} \label{steerSystem}}
+		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/autonomousVehiclesSteering}}
+	\caption{Autonomous Vehicle Fleet and Setup}
 \end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[height=4.5cm]{figs/img/autonomousVehiclesSteering}
-	\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
-	\label{fig:steerSystem}
-\end{figure}
-\begin{tiny}[h]
+
+\noindent \begin{tiny}
 	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:steerBlockDiag}, \autoref{fig:brakeBlockDiag}, \autoref{fig:accelBlockDiag}, \autoref{fig:shiftBlockDiag}, \autoref{fig:cruiseBlockDiag}, and \autoref{fig:speedBlockDiag}.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:subFunctionalBlock}.
+Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
+Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.
 
-\begin{figure}
+\begin{figure}[htb]
     \centering 
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=3in]{figs/inkscape/steeringModelArchitecture}
-    \caption{Block Diagram of the Vehicle Steering Model.}
-    \label{fig:steerBlockDiag}
-\end{figure}
-%
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-    \caption{Block Diagram of the Vehicle Brake Model.}
-    \label{fig:brakeBlockDiag}
-\end{figure}
-%
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-    \caption{Block Diagram of the Vehicle Acceleration Model.}
-    \label{fig:accelBlockDiag}
-\end{figure}
-%
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
+\begin{subfigure}{0.25\textwidth}
+  \includegraphics[width=2in]{figs/inkscape/steeringModelArchitecture}
+\end{subfigure}\hfill
+\begin{subfigure}{0.25\textwidth}
+  \includegraphics[width=2in]{figs/inkscape/brakeModelArchitecture}
+\end{subfigure}\hfill
+\begin{subfigure}{0.25\textwidth}
+  \includegraphics[width=2in]{figs/inkscape/accelerationModelArchitecture}
+\end{subfigure}
+
+\vspace{36pt}
+\begin{subfigure}{0.25\textwidth}
   \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
-    \caption{Block Diagram of the Vehicle Shift Model.}
-    \label{fig:shiftBlockDiag}
-\end{figure}
-%
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
+\end{subfigure}\hfill
+\begin{subfigure}{0.25\textwidth}
   \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
-    \caption{Block Diagram of the Vehicle Speed Control Model.}
-    \label{fig:cruiseBlockDiag}
-\end{figure}
-%
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
+\end{subfigure}\hfill
+\begin{subfigure}{0.25\textwidth}
   \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
-    \caption{Block Diagram of the Vehicle Speed Model.}
-    \label{fig:speedBlockDiag}
+\end{subfigure}
+\vspace{16pt}
+\caption{Autonomous Vehicle Subsystem Functional Block Diagrams}
+\label{fig:subFunctionalBlock}
 \end{figure}
@@
  \subsection{Parts List}
+	The following is the hardware required for this project:  
+	\begin{itemize}
+    		\item Laptop
+    		\item PACMod ECU
+    		\item CANCase 
+    		\item CAN bus 
+ 	\end{itemize}
+	The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+This data is sent or received using the CANCase and CAN bus.
+These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.
+
 	The following is the software required for this project: 
@@
  	\end{itemize}
-
-	The following is the hardware required for this project:  
-	\begin{itemize}
-    		\item Laptop
-    		\item PAC Mod 
-    		\item CAN Case 
-    		\item CAN Bus 
- 	\end{itemize}
+ 	The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
+This is how we were able to collect logs of data that we would use to develop models of the autonomous vehicle subsystems.
+MATLAB's System Identification Toolbox is the software that gave us the capabilities to develop these models of the vehicle subsystems.
+Using this toolbox, we are able to use the logs of data we collected to create sets of estimation and validation data that will be used for training the model.
 
 \subsection{Experimental Setup} \label{sec:setup}
-Each subsystem that we are modeling are set up in a similar manner.
-In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU).
+Each subsystem that we are modeling is set up in a similar manner.
+In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).
 In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode.
-In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem.
-Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
+In by-wire mode, the torque voltages from the vehicle's ECU are discarded by open-circuiting the motors that control each subsystem.
+Instead, the PACMod ECU built by AutonomouStuff sends the torque voltages to the motor using relays.
 In \autoref{fig:vehicleSetup}, the experimental setup for data collection is shown.
@@
 
-\subsection{Simulation Results} \label{sec:simresults}
-In \autoref{fig:byWireSteerModel}, the output steering angle is plotted versus time when the vehicle is in by-wire mode.
+\section{Validation and Testing} \label{sec:simresults}
+\subsection{Steering System}
+In \autoref{byWireSteerModel}, the output steering angle is plotted versus time when the vehicle is in by-wire mode.
 The figure shows the output steering angle from some data collected to depict the steering system behavior plotted with the behavior of the estimated model.
 The best fit percentage for this model is 85.54.
-Likewise, \autoref{fig:manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode.
+Likewise, \autoref{manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode.
 The best fit percentage for this model is 90.27.
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=5in]{figs/img/byWireSteeringTransferFunctionModel}
-    \caption{Output of Estimated By-Wire System Model}
-    \label{fig:byWireSteerModel}
+	\subcaptionbox{Output of Estimated By-Wire System Model \label{byWireSteerModel}}
+		{\includegraphics[width=0.4\linewidth]{figs/img/byWireSteeringTransferFunctionModel}}
+	\hfill
+	\subcaptionbox{Output of Estimated Manual System Model \label{manualSteerModel}}
+		{\includegraphics[width=0.4\linewidth]{figs/img/manualSteeringTransferFunctionModel}}
+	\caption{Steering System Estimated Steering Angle Comparison}
 \end{figure}
-\begin{figure}
+
+\vspace{12pt}
+\noindent The model of the by-wire steering system is a twentieth order transfer function.
+The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
+\autoref{byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.
+\autoref{byWireSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.
+\begin{figure}[h]
+	\resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
+      \bottomrule
+    \end{tabular}}
+
+	\begin{center}
+		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    		\begin{tabular}{*{21}{c}}
+      	\toprule
+      	$b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      	\midrule
+      	3.44E-16 & -2.203E-15 & 1.24E-13 & 5.975E-13 & 3.001E-12 & 5.23E-12\\
+      	\bottomrule
+    		\end{tabular}}
+	\end{center}	
+	\label{byWireSteerCoeffA}
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage A Coefficient Table}
+\end{figure}
+\begin{figure}[h]
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      2.92E-15 & 2.758E-13 & 1.761E-11 & 4.228E-10 & 1.422E-8 & 1.561E-7 & 1.501E-6 & 8.426E-6 & 5.981E-5 & 0.0002016 & 0.001226 & 0.002649 & 0.01456 & 0.02044 & 0.104 & 0.09228 & 0.4417 & 0.2257 & 1.025 & 0.2305 & 1\\
+      \bottomrule
+    \end{tabular}}
+	\begin{center}
+		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    		\begin{tabular}{*{21}{c}}
+     	 \toprule
+     	 $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+     	 \midrule
+      	-6.645E-15 & 2.161E-14 & -2.605E-14 & -4.744E-13 & -1.813E-13 & -4.858E-12\\
+      	\bottomrule
+    \end{tabular}}
+	\end{center}
+	\label{byWireSteerCoeffB}
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+\end{figure}
+
+\vspace{12pt}
+\noindent The model of the manual steering system is a twentieth order transfer function.
+The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
+\autoref{manualSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.
+\autoref{manualSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.
+
+\begin{figure}[h]
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
+      \bottomrule
+    \end{tabular}}
+    \begin{center}
+    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
+      \bottomrule
+    \end{tabular}}
+    \end{center}
+    \label{manualSteerCoeffA}
+	\caption{Manual Mode Steering Transfer Function Torque Voltage A Coefficient Table}
+\end{figure}
+\begin{figure}[h]
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
+      \midrule
+      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
+      \bottomrule
+    \end{tabular}}
+	\begin{center}
+	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{21}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
+      \midrule
+      1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
+      \bottomrule
+    \end{tabular}}
+	\end{center}	
+	\label{manualSteerCoeffB}
+	\caption{Manual Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+\end{figure}
+
+\subsection{Acceleration System}
+In \autoref{byWireAccelModel}, the output acceleration pedal position is plotted versus time when the vehicle is in by-wire mode.
+The figure shows the output acceleration pedal position from some data collected to depict the acceleration system behavior plotted with the behavior of the estimated model.
+The best fit percentage for this model is 97.69.
+Likewise, \autoref{manualAccelModel} depicts the output acceleration pedal position plotted versus time when the vehicle is in manual mode.
+The best fit percentage for this model is 98.3.
+
+\begin{figure}[h]
 	\centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=5in]{figs/img/manualSteeringTransferFunctionModel}
-    \caption{Output of Estimated Manual System Model}
-    \label{fig:manualSteerModel}
+	\subcaptionbox{Output of Estimated By-Wire System Model \label{byWireAccelModel}}
+		{\includegraphics[width=0.4\linewidth]{figs/img/byWireAccelArxModel}}
+	\hfill
+	\subcaptionbox{Output of Estimated Manual System Model \label{manualAccelModel}}
+		{\includegraphics[width=0.4\linewidth]{figs/img/manualAccelTransferFunctionModel}}
+	\caption{Acceleration System Estimated Pedal Position Comparison}
+\end{figure}
+
+\vspace{12pt}
+\noindent The model of the by-wire acceleration system is a fourth order ARX model.
+The fourth order ARX model defined in \autoref{byWireAccelEq} represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$.
+\begin{figure}[h]
+	\begin{equation}
+		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
+	\end{equation}
+	%
+	where na = 4, nb = 4, nk = 0, and, 
+	%
+	\begin{equation}
+		A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
+	\end{equation}
+	\begin{equation}
+		B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
+	\end{equation}
+	\begin{equation}
+		B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
+	\end{equation}
+	\label{byWireAccelEq}
+	\caption{By-Wire Mode Acceleration System ARX Model Equations}
+\end{figure}
+
+\vspace{12pt}
+\noindent The model of the manual acceleration system is a twenty-fourth order transfer function.
+The twenty-fourth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
+\autoref{manualAccelCoeffA} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage A signal.
+\autoref{manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.
+
+\begin{figure}[h]
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{25}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
+      \midrule
+      2.307E7 & 8.369E7 & 9.137E8 & 1.992E9 & 3.753E9 & 5.454E9 & 5.548E9 & 5.869E9 & 3.453E9 & 3.161E9 & 1.54E9 & 9.654E8 & 3.556E8 & 1.789E8 & 5.082E7 & 2.071E7 & 4.569E6 & 1.498E6 & 2.553E5 & 6.532E4 & 8443 & 1559 & 147.3 & 15.5 & 1\\
+      \bottomrule
+    \end{tabular}}
+    \begin{center}
+    		\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{7}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
+      \midrule
+      -5.741E6 & -2.644E7 & -2.797E6 & -1.304E7 & -3.203E6 & -1.159E6 & -5.519E5\\
+      \bottomrule
+    \end{tabular}}
+    \end{center}
+    \label{manualAccelCoeffA}
+	\caption{Manual Mode Acceleration Transfer Function Torque Voltage A Coefficient Table}
+\end{figure}
+\begin{figure}[h]
+	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{25}{c}}
+      \toprule
+      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
+      \midrule
+      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
+      \bottomrule
+    \end{tabular}}
+    \begin{center}
+    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
+    \begin{tabular}{*{7}{c}}
+      \toprule
+      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
+      \midrule
+      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
+      \bottomrule
+    \end{tabular}}
+    \end{center}	
+	\label{manualAccelCoeffB}
+	\caption{Manual Mode Acceleration Transfer Function Torque Voltage B Coefficient Table}
 \end{figure}

### 2021-11-24 proposal.tex
Update labNotebook and proposal
I have made some changes to the lab notebook and proposal documents.

@@
 \section{Introduction}
-Autonomous vehicles are being developed by many companies for commercial and/or personal use.
+Autonomous vehicles are being developed by many companies for commercial and personal use.
 These autonomous vehicles, like the fleet AutonomouStuff has as shown in \autoref{fleet}, would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
@@
 
-\noindent There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
-We will be modeling these six subsystems for a Lexus vehicle platform using the System Identification Toolbox from Matlab.
+\noindent There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a speed control (cruise) model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
+We will be modeling these six subsystems for a Lexus vehicle platform using the System Identification Toolbox from MATLAB.
 The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
-There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected due to non-linear behaviors of the torques voltages required to control each subsystem.
+There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected due to non-linear behaviors of the torque voltages required to control each subsystem.
 The scope of this project includes developing mathematical models for each subsystem so AutonomouStuff can implement controls that improve the reliability of the autonomous vehicle platform.
@@
 The goal of the system identification methodology is to get an accurate estimation of the system response to any given input.
-Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
+Mathworks' MATLAB has the System Identification Toolbox, where a few existing examples demonstrate the working principle of this toolbox.
 
@@
 
-During this example in~\cite{example1} I learned how to create an iddata object from a dataset in order to get the inputs and the outputs.
+This example in~\cite{example1} shows how to create an iddata object from a dataset in order to get the inputs and the outputs.
 The next step was to look at the impulse and step responses in order to learn more about how the inputs and outputs act.
 From there the state space model was estimated using the first part of the given data.
-This model was compared to the step responses that were found earlier and with the second part of the data to see if it was a good fit.
+This model was compared to the step responses and with the second part of the data to see if it was a good fit.
 The model had a best fit percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\% for the speed data.
@@
 \label{sec:sysID-Example2}
-This example, \~cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example, ~\cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:subFunctionalBlock}.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in \autoref{fig:subFunctionalBlock}.
 Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
@@
  \begin{itemize}
-    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and it is important to the operation of the vehicle
+    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
+    \item The steering subsystem will be able to handle small steering angles
     \item Each vehicle subsystem will be modeled separately
-    \item The steering subsystem will be able to handle small steering angles
  \end{itemize}
@@
 \section{Preliminary Work}
-To start this project, we first read documentation outlining the uses of Matlab's System Identification Toolbox.
-From there we worked on Matlab tutorials on how to model systems from data using System Identification and then find the most accurate model.
+To start this project, we first read documentation outlining the uses of MATLAB's System Identification Toolbox.
+From there we worked on MATLAB tutorials on how to model systems from data using System Identification and then find the most accurate model.
 We specifically tried to find examples with Multiple-Input Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since most of the vehicle subsystems we will model fall into one of these categories.
@@
 This data is sent or received using the CANCase and CAN bus.
-These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.
+These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.\bigskip
 
@@
 The figure shows the output steering angle from some data collected to depict the steering system behavior plotted with the behavior of the estimated model.
-The best fit percentage for this model is 85.54.
+The best fit percentage for this model is 85.54\%.
 Likewise, \autoref{manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode.
-The best fit percentage for this model is 90.27.
+The best fit percentage for this model is 90.27\%.
 
@@
 \vspace{12pt}
-\noindent The model of the manual steering system is a twentieth order transfer function.
-The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
+\noindent The manual steering system is modeled by a twentieth order transfer function.
+After considering the system costs that come with a higher order transfer function and the need to achieve a sufficient best fit percentage, it is clear that a twentieth order transfer function is the best estimation of the system.
 \autoref{manualSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.
@@
 The figure shows the output acceleration pedal position from some data collected to depict the acceleration system behavior plotted with the behavior of the estimated model.
-The best fit percentage for this model is 97.69.
+The best fit percentage for this model is 97.69\%.
 Likewise, \autoref{manualAccelModel} depicts the output acceleration pedal position plotted versus time when the vehicle is in manual mode.
-The best fit percentage for this model is 98.3.
+The best fit percentage for this model is 98.3\%.
 
@@
 One of the biggest concerns with autonomous vehicles today is the risk associated with public safety.
-One solution to reducing the safety risk is ensuring that accurate controllers are developed to reliably control each subsystem involved with the controlling the movement of the autonomous vehicle.
+One solution to reducing the safety risk is ensuring that accurate controllers are developed to reliably control each subsystem involved with the movement of the autonomous vehicle.
 Due to non-linear behaviors, there is no simple solution for developing reliable controllers.

### 2021-11-30 proposalPres.tex
Updated proposalPres.tex
Adjusted slides to fit new figures
Edited font sizes to match

@@
 \usepackage{arydshln}
+\usepackage{multicol}
 
@@
   \begin{block}{Problem Statement}
+	\begin{minipage}[t]{0.62\linewidth}      
       Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
+	  \begin{multicols}{2}      
       \begin{itemize}
@@
         \end{itemize} 
+        \end{multicols}
         using input-output raw data available offline
-
+    \end{minipage}
+    \begin{minipage}[t]{0.34\textwidth}  
         \begin{figure}
 			\centering
-			\begin{minipage}[t]{0.4\textwidth}
-				%\centering
-
-				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
-				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
-
+			\captionsetup{justification=centering, margin=0.5cm, font=tiny}
+			\includegraphics[width=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+			\caption{AutonomouStuff Lexus RX450H Vehicle}
+		\end{figure}
 	\end{minipage}
-			\end{figure}
   \end{block}
@@
 \begin{frame}{System Requirements}
-	\tiny  
 \begin{block}{Specifications}
+	\begin{minipage}[t]{0.62\linewidth}    
     Proposed vehicle subsystem models are expected to fulfill requirements listed below:
@@
     \begin{itemize}
-		\tiny    		
 		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
@@
 	\end{itemize}
+	\end{minipage}
+	\begin{minipage}[t]{0.34\linewidth}
 	\begin{figure}[h]
-	\tiny    
 		\centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=1in]{figs/inkscape/nonlinearBehavior}
+    		\captionsetup{justification=centering, margin=0.5cm}
+    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
     		\caption{Steering Non-linear Behavior}
@@
 	\end{figure}
+	\end{minipage}
 \end{block}
@@
 		%
-		where na = 4, nb = 4, nk = 0, and, 
+		\centering where na = 4, nb = 4, nk = 0, and, 
 		%

### 2021-11-30 proposal.tex

@@
 
+  % %
+  % \begin{figure}
+  %   \centering
+  %   \begin{subfigure}[b]{0.48\linewidth}
+  %     \centering
+  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsTopViewV3}
+  %     \caption{}
+  %     \label{fig:PowertrainModelCorrectDimsTopViewV3}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.48\linewidth}
+  %     \centering
+  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsFrontViewV4}
+  %     \caption{}
+  %     \label{fig:PowertrainModelCorrectDimsFrontViewV4}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.48\linewidth}
+  %     \centering
+  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsSideViewV4}
+  %     \caption{}
+  %     \label{fig:PowertrainModelCorrectDimsSideViewV4}
+  %   \end{subfigure}
+  %   \caption{\subref{fig:PowertrainModelCorrectDimsTopViewV3} Top view,
+  %     \subref{fig:PowertrainModelCorrectDimsFrontViewV4} front view, and
+  %     \subref{fig:PowertrainModelCorrectDimsSideViewV4} side view of the
+  %     proposed disinfecting robot.}
+  %   \label{fig:2dViewsDisinfectingRobot}
+  % \end{figure}
+
 \begin{figure}[h]
@@
 \vspace{12pt}
-\noindent The manual steering system is modeled by a twentieth order transfer function.
-After considering the system costs that come with a higher order transfer function and the need to achieve a sufficient best fit percentage, it is clear that a twentieth order transfer function is the best estimation of the system.
-\autoref{manualSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.
-\autoref{manualSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.
-
-\begin{figure}[h]
+\noindent The manual steering system is modeled by a twentieth order transfer
+function. After considering the system costs that come with a higher order
+transfer function and the need to achieve a sufficient best fit percentage, it
+is clear that a twentieth order transfer function is the best estimation of the
+system. \autoref{tab:manualSteerCoeffA} shows the coefficients of the twentieth
+order transfer function for the output steering angle with respect to the input
+torque voltage A signal. %
+%
+  \begin{table}[hbtp]
+    \caption{Manual mode steering transfer function torque voltage A coefficient table. }
+    \label{tab:manualSteerCoeffA}
+    \centering
 	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
     \end{center}
-    \label{manualSteerCoeffA}
-	\caption{Manual Mode Steering Transfer Function Torque Voltage A Coefficient Table}
-\end{figure}
-\begin{figure}[h]
+  \end{table}
+%
+
+\autoref{tab:manualSteerCoeffB} shows the coefficients of
+the twentieth order transfer function for the output steering angle with respect
+to the input torque voltage B signal. %
+%
+\begin{table}[hbtp]
+	\caption{Manual Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+	\label{tab:manualSteerCoeffB}
+  \centering
   \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
 	\end{center}	
-	\label{manualSteerCoeffB}
-	\caption{Manual Mode Steering Transfer Function Torque Voltage B Coefficient Table}
-\end{figure}
+\end{table}
+%
 
@@
 The fourth order ARX model defined in \autoref{byWireAccelEq} represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$.
-\begin{figure}[h]
+% \begin{figure}[h]
 	\begin{equation}
-		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
+		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t),
 	\end{equation}
@@
 	%
-	\begin{equation}
-		A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
-	\end{equation}
-	\begin{equation}
-		B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
-	\end{equation}
-	\begin{equation}
-		B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
-	\end{equation}
-	\label{byWireAccelEq}
-	\caption{By-Wire Mode Acceleration System ARX Model Equations}
-\end{figure}
+  \begin{align*}
+		A(z) &= 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}\\
+    B_1(z) &= -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}\\
+		B_2(z) &= 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
+  \end{align*}
+% 	\label{byWireAccelEq}
+% 	\caption{By-Wire Mode Acceleration System ARX Model Equations}
+% \end{figure}
 

### 2021-12-01 proposal.tex
Update proposal.tex
I updated the gantt chart for the fall semester to reflect our progress.
Updated proposal.tex
Changed sim result figures to tables

@@
 	\subcaptionbox{Output of Estimated By-Wire System Model \label{byWireSteerModel}}
-		{\includegraphics[width=0.4\linewidth]{figs/img/byWireSteeringTransferFunctionModel}}
-	\hfill
+		{\includegraphics[width=0.48\linewidth]{figs/img/byWireSteeringTransferFunctionModel}}
 	\subcaptionbox{Output of Estimated Manual System Model \label{manualSteerModel}}
-		{\includegraphics[width=0.4\linewidth]{figs/img/manualSteeringTransferFunctionModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/manualSteeringTransferFunctionModel}}
 	\caption{Steering System Estimated Steering Angle Comparison}
@@
 The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
-\autoref{byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.
-\autoref{byWireSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.
-\begin{figure}[h]
+\autoref{tab:byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.%
+%
+\begin{table}[hbtp]
+	\label{tab:byWireSteerCoeffA}
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage A Coefficient Table}
+  \centering
   \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
 	\end{center}	
-	\label{byWireSteerCoeffA}
-	\caption{By-Wire Mode Steering Transfer Function Torque Voltage A Coefficient Table}
-\end{figure}
-\begin{figure}[h]
+\end{table}
+%
+
+\noindent \autoref{tab:byWireSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.%
+%
+\begin{table}[hbtp]
+	\label{tab:byWireSteerCoeffB}
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+  \centering
   \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
 	\end{center}
-	\label{byWireSteerCoeffB}
-	\caption{By-Wire Mode Steering Transfer Function Torque Voltage B Coefficient Table}
-\end{figure}
+\end{table}
+%
 
@@
 
-\autoref{tab:manualSteerCoeffB} shows the coefficients of
+\noindent \autoref{tab:manualSteerCoeffB} shows the coefficients of
 the twentieth order transfer function for the output steering angle with respect
@@
 	\subcaptionbox{Output of Estimated By-Wire System Model \label{byWireAccelModel}}
-		{\includegraphics[width=0.4\linewidth]{figs/img/byWireAccelArxModel}}
-	\hfill
+		{\includegraphics[width=0.48\linewidth]{figs/img/byWireAccelArxModel}}
 	\subcaptionbox{Output of Estimated Manual System Model \label{manualAccelModel}}
-		{\includegraphics[width=0.4\linewidth]{figs/img/manualAccelTransferFunctionModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/manualAccelTransferFunctionModel}}
 	\caption{Acceleration System Estimated Pedal Position Comparison}
@@
 \noindent The model of the by-wire acceleration system is a fourth order ARX model.
-The fourth order ARX model defined in \autoref{byWireAccelEq} represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$.
-% \begin{figure}[h]
-	\begin{equation}
-		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t),
-	\end{equation}
+The fourth order ARX model defined below represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$.
+% 
+	\begin{align*}
+		A(z)y(t) &= B_1(z)u_1(t) + B_2(z)u_2(t) + e(t),
+	\end{align*}
 	%
@@
   \end{align*}
-% 	\label{byWireAccelEq}
-% 	\caption{By-Wire Mode Acceleration System ARX Model Equations}
-% \end{figure}
+%
 
@@
 The twenty-fourth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
-\autoref{manualAccelCoeffA} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage A signal.
-\autoref{manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.
-
-\begin{figure}[h]
+\autoref{tab:manualAccelCoeffA} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage A signal.
+%
+%
+\begin{table}[hbtp]
+	\caption{Manual Mode Acceleration Transfer Function Torque Voltage A Coefficient Table}
+	\label{tab:manualAccelCoeffA}
+  \centering
   \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
     \end{center}
-    \label{manualAccelCoeffA}
-	\caption{Manual Mode Acceleration Transfer Function Torque Voltage A Coefficient Table}
-\end{figure}
-\begin{figure}[h]
+\end{table}
+%
+
+\noindent \autoref{tab:manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.%
+%
+\begin{table}[hbtp]
+	\caption{Manual Mode Acceleration Transfer Function Torque Voltage B Coefficient Table}
+	\label{tab:manualAccelCoeffB}
+  \centering
   \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
@@
     \end{center}	
-	\label{manualAccelCoeffB}
-	\caption{Manual Mode Acceleration Transfer Function Torque Voltage B Coefficient Table}
-\end{figure}
+\end{table}
+%
 
@@
      \ganttbar[progress = 100]{Parts Order Request}{8}{12}\\
-     \ganttbar[progress = 50]{Proposal Document}{9}{15}\\
-     \ganttbar[progress = 30]{Proposal Presentation}{9}{15}\\
+     \ganttbar[progress = 100]{Proposal Document}{9}{15}\\
+     \ganttbar[progress = 100]{Proposal Presentation}{9}{15}\\
 
 %     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
-     \ganttmilestone[progress = 30]{Model Steering System}{13}{14}\\
-     \ganttbar[progress = 0]{Model Acceleration System}{14}{15}\\
-     \ganttbar[progress = 0]{Model Braking System}{15}{16}\\
+     \ganttmilestone[progress = 100]{Model Steering System}{13}{14}\\
+     \ganttbar[progress = 100]{Model Acceleration System}{14}{15}\\
+     \ganttbar[progress = 100]{Model Braking System}{15}{15}\\
 

### 2021-12-06 proposal.tex
Update proposal.tex
I added a picture to the Preliminary Work section of the proposal document
Feedback on the introduction section

@@
 \usepackage{hyperref}
+\usepackage[colorinlistoftodos]{todonotes}
 \usepackage{soul}
@@
 \singlespacing
-%\onehalfspacing
-%\doublespacing
+% \onehalfspacing
+% \doublespacing
 % all packages are in the following tex file.
-%\input{paper-preamble.tex}
+% \input{paper-preamble.tex}
 \begin{document}
@@
 \section{Introduction}
-Autonomous vehicles are being developed by many companies for commercial and personal use.
-These autonomous vehicles, like the fleet AutonomouStuff has as shown in \autoref{fleet}, would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers.
-Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike.
-Accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage these vehicles.
+Autonomous vehicles are being developed by many companies for commercial and
+personal use. These autonomous vehicles (see the AutonomouStuff vehicle fleet
+shown in \autoref{fleet}) would allow companies to continue crucial deliveries
+or transports of their products even if there is a shortage of drivers. In
+addition, autonomous vehicles have the ability to make roads safer for drivers
+and pedestrians alike. To develop a reliable and safe transportation system for
+modern world, a large body of research in the field of autonomous vehicles is
+being conducted in recent decades [][]\todo[inline]{Add some references}.
+Therefore, it is apparent that researchers of the autonomous vehicle community
+have been focusing on analysis, design, and development of different subsystems
+of self-driving/autonomous vehicles. Furthermore, modeling vehicle subsystems is
+a pre-requisite for the development of reliable controllers for these vehicles
+to be managed in the era of modern transportation systems in general.
 
@@
 
-\noindent There are six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a speed control (cruise) model - that must be modeled to get an accurate representation of how the vehicle should be controlled.
-We will be modeling these six subsystems for a Lexus vehicle platform using the System Identification Toolbox from MATLAB.
-The first subsystem we will model is the steering model, and then we will move onto the other subsystems.
-There are already controllers in place for the Lexus vehicle platform, but their reliability is lower than expected due to non-linear behaviors of the torque voltages required to control each subsystem.
-The scope of this project includes developing mathematical models for each subsystem so AutonomouStuff can implement controls that improve the reliability of the autonomous vehicle platform.
-These models will be used by AutonomouStuff for their Hardware-in-the-Loop (HIL) testing.
-Models for each subsystem must created for both manual drive mode and by-wire, or autonomous, mode.
-\autoref{steerSystem} depicts how the by-wire mode controls the vehicle.
-Each subsystem, like the steering system in this example, sends torque voltages to a motor that will control the subsystem.
-In \autoref{steerSystem}, the motor would turn the pinion arms which would change the steering angle of the vehicle.
-This principle is applied to all other subsystems.
+\noindent Usually, there are six main subsystems of a self-driving vehicle: %
+%
+\begin{enumerate}
+\item  Steering,
+
+\item steering,
+
+\item acceleration,
+
+\item brake,
+
+\item shift, and
+
+\item speed and speed control
+  (cruise) subsystems.
+\end{enumerate}
+%
+These subsystems are to be modeled to get an accurate representation of how
+the vehicle should be controlled.
+Within the scope of this project and to expedite the modeling process, a commercially available modeling tool, called system identification toolbox, is used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belong to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+The first subsystem we will model is the steering model, and then we will move onto
+the other subsystems. There are already controllers in place for the Lexus
+vehicle platform, but their reliability is lower than expected due to non-linear
+behaviors of the torque voltages required to control each subsystem. The scope
+of this project includes developing mathematical models for each subsystem so
+AutonomouStuff can implement control systems that improve the \comment{reliability}{Define reliability} of the
+autonomous vehicle platform. These models will be used by AutonomouStuff for
+their Hardware-in-the-Loop (HIL) testing.
+There are to operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
+Models for each subsystem must be created
+for both manual drive mode and by-wire, or autonomous, mode.
+\autoref{steerSystem} depicts how the by-wire mode controls the vehicle. Each
+subsystem, like the steering system in this example, sends torque voltages to a
+motor that will control the subsystem. In \autoref{steerSystem}, the motor would
+turn the pinion arms which would change the steering angle of the vehicle. This
+principle is applied to all other subsystems.
 
@@
 The data we collected will be used to generate and then verify our models.
+\begin{figure}[h]
+	\centering
+	\captionbox{AutonomouStuff Lexus RX450H Vehicle}
+		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}}
+\end{figure}
 

### 2021-12-06 proposal.tex
Feedback on the proposal

@@
 %\usepackage{subfigure}
-\usepackage{subcaption}
+\usepackage[width=11cm,font=footnotesize,labelfont=bf, %
+format=default,justification=centerlast]{caption} % Figure caption text customization
+
+\usepackage[list=true,labelformat=simple]{subcaption}
+\renewcommand\thesubfigure{(\alph{subfigure})}
 \graphicspath{%
@@
 }
-\usepackage[width=11cm,font=footnotesize,labelfont=bf, %
-format=default,justification=centerlast]{caption} % Figure caption text customization
 
@@
 personal use. These autonomous vehicles (see the AutonomouStuff vehicle fleet
-shown in \autoref{fleet}) would allow companies to continue crucial deliveries
+shown in \autoref{fig:fleet}) would allow companies to continue crucial deliveries
 or transports of their products even if there is a shortage of drivers. In
@@
 for both manual drive mode and by-wire, or autonomous, mode.
-\autoref{steerSystem} depicts how the by-wire mode controls the vehicle. Each
+\autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
 subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. In \autoref{steerSystem}, the motor would
+motor that will control the subsystem. In \autoref{fig:steerSystem}, the motor would
 turn the pinion arms which would change the steering angle of the vehicle. This
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
   \centering
-	\subcaptionbox{AutonomouStuff Vehicle Fleet\textsuperscript{a} \label{fleet}}
-		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/autonomousVehiclesAStuff}}
-	\subcaptionbox{Autonomous Vehicle Steering System\textsuperscript{b} \label{steerSystem}}
-		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/autonomousVehiclesSteering}}
-	\caption{Autonomous Vehicle Fleet and Setup}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesAStuff}
+    \caption{}
+    \label{fig:fleet}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesSteering}
+    \caption{}
+    \label{fig:steerSystem}
+  \end{subfigure}
+  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerSystem} steering model setup (courtesy of AutonomouStuff). }
+  \label{fig:AstuffFleetSteeringSetup}
 \end{figure}
 
-\noindent \begin{tiny}
-	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
-\end{tiny}
+% \noindent \begin{tiny}
+% 	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+% \end{tiny}
 
@@
 
-Authors in~\cite{Hussain2011} illustrates identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.
+ Authors in~\cite{Hussain2011} illustrates identification of multiple-input
+ single-output model for maximum power point tracking of photovoltaic system. A
+ significant effort was conducted to model the photovoltaic system, where the two inputs were
+ Solar irradiance and Cell temperature, and the output was DC current. To model
+ this system, Matlab’s System Identification Toolbox was used. In order to
+ create different models, they collected and used data from an energy center in
+ Malaysia. After generating different models, the authors ended up going with a
+ fourth order ARX (also known as ARXQS) model because it was the most accurate,
+ with a best fit percentage of 93.42\%. The polynomial model equation for ARX is
+ shown below. %
+ %
+ \begin{align*}
+   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t), 
+ \end{align*}
+% 
+$y(t)$ is the system output at time $t,$ while $u(t)$ is the input.
+\comment{}{Didn't you say, it was a two input, one output system?
+Where is the other input in the above equation, other than $u(t)$?} The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
 
-In the paper “Identification of Multiple Input-Single Output (MISO) Model for MPPT of Photovoltaic System”, the researchers wanted to model a system where the two inputs were Solar irradiance and Cell temperature and the output was DC current.
-In order to model this system Matlab’s System Identification Toolbox was used.
-In order to create different models, they collected and used data from an energy center in Malaysia.
-After generating different models, the researchers ended up going with a fourth order ARX (also known as ARXQS) model because it was the most accurate, with a best fit percentage of 93.42\%.
-The polynomial model equation for ARX is shown below.
-
-$y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)$
-
-$y(t)$ is the output of the equation at a certain time t, while u(t) is the input at a certain time t.
-The noise disturbance of the system is represented by e(t).
-The variables na, nb, and nk are the system’s number of poles, amount of b parameters, and the samples before the inputs begin to affect the system’s output.
-
-\section{System Identification}
+\section{System Identification Preliminaries}
 
 System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system.
-There are many components or systems that engineers use to accomplish a task that they are assigned without knowing the exact behavior of this system for a given input.
+There are many components that are used to accomplish a task that they are assigned without knowing the exact behavior of the system for given input signals.
 Without knowing the response of this black-box, there could be unexpected consequences from a system.
@@
 
-This example in~\cite{example1} shows how to create an iddata object from a dataset in order to get the inputs and the outputs.
-The next step was to look at the impulse and step responses in order to learn more about how the inputs and outputs act.
-From there the state space model was estimated using the first part of the given data.
-This model was compared to the step responses and with the second part of the data to see if it was a good fit.
-The model had a best fit percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\% for the speed data.
-The frequency response of the model was estimated with spectral analysis and bode plots were also created.
-The tutorial explained that if the data doesn’t give nice models, then it is best to try out submodels for the different channels.
-Two single-input single-output (SISO) models were created and compared with the existing multiple-input multiple-output (MIMO) model and the actual data.
-The Nyquist plots were also compared.
-Both SISO models performed well during these comparisons.
-The next step in the tutorial was to create a multiple-input single-output (MISO) model in order to get a model that more accurately reflected the generated voltage data.
-By creating this model and comparing it to the validation data and previous models, we saw a best fit percentage of 90.18\%.
-The last thing the example showed was how to merge the two SISO models we created earlier.
+The example given in~\cite{example1} shows how to create an iddata object from a
+dataset in order to get the inputs and the outputs. The next step was to look at
+the impulse and step responses in order to learn more about how the inputs and
+outputs act. From there the state space model was estimated using the first part
+of the given data. This model was compared to the step responses and with the
+second part of the data to see if it was a good fit. The model had a best fit
+percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\%
+for the speed data. The frequency response of the model was estimated with
+spectral analysis and bode plots were also created. The tutorial explained that
+if the data doesn’t give nice models, then it is best to try out submodels for
+the different channels. Two single-input single-output (SISO) models were
+created and compared with the existing multiple-input multiple-output (MIMO)
+model and the actual data. The Nyquist plots were also compared. Both SISO
+models performed well during these comparisons. The next step in the tutorial
+was to create a multiple-input single-output (MISO) model in order to get a
+model that more accurately reflected the generated voltage data. By creating
+this model and comparing it to the validation data and previous models, we saw a
+best fit percentage of 90.18\%. The last thing the example showed was how to
+merge the two SISO models we created earlier.
+
+\todo[inline]{Place MATLAB figures for this example here. }
 
@@
 \label{sec:sysID-Example2}
-This example, ~\cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example~\cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
 
+\todo[inline]{Place MATLAB figures for this example here. }
 \subsection{Example 3: Identify Linear Models Using the Command Line}
 \label{sec:sysID-Example3}
-This example in~\cite{example3} shows how to create models for MISO systems using the command line.
-Before starting the model estimation process, the equilibrium values of the inputs and outputs had to be taken out.
-The data from each experiment also had to be separated into different iddata objects.
-The example showed how to estimate and compare non-parametric impulse response, transfer function, ARMA, state-space, and Box-Jenkins models with the measured experimental data.
-The state-space model with the five-step response prediction was the most accurate, with a best fit percentage of 85.83\%.
+This example in~\cite{example3} shows how to create models for MISO systems
+using the command line. Before starting the model estimation process, the
+equilibrium values of the inputs and outputs had to be taken out. The data from
+each experiment also had to be separated into different iddata objects. The
+example showed how to estimate and compare non-parametric impulse response,
+transfer function, ARMA, state-space, and Box-Jenkins models with the measured
+experimental data. The state-space model with the five-step response prediction
+was the most accurate, with a best fit percentage of 85.83\%.
+
+\todo[inline]{Place MATLAB figures for this example here. }
 

### 2021-12-06 proposal.tex
Feedback on the proposal

@@
     \centering 
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/steeringModelArchitecture}
-\end{subfigure}\hfill
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/brakeModelArchitecture}
-\end{subfigure}\hfill
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/accelerationModelArchitecture}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+  \caption{}
+  \label{fig:steeringmodelarchitecture}
 \end{subfigure}
-
-\vspace{36pt}
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
-\end{subfigure}\hfill
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
-\end{subfigure}\hfill
-\begin{subfigure}{0.25\textwidth}
-  \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+  \caption{}
+  \label{fig:brakeModelArchitecture}
 \end{subfigure}
-\vspace{16pt}
-\caption{Autonomous Vehicle Subsystem Functional Block Diagrams}
+\\
+\begin{subfigure}[b]{0.48\textwidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+  \caption{}
+  \label{fig:accelerationModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+  \caption{}
+  \label{fig:shiftModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+  \caption{}
+  \label{fig:speedControlModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+  \caption{}
+  \label{fig:speedModelArchitecture}
+\end{subfigure}
+\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
 \label{fig:subFunctionalBlock}

### 2021-12-07 proposal.tex
Proposal Changes
I added a figure to the proposal in the MATLAB examples section
Added two references; Updated proposal.tex intro section

@@
 modern world, a large body of research in the field of autonomous vehicles is
-being conducted in recent decades [][]\todo[inline]{Add some references}.
+being conducted in recent decades \cite{Liu2017} \cite{Prasad2020}.
 Therefore, it is apparent that researchers of the autonomous vehicle community
@@
 
-\item steering,
-
 \item acceleration,
@@
 
-\item shift, and
+\item shift,
 
-\item speed and speed control
-  (cruise) subsystems.
+\item speed, and
+
+\item speed control (cruise) subsystems.
 \end{enumerate}
@@
 of this project includes developing mathematical models for each subsystem so
-AutonomouStuff can implement control systems that improve the \comment{reliability}{Define reliability} of the
-autonomous vehicle platform. These models will be used by AutonomouStuff for
-their Hardware-in-the-Loop (HIL) testing.
-There are to operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
-Models for each subsystem must be created
-for both manual drive mode and by-wire, or autonomous, mode.
+AutonomouStuff can implement control systems that improve the reliability of the
+autonomous vehicle platform.
+These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
+Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
+Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
+There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
+for both manual-drive mode and by-wire, or autonomous, mode.
 \autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each

### 2021-12-08 proposal.tex
Update proposal.tex
I added the figures for two of the MATLAB examples and then created different subsections for the System Architecture, along with moving the block diagrams.

@@
 
-\todo[inline]{Place MATLAB figures for this example here. }
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/img/mimoExGrady}
+    \caption{Comparison of the state space model and merged SISO models with the validation data}
+    \label{fig:exMIMO}
+\end{figure}
 
@@
 was the most accurate, with a best fit percentage of 85.83\%.
-
-\todo[inline]{Place MATLAB figures for this example here. }
+\begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/img/commandLineIO}
+    \caption{Inputs and outputs of the given system}
+    \label{fig:exIO}
+\end{figure}
 
@@
 
-\begin{figure}[htb]
+ \subsection{Steeering Subsystem}
+
+ \begin{figure}[h]
     \centering
-\begin{subfigure}[b]{0.48\linewidth}
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+    \caption{Steering subsystem block diagram}
+    \label{fig:steeringmodelarchitecture}
+\end{figure}
+
+ \begin{figure}[h]
     \centering
-  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-  \caption{}
-  \label{fig:steeringmodelarchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
+    \caption{Steering block diagram}
+    \label{fig:steeringModelBlockDiagram}
+\end{figure}
+
+  \subsection{Brake Subsystem}
+ \begin{figure}[h]
     \centering
+    \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-  \caption{}
+    \caption{Brake subsystem block diagram}
     \label{fig:brakeModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\textwidth}
+\end{figure}
+
+  \subsection{Acceleration Subsystem}
+ \begin{figure}[h]
     \centering
+    \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-  \caption{}
+    \caption{Acceleration subsystem block diagram}
     \label{fig:accelerationModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
+\end{figure}
+
+  \subsection{Shift Subsystem}
+ \begin{figure}[h]
     \centering
+    \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-  \caption{}
+    \caption{Shift subsystem block diagram}
     \label{fig:shiftModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\linewidth}
+\end{figure}
+
+  \subsection{Speed Subsystem}
+ \begin{figure}[h]
     \centering
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+    \caption{Speed subsystem block diagram}
+    \label{fig:speedModelArchitecture}
+\end{figure}
+
+  \subsection{Speed Control Subsystem}
+ \begin{figure}[h]
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-  \caption{}
+    \caption{Speed Control subsystem block diagram}
     \label{fig:speedControlModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering
-  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-  \caption{}
-  \label{fig:speedModelArchitecture}
-\end{subfigure}
-\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-\label{fig:subFunctionalBlock}
 \end{figure}
+
+%\begin{figure}[htb]
+%    \centering 
+%\begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+%  \caption{}
+%  \label{fig:steeringmodelarchitecture}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%  \caption{}
+%  \label{fig:brakeModelArchitecture}
+%\end{subfigure}
+%\\
+%\begin{subfigure}[b]{0.48\textwidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+%  \caption{}
+%  \label{fig:accelerationModelArchitecture}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+%  \caption{}
+%  \label{fig:shiftModelArchitecture}
+%\end{subfigure}
+%\\
+%\begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+%  \caption{}
+%  \label{fig:speedControlModelArchitecture}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+%  \caption{}
+%  \label{fig:speedModelArchitecture}
+%\end{subfigure}
+%\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+%\label{fig:subFunctionalBlock}
+%\end{figure}
 

### 2021-12-08 proposal.tex
Update proposal.tex

@@
 modern world, a large body of research in the field of autonomous vehicles is
-being conducted in recent decades \cite{Liu2017} \cite{Prasad2020}.
+being conducted in recent decades [][]\todo[inline]{Add some references}.
 Therefore, it is apparent that researchers of the autonomous vehicle community
@@
 
+\item steering,
+
 \item acceleration,
@@
 
-\item shift,
+\item shift, and
 
-\item speed, and
-
-\item speed control (cruise) subsystems.
+\item speed and speed control
+  (cruise) subsystems.
 \end{enumerate}
@@
 of this project includes developing mathematical models for each subsystem so
-AutonomouStuff can implement control systems that improve the reliability of the
-autonomous vehicle platform.
-These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
-Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
-Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
-for both manual-drive mode and by-wire, or autonomous, mode.
+AutonomouStuff can implement control systems that improve the \comment{reliability}{Define reliability} of the
+autonomous vehicle platform. These models will be used by AutonomouStuff for
+their Hardware-in-the-Loop (HIL) testing.
+There are to operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
+Models for each subsystem must be created
+for both manual drive mode and by-wire, or autonomous, mode.
 \autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each

### 2021-12-08 proposal.tex
Update proposal.tex
Added text to some of the System Architecture Vehicle Subsystem subsections.

--- 2021-12-08 proposal.tex
@@
  \subsection{Steeering Subsystem}
+In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle.
+This desired angle is entered by the user.
+$\theta$, the actual steering wheel angle, is subtracted from the desired steering wheel angle to find the error between the two positions.
+This error value is sent to the steering subsystem’s controller.
+Using this information, the controller generates torque voltages A and B, which are sent to the steering subsystem.
+New torque voltages are then generated and the actual steering wheel angle is updated.
 
@@
   \subsection{Brake Subsystem}
+  The brake subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
+Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed.
+This boolean value indicates to the user whether or not the brake pedal is being pressed.
+The brake subsystem is another example of a multiple-input multiple-output system.
  \begin{figure}[h]
@@
   \subsection{Acceleration Subsystem}
+  The acceleration subsystem is a multiple-input multiple-output (MIMO) system.
+Acceleration pedal voltages are sent to the subsystem.
+A new acceleration pedal position value is generated to better match the real-time pedal position.
  \begin{figure}[h]
@@
   \subsection{Shift Subsystem}
+ This subsystem can be classified as a single-input single-output system.
+The subsystem takes the desired shifter gear value from the user.
+Within the subsystem, the actual shifter gear changes to better reflect the desired gear.
+This actual shifter gear value is then the output of the shift subsystem.
  \begin{figure}[h]
@@
   \subsection{Speed Control Subsystem}
+  The speed control subsystem is a straightforward single-input single-output system.
+The desired vehicle speed is set by the user and sent to the speed control subsystem.
+Taking this input, the subsystem calculates the new vehicle speed.
+This value is then sent out to the rest of the vehicle system.
  \begin{figure}[h]

### 2021-12-08 proposal.tex
Added figures for system id example 2; Updated Work section of proposal.tex

--- 2021-12-08 proposal.tex
@@
  \begin{align*}
-   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t), 
+   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
  \end{align*}
@@
 $y(t)$ is the system output at time $t,$ while $u(t)$ is the input.
-\comment{}{Didn't you say, it was a two input, one output system?
-Where is the other input in the above equation, other than $u(t)$?} The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
+The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
 
@@
 
-\todo[inline]{Place MATLAB figures for this example here. }
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=5cm]{figs/img/example2Fig1}
+    \caption{}
+    \label{fig:ex2fig1}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=5cm]{figs/img/example2Fig2}
+    \caption{}
+    \label{fig:ex2fig2}
+  \end{subfigure}
+  \caption{\subref{fig:ex2fig1} State-space model of a MIMO system with a validation data comparison and \subref{fig:ex2fig2} State-space model of a MIMO system and system-sized based state-space model with a validation data comparison }
+  \label{fig:AstuffFleetSteeringSetup}
+\end{figure}
+
 \subsection{Example 3: Identify Linear Models Using the Command Line}
@@
 
-\section{Preliminary Work}
+\section{Main Project Work (Modeling Vehicle Subsystems)}
 To start this project, we first read documentation outlining the uses of MATLAB's System Identification Toolbox.
@@
 The data we collected will be used to generate and then verify our models.
+We collected data on the Lexus RX450H vehicle platform shown in \autoref{fig:exusvehicle}.
+
 \begin{figure}[h]
@@
 	{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}}
+	\label{fig:lexusvehicle}
 \end{figure}
 
- \subsection{Modeling} \label{sec:model}
- All modeling of vehicle subsystems will be done using Matlab's System Identification Toolbox feature.
-The subsystems can be grouped into four different categories: Single-Input Single-Output (SISO), Multiple-Input Multiple-Output (MIMO), Single-Input Multiple-Output (SIMO), and Multiple-Input Single-Output (MISO).
-
- \subsection{Parts List}
-	The following is the hardware required for this project:  
+\noindent The following is the hardware required for this project:  
 	\begin{itemize}
@@
  	\end{itemize}
-	The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+
+	\noindent The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
 This data is sent or received using the CANCase and CAN bus.
@@
 
-	The following is the software required for this project: 
+	\noindent The following is the software required for this project: 
 	\begin{itemize}
@@
  	\end{itemize}
- 	The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
+
+ 	\noindent The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
 This is how we were able to collect logs of data that we would use to develop models of the autonomous vehicle subsystems.
@@
 
-\subsection{Experimental Setup} \label{sec:setup}
-Each subsystem that we are modeling is set up in a similar manner.
+\noindent Each subsystem that we are modeling is set up in a similar manner.
 In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).

### 2021-12-09 proposal.tex
Updated proposal.tex

@@
   \subsection{Acceleration Subsystem}
-  The acceleration subsystem is a multiple-input multiple-output (MIMO) system.
+  The acceleration subsystem is a multiple-input multiple-output system. 
 Acceleration pedal voltages are sent to the subsystem. 
-A new acceleration pedal position value is generated to better match the real-time pedal position.
+A new acceleration pedal position value is generated to better match 
+the real-time pedal position. This is then the output 
+of the acceleration subsystem.
  \begin{figure}[h]
@@
   \subsection{Speed Subsystem}
+This speed subsystem would fall under the multiple-input single-output system.
+There are four inputs, the position of the acceleration pedal and the brake pedal, along with the shifter actual gear.
+Taking these inputs, the speed subsystem finds the vehicle speed.
+This vehicle speed is the output of the system.
  \begin{figure}[h]

### 2021-12-09 proposal.tex
Fixed typo

@@
 
- \subsection{Steeering Subsystem}
+ \subsection{Steering Subsystem}
 In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle.

### 2021-12-09 proposal.tex
Removed refernces to deleted figure

@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in \autoref{fig:subFunctionalBlock}.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
 Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
-Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.
+Some of the systems are multiple output and some are single output.
 

### 2022-01-24 proposal.tex
~

--- 2021-12-09 proposal.tex
@@
  \begin{align*}
-   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
+   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t), 
  \end{align*}
@@
 $y(t)$ is the system output at time $t,$ while $u(t)$ is the input.
-The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
+\comment{}{Didn't you say, it was a two input, one output system?
+Where is the other input in the above equation, other than $u(t)$?} The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/img/mimoExGrady}
-    \caption{Comparison of the state space model and merged SISO models with the validation data}
-    \label{fig:exMIMO}
-\end{figure}
+\todo[inline]{Place MATLAB figures for this example here. }
 
@@
 
-\begin{figure}[htbp]
-  \centering
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=5cm]{figs/img/example2Fig1}
-    \caption{}
-    \label{fig:ex2fig1}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=5cm]{figs/img/example2Fig2}
-    \caption{}
-    \label{fig:ex2fig2}
-  \end{subfigure}
-  \caption{\subref{fig:ex2fig1} State-space model of a MIMO system with a validation data comparison and \subref{fig:ex2fig2} State-space model of a MIMO system and system-sized based state-space model with a validation data comparison }
-  \label{fig:AstuffFleetSteeringSetup}
-\end{figure}
-
+\todo[inline]{Place MATLAB figures for this example here. }
 \subsection{Example 3: Identify Linear Models Using the Command Line}
@@
 was the most accurate, with a best fit percentage of 85.83\%.
-\begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/img/commandLineIO}
-    \caption{Inputs and outputs of the given system}
-    \label{fig:exIO}
-\end{figure}
+
+\todo[inline]{Place MATLAB figures for this example here. }
 
@@
 Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.
-
- \subsection{Steering Subsystem}
-In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle.
-This desired angle is entered by the user.
-$\theta$, the actual steering wheel angle, is subtracted from the desired steering wheel angle to find the error between the two positions.
-This error value is sent to the steering subsystem’s controller.
-Using this information, the controller generates torque voltages A and B, which are sent to the steering subsystem.
-New torque voltages are then generated and the actual steering wheel angle is updated.
-
- \begin{figure}[h]
+%
+%
+\begin{figure}[htb]
     \centering 
-    \captionsetup{justification=centering, margin=3cm}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-    \caption{Steering subsystem block diagram}
+  \caption{}
   \label{fig:steeringmodelarchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+  \caption{}
+  \label{fig:brakeModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\textwidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+  \caption{}
+  \label{fig:accelerationModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+  \caption{}
+  \label{fig:shiftModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+  \caption{}
+  \label{fig:speedControlModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+  \caption{}
+  \label{fig:speedModelArchitecture}
+\end{subfigure}
+\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+\label{fig:subFunctionalBlock}
 \end{figure}
-
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
-    \caption{Steering block diagram}
-    \label{fig:steeringModelBlockDiagram}
-\end{figure}
-
-  \subsection{Brake Subsystem}
-  The brake subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
-Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed.
-This boolean value indicates to the user whether or not the brake pedal is being pressed.
-The brake subsystem is another example of a multiple-input multiple-output system.
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-    \caption{Brake subsystem block diagram}
-    \label{fig:brakeModelArchitecture}
-\end{figure}
-
-  \subsection{Acceleration Subsystem}
-  The acceleration subsystem is a multiple-input multiple-output system. 
-Acceleration pedal voltages are sent to the subsystem. 
-A new acceleration pedal position value is generated to better match 
-the real-time pedal position. This is then the output 
-of the acceleration subsystem.
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-    \caption{Acceleration subsystem block diagram}
-    \label{fig:accelerationModelArchitecture}
-\end{figure}
-
-  \subsection{Shift Subsystem}
- This subsystem can be classified as a single-input single-output system.
-The subsystem takes the desired shifter gear value from the user.
-Within the subsystem, the actual shifter gear changes to better reflect the desired gear.
-This actual shifter gear value is then the output of the shift subsystem.
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-    \caption{Shift subsystem block diagram}
-    \label{fig:shiftModelArchitecture}
-\end{figure}
-
-  \subsection{Speed Subsystem}
-This speed subsystem would fall under the multiple-input single-output system.
-There are four inputs, the position of the acceleration pedal and the brake pedal, along with the shifter actual gear.
-Taking these inputs, the speed subsystem finds the vehicle speed.
-This vehicle speed is the output of the system.
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-    \caption{Speed subsystem block diagram}
-    \label{fig:speedModelArchitecture}
-\end{figure}
-
-  \subsection{Speed Control Subsystem}
-  The speed control subsystem is a straightforward single-input single-output system.
-The desired vehicle speed is set by the user and sent to the speed control subsystem.
-Taking this input, the subsystem calculates the new vehicle speed.
-This value is then sent out to the rest of the vehicle system.
- \begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-    \caption{Speed Control subsystem block diagram}
-    \label{fig:speedControlModelArchitecture}
-\end{figure}
-
-%\begin{figure}[htb]
-%    \centering 
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-%  \caption{}
-%  \label{fig:steeringmodelarchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-%  \caption{}
-%  \label{fig:brakeModelArchitecture}
-%\end{subfigure}
-%\\
-%\begin{subfigure}[b]{0.48\textwidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-%  \caption{}
-%  \label{fig:accelerationModelArchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-%  \caption{}
-%  \label{fig:shiftModelArchitecture}
-%\end{subfigure}
-%\\
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-%  \caption{}
-%  \label{fig:speedControlModelArchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-%  \caption{}
-%  \label{fig:speedModelArchitecture}
-%\end{subfigure}
-%\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-%\label{fig:subFunctionalBlock}
-%\end{figure}
+%
 
@@
 
-\section{Main Project Work (Modeling Vehicle Subsystems)}
-To start this project, we first read documentation outlining the uses of MATLAB's System Identification Toolbox.
-From there we worked on MATLAB tutorials on how to model systems from data using System Identification and then find the most accurate model.
-We specifically tried to find examples with Multiple-Input Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since most of the vehicle subsystems we will model fall into one of these categories.
-A literature review was also conducted to see how systems with small non-linearities like our steering subsystem were modeled using System Identification.
-On October 7th we traveled to AutonomouStuff in order to collect data from the steering, acceleration, and braking subsystems in an autonomous vehicle.
-The data we collected will be used to generate and then verify our models.
-We collected data on the Lexus RX450H vehicle platform shown in \autoref{fig:exusvehicle}.
-
+\section{Modeling Vehicle Subsystems}
+To start this project, we first read documentation outlining the uses of
+MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
+on how to model systems from data using System Identification and then find the
+most accurate model. We specifically tried to find examples with Multiple-Input
+Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
+most of the vehicle subsystems we will model fall into one of these categories.
+A literature review was also conducted to see how systems with small
+non-linearities like our steering subsystem were modeled using System
+Identification. On October 7th we traveled to AutonomouStuff in order to collect
+data from the steering, acceleration, and braking subsystems in an autonomous
+vehicle. The data we collected will be used to generate and then verify our
+models.
 \begin{figure}[h]
@@
 		{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}}
-	\label{fig:lexusvehicle}
 \end{figure}
 
-\noindent The following is the hardware required for this project:  
+ \subsection{Modeling} \label{sec:model}
+ All modeling of vehicle subsystems will be done using Matlab's System Identification Toolbox feature.
+The subsystems can be grouped into four different categories: Single-Input Single-Output (SISO), Multiple-Input Multiple-Output (MIMO), Single-Input Multiple-Output (SIMO), and Multiple-Input Single-Output (MISO).
+
+ \subsection{Parts List}
+	The following is the hardware required for this project:  
 	\begin{itemize}
@@
  	\end{itemize}
-
-	\noindent The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+	The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
 This data is sent or received using the CANCase and CAN bus.
@@
 
-	\noindent The following is the software required for this project: 
+	The following is the software required for this project: 
 	\begin{itemize}
@@
  	\end{itemize}
-
- 	\noindent The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
+ 	The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
 This is how we were able to collect logs of data that we would use to develop models of the autonomous vehicle subsystems.
@@
 
-\noindent Each subsystem that we are modeling is set up in a similar manner.
+\subsection{Experimental Setup} \label{sec:setup}
+Each subsystem that we are modeling is set up in a similar manner.
 In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).
@@
 \section{Validation and Testing} \label{sec:simresults}
-\subsection{Steering System}
-In \autoref{byWireSteerModel}, the output steering angle is plotted versus time when the vehicle is in by-wire mode.
-The figure shows the output steering angle from some data collected to depict the steering system behavior plotted with the behavior of the estimated model.
-The best fit percentage for this model is 85.54\%.
-Likewise, \autoref{manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode.
-The best fit percentage for this model is 90.27\%.
+\subsection{Steering Subsystem}
+In \autoref{byWireSteerModel}, the output steering angle is plotted versus time
+when the vehicle is in by-wire mode. The figure shows the output steering angle
+from some data collected to depict the steering system behavior plotted with the
+behavior of the estimated model. The best fit percentage for this model is
+85.54\%. Likewise, \autoref{manualSteerModel} depicts the output steering angle
+plotted versus time when the vehicle is in manual mode. The best fit percentage
+for this model is 90.27\%.
 

### 2022-01-31 proposal.tex
Update proposal.tex
I added the paragraphs about the spring 2022 deliverables to the proposal document.

--- 2021-12-09 proposal.tex
@@
 
-We plan on demonstrating our project for AutonomouStuff along with including a full report on how we modeled the vehicle subsystems.
+%We plan on demonstrating our project for AutonomouStuff along with including a full report on how we modeled the vehicle subsystems.
 As for the final report and presentation, we plan on working on it as soon as possible next semester.
 This presentation will also be shown to the Industrial Advisory Board.
+
+At the beginning of the spring semester we will present the work we have completed so far to Dr.
+Miah and to representatives from AutonomouStuff.
+This is to let them see how the project is progressing and what our plans are for this semester.
+
+Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the Shift, Speed Control, and Speed subsystems.
+We will make sure to collect a large amount of data in order to ensure that we will get accurate models.
+This process should only take a day.
+
+Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s Hardware in the Loop testbench.
+This allows us to see how our models will perform in the real world.
+Once these models have been tested, they will either be changed or kept as is.
+
+We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project.
+We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.
+
+Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff.
+This is an important demonstration since AutonomouStuff has sponsored this senior project and is waiting to see if we have solved the problem of creating accurate mathematical models for their vehicle subsystems.
+
+Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with.
+This presentation will be conducted in front of a faculty panel, along with AutonomouStuff representatives and other interested parties.
+It will be the culmination of everything we have done over the course of the year.
+
+The final report will sum up all of our efforts and findings for this project.
+It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data.
+We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.
+
+Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB.
+This will allow the board to see some of the projects that the senior class has been working on this year.
+Since the IAB plays a large role in choosing senior projects, it will be important to show them the progress we have made on one of the projects they selected.
 

### 2022-01-31 proposal.tex
~

--- 2021-12-09 proposal.tex
@@
 vehicle platform, but their reliability is lower than expected due to non-linear
-behaviors of the torque voltages required to control each subsystem. The scope
+behaviors of the torque voltages required to control each subsystem. \hl{The scope
 of this project includes developing mathematical models for each subsystem so
 AutonomouStuff can implement control systems that improve the reliability of the
-autonomous vehicle platform.
-These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
+autonomous vehicle platform.} These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
 Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
@@
 motor that will control the subsystem. In \autoref{fig:steerSystem}, the motor would
-turn the pinion arms which would change the steering angle of the vehicle. This
+turn the pinion arms\todo{Annotate in figure} which would change the steering angle of the vehicle. This
 principle is applied to all other subsystems.
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in \autoref{fig:subFunctionalBlock}.
 Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
-Some of the systems are multiple output and some are single output.
-
- \subsection{Steering Subsystem}
-In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle.
-This desired angle is entered by the user.
-$\theta$, the actual steering wheel angle, is subtracted from the desired steering wheel angle to find the error between the two positions.
-This error value is sent to the steering subsystem’s controller.
-Using this information, the controller generates torque voltages A and B, which are sent to the steering subsystem.
-New torque voltages are then generated and the actual steering wheel angle is updated.
-
- \begin{figure}[h]
+Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.
+%
+%
+\begin{figure}[htb]
     \centering 
-    \captionsetup{justification=centering, margin=3cm}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-    \caption{Steering subsystem block diagram}
+  \caption{}
   \label{fig:steeringmodelarchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+  \caption{}
+  \label{fig:brakeModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\textwidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+  \caption{}
+  \label{fig:accelerationModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering 
+  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+  \caption{}
+  \label{fig:shiftModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+  \caption{}
+  \label{fig:speedControlModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+  \centering
+  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+  \caption{}
+  \label{fig:speedModelArchitecture}
+\end{subfigure}
+\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+\label{fig:subFunctionalBlock}
 \end{figure}
+%
 
@@
 
+\section{Modeling Vehicle Subsystems}
+To start this project, we first read documentation outlining the uses of
+MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
+on how to model systems from data using System Identification and then find the
+most accurate model. We specifically tried to find examples with Multiple-Input
+Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
+most of the vehicle subsystems we will model fall into one of these categories.
+A literature review was also conducted to see how systems with small
+non-linearities like our steering subsystem were modeled using System
+Identification. On October 7th we traveled to AutonomouStuff in order to collect
+data from the steering, acceleration, and braking subsystems in an autonomous
+vehicle. The data we collected will be used to generate and then verify our
+models.
 \section{Main Project Work (Modeling Vehicle Subsystems)}
@@
 
-% The Gantt charts in Figures \ref{fig:gantt1} and \ref{fig:gantt2} show our planned schedule to complete this project.
-In these charts, there are four sections in each month represented by the dotted grid.
-This is to approximate a weekly schedule.
-Our first milestone is to complete the simulation of the system in MATLAB and CoppeliaSim.
-This includes simulating a remote as well as the robotic cart.
-The simulation of the RSSI detection will be handled in Matlab based on the positions of the cart and remote.
-We will add noise to the simulated RSSI in order to simulate the multipath effect.
-The expected functionality is that the cart will follow the remote.
+\begin{description}
+\item[Collect shift, speed control, and speed data] $\ldots$
 
-% The second milestone is to complete the assembly of both the cart and the remote.
-The cart assembly involves replacing the existing motors with the purchased motors, as well as mounting the stepper motor, reflector, and XBee on top of the robot.
-The assembly of the remote involves constructing the voltage regulator circuit.
+\item[Model shift system] $\ldots$
 
-% The third milestone is to integrate the subsystems into one system.
-This will involve testing the angle and distance estimation from the cart to the remote.
-It will also include testing the following capabilities of the overall system.
-We expect that this will require a large amount of debugging and tuning.
-Therefore, we have allotted several weeks for this purpose.
-
-% The fourth and final milestone is to complete the final report and presentation.
-This involves documenting our findings in a report and presenting our work.
-At this point, the project will be complete.
+\item[Model speed control system] $\ldots$
+\end{description}
 

### 2022-02-02 proposal.tex
Update proposal.tex
I updated the paragraphs for the spring 2022 deliverables and added some headings. I also updated the Gantt chart for the spring semester.

@@
      \gantttitle{Jan}{2}
-     \gantttitle{Feb}{4}
+     \gantttitle{Feb}{5}
      \gantttitle{Mar}{4}
@@
 %     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
-     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{3}{3}\\
-     \ganttbar[progress = 0]{Model Shift System}{3}{4}\\
-     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
-     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\
+     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{4}{4}\\
+     \ganttbar[progress = 0]{Model Shift, Speed Control, and Speed Subsystems}{4}{5}\\
+     \ganttbar[progress = 0]{Progress Presentation}{6}{6}\\
+%     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
+%     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\
 
 %     \ganttgroup[progress = 10]{Software}{5}{6}\\
-     \ganttbar[progress = 0]{Test Subsystems}{9}{12}\\
-     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{12}{15}\\
+     \ganttbar[progress = 0]{Test Subsystems}{6}{7}\\
+     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{7}{7}\\
+     \ganttbar[progress = 0]{AutonomouStuff Demo}{8}{9}\\
 
@@
      \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
-     \ganttbar[progress = 0]{Project Demo}{17}{17}\\
 
@@
 
-At the beginning of the spring semester we will present the work we have completed so far to Dr.
-Miah and to representatives from AutonomouStuff.
-This is to let them see how the project is progressing and what our plans are for this semester.
+\begin{description}
+\item[Progress presentation] 
+We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project.
+We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.
 
-Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the Shift, Speed Control, and Speed subsystems.
+\item[Collect shift, speed control, and speed data] 
+Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the shift, speed control, and speed subsystems.
 We will make sure to collect a large amount of data in order to ensure that we will get accurate models.
@@
 
+\item[Model shift, speed control, and speed subsystems] 
+Once we have collected the necessary data from the Lexus vehicle, we will work on developing individual mathematical models for each subsystem.
+We will be using MATLAB’s System Identification Toolbox in order to try out different models and see which best represents each subsystem.
+These models will first be tested by us, and if they pass they will then be tested using AutonomouStuff’s HIL testbench.
+
+\item[Test subsystems] 
+Before we do any HIL testing, we will first work on testing the models ourselves in order to ensure that they are accurate.
+We are still determining the best way to test these models, but this is an important step since we do not want to take inaccurate models to be tested using the HIL testbench.
+Using an inaccurate model would cause us to lose time that could have been spent coming up with a better one.
+
+\item[Test subsystems with HIL] 
 Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s Hardware in the Loop testbench.
@@
 
-We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project.
-We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.
-
+\item[AutonomouStuff demonstration] 
 Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff.
@@
 
+\item[Final report] 
+The final report will sum up all of our efforts and findings for this project.
+It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data.
+We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.
+
+\item[Final presentation] 
 Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with.
@@
 
-The final report will sum up all of our efforts and findings for this project.
-It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data.
-We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.
-
+\item[Presentation to IAB] 
 Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB.
@@
 
-\begin{description}
-\item[Collect shift, speed control, and speed data] $\ldots$
-
-\item[Model shift system] $\ldots$
-
-\item[Model speed control system] $\ldots$
 \end{description}

### 2022-02-02 proposal.tex
Updated proposal.tex
Added section about using only manual mode data

@@
 motor that will control the subsystem. In \autoref{fig:steerSystem}, the motor would
-turn the pinion arms\todo{Annotate in figure} which would change the steering angle of the vehicle. This
+turn the pinion arms which would change the steering angle of the vehicle. This
 principle is applied to all other subsystems.
@@
 Using this toolbox, we are able to use the logs of data we collected to create sets of estimation and validation data that will be used for training the model.
+\\
 
@@
 The ECU and PAC Mod are not shown in \autoref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
+\\
+%
+\\
+\noindent Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze data for the by-wire mode and manual mode individually.
+This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems are operating in.
+After analyzing the models we developed, we determined that these models are not interchangeable as there were differences in the model.
+When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor.
+Because of this, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
+For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems.
+For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
 

### 2022-02-02 proposal.tex
Update proposal.tex

@@
 \\
-\noindent Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze data for the by-wire mode and manual mode individually.
-This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems are operating in.
-After analyzing the models we developed, we determined that these models are not interchangeable as there were differences in the model.
+\noindent Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
+This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in.
+After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models.
 When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor.
-Because of this, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
+As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
 For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems.
@@
      bar progress label anchor = east,
-     ]{1}{18}
+     ]{1}{19}
      %\gantttitle{2021}{18}\\
@@
 \begin{description}
-\item[Progress presentation] 
+\item[Progress presentation]: 
 We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project.
-We will be evaluated on our ability to demonstrate that we are making progress on the project and will be able to complete the goals that we set.
+We will be evaluated on our ability to demonstrate that we are making progress on the project and on our ability to complete the goals that we set.
 
-\item[Collect shift, speed control, and speed data] 
-Once we have satisfactorily modeled the Steering, Acceleration, and Brake systems, we will then travel to AutonomouStuff and collect the necessary data for the shift, speed control, and speed subsystems.
-We will make sure to collect a large amount of data in order to ensure that we will get accurate models.
+\item[Collect shift, speed control, and speed data]: 
+Once we have satisfactorily modeled the steering, acceleration, and brake systems, we will then travel to AutonomouStuff and collect the necessary data for the shift, speed control, and speed subsystems.
+We will make sure to collect a large amount of data to work with.
 This process should only take a day.
 
-\item[Model shift, speed control, and speed subsystems] 
+\item[Model shift, speed control, and speed subsystems]: 
 Once we have collected the necessary data from the Lexus vehicle, we will work on developing individual mathematical models for each subsystem.
@@
 
-\item[Test subsystems] 
+\item[Test subsystems]: 
 Before we do any HIL testing, we will first work on testing the models ourselves in order to ensure that they are accurate.
@@
 
-\item[Test subsystems with HIL] 
-Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s Hardware in the Loop testbench.
+\item[Test subsystems with HIL]: 
+Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s HIL testbench.
 This allows us to see how our models will perform in the real world.
@@
 
-\item[AutonomouStuff demonstration] 
+\item[AutonomouStuff demonstration]: 
 Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff.
@@
 
-\item[Final report] 
+\item[Final report]: 
 The final report will sum up all of our efforts and findings for this project.
@@
 
-\item[Final presentation] 
+\item[Final presentation]: 
 Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with.
 This presentation will be conducted in front of a faculty panel, along with AutonomouStuff representatives and other interested parties.
-It will be the culmination of everything we have done over the course of the year.
+It will be the culmination of everything we have done over the course of our senior year.
 
-\item[Presentation to IAB] 
+\item[Presentation to IAB]: 
 Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB.

### 2022-02-02 proposal.tex
Update proposal.tex
I removed highlighting from some text in section one of the proposal document.

@@
 vehicle platform, but their reliability is lower than expected due to non-linear
-behaviors of the torque voltages required to control each subsystem. \hl{The scope
+behaviors of the torque voltages required to control each subsystem. The scope
 of this project includes developing mathematical models for each subsystem so
 AutonomouStuff can implement control systems that improve the reliability of the
-autonomous vehicle platform.} These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
+autonomous vehicle platform.
+These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
 Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.

### 2022-02-09 proposal.tex
Update proposal.tex
I made changes to the introduction of the proposal document. I also added a section to talk about the brake system modeling.

@@
 Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
-for both manual-drive mode and by-wire, or autonomous, mode.
+By developing models for these vehicle subsystems, this allows AutonomouStuff to save money and time that would normally be spent on vehicle maintenance.
+This is the first time that the company will have a model of one of their vehicles.
+There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
+Originally, models were created for the steering and acceleration subsystems in both manual and by-wire mode.
+However, as the project progressed, it was decided that only models in manual mode needed to be created.
+The controller handles most of the self-driving characteristics, and since the subsystem models will be used to develop new controllers, it doesn’t make sense to model the present controllers if they are going to change.
 \autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
@@
 %
+%
 
@@
 \end{table}
+
+\subsection{Brake System}
+
+%
+
+%
+
+%
+
+%
+
+%
+
 %

### 2022-02-09 proposal.tex
Updated labNotebook.tex and proposal.tex

--- 2022-02-02 proposal.tex
@@
 Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
-for both manual-drive mode and by-wire, or autonomous, mode.
+By developing models for these vehicle subsystems, this allows AutonomouStuff to save money and time that would normally be spent on vehicle maintenance.
+This is the first time that the company will have a model of one of their vehicles.
+
 \autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each

### 2022-02-17 reportTII-ArticleHIL.tex
~

--- 2022-02-02 proposal.tex
@@
-\documentclass[letterpaper,12pt]{article}   %%% Can be report
-
-%% set paper margins
-\oddsidemargin=0.1in
-\evensidemargin=0.1in
-\textwidth=6.0in
-\topmargin=-0.7in
-\textheight=9.0in
-\parindent=0.2in
-
-\usepackage{amsmath,amssymb,bm}
+\documentclass[journal,twoside,web]{ieeecolor}
+\usepackage{generic}
+\usepackage{amsmath,amssymb,amsfonts,bm}
 \usepackage{graphicx}
 \usepackage{rotating}
-%\usepackage{subfigure}
-\usepackage[width=11cm,font=footnotesize,labelfont=bf, %
-format=default,justification=centerlast]{caption} % Figure caption text customization
+% \usepackage{subfigure}
+\usepackage[format=default,justification=centerlast]{caption} % Figure caption text customization
 
@@
 \usepackage{siunitx}
-%\sisetup{unitsep=\cdot}
+% \sisetup{unitsep=\cdot}
+% \usepackage{textcomp}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\markboth{\journalname, VOL. XX, NO. XX, XXXX}
+{Author \MakeLowercase{\textit{et al.}}: Title}
+\begin{document}
+\title{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}
+\author{First A. Author, \IEEEmembership{Fellow, IEEE}, Second B. Author, and Third C. Author, Jr., \IEEEmembership{Member, IEEE}
+\thanks{This paragraph of the first footnote will contain the date on 
+which you submitted your paper for review. It will also contain support 
+information, including sponsor and financial support acknowledgment. For 
+example, ``This work was supported in part by the U.S. Department of 
+Commerce under Grant BS123456.'' }
+\thanks{The next few paragraphs should contain 
+the authors' current affiliations, including current address and e-mail. For 
+example, F. A. Author is with the National Institute of Standards and 
+Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov). }
+\thanks{S. B. Author, Jr., was with Rice University, Houston, TX 77005 USA. He is 
+now with the Department of Physics, Colorado State University, Fort Collins, 
+CO 80523 USA (e-mail: author@lamar.colostate.edu).}
+\thanks{T. C. Author is with 
+the Electrical Engineering Department, University of Colorado, Boulder, CO 
+80309 USA, on leave from the National Research Institute for Metals, 
+Tsukuba, Japan (e-mail: author@nrim.go.jp).}
+}
 
-\title{ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\
-\vspace{0.5in}
-Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle 
-\vspace{1.0in}
-\author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}
-}
-%\date{February 6, 2003}  No need to write, Date will be automatically on the title page
-\date{}  % Do not show date on the title page
-
-%%%%%%%%%%%%%%%%% Set document line spacing %%%%%%%%%%%%%%%%%%%%%
-\singlespacing
-% \onehalfspacing
-% \doublespacing
-% all packages are in the following tex file.
-% \input{paper-preamble.tex}
-\begin{document}
-
-%%% Make title page 
-\begin{titlepage}
 \maketitle
 
-  \vspace*{4.0cm}
-  \begin{center}
-    \normalsize
-    Electrical and Computer Engineering Department\\
-    Caterpillar College of Engineering and Technology\\
-\href{http://www.bradley.edu/}{Bradley University}\\
+\begin{abstract}
+These instructions give you guidelines for preparing papers for 
+IEEE Transactions and Journals. Use this document as a template if you are 
+using \LaTeX. Otherwise, use this document as an 
+instruction set. The electronic file of your paper will be formatted further 
+at IEEE. Paper titles should be written in uppercase and lowercase letters, 
+not all uppercase. Avoid writing long formulas with subscripts in the title; 
+short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
+not write ``(Invited)'' in the title. Full names of authors are preferred in 
+the author field, but are not required. Put a space between authors' 
+initials. The abstract must be a concise yet comprehensive reflection of 
+what is in your article. In particular, the abstract must be self-contained, 
+without abbreviations, footnotes, or references. It should be a microcosm of 
+the full article. The abstract must be between 150--250 words. Be sure that 
+you adhere to these limits; otherwise, you will need to edit your abstract 
+accordingly. The abstract must be written as one paragraph, and should not 
+contain displayed mathematical equations or tabular material. The abstract 
+should include three or four different keywords or phrases, as this will 
+help readers to find it. It is important to avoid over-repetition of such 
+phrases as this can result in a page being rejected by search engines. 
+Ensure that your abstract reads well and is grammatically correct.
+\end{abstract}
 
-\vspace*{3.0cm}
-\copyright~H.~Grady~and~N.~Nauman, Peoria, IL, USA, 2021\\
-
-\end{center}
-\thispagestyle{empty}
-
-\end{titlepage} 
-%%%%%%%%%%%%
-%\thispagestyle{empty}
-%\maketitle
-\newpage
-\renewcommand{\contentsname}{Table of Contents}
-\tableofcontents
-\newpage
+\begin{IEEEkeywords}
+Enter key words or phrases in alphabetical 
+order, separated by commas. For a list of suggested keywords, send a blank 
+e-mail to keywords@ieee.org or visit \underline
+{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
+\end{IEEEkeywords}
 
 \section{Introduction}
-Autonomous vehicles are being developed by many companies for commercial and
+\label{sec:introduction}
+\IEEEPARstart{A}{utonomous} vehicles are being developed by many companies for commercial and
 personal use. These autonomous vehicles (see the AutonomouStuff vehicle fleet
-shown in \autoref{fig:fleet}) would allow companies to continue crucial deliveries
+shown in Fig.~\ref{fig:fleet}) would allow companies to continue crucial deliveries
 or transports of their products even if there is a shortage of drivers. In
@@
 
-\vspace*{12pt}
+% \vspace*{12pt}
 
@@
 for both manual-drive mode and by-wire, or autonomous, mode.
-\autoref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
+Fig.~\ref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
 subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. In \autoref{fig:steerSystem}, the motor would
+motor that will control the subsystem. In Fig.~\ref{fig:steerSystem}, the motor would
 turn the pinion arms which would change the steering angle of the vehicle. This
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.48\linewidth}
+  \begin{subfigure}[b]{0.45\linewidth}
     \centering
@@
     \centering
-    \captionsetup{justification=centering, margin=3cm}
+    % \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/img/mimoExGrady}
@@
   \end{subfigure}
+  \\
   \begin{subfigure}[b]{0.48\linewidth}
@@
     \centering
-    \captionsetup{justification=centering, margin=3cm}
+    % \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/img/commandLineIO}
@@
 For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle.
-The non-linear behavior is depicted in \autoref{fig:nonlinGraph}.
+The non-linear behavior is depicted in Fig.~\ref{fig:nonlinGraph}.
     \end{itemize}
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in \autoref{fig:subFunctionalBlock}.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in Fig.~\ref{fig:subFunctionalBlock}.
 Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
-Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.
+Some of the systems are multiple output and some are single output as depicted in Fig.~\ref{fig:subFunctionalBlock}.
 %
@@
 \end{subfigure}
+\\
 \begin{subfigure}[b]{0.48\linewidth}
@@
     \centering
-    \captionsetup{justification=centering, margin=3cm}
+    % \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
@@
     \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+    % \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=0.48\textwidth]{figs/inkscape/speedControlModelArchitecture}
     \caption{Speed Control subsystem block diagram}
@@
 
-%\begin{figure}[htb]
-%    \centering 
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-%  \caption{}
-%  \label{fig:steeringmodelarchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-%  \caption{}
-%  \label{fig:brakeModelArchitecture}
-%\end{subfigure}
-%\\
-%\begin{subfigure}[b]{0.48\textwidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-%  \caption{}
-%  \label{fig:accelerationModelArchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-%  \caption{}
-%  \label{fig:shiftModelArchitecture}
-%\end{subfigure}
-%\\
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-%  \caption{}
-%  \label{fig:speedControlModelArchitecture}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-%  \caption{}
-%  \label{fig:speedModelArchitecture}
-%\end{subfigure}
-%\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-%\label{fig:subFunctionalBlock}
-%\end{figure}
+\begin{figure}[htb]
+   \centering 
+\begin{subfigure}[b]{0.48\linewidth}
+ \centering 
+ \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+ \caption{}
+ \label{fig:steeringmodelarchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+ \centering
+ \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+ \caption{}
+ \label{fig:brakeModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\textwidth}
+ \centering 
+ \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+ \caption{}
+ \label{fig:accelerationModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+ \centering 
+ \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+ \caption{}
+ \label{fig:shiftModelArchitecture}
+\end{subfigure}
+\\
+\begin{subfigure}[b]{0.48\linewidth}
+ \centering
+ \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+ \caption{}
+ \label{fig:speedControlModelArchitecture}
+\end{subfigure}
+\begin{subfigure}[b]{0.48\linewidth}
+ \centering
+ \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+ \caption{}
+ \label{fig:speedModelArchitecture}
+\end{subfigure}
+\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+\label{fig:subFunctionalBlock}
+\end{figure}
 
@@
  \begin{itemize}
-    \item The steering subsystem will be modeled first due to its non-linearities, depicted in \autoref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
+    \item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
     \item The steering subsystem will be able to handle small steering angles
@@
 The data we collected will be used to generate and then verify our models.
-We collected data on the Lexus RX450H vehicle platform shown in \autoref{fig:exusvehicle}.
-
-\begin{figure}[h]
+We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:exusvehicle}.
+%
+%
+\begin{figure}
 	\centering
-	\captionbox{AutonomouStuff Lexus RX450H Vehicle}
-	{\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}}
+	\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\caption{AutonomouStuff Lexus RX450H vehicle.}
 	\label{fig:lexusvehicle}
@@
 Instead, the PACMod ECU built by AutonomouStuff sends the torque voltages to the motor using relays.
-In \autoref{fig:vehicleSetup}, the experimental setup for data collection is shown.
+In Fig.~\ref{fig:vehicleSetup}, the experimental setup for data collection is shown.
 The laptop is used to collect the data from the desired vehicle subsystem by the use of Vector's CANAlyzer software.
 The CAN Case collects data from the PAC Mod and ECU and sends the data using a CAN bus to the laptop which is then parsed and displayed through the use of CANAlyzer.
-The ECU and PAC Mod are not shown in \autoref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
+The ECU and PAC Mod are not shown in Fig.~\ref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
 \\
@@
 	\centering
-    	\captionsetup{justification=centering, margin=3cm}
-    	\includegraphics[width=5in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    	% \captionsetup{justification=centering, margin=3cm}
+    	\includegraphics[width=.48\textwidth]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
     	\caption{Autonomous Vehicle Data Collection Setup}
@@
 \subsection{Steering Subsystem}
-In \autoref{byWireSteerModel}, the output steering angle is plotted versus time
+In Fig.~\ref{byWireSteerModel}, the output steering angle is plotted versus time
 when the vehicle is in by-wire mode. The figure shows the output steering angle
@@
 behavior of the estimated model. The best fit percentage for this model is
-85.54\%. Likewise, \autoref{manualSteerModel} depicts the output steering angle
+85.54\%. Likewise, Fig.~\ref{manualSteerModel} depicts the output steering angle
 plotted versus time when the vehicle is in manual mode. The best fit percentage
@@
 The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
-\autoref{tab:byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.%
+Table~\ref{tab:byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.%
 %
@@
 
-\noindent \autoref{tab:byWireSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.%
+\noindent Table~\ref{tab:byWireSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.%
 %
@@
 is clear that a twentieth order transfer function is the best estimation of the
-system. \autoref{tab:manualSteerCoeffA} shows the coefficients of the twentieth
+system. Table~\ref{tab:manualSteerCoeffA} shows the coefficients of the twentieth
 order transfer function for the output steering angle with respect to the input
@@
 
-\noindent \autoref{tab:manualSteerCoeffB} shows the coefficients of
+\noindent Table~\ref{tab:manualSteerCoeffB} shows the coefficients of
 the twentieth order transfer function for the output steering angle with respect
@@
 The twenty-fourth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
-\autoref{tab:manualAccelCoeffA} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage A signal.
+Table~\ref{tab:manualAccelCoeffA} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage A signal.
 %
@@
 
-\noindent \autoref{tab:manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.%
+\noindent Table~\ref{tab:manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.%
 %
@@
 
-\section{Timeline and Milestones} \label{sec:timeline}
-
-The Gantt chart highlighting the progress and potential schedule of the project in Fall 2021 is shown in Figure~\ref{fig:gantt1}.
-
- \begin{figure}
-   \centering
-   \begin{ganttchart}[
-     hgrid,
-     vgrid,
-     x unit=.6cm,
-     y unit title=.8cm,
-     y unit chart=.6cm,
-     milestone label font=\tiny,
-     milestone progress label font = \tiny,
-     milestone progress label anchor = east,
-     bar label font=\tiny,
-     group label font=\small,
-     bar/.append style={fill=green},
-     bar incomplete/.append style={fill=red},
-     group progress label font = \tiny,
-     progress label text={$\displaystyle#1\%$},
-     group progress label anchor = east,
-     bar progress label font = \tiny,
-     bar progress label anchor = east,
-     ]{1}{17}
-
-%     \gantttitle{2020}{17}\\
-     \gantttitle{Sep}{4}
-     \gantttitle{Oct}{4}
-     \gantttitle{Nov}{4}
-     \gantttitle{Dec}{4}
-     \gantttitle{}{1}\\
-
-%     \ganttgroup[progress = 100]{Research}{3}{12} \\
-     \ganttbar[progress = 100]{Read System Identification Documentation}{3}{6}\\
-     \ganttbar[progress = 100]{Collect Steering, Acceleration, and Braking Data}{6}{7}\\
-
-%     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
-     \ganttbar[progress = 100]{System Identification Tutorials}{4}{7}\\
-     \ganttbar[progress = 100]{System Functional Requirements Document}{4}{9}\\
-          \ganttbar[progress = 100]{System Functional Requirements Presentation}{4}{9}\\
-
-     \ganttbar[progress = 100]{Parts Order Request}{8}{12}\\
-     \ganttbar[progress = 100]{Proposal Document}{9}{15}\\
-     \ganttbar[progress = 100]{Proposal Presentation}{9}{15}\\
-
-%     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
-     \ganttmilestone[progress = 100]{Model Steering System}{13}{14}\\
-     \ganttbar[progress = 100]{Model Acceleration System}{14}{15}\\
-     \ganttbar[progress = 100]{Model Braking System}{15}{15}\\
-
-   \end{ganttchart}
- \caption{Gantt chart for Fall 2021}
- \label{fig:gantt1}
- \end{figure}
-
-The potential schedule for our project in Spring 2022 is highlighted in the gantt chart shown in Figure~\ref{fig:gantt2}.
-
- \begin{figure}
-   \centering
-   \begin{ganttchart}[
-     hgrid,
-     vgrid,
-     x unit=.6cm,
-     y unit title=.8cm,
-     y unit chart=.6cm,
-     milestone label font=\tiny,
-     milestone progress label font = \tiny,
-     milestone progress label anchor = east,
-     bar label font=\tiny,
-     group label font=\small,
-     bar/.append style={fill=green},
-     bar incomplete/.append style={fill=red},
-     group progress label font = \tiny,
-     progress label text={$\displaystyle#1\%$},
-     group progress label anchor = east,
-     bar progress label font = \tiny,
-     bar progress label anchor = east,
-     ]{1}{19}
-     %\gantttitle{2021}{18}\\
-     \gantttitle{Jan}{2}
-     \gantttitle{Feb}{5}
-     \gantttitle{Mar}{4}
-     \gantttitle{Apr}{4}
-     \gantttitle{May}{4}\\
-
-%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
-     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{4}{4}\\
-     \ganttbar[progress = 0]{Model Shift, Speed Control, and Speed Subsystems}{4}{5}\\
-     \ganttbar[progress = 0]{Progress Presentation}{6}{6}\\
-%     \ganttbar[progress = 0]{Model Speed Control System}{5}{6}\\
-%     \ganttbar[progress = 0]{Model Speed System}{7}{8}\\
-
-%     \ganttgroup[progress = 10]{Software}{5}{6}\\
-     \ganttbar[progress = 0]{Test Subsystems}{6}{7}\\
-     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{7}{7}\\
-     \ganttbar[progress = 0]{AutonomouStuff Demo}{8}{9}\\
-
-%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
-     \ganttmilestone[progress = 0]{Final Report}{15}{15}\\
-     \ganttmilestone[progress = 0]{Final Presentation}{16}{16}\\
-     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
-
-%     \ganttmilestone[progress = 0]{Project Complete}{17}
-   \end{ganttchart}
-   \caption{Gantt Chart for Spring 2022}
-   \label{fig:gantt2}
- \end{figure}
-
-	Our Gantt charts shown in Figures \ref{fig:gantt1} and \ref{fig:gantt2} outline our project work and milestones for the year.
-While we are still working on the details, we plan on splitting the work equally to make sure that we each get a chance to learn from this project and to keep it fair for all team members.
-
-The first milestone on our list will be to model the steering system.
-This will be a challenge due to its small non-linearities around very small steering angle changes.
-The next milestone will be to test our subsystem models on AutonomouStuff's HIL system.
-This is one of the most important milestones because the company sponsors our project and we are working to help solve one of their problems.
-Our last two milestones will be to present our work in the form of a final report and presentation.
-This is where all of our work will come together and we will get a chance to explain how we solved the problem.
-
-%We plan on demonstrating our project for AutonomouStuff along with including a full report on how we modeled the vehicle subsystems.
-As for the final report and presentation, we plan on working on it as soon as possible next semester.
-This presentation will also be shown to the Industrial Advisory Board.
-
-\begin{description}
-\item[Progress presentation]: 
-We will create a presentation that outlines the work that we have completed up to this point as well as what we intend to complete for the remaining time of the project.
-We will be evaluated on our ability to demonstrate that we are making progress on the project and on our ability to complete the goals that we set.
-
-\item[Collect shift, speed control, and speed data]: 
-Once we have satisfactorily modeled the steering, acceleration, and brake systems, we will then travel to AutonomouStuff and collect the necessary data for the shift, speed control, and speed subsystems.
-We will make sure to collect a large amount of data to work with.
-This process should only take a day.
-
-\item[Model shift, speed control, and speed subsystems]: 
-Once we have collected the necessary data from the Lexus vehicle, we will work on developing individual mathematical models for each subsystem.
-We will be using MATLAB’s System Identification Toolbox in order to try out different models and see which best represents each subsystem.
-These models will first be tested by us, and if they pass they will then be tested using AutonomouStuff’s HIL testbench.
-
-\item[Test subsystems]: 
-Before we do any HIL testing, we will first work on testing the models ourselves in order to ensure that they are accurate.
-We are still determining the best way to test these models, but this is an important step since we do not want to take inaccurate models to be tested using the HIL testbench.
-Using an inaccurate model would cause us to lose time that could have been spent coming up with a better one.
-
-\item[Test subsystems with HIL]: 
-Once we have modeled our subsystems, we will then take these models and test them using AutonomouStuff’s HIL testbench.
-This allows us to see how our models will perform in the real world.
-Once these models have been tested, they will either be changed or kept as is.
-
-\item[AutonomouStuff demonstration]: 
-Around the time we test the subsystems using HIL, we will also demonstrate what we have worked on to representatives from AutonomouStuff.
-This is an important demonstration since AutonomouStuff has sponsored this senior project and is waiting to see if we have solved the problem of creating accurate mathematical models for their vehicle subsystems.
-
-\item[Final report]: 
-The final report will sum up all of our efforts and findings for this project.
-It will contain all of the information so that readers will be able to understand how we generated the models and how we collected the necessary data.
-We will make sure to detail the steps we took and especially how we dealt with the non-linearity considerations for the steering system.
-
-\item[Final presentation]: 
-Similarly to the fall semester, we will give a complete presentation of the work we have done on this project and the resulting models we have come up with.
-This presentation will be conducted in front of a faculty panel, along with AutonomouStuff representatives and other interested parties.
-It will be the culmination of everything we have done over the course of our senior year.
-
-\item[Presentation to IAB]: 
-Near the end of the semester we will be presenting our work on this project to the Industrial Advisory Board, or IAB.
-This will allow the board to see some of the projects that the senior class has been working on this year.
-Since the IAB plays a large role in choosing senior projects, it will be important to show them the progress we have made on one of the projects they selected.
-
-\end{description}
-
-\section{Concluding Remarks}
-Autonomous vehicles have a numerous amount of useful applications in today's society.
-From being used for delivering packages to allowing drivers to rest while traveling, as the technology for autonomous vehicles is enhanced, they will become an enticing product that many consumers will purchase and use.
-One of the biggest concerns with autonomous vehicles today is the risk associated with public safety.
-One solution to reducing the safety risk is ensuring that accurate controllers are developed to reliably control each subsystem involved with the movement of the autonomous vehicle.
-Due to non-linear behaviors, there is no simple solution for developing reliable controllers.
-This project will focus on deriving models of some main subsystems so that these non-linear behaviors are removed and smooth controllers can be developed.
-
-\pagebreak
 \bibliographystyle{IEEEtran}
@@
 
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.eps}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
+% biographies. Biographies are often not included in conference-related
+% papers. This author became a Member (M) of IEEE in 1976, a Senior
+
+%
+% Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
+% contain a place and/or date of birth (list place, then date). Next,
+% the author's educational background is listed. The degrees should be
+% listed with type of degree in what field, which institution, city,
+% state, and country, and year the degree was earned. The author's major
+% field of study should be lower-cased.
+
+% The second paragraph uses the pronoun of the person (he or she) and not the 
+% author's last name. It lists military and work experience, including summer 
+% and fellowship jobs. Job titles are capitalized. The current job must have a 
+% location; previous positions may be listed 
+% without one. Information concerning previous publications may be included. 
+% Try not to list more than three books or published articles. The format for 
+% listing publishers of a book within the biography is: title of book 
+% (publisher name, year) similar to a reference. Current and previous research 
+% interests end the paragraph. The third paragraph begins with the author's 
+% title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
+% List any memberships in professional societies other than the IEEE. Finally, 
+% list any awards and work for IEEE committees and publications. If a 
+% photograph is provided, it should be of good quality, and 
+% professional-looking. Following are two examples of an author's biography.
+% \end{IEEEbiography}
+
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.eps}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
+% 1977. He received the B.S. and M.S. degrees in aerospace engineering from 
+% the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
+% mechanical engineering from Drexel University, Philadelphia, PA, in 2008.
+
+% From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
+% Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
+% Mechanical Engineering Department, Texas A{\&}M University, College Station. 
+% He is the author of three books, more than 150 articles, and more than 70 
+% inventions. His research interests include high-pressure and high-density 
+% nonthermal plasma discharge processes and applications, microscale plasma 
+% discharges, discharges in liquids, spectroscopic diagnostics, plasma 
+% propulsion, and innovation plasma applications. He is an Associate Editor of 
+% the journal \emph{Earth, Moon, Planets}, and holds two patents.
+
+% Dr. Author was a recipient of the International Association of Geomagnetism 
+% and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
+% Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
+% \end{IEEEbiography}
+
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.eps}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
+% engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
+% and the M.S. degree in mechanical engineering from National Tsing Hua 
+% University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
+% degree in mechanical engineering at Texas A{\&}M University, College 
+% Station, TX, USA.
+
+% From 2008 to 2009, he was a Research Assistant with the Institute of 
+% Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
+% development of surface processing and biological/medical treatment 
+% techniques using nonthermal atmospheric pressure plasmas, fundamental study 
+% of plasma sources, and fabrication of micro- or nanostructured surfaces.
+
+% Mr. Author's awards and honors include the Frew Fellowship (Australian 
+% Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
+% Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
+% Award and the Adolph Lomb Medal (OSA).
+% \end{IEEEbiography}
+
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2022-02-18 reportTII-ArticleHIL.tex
Report template updated

@@
 \graphicspath{%
-  {figs/ipe/}
-  {figs/dia/}
   {figs/matlab/}
-  {figs/imag/}
 }
@@
 \usepackage{tikz}
-\usetikzlibrary{positioning,fit}
+% \usetikzlibrary{calc,tikzmark}
+\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
 
@@
   \centering
-  \begin{subfigure}[b]{0.48\linewidth}
+  \begin{subfigure}[b]{0.40\linewidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.45\linewidth}
+  \begin{subfigure}[b]{0.40\linewidth}
     \centering
@@
  %
- \begin{align*}
-   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
- \end{align*}
+ \begin{multline*}
+   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = \\
+   b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
+ \end{multline*}
 % 
@@
 %
-\begin{figure}[htb]
+\begin{figure}[htbp]
   \centering
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering 
-  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-  \caption{}
-  \label{fig:steeringmodelarchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering
-  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-  \caption{}
-  \label{fig:brakeModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\textwidth}
-  \centering 
-  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-  \caption{}
-  \label{fig:accelerationModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering 
-  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-  \caption{}
-  \label{fig:shiftModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering
-  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-  \caption{}
-  \label{fig:speedControlModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
-  \centering
-  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-  \caption{}
-  \label{fig:speedModelArchitecture}
-\end{subfigure}
-\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-\label{fig:subFunctionalBlock}
+  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
+  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
+  \label{fig:highLevelSystemArchitecture}
 \end{figure}
-%
+% \begin{figure}[htb]
+%     \centering 
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+%   \caption{}
+%   \label{fig:steeringmodelarchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%   \caption{}
+%   \label{fig:brakeModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\textwidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+%   \caption{}
+%   \label{fig:accelerationModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+%   \caption{}
+%   \label{fig:shiftModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+%   \caption{}
+%   \label{fig:speedControlModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+%   \caption{}
+%   \label{fig:speedModelArchitecture}
+% \end{subfigure}
+% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+% \label{fig:subFunctionalBlock}
+% \end{figure}
+% %
+
+\subsection{Steering Subsystem}
+\label{sec:steeringSubsystem}
+
+The steering subsystem consists of steering, the power steering motors, $\ldots$ The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
+Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
+The block diagram of the control system designed for this subsystem is shown in Fig.~
 
@@
   \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
-    \caption{Steering block diagram}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
+    \tikzstyle{sum} = [draw, circle,fill=orange!15]
+    % place nodes
+    \node[sum](sum){$\sum$};
+    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
+    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
+    \draw[-stealth,thick]
+    (sum.east)--node[midway,above]{Error}(steeringController);
+    \draw[-stealth,thick]
+    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
+    \draw[-stealth,thick]
+    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
+    \draw[-stealth,thick]
+    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
+    \fill
+    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
+    \draw[-stealth,thick]
+    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
+
+  \end{tikzpicture}
+  % \captionsetup{justification=centering, margin=3cm}
+  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
+  \caption{Steering subsystem block diagram.}
   \label{fig:steeringModelBlockDiagram}
@@
 The brake subsystem is another example of a multiple-input multiple-output system.
- \begin{figure}[h]
+ \begin{figure}[htbp]
     \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (brakeSubsystem.150)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.-150)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.15)--node[pos=0.5,above]{Pedal position}++(1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.-15)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
     \caption{Brake subsystem block diagram}
@@
 
-\begin{figure}[htb]
-   \centering 
-\begin{subfigure}[b]{0.48\linewidth}
- \centering 
- \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
- \caption{}
- \label{fig:steeringmodelarchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
- \centering
- \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
- \caption{}
- \label{fig:brakeModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\textwidth}
- \centering 
- \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
- \caption{}
- \label{fig:accelerationModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
- \centering 
- \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
- \caption{}
- \label{fig:shiftModelArchitecture}
-\end{subfigure}
-\\
-\begin{subfigure}[b]{0.48\linewidth}
- \centering
- \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
- \caption{}
- \label{fig:speedControlModelArchitecture}
-\end{subfigure}
-\begin{subfigure}[b]{0.48\linewidth}
- \centering
- \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
- \caption{}
- \label{fig:speedModelArchitecture}
-\end{subfigure}
-\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-\label{fig:subFunctionalBlock}
-\end{figure}
+% \begin{figure}[htb]
+%    \centering 
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+%  \caption{}
+%  \label{fig:steeringmodelarchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%  \caption{}
+%  \label{fig:brakeModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\textwidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+%  \caption{}
+%  \label{fig:accelerationModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+%  \caption{}
+%  \label{fig:shiftModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+%  \caption{}
+%  \label{fig:speedControlModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+%  \caption{}
+%  \label{fig:speedModelArchitecture}
+% \end{subfigure}
+% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+% \label{fig:subFunctionalBlock}
+% \end{figure}
 

### 2022-02-26 progressPresentation.tex
Create Progress Presentation
Using the proposal presentation as a guide, I created a new slideshow for the progress presentation.

--- 2021-11-19 proposalPres.tex
@@
 % % A subtitle is optional and this may be deleted
-\subtitle{Modeling, Simulation, and Testing}
+\subtitle{Progress Presentation}
 
@@
 
-\date[November~18,~2021]{Thursday, November~18,~2021}
+\date[March~1,~2022]{Tuesday, March~1,~2022}
 
@@
 \begin{frame}{Introduction}{}
-    \begin{block}{Applications of Autonomous Vehicles}
+    \begin{block}{}
     	\begin{itemize}
-    		\item Autonomous vehicles are being developed by many companies for commercial and personal use
-    		\item Modeling different subsystems (such as, steering, brake,
-          acceleration, $\ldots$)  for autonomous vehicles is a challenging task
-     		\item Models for autonomous vehicle subsystems must be very accurate due to safety factors
-		\end{itemize}
-    \end{block}
-        \begin{figure}
-			\centering
-			\begin{minipage}[t]{0.4\textwidth}
-				\centering
-				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesAStuff}
-				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
-				\label{fig:fleet}
-			\end{minipage}
-			\begin{minipage}[t]{0.4\textwidth}
-				\centering
-				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesSteering}
-				\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
-				\label{fig:steerSystem}
-			\end{minipage}
-        \end{figure}
-    \begin{tiny}
-		\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
-    \end{tiny}
-\end{frame}
-
-\begin{frame}{Problem Statement}
-  \begin{block}{Problem Statement}
-      Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
-      \begin{itemize}
-          \item Steering
-          \item Acceleration
-          \item Brake
-          \item Shift
-          \item Speed
-          \item Speed control
-        \end{itemize} 
-        using input-output raw data available offline
-
-          \begin{figure}
-			\centering
-			\begin{minipage}[t]{0.4\textwidth}
-				%\centering
-
-				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
-				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
-
-			\end{minipage}
-			\end{figure}
-  \end{block}
-
-  \pause
-  \begin{block}{Proposed Solution}
-    \begin{large}
-      A potential solution is to develop conventional System Identification techniques for modeling subsystems using available raw data.  
-    \end{large}
-  \end{block}
-\end{frame}
-
-%----------------------------------
-
-\section{Literature Review}
-
-\begin{frame}{Literature Review}
-  \begin{block}{Existing Solutions}
- \begin{itemize}
-        \item Use of System Identification Toolbox in MATLAB to create models from data~\cite{Adnan2010}
-	 \begin{itemize}
-     \tiny
-		    		\item Offers a variety of model choices
-				\item Needs a large amount of raw data to produce an accurate model
-	\end{itemize}
-	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
-	 \begin{itemize}
-     \tiny
-		    		\item Allows the use of traditional analysis methods to create a model 
-				\item More room for error during calculations
-	\end{itemize}
-	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
-	 \begin{itemize}
-     \tiny
-		    		\item Can model systems with small non-linearities 
-				\item Mechanical components replaced by electrical components 
-	\end{itemize}
-	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
-	\begin{itemize}
-    \tiny
-		\item Fourth order ARX model ended up giving the best fit
-	\end{itemize}
-\end{itemize}
-  \end{block}
-    % \begin{figure}[b]
-    %     \centering
-    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
-    %     \caption{CompaRob}
-    %     %\label{fig:sysBlockDiag}
-    % \end{figure}
-\end{frame}
-
-%----------------------------------
-
-\section{System Requirements}
-
-\begin{frame}{System Requirements}
-	\tiny  
-  \begin{block}{Specifications}
-    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
-\begin{itemize}
-    \item Resulting plant model will consist of reasonably accurate subsystem models
-    \item Subsystems can be used to create a HIL testbench
-    \item Steering model can handle very small changes in steering angles
-    \begin{itemize}
-		\tiny    		
-    		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
-    \end{itemize}
-\end{itemize}
-\begin{figure}[h]
-	\tiny    
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=1in]{figs/inkscape/nonlinearBehavior}
-    \caption{Steering Non-linear Behavior}
-    \label{fig:nonlinGraph}
-\end{figure}
-  \end{block}
-\end{frame}
-
-%--------------------------------
-
-\section{System Architecture}
-
-\begin{frame}{System Architecture}
-  \begin{block}{System Architecture}
-    \begin{large}
-      The overall system architecture of this project consists of six subsystems: 
-      \begin{itemize}
-          \item Steering
-          \item Acceleration
-          \item Brake %Model
-          \item Shift %Model
-          \item Speed %Model
-          \item Speed control %Model
-        \end{itemize} 
-    \end{large}
-  \end{block}
-\end{frame}
-
-\begin{frame}{System Architecture}
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
-\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System \item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
-\end{frame}
-
-\begin{frame}{System Architecture}
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
-\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
-\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
-\end{frame}
-
-\begin{frame}{System Architecture}
-\begin{figure}[h]
-    \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=4in]{figs/inkscape/steeringModelBlockDiagram}
-    \caption{Steering System Block Diagram}
-    \label{fig:steerBlockDiag}
-\end{figure}
-\end{frame}
-
-\begin{frame}{System Inputs and Outputs}
-\begin{minipage}[t]{0.48\linewidth}
-\tiny
-	\begin{block}{System Inputs}
-		\begin{itemize}
-			\tiny
-		    \item Steering Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Torque Voltages
-		    		\begin{itemize}
-		    		\tiny
-		    			\item Desired Steering Wheel Angle
-		    			\item Actual Steering Wheel Angle
-		    		\end{itemize}
-		    \end{itemize}
-		    \item Acceleration Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Acceleration Pedal Voltages
-		    \end{itemize}
-		    \item Brake Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Brake Pedal Pressure Voltages
-		    		\item Brake Pedal Stroke Voltages 
-		    		\item Brake Pedal On/Off Switch
-		    \end{itemize}
-		    \item Shift Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Desired Shift Gear
-		    \end{itemize}
-		    \item Speed Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Acceleration Pedal Position
-		    		\item Brake Pedal Position
-		    		\item Shifter Actual Gear
-		    \end{itemize}
-		    \item Speed Control Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Desired Vehicle Speed
-		    \end{itemize}
-		\end{itemize}
-	\end{block}
-\end{minipage}%
-\hfill%
-\begin{minipage}[t]{0.48\linewidth}
-\begin{block}{System Outputs}
-		\begin{itemize}
-			\tiny
-		    \item Steering Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Wheel Angle
-		    		\item Actual Steering Angle
-		    \end{itemize}
-		    \item Acceleration Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Acceleration Pedal Position
-		    \end{itemize}
-		    \item Brake Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Brake Pedal Position
-		    		\item Brake Pressed
-		    \end{itemize}
-		    \item Shift Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Actual Shift Gear
-		    \end{itemize}
-		    \item Speed Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Vehicle Speed
-		    \end{itemize}
-		    \item Speed Control Model
-		    \begin{itemize}
-		    \tiny
-		    		\item Vehicle Speed
-		    \end{itemize}
-		\end{itemize}
-	\end{block}
-\end{minipage}
-\end{frame}
-
-%----------------------------------
-
-\section{System Identification}
-
-\begin{frame}{System Identification}
-  \begin{block}{System Identification}
- \begin{itemize}
-        \item Developing mathematical models for a dynamic system
-        \item Uses the measurement of the input and output signals
-        \begin{itemize}
-        		\item Single Input Single Output (SISO)
-        		\item Single Input Multiple Output (SIMO)
-        		\item Multiple Input Single Output (MISO)
-        		\item Multiple Input Multiple Output (MIMO)
-        \end{itemize}
-        \item Achieve an accurate estimation of the system response for any given input
-        \item Mathworks' MATLAB System Identification Toolbox
-\end{itemize}
-  \end{block}
-\end{frame}
-
-\subsection{Preliminary Work}
-
-\begin{frame}{Preliminary Work}
-  \begin{block}{Preliminary Work}
- \begin{itemize}
-        \item Documentation on MATLAB's System Identification Toolbox and tutorials
-        \item Literature Review 
-        \item Data Collection for steering, braking and acceleration subsystems
-\end{itemize}
-  \end{block}
-
-   \begin {block}{MATLAB Example: Dealing with Multi-Variable Systems: Identification and Analysis}
-  \begin{itemize}
-  	\item  Learned how to create an iddata object from a given data set 
-  	\item Created a state space model and compared it to the validation data 
-  	\item Tried creating submodels for some of the channels in order to try and get a better fit 
-  	\item Then created a MISO model and learned how to merge the two SISO models that were created earlier 
-  	\end{itemize}
-  	\end{block}
-
-\end{frame}
-
-%----------------------------------
-\subsection{Experimental Setup}
-
-\begin{frame}{Experimental Setup}
-	\begin{block}{Control Method}
-		\begin{itemize}
-			\item Manual Mode
-			\begin{itemize}
-				\item Vehicle is not autonomous
-				\item Torque voltages are sent by the ECU
-			\end{itemize}
-			\item By-Wire Mode
-			\begin{itemize}
-				\item Vehicle is autonomous
-				\item Torque voltages are sent by the PACMod
-				\item Torque voltages sent from the ECU are discarded by open-circuiting the motors
-			\end{itemize}
-		\end{itemize}
-		\begin{figure}
-			\centering
-    			\captionsetup{justification=centering, margin=3cm}
-    			\includegraphics[width=1in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
-    			\caption{Autonomous Vehicle Data Collection Setup}
-    			\label{fig:vehicleSetup}
-		\end{figure}
-	\end{block}
-\end{frame}
-
-%----------------------------------
-\subsection{Parts List}
-
-\begin{frame}{Parts List}
-  \begin{block}{Software and Hardware}
- \begin{itemize}
-        \item Software
-        \begin{itemize}
-        \small
-        \item MATLAB's System Identification Toolbox
-        \item Vector CANAlyzer
-        \end{itemize}
-	\item Hardware
-	\begin{itemize}
-	\small
-	\item Laptop
-	\item PACMod ECU
-	\item CANCase 
-	\item CAN bus
-	\end{itemize}
-\end{itemize}
-  \end{block}
-\end{frame}
-
-%----------------------------------
-\subsection{Modeling}
-
-\begin{frame}{Model Equations}
-	\begin{block}{Model Equations}
-		\begin{itemize}
-			\item Transfer Function Model: 
-			\begin{equation}
-				\frac{Y(s)}{U_A(s)} = \frac{b_{n}s^{n} + b_{n-1}s^{n-1} + ... + b_1s + b_0}{a_{m}s^{m} + a_{m-1}s^{m-1} + ... + a_1s + a_0}
-			\end{equation}
-			where m = number of poles and n = number of zeros
-			\item ARX Model: 
-			\begin{equation}
-				A(z)y(t) = B(z)u(t) + e(t)
-			\end{equation}
-		\end{itemize}
-	\end{block}
-\end{frame}
-
-\begin{frame}{Model Equations}
-	\tiny	
-	\begin{block}{ARX Model MATLAB Representation}
-		The polynomial equation for an ARX Model is:
-		\begin{equation}
-			y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)
-		\end{equation}
-		where na, nb, and nk are the system’s number of poles, number of zeros, and the system dead time, respectively
-		MATLAB represents the ARX Model with the following equation:
-		\begin{equation}
-			A(z)y(t) = B(z)u(t - n_k) + e(t)
-		\end{equation}
-		where z is a delay operator and 
-		\begin{equation}
-			A(z) = 1 + a_1z^{-1} + ... + a_{na}z^{-n_a}
-		\end{equation}
-		\begin{equation}
-			B(z) = b_1 + b_2z^{-1} + ... + b_{nb}z^{-n_b}
-		\end{equation}
-		For MISO systems, MATLAB uses the following equation to represent the ARX Model:
-		\begin{equation}
-			A(z)y(t) = B_1(z)u_1(t - nk_{1}) + B_2(z)u_2(t - nk_{2}) + ... + B_{nu}(z)u_{nu}(t - nk_{nu})
-		\end{equation}
-		where nu is the number of system inputs
-	\end{block}
-\end{frame}
-
-%----------------------------------
-\section{Validation and Testing}
-
-\begin{frame}{Simulation Results}
-  \begin{block}{Steering System}
- \begin{itemize}
-	\item Best fit percentage of the by-wire steering estimated model is 85.54
-	\item Best fit percentage of the manual steering estimated model is 90.27
- \end{itemize}
- \begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-        \caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireSteerModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
-        \caption{Output of Estimated Manual System Model}
-        \label{fig:manualSteerModel}
-    \end{minipage}
-\end{figure}
-  \end{block}
-\end{frame}
-
-\begin{frame}{By-Wire Steering System Transfer Function}
-
-\begin{block}{Torque Voltage A}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
-      \midrule
-      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
-      \bottomrule
-    \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
-      \midrule
-      3.44E-16 & -2.203E-15 & 1.24E-13 & 5.975E-13 & 3.001E-12 & 5.23E-12\\
-      \bottomrule
-    \end{tabular}}
-\end{block}
-\begin{block}{Torque Voltage B}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
-      \midrule
-      2.92E-15 & 2.758E-13 & 1.761E-11 & 4.228E-10 & 1.422E-8 & 1.561E-7 & 1.501E-6 & 8.426E-6 & 5.981E-5 & 0.0002016 & 0.001226 & 0.002649 & 0.01456 & 0.02044 & 0.104 & 0.09228 & 0.4417 & 0.2257 & 1.025 & 0.2305 & 1\\
-      \bottomrule
-    \end{tabular}}
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
-      \midrule
-      -6.645E-15 & 2.161E-14 & -2.605E-14 & -4.744E-13 & -1.813E-13 & -4.858E-12\\
-      \bottomrule
-    \end{tabular}}
-\end{block}  
-\end{frame}
-
-\begin{frame}{Manual Steering System Transfer Function}
-
-\begin{block}{Torque Voltage A}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
-      \midrule
-      1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
-      \bottomrule
-    \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
-      \midrule
-      6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
-      \bottomrule
-    \end{tabular}}
-\end{block}
-\begin{block}{Torque Voltage B}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
-      \midrule
-      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
-      \bottomrule
-    \end{tabular}}
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{21}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
-      \midrule
-      1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
-      \bottomrule
-    \end{tabular}}
-\end{block}
-\end{frame}
-
-\begin{frame}{Simulation Results}
-  \begin{block}{Acceleration System}
- \begin{itemize}
-	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
-	\item Best fit percentage of the manual acceleration estimated model is 98.3
- \end{itemize}
- \begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
-        \caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireAccelModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
-        \caption{Output of Estimated Manual System Model}
-        \label{fig:manualAccelModel}
-    \end{minipage}
-\end{figure}
-  \end{block}
-\end{frame}
-
-\begin{frame}{By-Wire Acceleration System Transfer Function}
-	\begin{block}{Fourth-Order ARX Model}
-		\begin{equation}
-			A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
-		\end{equation}
-		%
-		where na = 4, nb = 4, nk = 0, and, 
-		%
-		\begin{equation}
-			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
-		\end{equation}
-		\begin{equation}
-			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
-		\end{equation}
-		\begin{equation}
-			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
-		\end{equation}
-	\end{block}
-\end{frame}
-
-\begin{frame}{Manual Acceleration System Transfer Function}
-\begin{block}{Torque Voltage A}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{25}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
-      \midrule
-      2.307E7 & 8.369E7 & 9.137E8 & 1.992E9 & 3.753E9 & 5.454E9 & 5.548E9 & 5.869E9 & 3.453E9 & 3.161E9 & 1.54E9 & 9.654E8 & 3.556E8 & 1.789E8 & 5.082E7 & 2.071E7 & 4.569E6 & 1.498E6 & 2.553E5 & 6.532E4 & 8443 & 1559 & 147.3 & 15.5 & 1\\
-      \bottomrule
-    \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{7}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
-      \midrule
-      -5.741E6 & -2.644E7 & -2.797E6 & -1.304E7 & -3.203E6 & -1.159E6 & -5.519E5\\
-      \bottomrule
-    \end{tabular}}
-\end{block}
-\begin{block}{Torque Voltage B}
-	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{25}{c}}
-      \toprule
-      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
-      \midrule
-      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
-      \bottomrule
-    \end{tabular}}
-
-    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
-    \begin{tabular}{*{7}{c}}
-      \toprule
-      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
-      \midrule
-      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
-      \bottomrule
-    \end{tabular}}
-\end{block}
-\end{frame}
-
-%----------------------------------
-\section{Timeline and Milestones}
-
-\begin{frame}{Timeline and Milestones}
-  \begin{block}{Milestones}
- \begin{itemize}
-        \item Model steering subsystem 
-	\item Test subsystem models with HIL system 
-	\item Final report and presentation 
-\end{itemize}
-  \end{block}
-
-  \begin{block}{Timeline}
-  \begin{itemize}
-  \item Fall Semester
-  \begin{itemize}
-	\begin{tiny}
-	\item System Identification Documentation 
-	\item Collect Steering, Acceleration, and Brake Data 
-	\item System Identification Tutorials
-	\item System Functional Requirements Document and Presentation
-	\item Proposal Document and Presentation 
-	\item Model Steering, Acceleration, and Brake Subsystems 
-	\end{tiny}
-	\end{itemize}
-	\item Spring Semester
-	\begin{itemize}
-	\begin{tiny}
-	\item Collect Shift, Speed Control, and Speed Data  
-	\item Model Shift, Speed Control, and Speed Subsystems  
-	\item Test Subsystems
-	\item Test Subsystems with HIL
-	\item Final Report and Presentation 
-	\item IAB Presentation 
-	\item Project Demonstration  
-	\end{tiny}
-	\end{itemize}
+    		\item 
 		\end{itemize}
@@
 
-%\begin{frame}{Other Considerations}
-%  \begin{block}{Factors}
-%  	\begin{small}
-%      \begin{itemize}
-%        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
-%and driving fatalities and injuries. As a result, people will be able to live longer and
-%healthier lives. By creating accurate models, we will help advance the development of
-%autonomous vehicles and make this a reality.
-%		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle.
-We will address this by creating a rigorous test plan for our models.
-%		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
-%ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
-%		\item Global Factors: 
-%		\item Cultural Factors: 
-%		\item Social Factors: 
-%		\item Environmental Factors: 
-%		\item Business Factors: 
-%		\item Economic Factors: 
-%      \end{itemize}
-%     \end{small}
-%  \end{block}
-%\end{frame}
+\section{Steering Subsystem}
+
+\begin{frame}{Steering Subsystem}
+  \begin{block}{}
+ \begin{itemize}
+        \item 
+	\end{itemize}
+
+  \end{block}
+
+\end{frame}
+
+%----------------------------------
+
+\section{Acceleration Subsystem}
+
+\begin{frame}{Acceleration Subsystem}
+  \begin{block}{}
+ \begin{itemize}
+        \item 
+	\end{itemize}
+
+  \end{block}
+
+\end{frame}
+
+%--------------------------------
+
+\section{Brake Subsystem}
+
+\begin{frame}{Brake Subsystem}
+  \begin{block}{Brake Model}
+ \begin{itemize}
+        \item System Identification Toolbox
+        \item Neural Net Time Series Toolbox
+	\end{itemize}
+
+  \end{block}
+
+\end{frame}
 
@@
 \begin{frame}{Concluding Remarks}
-  \begin{block}{Project goals}
+  \begin{block}{Semester goals}
     %\begin{LARGE}
       \begin{itemize}
-        \item Develop reliable and accurate models of an autonomous vehicle's subsystems 
-        \item Help further the work on autonomous vehicle development
-%        \begin{itemize}
-%          \item Steering %  Model
-%          \item Acceleration % Model
-%          \item Brake % Model
-%          \item Shift % Model
-%          \item Speed % Model
-%          \item Speed control %Model
-%        \end{itemize}
+        \item 
       \end{itemize}
@@
     \begin{itemize}
-      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes of command inputs, such as steering angle
+      \item 
     \end{itemize}

### 2022-02-28 progressPresentation.tex
Updated references, progressPresentation, and added result figures

@@
     	\begin{itemize}
-    		\item 
+    		\item Modeled
+			\begin{itemize}
+				\item Steering Subsystem
+    				\item Acceleration Pedal Subsystem
+    				\item Brake Pedal Subsystem
+			\end{itemize}			    			
+    		\item Not Modeled
+			\begin{itemize}
+				\item Shift Subsystem
+    				\item Speed Subsystem
+    				\item Speed Control Subsystem
+			\end{itemize}			    			
+    		\item Manual Data vs. By-Wire Data
+    		\item Neural Network Modeling \cite{Zhou2019} \cite{matlabNeuralNet}
 		\end{itemize}
@@
 	\begin{block}{}
- \begin{itemize}
-        \item 
-	\end{itemize}
-
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item Only a few samples are just outside of the accuracy requirements
+			\item Transfer function model did not meet the accuracy requirements
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
 	\end{block}
-
 \end{frame}
@@
 	\begin{block}{}
- \begin{itemize}
-        \item 
-	\end{itemize}
-
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item All samples within 2\% of the actual output
+			\item Transfer function model did not have the same accuracy bounds
+			\item Fewer concerns about connections in Simulink
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
 	\end{block}
-
 \end{frame}
@@
   \begin{block}{Semester goals}
-    %\begin{LARGE}
       \begin{itemize}
-        \item 
+        \item Test our modeled subsystems on the HIL bench
+        \item Collect data for the remaining subsystems
+        \item Model the remaining subsystems and test on the HIL bench
+        \item Create final report highlighting our findings
+        \item Present our findings
       \end{itemize}
-    %\end{LARGE}
   \end{block}
@@
       \begin{itemize}
-      \item 
+      	\item Having time to model the remaining subsystems
+      	\item Needing to correct any models
       \end{itemize}
@@
 \section{References}
-
-%\begin{frame}{References}
-%  \bibliographystyle{IEEEtran}
-%   \begin{itemize}
-%     \item N. Rawashdeh, R. Haddad, O. Jadallah, and A. To’ma, “A person-following
-% robotic cart controlled via a smartphone application: design and evaluation,”
-% 09 2017, pp. 1–5.
-%     \item M. M. Islam, A. Lam, H. Fukuda, Y. Kobayashi, and Y. Kuno, “An intelligent
-% shopping support robot: understanding shopping behavior from 2d skeleton data using gru network,” ROBOMECH Journal, vol. 6, no. 1, 2019.
-%     \item J. Sales, J. Marti, R. Marin Prades, E. Cervera, and P. Sanz, “Comparob: The
-% shopping cart assistance robot,” International Journal of Distributed Sensor Networks, vol. 2016, pp. 1–15, 02 2016.
-%     \item M. S. Miah, J. Knoll, and K. Hevrdejs, “Intelligent range-only mapping and navigation for mobile robots,” IEEE Transactions on Industrial Informatics, vol. 14, no. 3, pp. 1164–1174, 2018.
-%     \item D. Li and S. Lane, “A novel and versatile parabolic reflector that significantly
-% improves wi-fi reception at different distances and angles,” 2013.
-
-%   \end{itemize}
-
-% \end{frame}
-
-%----------------------------------
-
 \begin{frame}[allowframebreaks]{References}
@@
   \bibliography{bib/references.bib}
-
-%\begin{itemize}
-%\item
-%@INPROCEEDINGS{Donjaroennon2021,
-%  author={Donjaroennon, Natthapon and Nuchkum, Suphatchakan and Leeton, Uthen},
-%  booktitle={2021 9th International Electrical Engineering Congress (iEECON)}, 
-%  title={Mathematical model construction of DC Motor by closed-loop system Identification technique Using Matlab/Simulink}, 
-%  year={2021},
-%  volume={},
-%  number={},
-%  pages={289-292},
-%  doi={10.1109/iEECON51072.2021.9440305}}
-%\end{itemize}
-% 	\begin{itemize}
-% 		\item T. Xie, H. Jiang, X. Zhao, and C. Zhang, “A wi-fi-based wireless indoor position sensing system with multipath interference mitigation,” Sep 2019. [Online].
-% Available: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6767237/
-% 		\item A. M. Ladd, K. E. Bekris, A. Rudys, L. E. Kavraki, and D. S. Wallach, “Robotics-
-% based location sensing using wireless ethernet,” Wireless Networks, vol. 11, no. 1-2, p. 189–204, 2005.
-% 		\item M. Lindhe, K. Johansson, and A. Bicchi, “An experimental study of exploiting multipath fading for robot communications,” Robotics: Science and Systems III, 2007.
-% 		\item M. Lindhe and K. Johansson, “Using robot mobility to exploit multipath fading,”Wireless Communications, IEEE, vol. 16, pp. 30 – 37, 03 2009.
-% 	\end{itemize}
 

### 2022-03-01 progressPresentation.tex
progressPresentation update
Progress presentation update
Progress Presentation update

@@
 \begin{frame}{Brake Subsystem}
-  \begin{block}{Brake Model}
- \begin{itemize}
-        \item System Identification Toolbox
-        \item Neural Net Time Series Toolbox
-	\end{itemize}
+  \begin{block}{}
+\begin{figure}[H]
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item All samples within 2\% of the actual output
+			\item Transfer function model did not have the same accuracy bounds
+			\item Fewer concerns about connections in Simulink
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
+  		\end{figure}
 

### 2022-03-01 progressPresentation.tex
Progress Presentation Update
I added some text to the brake slide of the progress presentation

@@
 \begin{figure}[H]
-  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock.jpg}\quad%
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item All samples within 2\% of the actual output
-			\item Transfer function model did not have the same accuracy bounds
-			\item Fewer concerns about connections in Simulink
+			\item With this model, the error is kept below 5\%
+			\item Able to easily track model performance
+			\item Provides better results than the transfer function model
 			\end{itemize} \end{minipage}\\[1em]

### 2022-03-02 reportTII-ArticleHIL.tex
Update reportTII-ArticleHIL.tex

@@
 \begin{abstract}
-These instructions give you guidelines for preparing papers for 
-IEEE Transactions and Journals. Use this document as a template if you are 
-using \LaTeX. Otherwise, use this document as an 
-instruction set. The electronic file of your paper will be formatted further 
-at IEEE. Paper titles should be written in uppercase and lowercase letters, 
-not all uppercase. Avoid writing long formulas with subscripts in the title; 
-short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
-not write ``(Invited)'' in the title. Full names of authors are preferred in 
-the author field, but are not required. Put a space between authors' 
-initials. The abstract must be a concise yet comprehensive reflection of 
-what is in your article. In particular, the abstract must be self-contained, 
-without abbreviations, footnotes, or references. It should be a microcosm of 
-the full article. The abstract must be between 150--250 words. Be sure that 
-you adhere to these limits; otherwise, you will need to edit your abstract 
-accordingly. The abstract must be written as one paragraph, and should not 
-contain displayed mathematical equations or tabular material. The abstract 
-should include three or four different keywords or phrases, as this will 
-help readers to find it. It is important to avoid over-repetition of such 
-phrases as this can result in a page being rejected by search engines. 
-Ensure that your abstract reads well and is grammatically correct.
+This report presents the results of modeling vehicle systems and testing them using Hardware-in-the-Loop (HIL).
+First, data was collected for each system using a Lexus RX450H vehicle.
+After data collection, models were developed in order to accurately simulate the physical vehicle system.
+MATLAB’s System Identification Toolbox was initially used to create these models.
+However, the transfer function models it provided weren’t able to accurately represent these systems and their non-linear behaviors.
+After this was established, modeling was done using MATLAB’s Neural Network Time Series application.
+Once a Neural Network model was created, it was then exported to Simulink and modified to be able to run without the use of the Deep Learning toolbox.
+These models gave much more accurate results when compared to the transfer function models developed using the System Identification Toolbox.
+(Add section about testing and results).
+
+%These instructions give you guidelines for preparing papers for 
+%IEEE Transactions and Journals. Use this document as a template if you are 
+%using \LaTeX. Otherwise, use this document as an 
+%instruction set. The electronic file of your paper will be formatted further 
+%at IEEE. Paper titles should be written in uppercase and lowercase letters, 
+%not all uppercase. Avoid writing long formulas with subscripts in the title; 
+%short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
+%not write ``(Invited)'' in the title. Full names of authors are preferred in 
+%the author field, but are not required. Put a space between authors' 
+%initials. The abstract must be a concise yet comprehensive reflection of 
+%what is in your article. In particular, the abstract must be self-contained, 
+%without abbreviations, footnotes, or references. It should be a microcosm of 
+%the full article. The abstract must be between 150--250 words. Be sure that 
+%you adhere to these limits; otherwise, you will need to edit your abstract 
+%accordingly. The abstract must be written as one paragraph, and should not 
+%contain displayed mathematical equations or tabular material. The abstract 
+%should include three or four different keywords or phrases, as this will 
+%help readers to find it. It is important to avoid over-repetition of such 
+%phrases as this can result in a page being rejected by search engines. 
+%Ensure that your abstract reads well and is grammatically correct.
 \end{abstract}
@@
 %
+\subsection{Brake System}
 

### 2022-03-02 reportTII-ArticleHIL.tex
Updated reportTII-ArticleHIL.tex

--- 2022-02-18 reportTII-ArticleHIL.tex
@@
 the vehicle should be controlled.
-Within the scope of this project and to expedite the modeling process, a commercially available modeling tool, called system identification toolbox, is used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belong to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
 The first subsystem we will model is the steering model, and then we will move onto
@@
 autonomous vehicle platform.
-These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
+These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
 Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
 Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
-for both manual-drive mode and by-wire, or autonomous, mode.
-Fig.~\ref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
+There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
+Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
 subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. In Fig.~\ref{fig:steerSystem}, the motor would
+motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
 turn the pinion arms which would change the steering angle of the vehicle. This
@@
   \centering
-  \begin{subfigure}[b]{0.40\linewidth}
+  \begin{subfigure}[b]{0.48\linewidth}
     \centering
-    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesAStuff}
+    \includegraphics[height=3cm]{figs/img/autonomousVehiclesAStuff}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.40\linewidth}
+  \begin{subfigure}[b]{0.48\linewidth}
     \centering
-    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesSteering}
+    \includegraphics[height=3cm]{figs/img/autonomousVehiclesSteering}
     \caption{}
-    \label{fig:steerSystem}
+    \label{fig:steerOverview}
   \end{subfigure}
-  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerSystem} steering model setup (courtesy of AutonomouStuff). }
+  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerOverview} steering model setup (courtesy of AutonomouStuff). }
   \label{fig:AstuffFleetSteeringSetup}
 \end{figure}
-
-% \noindent \begin{tiny}
-% 	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
-% \end{tiny}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
 \label{sec:sysID-Example2}
-This example~\cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example~\cite{Matlab2} discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
   \centering
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=5cm]{figs/img/example2Fig1}
+  \begin{subfigure}[b]{\linewidth}
+    \includegraphics[height=4.25cm]{figs/img/example2Fig1}
     \caption{}
@@
   \\
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=5cm]{figs/img/example2Fig2}
+  \begin{subfigure}[b]{\linewidth}
+    \includegraphics[height=4.25cm]{figs/img/example2Fig2}
     \caption{}
@@
   \caption{\subref{fig:ex2fig1} State-space model of a MIMO system with a validation data comparison and \subref{fig:ex2fig2} State-space model of a MIMO system and system-sized based state-space model with a validation data comparison }
-  \label{fig:AstuffFleetSteeringSetup}
+  \label{fig:ex2}
 \end{figure}
@@
 was the most accurate, with a best fit percentage of 85.83\%.
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
 \begin{itemize}
-    \item The resulting plant model will consist of accurate subsystem models
-    \item The subsystems can be used to create an HIL testbench
-    \item The steering model can handle very small changes in steering angles
-    \begin{itemize}
-    		\item The steering model should have a very smooth, continuous output as a choppy, discontinuous output would translate into difficulty tracking the vehicle in a straight line for instances such as keeping the vehicle in its lane.
-For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle.
-The non-linear behavior is depicted in Fig.~\ref{fig:nonlinGraph}.
+    \item The resulting plant model will consist of accurate subsystem models, as defined above
+    \item The subsystems can be used to create a HIL testbench
+    \item The subsystems can handle very small changes in values accurately
 \end{itemize}
-\end{itemize}
-\begin{figure}[h]
+
+All of the subsystems have nonlinear behaviors when there are small changes in the output of the subsystem.
+The steering subsystem, for example, should behave in a smooth, continuous manner.
+However, AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
+These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer and smoother manner.
+
+\begin{figure}[htbp]
     \centering
-    \captionsetup{justification=centering, margin=3cm}
+    \captionsetup{justification=centering}
     \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in Fig.~\ref{fig:subFunctionalBlock}.
-Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
-Some of the systems are multiple output and some are single output as depicted in Fig.~\ref{fig:subFunctionalBlock}.
-%
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
+Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
+For each subsystem, every input that is a torque voltage is actually two torque voltage signals, thus can not be treated as a single input.
+Also, each subsystem will be treated as a single output system.
+The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based  on the other output's behavior.
 %
@@
 \end{figure}
-% \begin{figure}[htb]
-%     \centering 
-% \begin{subfigure}[b]{0.48\linewidth}
-%   \centering 
-%   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-%   \caption{}
-%   \label{fig:steeringmodelarchitecture}
-% \end{subfigure}
-% \\
-% \begin{subfigure}[b]{0.48\linewidth}
-%   \centering
-%   \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-%   \caption{}
-%   \label{fig:brakeModelArchitecture}
-% \end{subfigure}
-% \\
-% \begin{subfigure}[b]{0.48\textwidth}
-%   \centering 
-%   \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-%   \caption{}
-%   \label{fig:accelerationModelArchitecture}
-% \end{subfigure}
-% \begin{subfigure}[b]{0.48\linewidth}
-%   \centering 
-%   \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-%   \caption{}
-%   \label{fig:shiftModelArchitecture}
-% \end{subfigure}
-% \\
-% \begin{subfigure}[b]{0.48\linewidth}
-%   \centering
-%   \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-%   \caption{}
-%   \label{fig:speedControlModelArchitecture}
-% \end{subfigure}
-% \begin{subfigure}[b]{0.48\linewidth}
-%   \centering
-%   \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-%   \caption{}
-%   \label{fig:speedModelArchitecture}
-% \end{subfigure}
-% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-% \label{fig:subFunctionalBlock}
-% \end{figure}
-% %
 
@@
 Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
-The block diagram of the control system designed for this subsystem is shown in Fig.~
+The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}
 
@@
 of the acceleration subsystem.
- \begin{figure}[h]
+ \begin{figure}[htbp]
     \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (accelSubsystem.180)--node[pos=0.5,above]{Acceleration Pedal Voltages}++(-1.7,0);
+    \draw[-stealth,thick]
+    (accelSubsystem.0)--node[pos=0.5,above]{Acceleration Pedal Position}++(1.7,0);
+
+  \end{tikzpicture}
     \caption{Acceleration subsystem block diagram}
-    \label{fig:accelerationModelArchitecture}
+    \label{fig:accelModelArchitecture}
  \end{figure}
@@
 This actual shifter gear value is then the output of the shift subsystem.
- \begin{figure}[h]
+ \begin{figure}[htbp]
     \centering
-    % \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (shiftSubsystem.180)--node[pos=0.5,above]{Desired Shifter Gear}++(-1.7,0);
+    \draw[-stealth,thick]
+    (shiftSubsystem.0)--node[pos=0.5,above]{Actual Shifter Gear}++(1.7,0);
+
+  \end{tikzpicture}
     \caption{Shift subsystem block diagram}
@@
 This vehicle speed is the output of the system.
- \begin{figure}[h]
+ \begin{figure}[htbp]
     \centering
-    \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedSubsystem.150)--node[pos=0.65,above]{Acceleration Pedal Position}++(-1.7,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.180)--node[pos=0.65,above]{Brake Pedal Position}++(-1.7,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.-150)--node[pos=0.65,above]{Shifter Gear}++(-1.7,0);
+    \draw[-stealth,thick]
+    (speedSubsystem.0)--node[pos=0.5,above]{Vehicle Speed}++(1.7,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
     \caption{Speed subsystem block diagram}
@@
 This value is then sent out to the rest of the vehicle system.
- \begin{figure}[h]
+ \begin{figure}[htbp]
     \centering
-    % \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=0.48\textwidth]{figs/inkscape/speedControlModelArchitecture}
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedControlSubsystem.180)--node[pos=0.5,above]{Desired Vehicle Speed}++(-1.7,0);
+    \draw[-stealth,thick]
+    (speedControlSubsystem.0)--node[pos=0.5,above]{Actual Vehicle Speed}++(1.7,0);
+
+  \end{tikzpicture}
     \caption{Speed Control subsystem block diagram}
@@
  \end{figure}
-
-% \begin{figure}[htb]
-%    \centering 
-% \begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
-%  \caption{}
-%  \label{fig:steeringmodelarchitecture}
-% \end{subfigure}
-% \begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-%  \caption{}
-%  \label{fig:brakeModelArchitecture}
-% \end{subfigure}
-% \\
-% \begin{subfigure}[b]{0.48\textwidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
-%  \caption{}
-%  \label{fig:accelerationModelArchitecture}
-% \end{subfigure}
-% \begin{subfigure}[b]{0.48\linewidth}
-%  \centering 
-%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
-%  \caption{}
-%  \label{fig:shiftModelArchitecture}
-% \end{subfigure}
-% \\
-% \begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
-%  \caption{}
-%  \label{fig:speedControlModelArchitecture}
-% \end{subfigure}
-% \begin{subfigure}[b]{0.48\linewidth}
-%  \centering
-%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
-%  \caption{}
-%  \label{fig:speedModelArchitecture}
-% \end{subfigure}
-% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
-% \label{fig:subFunctionalBlock}
-% \end{figure}
 
@@
 models.
+
 \section{Main Project Work (Modeling Vehicle Subsystems)}
@@
 The data we collected will be used to generate and then verify our models.
-We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:exusvehicle}.
+We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:lexusvehicle}.
 %
 %
-\begin{figure}
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
 	\caption{AutonomouStuff Lexus RX450H vehicle.}
@@
 
-\noindent Each subsystem that we are modeling is set up in a similar manner.
+Each subsystem that we are modeling is set up in a similar manner.
 In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).
@@
 \\
-%
-\\
-\noindent Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
+
+\begin{figure}[htbp]
+	\centering
+    	% \captionsetup{justification=centering, margin=3cm}
+    	\includegraphics[width=.48\textwidth]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    	\caption{Autonomous Vehicle Data Collection Setup}
+    	\label{fig:vehicleSetup}
+\end{figure}
+
+Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
 This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in.
@@
 For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
-
-\begin{figure}
-	\centering
-    	% \captionsetup{justification=centering, margin=3cm}
-    	\includegraphics[width=.48\textwidth]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
-    	\caption{Autonomous Vehicle Data Collection Setup}
-    	\label{fig:vehicleSetup}
-\end{figure}
 

### 2022-03-07 reportTII-ArticleHIL.tex
Update report
I added some text to the main project work section of the report.

@@
 For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
+\\
+
+Another decision we made was to start using the Neural Network to create models.
+We decided to do this instead of continuing with the System Identification Toolbox for multiple reasons.
+The main one is because while transfer function models are able to accurately model linear systems, they struggle to model highly non-linear systems.
+Neural Networks work well with highly non-linear systems and are able to accurately model them.
+Since our systems, and the steering system in particular, exhibit non-linear behavior, they are not able to be accurately modeled by transfer functions.
+Another reason is that once the System Identification models were created in Simulink, there was confusion over how they would connect to produce the output.
+Some of the system models, such as the brake system, had four transfer functions due to having four inputs.
+These models were easily generated, but it wasn’t clear on how they should be connected in order to reflect the physical system.
+By using Neural Network models this problem can be avoided.
 

### 2022-03-07 reportTII-ArticleHIL.tex
Update report, labNotebook, add images

@@
 \subsection{Brake System}
+The brake system was modeled using only the manual log data.
+It was trained using the data from the first brake log, and the result and error plots can be seen in \autoref{initalBrakeModel}.
+The plots show that the model is able to predict the outputs relatively accurately, along with keeping the error below 5\%.
+In order to further verify the accuracy of the model, it was tested using data from the second brake log.
+The results from that test, shown in \autoref{testedBrakeModel}, also show that the model can accurately predict the output values and do this within the accepted error bound of 5\%.
+\begin{figure}[h]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots \label{initalBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Log Two Data \label{testedBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
+	\caption{Brake System Training Plots}
+\end{figure}
+
+Once the model was created, it was exported to Simulink and further tested.
+One test involved using constant blocks to represent the pressure voltages, position voltages, and desired pedal position for a given time instant in the first brake log.
+The actual pedal position and the error between the desired and actual pedal positions were then plotted.
+The actual pedal position plot can be seen in \autoref{brakeWorkspacePedalPosition}.
+The resulting error plot between the desired pedal position and the model generated position can be found in \autoref{brakeWorkspacePedalError}.
+
+\begin{figure}[h]
+	\centering
+	\subcaptionbox{ \label{brakeWorkspacePedalPosition}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
+	\subcaptionbox{ \label{brakeWorkspacePedalError}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
+	\caption{Actual Pedal Position and Error Plots Using the From Workspace Block}
+\end{figure}
 

### 2022-03-11 reportTII-ArticleHIL.tex
~

--- 2022-03-02 reportTII-ArticleHIL.tex
@@
 \usepackage{tikz}
-% \usetikzlibrary{calc,tikzmark}
-\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
+\usetikzlibrary{calc}
 
@@
 \begin{abstract}
-This report presents the results of modeling vehicle systems and testing them using Hardware-in-the-Loop (HIL).
-First, data was collected for each system using a Lexus RX450H vehicle.
-After data collection, models were developed in order to accurately simulate the physical vehicle system.
-MATLAB’s System Identification Toolbox was initially used to create these models.
-However, the transfer function models it provided weren’t able to accurately represent these systems and their non-linear behaviors.
-After this was established, modeling was done using MATLAB’s Neural Network Time Series application.
-Once a Neural Network model was created, it was then exported to Simulink and modified to be able to run without the use of the Deep Learning toolbox.
-These models gave much more accurate results when compared to the transfer function models developed using the System Identification Toolbox.
-(Add section about testing and results).
-
-%These instructions give you guidelines for preparing papers for 
-%IEEE Transactions and Journals. Use this document as a template if you are 
-%using \LaTeX. Otherwise, use this document as an 
-%instruction set. The electronic file of your paper will be formatted further 
-%at IEEE. Paper titles should be written in uppercase and lowercase letters, 
-%not all uppercase. Avoid writing long formulas with subscripts in the title; 
-%short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
-%not write ``(Invited)'' in the title. Full names of authors are preferred in 
-%the author field, but are not required. Put a space between authors' 
-%initials. The abstract must be a concise yet comprehensive reflection of 
-%what is in your article. In particular, the abstract must be self-contained, 
-%without abbreviations, footnotes, or references. It should be a microcosm of 
-%the full article. The abstract must be between 150--250 words. Be sure that 
-%you adhere to these limits; otherwise, you will need to edit your abstract 
-%accordingly. The abstract must be written as one paragraph, and should not 
-%contain displayed mathematical equations or tabular material. The abstract 
-%should include three or four different keywords or phrases, as this will 
-%help readers to find it. It is important to avoid over-repetition of such 
-%phrases as this can result in a page being rejected by search engines. 
-%Ensure that your abstract reads well and is grammatically correct.
+These instructions give you guidelines for preparing papers for 
+IEEE Transactions and Journals. Use this document as a template if you are 
+using \LaTeX. Otherwise, use this document as an 
+instruction set. The electronic file of your paper will be formatted further 
+at IEEE. Paper titles should be written in uppercase and lowercase letters, 
+not all uppercase. Avoid writing long formulas with subscripts in the title; 
+short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
+not write ``(Invited)'' in the title. Full names of authors are preferred in 
+the author field, but are not required. Put a space between authors' 
+initials. The abstract must be a concise yet comprehensive reflection of 
+what is in your article. In particular, the abstract must be self-contained, 
+without abbreviations, footnotes, or references. It should be a microcosm of 
+the full article. The abstract must be between 150--250 words. Be sure that 
+you adhere to these limits; otherwise, you will need to edit your abstract 
+accordingly. The abstract must be written as one paragraph, and should not 
+contain displayed mathematical equations or tabular material. The abstract 
+should include three or four different keywords or phrases, as this will 
+help readers to find it. It is important to avoid over-repetition of such 
+phrases as this can result in a page being rejected by search engines. 
+Ensure that your abstract reads well and is grammatically correct.
 \end{abstract}
@@
 the vehicle should be controlled.
-Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+Within the scope of this project and to expedite the modeling process, a commercially available modeling tool, called system identification toolbox, is used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belong to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
 The first subsystem we will model is the steering model, and then we will move onto
@@
 autonomous vehicle platform.
-These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
+These models will be considered reliable if they can track actual vehicle subsystem behaviors with a best fit percentage between 85 to 95 percent.
 Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
 Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
-Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
+There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous. Models for each subsystem must be created
+for both manual-drive mode and by-wire, or autonomous, mode.
+Fig.~\ref{fig:steerSystem} depicts how the by-wire mode controls the vehicle. Each
 subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
+motor that will control the subsystem. In Fig.~\ref{fig:steerSystem}, the motor would
 turn the pinion arms which would change the steering angle of the vehicle. This
@@
   \centering
-  \begin{subfigure}[b]{0.48\linewidth}
+  \begin{subfigure}[b]{0.40\linewidth}
     \centering
-    \includegraphics[height=3cm]{figs/img/autonomousVehiclesAStuff}
+    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesAStuff}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.48\linewidth}
+  \begin{subfigure}[b]{0.40\linewidth}
     \centering
-    \includegraphics[height=3cm]{figs/img/autonomousVehiclesSteering}
+    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesSteering}
     \caption{}
-    \label{fig:steerOverview}
+    \label{fig:steerSystem}
   \end{subfigure}
-  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerOverview} steering model setup (courtesy of AutonomouStuff). }
+  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerSystem} steering model setup (courtesy of AutonomouStuff). }
   \label{fig:AstuffFleetSteeringSetup}
 \end{figure}
+
+% \noindent \begin{tiny}
+% 	\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+% \end{tiny}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
@@
 \label{sec:sysID-Example2}
-This example~\cite{Matlab2} discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example~\cite{Matlab2}, discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
   \centering
-  \begin{subfigure}[b]{\linewidth}
-    \includegraphics[height=4.25cm]{figs/img/example2Fig1}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=5cm]{figs/img/example2Fig1}
     \caption{}
@@
   \\
-  \begin{subfigure}[b]{\linewidth}
-    \includegraphics[height=4.25cm]{figs/img/example2Fig2}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=5cm]{figs/img/example2Fig2}
     \caption{}
@@
   \caption{\subref{fig:ex2fig1} State-space model of a MIMO system with a validation data comparison and \subref{fig:ex2fig2} State-space model of a MIMO system and system-sized based state-space model with a validation data comparison }
-  \label{fig:ex2}
+  \label{fig:AstuffFleetSteeringSetup}
 \end{figure}
@@
 was the most accurate, with a best fit percentage of 85.83\%.
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
@@
 \begin{itemize}
-    \item The resulting plant model will consist of accurate subsystem models, as defined above
-    \item The subsystems can be used to create a HIL testbench
-    \item The subsystems can handle very small changes in values accurately
+    \item The resulting plant model will consist of accurate subsystem models
+    \item The subsystems can be used to create an HIL testbench
+    \item The steering model can handle very small changes in steering angles
+    \begin{itemize}
+    		\item The steering model should have a very smooth, continuous output as a choppy, discontinuous output would translate into difficulty tracking the vehicle in a straight line for instances such as keeping the vehicle in its lane.
+For this reason, that model that we create should be able to smooth out any discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle.
+The non-linear behavior is depicted in Fig.~\ref{fig:nonlinGraph}.
     \end{itemize}
-
-All of the subsystems have nonlinear behaviors when there are small changes in the output of the subsystem.
-The steering subsystem, for example, should behave in a smooth, continuous manner.
-However, AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
-This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
-These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer and smoother manner.
-
-\begin{figure}[htbp]
+\end{itemize}
+\begin{figure}[h]
     \centering
-    \captionsetup{justification=centering}
+    \captionsetup{justification=centering, margin=3cm}
     \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
@@
 \section{System Architecture}
-The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
-Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
-For each subsystem, every input that is a torque voltage is actually two torque voltage signals, thus can not be treated as a single input.
-Also, each subsystem will be treated as a single output system.
-The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based  on the other output's behavior.
+The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in Fig.~\ref{fig:subFunctionalBlock}.
+Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem.
+Some of the systems are multiple output and some are single output as depicted in Fig.~\ref{fig:subFunctionalBlock}.
+%
 %
@@
 \end{figure}
+% \begin{figure}[htb]
+%     \centering 
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+%   \caption{}
+%   \label{fig:steeringmodelarchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%   \caption{}
+%   \label{fig:brakeModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\textwidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+%   \caption{}
+%   \label{fig:accelerationModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering 
+%   \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+%   \caption{}
+%   \label{fig:shiftModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+%   \caption{}
+%   \label{fig:speedControlModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%   \centering
+%   \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+%   \caption{}
+%   \label{fig:speedModelArchitecture}
+% \end{subfigure}
+% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+% \label{fig:subFunctionalBlock}
+% \end{figure}
+% %
 
@@
 Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
-The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}
+The block diagram of the control system designed for this subsystem is shown in Fig.~
 
@@
 of the acceleration subsystem.
- \begin{figure}[htbp]
+ \begin{figure}[h]
     \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (accelSubsystem.180)--node[pos=0.5,above]{Acceleration Pedal Voltages}++(-1.7,0);
-    \draw[-stealth,thick]
-    (accelSubsystem.0)--node[pos=0.5,above]{Acceleration Pedal Position}++(1.7,0);
-
-  \end{tikzpicture}
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
     \caption{Acceleration subsystem block diagram}
-    \label{fig:accelModelArchitecture}
+    \label{fig:accelerationModelArchitecture}
 \end{figure}
@@
 This actual shifter gear value is then the output of the shift subsystem.
- \begin{figure}[htbp]
+ \begin{figure}[h]
     \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (shiftSubsystem.180)--node[pos=0.5,above]{Desired Shifter Gear}++(-1.7,0);
-    \draw[-stealth,thick]
-    (shiftSubsystem.0)--node[pos=0.5,above]{Actual Shifter Gear}++(1.7,0);
-
-  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
     \caption{Shift subsystem block diagram}
@@
 This vehicle speed is the output of the system.
- \begin{figure}[htbp]
+ \begin{figure}[h]
     \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (speedSubsystem.150)--node[pos=0.65,above]{Acceleration Pedal Position}++(-1.7,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.180)--node[pos=0.65,above]{Brake Pedal Position}++(-1.7,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.-150)--node[pos=0.65,above]{Shifter Gear}++(-1.7,0);
-    \draw[-stealth,thick]
-    (speedSubsystem.0)--node[pos=0.5,above]{Vehicle Speed}++(1.7,0);
-
-  \end{tikzpicture}
-    % \captionsetup{justification=centering, margin=3cm}
-    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
     \caption{Speed subsystem block diagram}
@@
 This value is then sent out to the rest of the vehicle system.
- \begin{figure}[htbp]
+ \begin{figure}[h]
     \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[pos=0.5,above]{Desired Vehicle Speed}++(-1.7,0);
-    \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[pos=0.5,above]{Actual Vehicle Speed}++(1.7,0);
-
-  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    \includegraphics[width=0.48\textwidth]{figs/inkscape/speedControlModelArchitecture}
     \caption{Speed Control subsystem block diagram}
@@
 \end{figure}
+
+% \begin{figure}[htb]
+%    \centering 
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
+%  \caption{}
+%  \label{fig:steeringmodelarchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%  \caption{}
+%  \label{fig:brakeModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\textwidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
+%  \caption{}
+%  \label{fig:accelerationModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering 
+%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
+%  \caption{}
+%  \label{fig:shiftModelArchitecture}
+% \end{subfigure}
+% \\
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
+%  \caption{}
+%  \label{fig:speedControlModelArchitecture}
+% \end{subfigure}
+% \begin{subfigure}[b]{0.48\linewidth}
+%  \centering
+%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
+%  \caption{}
+%  \label{fig:speedModelArchitecture}
+% \end{subfigure}
+% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
+% \label{fig:subFunctionalBlock}
+% \end{figure}
 
@@
 models.
-
 \section{Main Project Work (Modeling Vehicle Subsystems)}
@@
 The data we collected will be used to generate and then verify our models.
-We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:lexusvehicle}.
+We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:exusvehicle}.
 %
 %
-\begin{figure}[htbp]
+\begin{figure}
 	\centering
-	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\includegraphics[height=3.5cm, width=0.4\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}
 	\caption{AutonomouStuff Lexus RX450H vehicle.}
@@
 
-Each subsystem that we are modeling is set up in a similar manner.
+\noindent Each subsystem that we are modeling is set up in a similar manner.
 In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).
@@
 \\
+%
+\\
+\noindent Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
+This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in.
+After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models.
+When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor.
+As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
+For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems.
+For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
 
-\begin{figure}[htbp]
+\begin{figure}
 	\centering
@@
 \end{figure}
-
-Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
-This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in.
-After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models.
-When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor.
-As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
-For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems.
-For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
 
@@
 %
-\subsection{Brake System}
 

### 2022-03-11 reportTII-ArticleHIL.tex

--- 2022-03-07 reportTII-ArticleHIL.tex
@@
 \begin{IEEEkeywords}
-Enter key words or phrases in alphabetical 
-order, separated by commas. For a list of suggested keywords, send a blank 
-e-mail to keywords@ieee.org or visit \underline
-{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
+Hardware-in-the-Loop, Neural Network, System Identification
 \end{IEEEkeywords}
@@
 
-Once the model was created, it was exported to Simulink and further tested.
-One test involved using constant blocks to represent the pressure voltages, position voltages, and desired pedal position for a given time instant in the first brake log.
-The actual pedal position and the error between the desired and actual pedal positions were then plotted.
+Once the model was created, it was exported to Simulink and tested again.
+One test involved using To Workspace blocks to access the pressure voltages, position voltages, and desired pedal position values in the first brake log.
+These values were used as inputs for the model, and the actual pedal position along with the error between the desired and actual pedal positions were then plotted.
 The actual pedal position plot can be seen in \autoref{brakeWorkspacePedalPosition}.
 The resulting error plot between the desired pedal position and the model generated position can be found in \autoref{brakeWorkspacePedalError}.
+Despite an initial spike within the first few seconds of the graph, the error plot shows that the difference between the pedal positions generated by the system and the desired pedal positions is never more than 5\%.
 
@@
 	\centering
-	\subcaptionbox{ \label{brakeWorkspacePedalPosition}}
+	\subcaptionbox{Actual Pedal Position \label{brakeWorkspacePedalPosition}}
 		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
-	\subcaptionbox{ \label{brakeWorkspacePedalError}}
+	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeWorkspacePedalError}}
 		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
-	\caption{Actual Pedal Position and Error Plots Using the From Workspace Block}
+	\caption{Actual Pedal Position and Error Plots Using the From Workspace Blocks}
+\end{figure}
+
+The second test used constant blocks to represent the voltages and desired pedal position at a specific time instant in the first brake log.
+The error and the actual pedal position were then plotted again.
+The pedal position plot is shown in \autoref{brakeConstantsPedalPosition}, and the error plot is represented by \autoref{brakeConstantsPedalError}.
+As the plots show, the model is able to produce the desired pedal position and the error falls to 0\% after a spike at the start.
+
+\begin{figure}[h]
+	\centering
+	\subcaptionbox{Actual Pedal Position \label{brakeConstantsPedalPosition}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionConstantBlocks}}
+	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeConstantsPedalError}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorConstantBlocks}}
+	\caption{Actual Pedal Position and Error Plots Using the Constant Blocks}
 \end{figure}

### 2022-03-11 reportTII-ArticleHIL.tex
Fixed input and output labels of a few figures

@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (brakeSubsystem.150)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
+    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
     \draw[stealth-,thick]
@@
     \draw[stealth-,thick]
-    (brakeSubsystem.-150)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
+    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
     \draw[-stealth,thick]
-    (brakeSubsystem.15)--node[pos=0.5,above]{Pedal position}++(1.7,0);
+    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(1.7,0);
     \draw[-stealth,thick]
-    (brakeSubsystem.-15)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
+    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
 
@@
 the real-time pedal position. This is then the output 
-of the acceleration subsystem.
+of the acceleration subsystem. %
+%
  \begin{figure}[htbp]
@@
     \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
-
     % Connections
     \draw[stealth-,thick]
-    (accelSubsystem.180)--node[pos=0.5,above]{Acceleration Pedal Voltages}++(-1.7,0);
+    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.0,0);
     \draw[-stealth,thick]
-    (accelSubsystem.0)--node[pos=0.5,above]{Acceleration Pedal Position}++(1.7,0);
-
+    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.0,0);
   \end{tikzpicture}
@@
     \draw[stealth-,thick]
-    (shiftSubsystem.180)--node[pos=0.5,above]{Desired Shifter Gear}++(-1.7,0);
+    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
     \draw[-stealth,thick]
-    (shiftSubsystem.0)--node[pos=0.5,above]{Actual Shifter Gear}++(1.7,0);
+    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
 
@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (speedSubsystem.150)--node[pos=0.65,above]{Acceleration Pedal Position}++(-1.7,0);
+    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
     \draw[stealth-,thick]
-    (speedSubsystem.180)--node[pos=0.65,above]{Brake Pedal Position}++(-1.7,0);
+    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
     \draw[stealth-,thick]
-    (speedSubsystem.-150)--node[pos=0.65,above]{Shifter Gear}++(-1.7,0);
+    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
     \draw[-stealth,thick]
-    (speedSubsystem.0)--node[pos=0.5,above]{Vehicle Speed}++(1.7,0);
+    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
 
@@
     \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[pos=0.5,above]{Desired Vehicle Speed}++(-1.7,0);
+    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
     \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[pos=0.5,above]{Actual Vehicle Speed}++(1.7,0);
+    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);
 

### 2022-03-21 reportTII-ArticleHIL.tex
Worked on the structure of the final report

@@
 percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\%
+
 for the speed data. The frequency response of the model was estimated with
@@
 
-\section{System Requirements}
-The vehicle plant model will fulfill the requirements listed below:
-\begin{itemize}
-    \item The resulting plant model will consist of accurate subsystem models, as defined above
-    \item The subsystems can be used to create a HIL testbench
-    \item The subsystems can handle very small changes in values accurately
-\end{itemize}
-
-All of the subsystems have nonlinear behaviors when there are small changes in the output of the subsystem.
-The steering subsystem, for example, should behave in a smooth, continuous manner.
-However, AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
-This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
-These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer and smoother manner.
-
-\begin{figure}[htbp]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
-    \caption{Steering Non-linear Behavior}
-    \label{fig:nonlinGraph}
-\end{figure}
-
 \section{System Architecture}
@@
   \label{fig:highLevelSystemArchitecture}
+\end{figure}
+
+% 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\caption{AutonomouStuff Lexus RX450H vehicle.}
+	\label{fig:lexusvehicle}
 \end{figure}
@@
   % \captionsetup{justification=centering, margin=3cm}
+
   % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
@@
 
- \subsection{Specifications}
- Based on the system requirements listed above, the plant model will meet the following specifications:
- \begin{itemize}
-    \item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
-    \item The steering subsystem will be able to handle small steering angles
-    \item Each vehicle subsystem will be modeled separately
- \end{itemize}
+ \section{Modeling Dynamic System using Neural Network}
+
+ In this section, we illustrate how a neural network can be used to model a
+ dynamic system in general. Neural network is a system approximation technique
+ that .......
+ The main structure of a neural network consists neurons, input layer of
+ neurons, one or more hidden layers, and the output layer of neurons. The
+ neurons of the hidden layers and the output layer have processing capabilities.
+ The actual network of a nural network following parallel and distributed system
+ architecture. .....
+
+ \missingfigure{Add a generic picture/block diagram of a multiple-input multiple output
+   dynamic system}
+ \todo[inline]{Add a generic picture of a neural network}
+ \todo[inline]{Weights of a neural network}
+
+ \todo[inline]{Training of a neural network}
+ \todo[inline]{Testing a neural network}
 
@@
 
-\section{Main Project Work (Modeling Vehicle Subsystems)}
-To start this project, we first read documentation outlining the uses of MATLAB's System Identification Toolbox.
-From there we worked on MATLAB tutorials on how to model systems from data using System Identification and then find the most accurate model.
-We specifically tried to find examples with Multiple-Input Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since most of the vehicle subsystems we will model fall into one of these categories.
-A literature review was also conducted to see how systems with small non-linearities like our steering subsystem were modeled using System Identification.
-On October 7th we traveled to AutonomouStuff in order to collect data from the steering, acceleration, and braking subsystems in an autonomous vehicle.
-The data we collected will be used to generate and then verify our models.
-We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:lexusvehicle}.
-%
-%
+\subsection{System Requirements}
+Based on the system requirements listed above, the plant model will meet the following specifications:
+\begin{itemize}
+\item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
+\item The steering subsystem will be able to handle small steering angles
+\item Each vehicle subsystem will be modeled separately
+\end{itemize}
+The vehicle plant model will fulfill the requirements listed below:
+\begin{itemize}
+    \item The resulting plant model will consist of accurate subsystem models, as defined above
+    \item The subsystems can be used to create a HIL testbench
+    \item The subsystems can handle very small changes in values accurately
+\end{itemize}
+
+All of the subsystems have nonlinear behaviors when there are small changes in the output of the subsystem.
+The steering subsystem, for example, should behave in a smooth, continuous manner.
+However, AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
+These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer and smoother manner.
+
 \begin{figure}[htbp]
     \centering
-	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
-	\caption{AutonomouStuff Lexus RX450H vehicle.}
-	\label{fig:lexusvehicle}
+    \captionsetup{justification=centering}
+    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
+    \caption{Steering Non-linear Behavior}
+    \label{fig:nonlinGraph}
 \end{figure}
+
+\todo[inline]{Add subsections for each subsystem on how NNs are used to model each subsystem}
+
+\todo[inline]{For each subsystem you will need to draw different NN structure }
+
+\section{Validation and Testing} \label{sec:simresults}
+
+To start this project, we first read documentation outlining the uses of
+MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
+on how to model systems from data using System Identification and then find the
+most accurate model. We specifically tried to find examples with Multiple-Input
+Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
+most of the vehicle subsystems we will model fall into one of these categories.
+A literature review was also conducted to see how systems with small
+non-linearities like our steering subsystem were modeled using System
+Identification.
+
+\subsection{Experimental Setup}
+\label{sec:experimentalSetup}
+
+On October 7th we traveled to AutonomouStuff in order to collect
+data from the steering, acceleration, and braking subsystems in an autonomous
+vehicle. The data we collected will be used to generate and then verify our
+models. We collected data on the Lexus RX450H vehicle platform shown in
+Fig.~\ref{fig:lexusvehicle}. %
 
@@
 
-\section{Validation and Testing} \label{sec:simresults}
-\subsection{Steering Subsystem}
+\subsection{Transfer Function Modeling}
+\label{sec:TransferFunctionModeling}
+
+\todo[inline]{Discuss results using the setup you explained in the previous section. See some IEEE papers}
+
+\subsubsection{Steering Subsystem}
 In Fig.~\ref{byWireSteerModel}, the output steering angle is plotted versus time
@@
 
-\subsection{Acceleration System}
+\subsubsection{Acceleration System}
 In \autoref{byWireAccelModel}, the output acceleration pedal position is plotted versus time when the vehicle is in by-wire mode.
@@
 %
-\subsection{Brake System}
+\subsubsection{Brake System}
 The brake system was modeled using only the manual log data.
@@
 \end{figure}
+
+\subsection{Neural Network Modeling}
+\label{sec:NN-Modeling}
+
+\todo[inline]{Discuss results  NN modeling using the setup you explained in the previous section. See some IEEE papers}
+
+\subsection{Discussion}
+\label{sec:discussion}
+
+\todo[inline]{Discuss pros and cons of the results you presented in the previous sections on each of the techniques you incorporated}
+
+\section{Conclusion and Future Work}
+\label{sec:conclustionAndFutureWork}
+
+\todo[inline]{One paragraph on conclusion, make sure you to recommend what modeling technique for the company }
+\todo[inline]{One paragraph on future work}
 

### 2022-03-23 finalReportPres.tex
Update finalReportPres.tex

@@
 %==============================================================================
-\title[Smart Robotic Cart]{Smart Robotic Cart: A Prototype}
+\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}
 
-\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and Jason~Braker
-Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
+\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
+\linebreak Advisor:~Dr.~Suruz~Miah}
 % - Give the names in the same order as the appear in the paper.
@@
 
-\date[April~20,~2021]{Tuesday, April~27,~2021}
+\date[April~29,~2022]{Tuesday, April~29,~2022}
 

### 2022-03-23 reportTII-ArticleHIL.tex
Report Update
I added to the future work and conclusion section, the transfer function modeling section, and the neural network modeling section.

@@
 Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
-For each subsystem, every input that is a torque voltage is actually two torque voltage signals, thus can not be treated as a single input.
+For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus can not be treated as a single input.
 Also, each subsystem will be treated as a single output system.
@@
 Taking these inputs, the speed subsystem finds the vehicle speed.
-This vehicle speed is the output of the system.
+This vehicle speed is then the output of the system.
  \begin{figure}[htbp]
@@
 \subsubsection{Brake System}
+While some by-wire models were created for the brake system, the models created using manual data were the only ones considered once we decided to use only manual data.
+It was found that a transfer function of 28 poles and 12 zeros gave an acceptable best fit percentage for most of the data log combinations that were tried.
+However, it was only within the 5\% error bound for one of the data log combinations.
+Another problem was that the brake system required four transfer functions, one for each input.
+Once these transfer functions were exported, there was uncertainty on how to connect them in order to produce the output value.
+As a result, we ended up switching to using Neural Networks to create a model for the brake system.
+
+\subsection{Neural Network Modeling}
+\label{sec:NN-Modeling}
+
+\subsubsection{Brake System}
 The brake system was modeled using only the manual log data.
@@
 
-\subsection{Neural Network Modeling}
-\label{sec:NN-Modeling}
-
 \todo[inline]{Discuss results  NN modeling using the setup you explained in the previous section. See some IEEE papers}
@@
 \label{sec:conclustionAndFutureWork}
+Our initial approach was to model the subsystems using the System Identification Toolbox from MATLAB, but it produced unsatisfactory results.
+Switching to the Neural Network Time Series app allowed us to train models using the data we collected.
+These models that were developed met the predefined accuracy requirements, and so were tested using an open loop setup.
+In the future if AutonomouStuff would like to model other vehicle subsystems, we would recommend modeling them using Neural Networks.
+Creating the Neural Networks and exporting the models to Simulink was easy to do and produced accurate results.
+
+For this project, further testing should be completed for these subsystem models.
+Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop, this would be a good place to start.
+Further testing is important to make sure the developed models are accurate and compatible with testing using hardware.
+Depending on what AutonomouStuff decides, future engineers working on this project could start developing controllers based off of these models.
+Currently, AutonomouStuff develops their own controllers for their vehicle subsystems, but they could allow students to design some as part of this senior project.
 

### 2022-03-26 reportTII-ArticleHIL.tex
Report Update
Updated the NN Model, Modeling Vehicle Subsystems, and Validation & Testing sections.

@@
 \usepackage{tikz}
-% \usetikzlibrary{calc,tikzmark}
+\usetikzlibrary{shapes,arrows, positioning, quotes}
+\usetikzlibrary{arrows.meta, positioning, decorations.markings}
+\usetikzlibrary{calc,tikzmark}
 \usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
@@
 
- \section{Modeling Dynamic System using Neural Network}
+ \section{Modeling Dynamic Systems using Neural Networks}
 
@@
  that .......
- The main structure of a neural network consists neurons, input layer of
+ The main structure of a neural network consists of neurons, input layer of
  neurons, one or more hidden layers, and the output layer of neurons. The
  neurons of the hidden layers and the output layer have processing capabilities.
- The actual network of a nural network following parallel and distributed system
+ The actual structure of a neural network follows parallel and distributed system
  architecture. .....
 
- \missingfigure{Add a generic picture/block diagram of a multiple-input multiple output
-   dynamic system}
- \todo[inline]{Add a generic picture of a neural network}
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](plant){};
+
+    % Connections
+	\draw[stealth-,thick]
+    (plant.-130)--node[very near end,above](in1){Input 1}++(-1.9,0);    
+    \draw[stealth-,thick]
+    (plant.180)--node[very near end,above](in2){Input 2}++(-1.9,0);
+    %\draw[ultra thick,Dotted] (in2) -- (inn);
+    \draw[-stealth,thick]
+    (plant.130)--node[very near end,above](inn){Input n}++(1.9,0);
+
+    \draw[-stealth,thick]
+    (plant.-45)--node[very near end,above](out1){Output 1}++(1.9,0);
+    \draw[-stealth,thick]
+    (plant.0)--node[very near end,above](out2){Output 2}++(1.9,0);
+    %\draw[ultra thick,Dotted] (out2) -- (outm);
+    \draw[-stealth,thick]
+    (plant.0)--node[very near end,above](outm){Output m}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Multiple Input Multiple Output Dynamic System Block Diagram}
+    \label{fig:mimoDynamicBlockDiagram}
+ \end{figure}
+
+ Figure~\ref{fig:nnActor} shows a generic actor neural network structure. ...
+ \begin{figure}
+  \centering
+      \tikzset{%
+        input neuron/.style={
+          circle,
+          fill=green!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        hidden neuron/.style={
+          circle,
+          fill=blue!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        output neuron/.style={
+          circle,
+          fill=red!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+
+        \foreach \m/\l [count=\y] in {1,2,missing,3}
+        \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
+
+        \foreach \m [count=\y] in {1,2,3,missing,4}
+        \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
+
+        \foreach \m [count=\y] in {1,missing,2}
+        \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*1.2) {};
+
+        \foreach \l [count=\i] in {1,2,n}
+        \draw [<-] (input-\i) -- ++(-1,0)
+        node [above, midway] {$\mathbf{e}_{k,\l}$};
+
+        \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
+        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};
+
+        \foreach \l [count=\i] in {1,m}
+        \draw [->] (output-\i) -- ++(1,0)
+        node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};
+
+        \foreach \i in {1,...,3}
+        \foreach \j in {1,...,4}
+        \draw [->] (input-\i) -- (hidden-\j);
+
+        \foreach \i in {1,...,4}
+        \foreach \j in {1,2}
+        \draw [->] (hidden-\i) -- (output-\j);
+
+        \foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
+        \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
+
+        \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
+        \draw[->,ultra thick](3,-2.5) -- (3,1.6);
+
+      \end{tikzpicture}
+  \caption{Actor neural network structure for approximating control input.}
+  \label{fig:nnActor}
+\end{figure}
+
  \todo[inline]{Weights of a neural network}
@@
 \section{Modeling Vehicle Subsystems}
-To start this project, we first read documentation outlining the uses of
-MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
-on how to model systems from data using System Identification and then find the
-most accurate model. We specifically tried to find examples with Multiple-Input
-Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
-most of the vehicle subsystems we will model fall into one of these categories.
-A literature review was also conducted to see how systems with small
-non-linearities like our steering subsystem were modeled using System
-Identification. On October 7th we traveled to AutonomouStuff in order to collect
-data from the steering, acceleration, and braking subsystems in an autonomous
-vehicle. The data we collected will be used to generate and then verify our
-models.
+
+To start the project, we researched methods of plant modeling for autonomous vehicles and more generically, nonlinear systems.
+From our research, we found a few methods of modeling that we employed to discover the most accurate representation of each vehicle subsystem.
+The first method that we tried was developing different system types using Mathworks' MATLAB System Identification Toolbox.
+Using data we collected from the Lexus vehcile platform at AutonomouStuff,this toolbox allowed us to add input and output data for each vehicle subsystem.
+With this data, we used one subset to train the system and another subset for validation.
+Using this toolbox, we tried developing state-space models, NARX models, and transfer function models.
+We also used Mathworks' MATLAB Neural Network Time Series toolbox to develop a model of each vehicle subsystem using neural network modeling making use of the Bayesian Regularization training method.
+The following requirements were used to evaluate the effectiveness of our models to determine which plant model should be presented to AutonomouStuff.
 
 \subsection{System Requirements}
-Based on the system requirements listed above, the plant model will meet the following specifications:
+
+In order to accurately model each vehicle subsystem so that safe, reliable controllers can be developed for autonomous control, the following criteria will be met:
 \begin{itemize}
-\item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
-\item The steering subsystem will be able to handle small steering angles
-\item Each vehicle subsystem will be modeled separately
+\item Each vehicle subsystem will be able to track nonlinearities depicted in Fig.~\ref{fig:nonlinGraph} associated with small changes in the output of each subsystem
+\item Each vehicle subsystem plant model will track any desired inputs within the specified error bounds
+	\begin{itemize}
+		\item Steering Angle within 5 degrees
+		\item Pedal Positions within 5\%
 	\end{itemize}
+\item Each vehicle subsystem will be modeled independently from other vehicle subsystems
+\end{itemize}
+
 The vehicle plant model will fulfill the requirements listed below:
@@
     \item The subsystems can be used to create a HIL testbench
-    \item The subsystems can handle very small changes in values accurately
+    \item The subsystems can handle very small changes in their output accurately
 \end{itemize}
@@
 This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
-These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer and smoother manner.
+These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
 
@@
 
+\subsection{Steering System Modeling}
+
+\subsection{Acceleration System Modeling}
+
+\subsection{Brake System Modeling}
+
 \todo[inline]{Add subsections for each subsystem on how NNs are used to model each subsystem}
@@
 
-To start this project, we first read documentation outlining the uses of
-MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
-on how to model systems from data using System Identification and then find the
-most accurate model. We specifically tried to find examples with Multiple-Input
-Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
-most of the vehicle subsystems we will model fall into one of these categories.
-A literature review was also conducted to see how systems with small
-non-linearities like our steering subsystem were modeled using System
-Identification.
+%To start this project, we first read documentation outlining the uses of
+%MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
+%on how to model systems from data using System Identification and then find the
+%most accurate model. We specifically tried to find examples with Multiple-Input
+%Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
+%most of the vehicle subsystems we will model fall into one of these categories.
+%A literature review was also conducted to see how systems with small
+%non-linearities like our steering subsystem were modeled using System
+%Identification.
 
@@
 
-On October 7th we traveled to AutonomouStuff in order to collect
+We traveled to AutonomouStuff in order to collect
 data from the steering, acceleration, and braking subsystems in an autonomous
@@
 
-\noindent The following is the hardware required for this project:  
+\noindent The following is the hardware components required to collect the data:  
 	\begin{itemize}
@@
 This data is sent or received using the CANCase and CAN bus.
-These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.\bigskip
-
-	\noindent The following is the software required for this project: 
-	\begin{itemize}
-    		\item MATLAB's System Identification Toolbox 
-    		\item Vector CANAlyzer 
- 	\end{itemize}
-
-\noindent The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
+These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.
+The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
 This is how we were able to collect logs of data that we would use to develop models of the autonomous vehicle subsystems.
-MATLAB's System Identification Toolbox is the software that gave us the capabilities to develop these models of the vehicle subsystems.
-Using this toolbox, we are able to use the logs of data we collected to create sets of estimation and validation data that will be used for training the model.
 \\
@@
 For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
-\\
-
-Another decision we made was to start using the Neural Network to create models.
-We decided to do this instead of continuing with the System Identification Toolbox for multiple reasons.
-The main one is because while transfer function models are able to accurately model linear systems, they struggle to model highly non-linear systems.
-Neural Networks work well with highly non-linear systems and are able to accurately model them.
-Since our systems, and the steering system in particular, exhibit non-linear behavior, they are not able to be accurately modeled by transfer functions.
-Another reason is that once the System Identification models were created in Simulink, there was confusion over how they would connect to produce the output.
-Some of the system models, such as the brake system, had four transfer functions due to having four inputs.
-These models were easily generated, but it wasn’t clear on how they should be connected in order to reflect the physical system.
-By using Neural Network models this problem can be avoided.
 
@@
 
+\subsubsection{Steering System}
+
+The following are the results of neural network training for the steering system.
+
+\begin{figure}[htbp]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+	\caption{Steering System Training Plots}
+\end{figure}
+
+\subsubsection{Acceleration System}
+
+The following are the results of neural network training for the acceleration system.
+
+\begin{figure}[htbp]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
+	\caption{Acceleration System Training Plots}
+\end{figure}
+
 \subsubsection{Brake System}
+
 The brake system was modeled using only the manual log data.
@@
 
-\todo[inline]{Discuss pros and cons of the results you presented in the previous sections on each of the techniques you incorporated}
+For each vehicle subsystem, the results show that the neural network models were the most accurate models.
+Other models that we developed, such as the transfer function models, were relatively accurate when tracking the data, but those models were consistently falling outside of the error bounds that were defined at the start of the project.
+The neural network models, however, track the data more accurately and reduced the error significantly so that all error requirements were met.
+One downside to using neural networks as the plant model is it causes some complexities when trying to include these models into the HIL bench software for use in developing and testing controllers.
 
@@
 Currently, AutonomouStuff develops their own controllers for their vehicle subsystems, but they could allow students to design some as part of this senior project.
-
-\todo[inline]{One paragraph on conclusion, make sure you to recommend what modeling technique for the company }
-\todo[inline]{One paragraph on future work}
 

### 2022-03-28 finalReportPres.tex
Update finalReportPres
I added some slides to the final report.

@@
 \begin{frame}{Introduction}{}
- % \begin{center}
- %    \href{videos/smartRoboticCartIntroVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/finalPresVideoTitle.png}}
- %  \end{center}
+
 \end{frame}
@@
     \begin{LARGE}
-      Design a robotic cart that follows the user without line of sight (LoS) sensors
+
     \end{LARGE}
@@
     \begin{LARGE}
-      Utilize wireless radio frequency (RF) signal strength to locate and then follow the user
+
     \end{LARGE}
@@
 
-\begin{frame}{Introduction}{Previous Work}
-  \begin{block}{Existing Solution}
-        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
-  \end{block}
-    % \begin{figure}[b]
-    %     \centering
-    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
-    %     \caption{CompaRob}
-    %     %\label{fig:sysBlockDiag}
-    % \end{figure}
+%\begin{frame}{Introduction}{Previous Work}
+%  \begin{block}{Existing Solution}
+%        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
+%  \end{block}
+%    % \begin{figure}[b]
+%    %     \centering
+%    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
+%    %     \caption{CompaRob}
+%    %     %\label{fig:sysBlockDiag}
+%    % \end{figure}
+%\end{frame}
+%
+%%----------------------------------
+%
+%\begin{frame}{Introduction}{Previous Work}
+%  \begin{block}{Existing Solution}
+%        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
+%  \end{block}
+%    % \begin{figure}[b]
+%    %     \centering
+%    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
+%    %     \caption{Shopping Support Robot}
+%    %     %\label{fig:sysBlockDiag}
+%    % \end{figure}
+%\end{frame}
+
+%----------------------------------
+\section{Literature Review}
+
+\begin{frame}{Literature Review}{}
+
+\end{frame}
+%---------------------------
+\section{System Identification Preliminaries}
+
+\begin{frame}{System Identification Preliminaries}{}
+
 \end{frame}
 
-%----------------------------------
+\begin{frame}{System Identification Preliminaries}{Examples}
+  \begin{block}{}
+    \begin{LARGE}
 
-\begin{frame}{Introduction}{Previous Work}
-  \begin{block}{Existing Solution}
-        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
+    \end{LARGE}
   \end{block}
-    % \begin{figure}[b]
-    %     \centering
-    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
-    %     \caption{Shopping Support Robot}
-    %     %\label{fig:sysBlockDiag}
-    % \end{figure}
+  \begin{block}{}
+    \begin{LARGE}
+
+    \end{LARGE}
+  \end{block}
+\end{frame}
+%-------------------------
+\section{System Architecture}
+
+\begin{frame}{System Architecture}{}
+
 \end{frame}
 
-%----------------------------------
+\begin{frame}{System Architecture}{Subsystems}
+
+\end{frame}
+
+\begin{frame}{System Architecture}{Subsystems}
+
+\end{frame}
+%---------------------------
+\section{System Modeling using Neural Networks}
+
+\begin{frame}{Modeling using Neural Networks}{}
+
+\end{frame}
+%-------------------------
+\section{Modeling Vehicle Subsystems}
+
+\begin{frame}{Modeling Vehicle Subsystems}{}
+
+\end{frame}
+
+\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
+
+\end{frame}
+%-------------------------
+\section{Validation and Testing}
+
+\begin{frame}{Validation and Testing}{Experimental Setup}
+
+\end{frame}
+
+\begin{frame}{Transfer Function Modeling}{Steering System}
+
+\end{frame}
+
+\begin{frame}{Transfer Function Modeling}{Acceleration System}
+
+\end{frame}
+
+\begin{frame}{Transfer Function Modeling}{Brake System}
+
+\end{frame}
+
+\begin{frame}{Neural Network Modeling}{Steering System}
+
+\end{frame}
+
+\begin{frame}{Neural Network Modeling}{Acceleration System}
+
+\end{frame}
+
+\begin{frame}{Neural Network Modeling}{Brake System}
+
+\end{frame}
 
@@
     \begin{itemize}
-      \item The algorithm we implemented works the majority of the time
-      \item Through tests and gathering data we were able iterate on our approach and tune the algorithms to function more reliably
-      \item Our design is cost effective in comparison to other robotic carts
+      \item 
     \end{itemize}
@@
     \begin{itemize}
-      \item Improve the localization algorithm for better angle estimation
-      \item Test more reflector designs to see if the XBee signals can be more refined
-      \item Implement obstacle detection and avoidance
-      \item Multi-frequency radio modules to try to improve distance estimation
+      \item 
     \end{itemize}

### 2022-03-28 reportTII-ArticleHIL.tex
Added figure to report
Updated Report

@@
  dynamic system in general. Neural network is a system approximation technique
- that .......
+ that utilizes the Universal Approximation Theorem, which states that any neural network architecture
+ can find a mathematical function $y=f(x)$ that maps inputs $x$ to outputs $y$. The architecture of the 
+ neural network and the complexity of the dataset employed affect the accuracy of the function. This theorem
+ shows that there will be a determinable function from some neural network architecture and this theorem holds
+ for any number of inputs and outputs. 
  The main structure of a neural network consists of neurons, input layer of
@@
  The actual structure of a neural network follows parallel and distributed system
- architecture. .....
+ architecture.
 
@@
 \subsection{Steering System Modeling}
+To develop a model of the steering system, we employed multiple methods.
+The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB.
+The NARX model we developed was not accurate and did not track the output of the steering system data.
+The transfer function model we developed was more reliable tracking the output of the steering system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
+Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
+With the neural network model, the model was able to reliably and accurately track the output of the steering system data and stayed within the error requirements.
 
 \subsection{Acceleration System Modeling}
+To develop a model of the acceleration system, we employed multiple methods.
+The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB.
+The NARX model we developed was not accurate and did not track the output of the acceleration system data.
+The transfer function model we developed was more reliable tracking the output of the acceleration system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
+Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
+With the neural network model, the model was able to reliably and accurately track the output of the acceleration system data and stayed within the error requirements.
 
@@
 
-The following are the results of neural network training for the steering system.
+To develop the model of the steering system using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked.
+The neural network model used a feedforward network that had one hidden layer containing three neurons.
+%The following are the results of neural network training for the steering system.
 

### 2022-03-28 reportTII-ArticleHIL.tex
Updated Report
Added acknowledgment section
I added an acknowledgment section to the end of the report.

@@
   \centering
-  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
+  %  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
+  	\includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
   \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
@@
 
+\section*{Acknowledgments}
+The authors would like to thank Erik Guetz, Joe Buckner, Sai Chittemsetty, Matt Goben, and AutonomouStuff for their help and collaboration with this project.
+Without their support this project would never have been possible.
+
 \bibliographystyle{IEEEtran}

### 2022-03-28 reportTII-ArticleHIL.tex
Updated Report

@@
  shows that there will be a determinable function from some neural network architecture and this theorem holds
- for any number of inputs and outputs. 
+ for any number of inputs and outputs, like the system show in Fig.~\ref{fig:mimoDynamicBlockDiagram}. 
  The main structure of a neural network consists of neurons, input layer of
@@
 The neural network model used a feedforward network that had one hidden layer containing three neurons.
-%The following are the results of neural network training for the steering system.
+The model was also trained with twelve delay units to achieve the required accuracy, meaning that the first twelve output samples of the model should be ignored.
 
@@
 
-The following are the results of neural network training for the acceleration system.
+To develop the model of the acceleration system using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked.
+The neural network model used a feedforward network that had one hidden layer containing three neurons.
+The model was also trained with three delay units to achieve the required accuracy, meaning that the first three output samples of the model should be ignored.
 

### 2022-03-30 reportTII-ArticleHIL.tex
Added to report
I added to the brake subsection in the Modeling Vehicle Subsystems section.

@@
 \subsection{Brake System Modeling}
+To create a brake system model, we first tried generating transfer function models using MATLAB’s System Identification Toolbox.
+After generating multiple transfer function models and trying many different data log combinations, we still couldn’t find a model that was completely accurate across all combinations and that was below the error bound of 5\% for all combinations.
+Once this became clear Neural Network models were created using the Neural Network Time Series Toolbox provided by MATLAB to see if they could create accurate brake models.
+Using this we were able to create a model that accurately tracked the data we collected from the brake system and that stayed within the 5\% error bound.
 

### 2022-04-04 poster.tex
Poster Updates
I made changes to the Objectives & Contribution section along with the Conclusions & Future Work section. I also made some changes to the title.

@@
 
-\title{Smart Control of 2 Degree of Freedom Helicopters} % Poster title
+\title{Plant Modeling for an Autonomous Vehicle} % Poster title
 
-\author{Glenn Janiak, Ken Vonckx, Advisor: Dr. Suruz Miah} % Author(s)
+\author{Nick Nauman, Hannah Grady, Advisor: Dr. Suruz Miah} % Author(s)
 
@@
 \begin{itemize}
-    \item Develop a platform allowing mobile devices to control the motion of a group of helicopters
+    \item Create models for the subsystems of an autonomous vehicle
 \end{itemize}
@@
 \begin{itemize}
-    \item Determine trade-offs between traditional control techniques and machine learning
+	\item Determine if System Identification or Neural Network modeling produces better models 
+	\item Non-linearity modeling
+%    \item Determine trade-offs between traditional control techniques and machine learning
     %\item Embedded System Implementation
     %\item Mobile Device Control 
-    \item Multi-Helicopter Application
+    %\item Multi-Helicopter Application
 \end{itemize}
@@
 \begin{itemize}
-    \item Teleoperation approach to search and rescue 
-    \item Aerial turbulence resistance 
+	\item Use in testing to help develop more accurate vehicle controllers
+	\item Create a guide for modeling future vehicle subsystems
+%    \item Teleoperation approach to search and rescue 
+%    \item Aerial turbulence resistance 
 \end{itemize}
@@
 \begin{itemize}
-    \item Model-based reinforcement learning technique (ADP)  is useful when system model is unknown
+    \item Using Neural Networks produced more accurate models than System Identification 
    % \item PI controller greatly reduces steady-state error, however increases overshoot and settling time
     \vskip .75cm
-    \item Implement PI controller for ADP algorithm
-    \item Use digital compass to increase accuracy of orientation and help identify initial position
+    \item Test models using Hardware-in-the-Loop
+    \item Create new vehicle controllers
 \end{itemize}

### 2022-04-04 reportTII-ArticleHIL.tex
Updated reportTII-ArticleHIL
Added to Modeling Dynamic System using Neural Networks Section

@@
 
- Figure~\ref{fig:nnActor} shows a generic actor neural network structure. ...
+ Figure~\ref{fig:nnActor} shows a generic actor neural network structure which represents a neural network designed for a multiple input multiple output system. 
  \begin{figure}
@@
 
- \todo[inline]{Weights of a neural network}
-
- \todo[inline]{Training of a neural network}
- \todo[inline]{Testing a neural network}
+The neural network inputs are mapped to the outputs by being assigned a set of weights. 
+The approximated neural network signal can be written as:
+\begin{align}
+  \label{eq:approximatePolicyActorWeights}
+    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
+  \end{align}
+%
+where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
+%
+\begin{align*}
+  {\bf W}_a = 
+  \begin{bmatrix}
+    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
+    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
+    \vdots & \ddots & \ldots &\vdots\\
+    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
+  \end{bmatrix}.
+\end{align*}
+%
+In compact form:
+  \begin{align*}
+    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
+    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
+  \end{align*}
+  %
+  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
+
+  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
+  \begin{align*}
+    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+  \end{align*}
+
+Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
+%
+\begin{align*}
+  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+\end{align*}
+%
+Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
+%
+\begin{align}
+  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
+  \label{eq:actorWeightsGradient}
+\end{align}
+%
+Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
+\begin{align*}
+  {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+\end{align*}
+
+ The neural network is trained by altering the weights to minimize the least square error by utilizing the gradient descent approach which is defined as:
+ \begin{multline}
+  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
+  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
+  \label{eq:actorWeightUpdate}
+\end{multline}
+
+ The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set.
+An acceptable neural network model will meet the desired error requirements.
 

### 2022-04-05 finalReportPres.tex
Update finalReportPres.tex
I added to the introduction slides of the final report presentation
Update finalReportPres.tex
I added to the Neural Network Modeling slide for the brake system

@@
   \begin{block}{Problem Statement}
-    \begin{LARGE}
-
-    \end{LARGE}
+    \begin{Large}
+    		Model autonomous vehicle subsystems for a Lexus platform
+    \end{Large}
   \end{block}
@@
   \begin{block}{Proposed Solution}
-    \begin{LARGE}
-
-    \end{LARGE}
+    \begin{Large}
+    		Use MATLAB's System Identification Toolbox to create models
+    \end{Large}
   \end{block}
@@
 \begin{frame}{Neural Network Modeling}{Brake System}
-
+  \begin{block}{Modeling Process}
+    		\begin{itemize}
+    			\item Trained using data from the first brake log
+    			\item Model tested with data from the second brake log
+    		\end{itemize}
+    		\begin{figure}[h]
+			\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}
+			\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}
+\end{figure}
+%    		\begin{figure}[H]
+%    		\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}
+%    		\end{figure}
+  \end{block}
 \end{frame}
@@
     \begin{itemize}
-      \item 
+      \item Transfer Function to Neural Network models
+      \item Neural Network modeling worked best 
     \end{itemize}
@@
     \begin{itemize}
-      \item 
+      \item Test models using Hardware-in-the-Loop
+      \item Create new vehicle controllers 
     \end{itemize}

### 2022-04-06 finalReportPres.tex
Updated Final Report Presentation and Poster

--- 2022-03-28 finalReportPres.tex
@@
 \begin{frame}{Introduction}{}
-
+	\begin{block}{Applications of Autonomous Vehicles}
+    	\begin{itemize}
+    		\item Autonomous vehicles are being developed by many companies for commercial and personal use
+    		\item Modeling different subsystems (such as, steering, brake,
+          acceleration, $\ldots$)  for autonomous vehicles is a challenging task
+     		\item Models for autonomous vehicle subsystems must be very accurate due to safety factors
+		\end{itemize}
+    \end{block}
+        \begin{figure}
+			\centering
+			\begin{minipage}[t]{0.4\textwidth}
+				\centering
+				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesAStuff}
+				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
+				\label{fig:fleet}
+			\end{minipage}
+			\begin{minipage}[t]{0.4\textwidth}
+				\centering
+				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesSteering}
+				\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
+				\label{fig:steerSystem}
+			\end{minipage}
+        \end{figure}
+    \begin{tiny}
+		\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
+    \end{tiny}
 \end{frame}
@@
   \begin{block}{Proposed Solution}
-    \begin{LARGE}
-
-    \end{LARGE}
+    \begin{Large}
+    		Use neural network modeling techniques to develop models
+    \end{Large}
   \end{block}
@@
 \begin{frame}{Literature Review}{}
-
+	\begin{block}{Existing Solutions}
+ 	\begin{itemize}
+        \item Use of System Identification Toolbox in MATLAB to create models from data~\cite{Adnan2010}
+	 \begin{itemize}
+     \tiny
+		    		\item Offers a variety of model choices
+				\item Needs a large amount of raw data to produce an accurate model
+	\end{itemize}
+	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
+	 \begin{itemize}
+     \tiny
+		    		\item Allows the use of traditional analysis methods to create a model 
+				\item More room for error during calculations
+	\end{itemize}
+	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
+	 \begin{itemize}
+     \tiny
+		    		\item Can model systems with small non-linearities 
+				\item Mechanical components replaced by electrical components 
+	\end{itemize}
+	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
+	\begin{itemize}
+    \tiny
+		\item Fourth order ARX model ended up giving the best fit
+	\end{itemize}
+\end{itemize}
+  \end{block}
 \end{frame}
@@
 \begin{frame}{System Identification Preliminaries}{}
+  \begin{block}{Preliminary Work}
+ \begin{itemize}
+        \item Documentation on MATLAB's System Identification Toolbox and tutorials
+        \item Literature Review 
+        \item Data Collection for steering, braking and acceleration subsystems
+\end{itemize}
+  \end{block}
 
+   \begin {block}{MATLAB Example: Dealing with Multi-Variable Systems: Identification and Analysis}
+  \begin{itemize}
+  	\item  Learned how to create an iddata object from a given data set 
+  	\item Created a state space model and compared it to the validation data 
+  	\item Tried creating submodels for some of the channels in order to try and get a better fit 
+  	\item Then created a MISO model and learned how to merge the two SISO models that were created earlier 
+  	\end{itemize}
+  	\end{block}
 \end{frame}
@@
 \begin{frame}{System Architecture}{}
-
+	\begin{block}{System Architecture}
+    \begin{large}
+      The overall system architecture of this project consists of six subsystems: 
+      \begin{itemize}
+          \item Steering
+          \item Acceleration
+          \item Brake %Model
+          \item Shift %Model
+          \item Speed %Model
+          \item Speed control %Model
+        \end{itemize} 
+    \end{large}
+  \end{block}
 \end{frame}
@@
 \begin{frame}{System Architecture}{Subsystems}
-
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
+	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System 			\item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
 \end{frame}
@@
 \begin{frame}{System Architecture}{Subsystems}
-
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
+	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
+	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
 \end{frame}
@@
 \begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
-
+	\begin{block}{Specifications}
+	\begin{minipage}[t]{0.62\linewidth}    
+    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
+	\begin{itemize}
+    		\item Resulting plant model will consist of reasonably accurate subsystem models
+    		\item Subsystems can be used to create a HIL testbench
+    		\item Steering model can handle very small changes in steering angles
+    \begin{itemize}
+		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
+    \end{itemize}
+	\end{itemize}
+	\end{minipage}
+	\begin{minipage}[t]{0.34\linewidth}
+	\begin{figure}[h]
+		\centering
+    		\captionsetup{justification=centering, margin=0.5cm}
+    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
+    		\caption{Steering Non-linear Behavior}
+    		\label{fig:nonlinGraph}
+	\end{figure}
+	\end{minipage}
+\end{block}
 \end{frame}
@@
 \begin{frame}{Validation and Testing}{Experimental Setup}
+  \begin{block}{Software and Hardware}
+ \begin{itemize}
+        \item Software
+        \begin{itemize}
+        \small
+        \item MATLAB's System Identification Toolbox
+        \item Vector CANAlyzer
+        \end{itemize}
+	\item Hardware
+	\begin{itemize}
+	\small
+	\item Laptop
+	\item PACMod ECU
+	\item CANCase 
+	\item CAN bus
+	\end{itemize}
+\end{itemize}
+  \end{block}
+\end{frame}
 
+\begin{frame}{Validation and Testing}{Experimental Setup}
+	\begin{block}{Control Method}
+		\begin{itemize}
+			\item Manual Mode
+			\begin{itemize}
+				\item Vehicle is not autonomous
+				\item Torque voltages are sent by the vehicle ECU
+			\end{itemize}
+			\item By-Wire Mode
+			\begin{itemize}
+				\item Vehicle is autonomous
+				\item Torque voltages are sent by the PACMod ECU
+				\item Torque voltages sent from the vehicle ECU are discarded by open-circuiting the motors
+			\end{itemize}
+		\end{itemize}
+		\begin{figure}
+			\centering
+    			\captionsetup{justification=centering, margin=3cm}
+    			\includegraphics[width=1in]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+    			\caption{Autonomous Vehicle Data Collection Setup}
+    			\label{fig:vehicleSetup}
+		\end{figure}
+	\end{block}
 \end{frame}
@@
 \begin{frame}{Transfer Function Modeling}{Steering System}
-
+	\begin{block}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire steering estimated model is 85.54
+	\item Best fit percentage of the manual steering estimated model is 90.27
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireSteerModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualSteerModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
 \end{frame}
@@
 \begin{frame}{Transfer Function Modeling}{Acceleration System}
-
+	\begin{block}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
+	\item Best fit percentage of the manual acceleration estimated model is 98.3
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireAccelModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualAccelModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
 \end{frame}
@@
 \begin{frame}{Neural Network Modeling}{Steering System}
-
+	\begin{block}
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item Only a few samples are just outside of the accuracy requirements
+			\item Transfer function model did not meet the accuracy requirements
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
+	\end{block}
 \end{frame}
@@
 \begin{frame}{Neural Network Modeling}{Acceleration System}
-
+	\begin{block}
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item All samples within 2\% of the actual output
+			\item Transfer function model did not have the same accuracy bounds
+			\item Fewer concerns about connections in Simulink
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
+	\end{block}
 \end{frame}
@@
 \begin{frame}{Neural Network Modeling}{Brake System}
+	\begin{block}
+\begin{figure}[H]
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item With this model, the error is kept below 5\%
+			\item Able to easily track model performance
+			\item Provides better results than the transfer function model
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
+  		\end{figure}
 
+  \end{block}
 \end{frame}

### 2022-04-06 poster.tex
Picture upload and poster change
I uploaded a picture from our visit to AutonomouStuff and made a small change to the poster.
Updated Final Report Presentation and Poster
Update poster.tex
I added new section headers to the poster and started adding to the Problem Setup section.

@@
 \usetheme{confposter} % Use the confposter theme supplied with this template
+\usetikzlibrary{calc}
 
@@
 
-\begin{alertblock}{Objective and Contribution}
+\begin{alertblock}{Objective and Contributions}
 %
@@
 \begin{itemize}
-    \item Create models for the subsystems of an autonomous vehicle
+    \item Provide accurate plant models of each autonomous vehicle subsystem to be used for designing controllers
 \end{itemize}
@@
 \begin{block}{Problem Setup}
-\vskip -1cm
+%\vskip -1cm
 %\begin{enumerate}
@@
 
+%\vskip -1cm
+$\bullet$ Conducted a literature review to look for existing solutions
+$\bullet$ System Architecture 
 \begin{figure}
 	\centering
-    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ProblemStatementImage_Gray2}}
-    % \fcolorbox{gray!20}{gray!20}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ipe/highLevel_gry_grn.eps}
-    % }
-    \caption{High level architecture of the proposed system.}
-    \label{fig:highLevelDiagram}
+	\begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
+    \tikzstyle{sum} = [draw, circle,fill=orange!15]
+    % place nodes
+    \node[sum](sum){$\sum$};
+    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
+    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
+    \draw[-stealth,thick]
+    (sum.east)--node[midway,above]{Error}(steeringController);
+    \draw[-stealth,thick]
+    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
+    \draw[-stealth,thick]
+    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
+    \draw[-stealth,thick]
+    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
+    \fill
+    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
+    \draw[-stealth,thick]
+    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
+
+  \end{tikzpicture}
+  % \captionsetup{justification=centering, margin=3cm}
+
+  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
+  \caption{Steering subsystem block diagram.}
+  \label{fig:steeringModelBlockDiagram}
 \end{figure}
+
 \begin{figure}
 	\centering
-    % \missingfigure{Insert figure.}
-    % \fcolorbox{gray!10}{gray!10}{
-    % \includegraphics[height=.2\textheight,width=.92\textwidth,keepaspectratio=true]{figs/img/quanserAero.png}
-    % }
-    \caption{2-DOF helicopter (Quanser Aero).}
-    %\caption{DC motors are attached to main and tail rotors which allow the helicopter to change its pitch and yaw respectively.}
-    \label{fig:helicoterModel}
+	 \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
+    % Connections
+    \draw[stealth-,thick]
+    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.0,0);
+    \draw[-stealth,thick]
+    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.0,0);
+  \end{tikzpicture}
+    \caption{Acceleration subsystem block diagram}
+    \label{fig:accelModelArchitecture}
 \end{figure}
-\vskip -1cm
-$\bullet$ State-space representation of 2-DOF helicopter
-\begin{align*}
-\begin{bmatrix}
-    \dot\theta\\
-    \dot\psi\\
-    \ddot{\theta}\\
-    \ddot{\psi}
-\end{bmatrix}&=
-%\label{eq:matrixA}
-\begin{bmatrix}
-    0 & 0 & 1 & 0 \\
-    0 & 0 & 0 & 1 \\
-    0 & -K_{sp}/J_p & -D_p/J_p & 0 \\
-    0 & 0 & 1 & -D_y/J_y 
-\end{bmatrix} 
-%\label{eq:stateMatrix} 
-\begin{bmatrix}
-    \theta\\
-    \psi\\
-    \dot{\theta}\\
-    \dot{\psi}
-\end{bmatrix}
-\\&+
-%\label{eq:matrixB}
-\begin{bmatrix}
-    0 & 0 \\
-    0 & 0 \\
-    K_{pp}/J_p & K_{py}/J_p \\
-    K_{yp}/J_y & K_{yy}/J_y 
-\end{bmatrix}
-%\label{eq:inputMatrix}
-\begin{bmatrix}
-    V_p \\
-    V_y 
-\end{bmatrix}
-\end{align*}
+
+\begin{figure}
+	\centering
+	  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Brake subsystem block diagram}
+    \label{fig:brakeModelArchitecture}
+\end{figure}
+
+\begin{figure}
+    \centering
+        \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Speed Control subsystem block diagram}
+    \label{fig:speedControlModelArchitecture}
+
+\end{figure}
+
+\begin{figure}
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{ Speed subsystem block diagram}
+    \label{fig:speedModelArchitecture}
+\end{figure}
+
+\begin{figure}
+    \centering
+\begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
+    \draw[-stealth,thick]
+    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Shift subsystem block diagram}
+    \label{fig:shiftModelArchitecture}
+\end{figure}
+
+$\bullet$ Data Collection Setup 
+\begin{itemize}
+	\item Lexus RX450H vehicle platform
+	\item Laptop
+	\item PACMod ECU 
+	\item CANCase
+	\item CAN Bus 
+\end{itemize}
 
@@
 %-----------------------------------------------------------
-% LQR
+% TRANSFER FUNCTION MODELING
 %-----------------------------------------------------------
 
-\begin{block}{Motion (Trajectory) Control Algorithm}
+\begin{block}{Transfer Function Modeling}
 \vskip -1cm
@@
 %-----------------------------------------------------------
-% LQG
+% NEURAL NETWORK MODELING 
 %-----------------------------------------------------------
 
-\begin{block}{Optimal Noise Resistant Control Algorithm}
+\begin{block}{Neural Network Modeling}
 \vskip -1cm
@@
 %-----------------------------------------------------------
-% ADP
+% NEURAL NETWORK ALGORITHM 
 %-----------------------------------------------------------
 
-\begin{block}{Reinforcement Learning Algorithm}
+\begin{block}{Neural Network Algorithm}
 \vskip -1cm
@@
 
-\begin{block}{Simulation Results}
-\vskip -1cm
-%\begin{itemize}
-%    \item \todo[inline]{add LQR and LQG simulation results}
-%\end{itemize}
-
-%Before implementing the algorithm, it was simulated using the industry standard robot simulator V-REP.
+%\begin{block}{Simulation Results}
+%\vskip -1cm
+%%\begin{itemize}
+%%    \item \todo[inline]{add LQR and LQG simulation results}
+%%\end{itemize}
+%
+%%Before implementing the algorithm, it was simulated using the industry standard robot simulator V-REP.
 With numerous robot models available, V-REP is able to accurately and consistently produce like those expected in real--world scenarios.
 Preliminary simulation results can be seen in Fig.~\ref{fig:vrepResults}.
-
-\begin{figure}
-    \centering
-    \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch}
-    \label{fig:simStepPitch}
-    }
-    \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw}
-    \label{fig:simStepYaw}
-    }
-    \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch_Volt}
-    \label{fig:simPitchVolt}
-    }
-    \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw_Volt}
-    \label{fig:simYawVolt}
-    }
-    \caption{A comparison between LQG and LQR control for a step input is shown for \subref{fig:simStepPitch}~the~main~rotor and \subref{fig:simStepYaw}~the~tail~rotor and the corresponding voltages in \subref{fig:simPitchVolt}~and~\subref{fig:simYawVolt}}
-    \label{fig:simResults}
-\end{figure}
-\vskip -2cm
-\end{block}
+%
+%\begin{figure}
+%    \centering
+%    \subfigure[][]{
+%    %\missingfigure{Insert figure.}
+%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch}
+%    \label{fig:simStepPitch}
+%    }
+%    \subfigure[][]{
+%    %\missingfigure{Insert figure.}
+%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw}
+%    \label{fig:simStepYaw}
+%    }
+%    \subfigure[][]{
+%    %\missingfigure{Insert figure.}
+%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch_Volt}
+%    \label{fig:simPitchVolt}
+%    }
+%    \subfigure[][]{
+%    %\missingfigure{Insert figure.}
+%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw_Volt}
+%    \label{fig:simYawVolt}
+%    }
+%    \caption{A comparison between LQG and LQR control for a step input is shown for \subref{fig:simStepPitch}~the~main~rotor and \subref{fig:simStepYaw}~the~tail~rotor and the corresponding voltages in \subref{fig:simPitchVolt}~and~\subref{fig:simYawVolt}}
+%    \label{fig:simResults}
+%\end{figure}
+%\vskip -2cm
+%\end{block}
 

### 2022-04-07 poster.tex
Poster Updates
I edited the vehicle subsystem models and added to the Neural Network and Transfer Function Modeling sections

@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=0.75 cm]
     \tikzstyle{sum} = [draw, circle,fill=orange!15]
@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width= 5 cm, minimum height=1.5 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.0,0);
+    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-5.0,0);
     \draw[-stealth,thick]
-    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.0,0);
+    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(5.0,0);
   \end{tikzpicture}
@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2.0 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
+    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-4.5,0);
     \draw[stealth-,thick]
-    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
+    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-4.5,0);
     \draw[stealth-,thick]
-    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
+    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-4.5,0);
     \draw[-stealth,thick]
-    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(1.7,0);
+    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(4.5,0);
     \draw[-stealth,thick]
-    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
+    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(4.5,0);
 
@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
+    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
     \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);
+    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
 
@@
     \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
     % place nodes
@@
     \draw[stealth-,thick]
-    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
+    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
     \draw[stealth-,thick]
-    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
+    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
     \draw[stealth-,thick]
-    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
+    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
     \draw[-stealth,thick]
-    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
+    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
 
@@
     \draw[stealth-,thick]
-    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
+    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
     \draw[-stealth,thick]
-    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
+    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
 
@@
 
-$\bullet$ Data Collection Setup 
+%$\bullet$ Data Collection Setup 
 \begin{itemize}
+	\item Data Collection Setup
 		\item Lexus RX450H vehicle platform
@@
 \vskip -1cm
-%\begin{itemize}
-%    \item Determines optimal control gain for dynamic systems
-%%    \begin{subequations}
-%%        \small
-%%        \begin{align}
-%%            & \dot{x} = Ax + Bu\\
-%%            & u = -Kx\\
-%%            & J(u) = \int_{0}^{\infty} (x^TQx + u^TRu + 2x^TNu)dt\\
-%%            & A^TS+SA-(SB+N)R^{-1}(B^TS+N^T)+Q=0\\
-%%            & K=R^{-1}(B^TS+N^T)
-%%        \end{align}
-%%    \label{eq:LQR_EQ}
-%%    \end{subequations}
-\begin{figure}
-    \centering
-    % \missingfigure{Insert figure.}
-    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.92\textwidth,keepaspectratio=true]{figs/ipe/algorithmFramework}}
-    \caption{A desired orientation is given by a user.
-The difference between this input and the actual position is calculated.
-The controller the calculates the proper amount of voltage to apply to the DC motors.}
-    \label{fig:algorithmFramework}
-\end{figure}
-%\end{itemize} 
+\begin{itemize}
+    \item MATLAB's System Identification Toolbox used to create models 
+    \item Models needed to meet best fit and error requirements
+
+\end{itemize} 
 \vskip -1cm
-\begin{enumerate}
-    \item Employ state-space representation of 2-DOF helicopter:
-    \begin{align*}
-        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
-    \end{align*}
-    \item Use state feedback law
-    \begin{center}
-        \vskip -1cm
-        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
-    \end{center}
-    \vskip -1cm
-    to minimize the quadratic cost function:
-    \begin{align*}
-        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
-    \end{align*}
-    \item Find the solution $\mathbf{S}$ to the Riccati equation
-    \begin{align*}
-        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
-    \end{align*}    
-    \item Calculate gain, $\mathbf{K}$
-    \begin{center}
-        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
-    \end{center}
-\end{enumerate}
+%\begin{enumerate}
+%    \item Employ state-space representation of 2-DOF helicopter:
+%    \begin{align*}
+%        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
+%    \end{align*}
+%    \item Use state feedback law
+%    \begin{center}
+%        \vskip -1cm
+%        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
+%    \end{center}
+%    \vskip -1cm
+%    to minimize the quadratic cost function:
+%    \begin{align*}
+%        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
+%    \end{align*}
+%    \item Find the solution $\mathbf{S}$ to the Riccati equation
+%    \begin{align*}
+%        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
+%    \end{align*}    
+%    \item Calculate gain, $\mathbf{K}$
+%    \begin{center}
+%        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
+%    \end{center}
+%\end{enumerate}
 
@@
 \begin{itemize}
-    \item Utilizes gain calculated in LQR
-    \item Added Kalman filter to reduce external disturbances to the system
-%    \begin{subequations}
-%        \small
-%        \begin{align}
-%            & some eq = x\\
-%            & some eq = y\\
-%            & some eq = z
-%        \end{align}
-%    \label{eq:LQG_EQ}
-%    \end{subequations}
+    \item Used MATLAB's Neural Network Time Series App
+    \item Generated models using the Bayesian Regularization Algorithm
+    \item Models trained using collected log data  
 \end{itemize}
-%\todo[inline]{Insert Dr. Miah's LQG image from his slides here}
+
 \begin{figure}
     \centering
-    % \missingfigure{Insert figure.}
-    % \fcolorbox{gray!10}{gray!10}{\includegraphics[width=1.05\textwidth,keepaspectratio=true]{figs/img/LQG_SimulinkResize.png}}
-    \caption{Noise resistant 2-DOF helicopter model.}
-    \label{fig:LQGModel}
+		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+	\caption{Steering System Training Plots}
+    \label{fig:SteeringSysNeuralNetwork}
+\end{figure}
+
+\begin{figure}
+    \centering
+		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
+	\caption{Acceleration System Training Plots}
+    \label{fig:AccelerationSysNeuralNetwork}
+\end{figure}
+
+\begin{figure}
+    \centering
+		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
+	\caption{Brake System Training Plots}
+    \label{fig:BrakeSysNeuralNetwork}
 \end{figure}

### 2022-04-08 poster.tex
Poster Updates
I added some graphs to the poster under the transfer function modeling section.

@@
 \vskip -1cm
-%\begin{enumerate}
-%    \item Employ state-space representation of 2-DOF helicopter:
-%    \begin{align*}
-%        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
-%    \end{align*}
-%    \item Use state feedback law
-%    \begin{center}
-%        \vskip -1cm
-%        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
-%    \end{center}
-%    \vskip -1cm
-%    to minimize the quadratic cost function:
-%    \begin{align*}
-%        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
-%    \end{align*}
-%    \item Find the solution $\mathbf{S}$ to the Riccati equation
-%    \begin{align*}
-%        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
-%    \end{align*}    
-%    \item Calculate gain, $\mathbf{K}$
-%    \begin{center}
-%        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
-%    \end{center}
-%\end{enumerate}
+\begin{figure}
+	\centering
+	{\includegraphics[width=0.48\linewidth]{figs/img/byWireSteeringTransferFunctionModel}}
+		{\includegraphics[width=0.48\linewidth]{figs/img/manualSteeringTransferFunctionModel}}
+	\caption{Steering System Estimated Steering Angle Comparison}
+\end{figure}
+
+\begin{figure}
+	\centering
+	{\includegraphics[width=0.48\linewidth]{figs/img/byWireAccelArxModel}}
+	{\includegraphics[width=0.48\linewidth]{figs/img/manualAccelTransferFunctionModel}}
+	\caption{Acceleration System Estimated Pedal Position Comparison}
+\end{figure}
 

### 2022-04-11 poster.tex
Poster Changes
I added to the Problem Setup and Experimental Results sections
Updated poster
Experimental Setup & Neural Network Algorithm Section

@@
 
-%$\bullet$ Data Collection Setup 
-\begin{itemize}
-	\item Data Collection Setup
-		\item Lexus RX450H vehicle platform
-	\item Laptop
-	\item PACMod ECU 
-	\item CANCase
-	\item CAN Bus 
-\end{itemize}
+$\bullet$ Collected data using a Lexus RX450H vehicle platform
 
@@
   \centering
-    % \fcolorbox{gray!10}{gray!10}{\includegraphics[width=.9\textwidth,keepaspectratio=true]{figs/ipe/ADP_Neural_Network.eps}}
-    \caption{ADP Neural Network}
-    \label{fig:NeuralNetwork}
+      \tikzset{%
+        input neuron/.style={
+          circle,
+          fill=green!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        hidden neuron/.style={
+          circle,
+          fill=blue!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        output neuron/.style={
+          circle,
+          fill=red!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+
+        \foreach \m/\l [count=\y] in {1,2,missing,3}
+        \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
+
+        \foreach \m [count=\y] in {1,2,3,missing,4}
+        \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
+
+        \foreach \m [count=\y] in {1,missing,2}
+        \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*1.2) {};
+
+        \foreach \l [count=\i] in {1,2,n}
+        \draw [<-] (input-\i) -- ++(-1,0)
+        node [above, midway] {$\mathbf{e}_{k,\l}$};
+
+        \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
+        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};
+
+        \foreach \l [count=\i] in {1,m}
+        \draw [->] (output-\i) -- ++(1,0)
+        node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};
+
+        \foreach \i in {1,...,3}
+        \foreach \j in {1,...,4}
+        \draw [->] (input-\i) -- (hidden-\j);
+
+        \foreach \i in {1,...,4}
+        \foreach \j in {1,2}
+        \draw [->] (hidden-\i) -- (output-\j);
+
+        \foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
+        \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
+
+        \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
+        \draw[->,ultra thick](3,-2.5) -- (3,1.6);
+
+      \end{tikzpicture}
+  \caption{Actor neural network structure for approximating control input.}
+  \label{fig:nnActor}
 \end{figure}
@@
 %-----------------------------------------------------------
-%\begin{block}{Subsystem Block Diagram}
-%\begin{figure}
-%    \centering
-%        \missingfigure{Insert figure.}
-%    % \boxed{\includegraphics[width=.92\textwidth,keepaspectratio=true]{figs/ipe/subsystemBlockDiagramAlternate2}}
-%    \label{fig:subsystem}
-%\end{figure}
-%\end{block}
 
@@
 %-----------------------------------------------------------
-
-%\begin{block}{Simulation Results}
-%\vskip -1cm
-%%\begin{itemize}
-%%    \item \todo[inline]{add LQR and LQG simulation results}
-%%\end{itemize}
-%
-%%Before implementing the algorithm, it was simulated using the industry standard robot simulator V-REP.
-With numerous robot models available, V-REP is able to accurately and consistently produce like those expected in real--world scenarios.
-Preliminary simulation results can be seen in Fig.~\ref{fig:vrepResults}.
-%
-%\begin{figure}
-%    \centering
-%    \subfigure[][]{
-%    %\missingfigure{Insert figure.}
-%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch}
-%    \label{fig:simStepPitch}
-%    }
-%    \subfigure[][]{
-%    %\missingfigure{Insert figure.}
-%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw}
-%    \label{fig:simStepYaw}
-%    }
-%    \subfigure[][]{
-%    %\missingfigure{Insert figure.}
-%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch_Volt}
-%    \label{fig:simPitchVolt}
-%    }
-%    \subfigure[][]{
-%    %\missingfigure{Insert figure.}
-%    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw_Volt}
-%    \label{fig:simYawVolt}
-%    }
-%    \caption{A comparison between LQG and LQR control for a step input is shown for \subref{fig:simStepPitch}~the~main~rotor and \subref{fig:simStepYaw}~the~tail~rotor and the corresponding voltages in \subref{fig:simPitchVolt}~and~\subref{fig:simYawVolt}}
-%    \label{fig:simResults}
-%\end{figure}
-%\vskip -2cm
-%\end{block}
 
@@
 \vskip -1cm
-%\begin{itemize}
-%    \item ADP Algorithm
-%\end{itemize}
+\begin{itemize}
+    \item Preliminary model testing conducted before sending models to AutonomouStuff 
+    \item Official testing conducted at AutonomouStuff using...
+\end{itemize}
 \begin{figure}
     \centering
-    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/ipe/setup.eps}}
+    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilBenchAstuff.jpg}}
     \caption{Experimental Setup}
@@
     \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Pitch_ADP_LQR}
-    \label{fig:stepPitchADP}
+    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
     }
     \subfigure[][]{
-    %\missingfigure{Insert figure.}
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Yaw_ADP_LQR}
-    \label{fig:stepYawADP}
+    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
     }
-    \caption{ADP experimental results for \subref{fig:stepPitchADP}~the~main~rotor and \subref{fig:stepYawADP}~the~tail~rotor given a step input}
-    \label{fig:ADP_Results}
+    \caption{Verifying voltage measurements on the HIL Bench}
 \end{figure}
-%\begin{itemize}
-%    \item Comparison between different controller architectures (proportional controller and proportional controller with integral term)
-%\end{itemize}
+
 \vskip -.5cm
 
-\begin{figure}
-    \centering
-    \subfigure[][]{
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Pitch_LQR_RMSE}
-    \label{fig:stepPitch}
-    }
-    \subfigure[][]{
-    % \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Yaw_LQR_RMSE}
-    \label{fig:stepYaw}
-    }
-    \caption{Comparison between P and PI control for a step input is shown for \subref{fig:stepPitch}~the~main~rotor and \subref{fig:stepYaw}~the~tail~rotor}
-    \label{fig:expResults}
-\end{figure}
 \vskip -2cm
 \end{block}
-
-\begin{figure}
-  \centering
-  \subfigure[][]{
-  \label{fig:time0}
-  % \includegraphics[width=0.4\textwidth]{figs/img/timeEquals0.jpg}
-  }
-  \subfigure[][]{
-  \label{fig:time10}
-  % \includegraphics[width=0.4\textwidth,height=0.057\textheight]{figs/img/timeEquals10_2}
-  }  
-  \caption{\subref{fig:time0} Time = 0~and~\subref{fig:time10} Time = 10}
-  \label{fig:posistionAtTime}
-\end{figure}
-
-%\begin{block}{Conclusion}
-
-%As seen in the experimental results, this system brings moderate accuracy considering its implementation.
-With a total cost of around \$140 for the system mounted on the mobile robot and around \$23 for the beacons, this system is much more attainable for those conducting research in mapping and localization algorithms and inexpensive to scale to commercial applications.
-
-%\end{block}
 

### 2022-04-13 reportTII-ArticleHIL.tex
Updated report
Included images from Astuff visit; cleaned formatting; pushed updated pdf

@@
 \title{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}
-\author{First A. Author, \IEEEmembership{Fellow, IEEE}, Second B. Author, and Third C. Author, Jr., \IEEEmembership{Member, IEEE}
-\thanks{This paragraph of the first footnote will contain the date on 
-which you submitted your paper for review. It will also contain support 
-information, including sponsor and financial support acknowledgment. For 
-example, ``This work was supported in part by the U.S. Department of 
-Commerce under Grant BS123456.'' }
-\thanks{The next few paragraphs should contain 
-the authors' current affiliations, including current address and e-mail. For 
-example, F. A. Author is with the National Institute of Standards and 
-Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov). }
-\thanks{S. B. Author, Jr., was with Rice University, Houston, TX 77005 USA. He is 
-now with the Department of Physics, Colorado State University, Fort Collins, 
-CO 80523 USA (e-mail: author@lamar.colostate.edu).}
-\thanks{T. C. Author is with 
-the Electrical Engineering Department, University of Colorado, Boulder, CO 
-80309 USA, on leave from the National Research Institute for Metals, 
-Tsukuba, Japan (e-mail: author@nrim.go.jp).}
+\author{Hannah Grady, Nicholas Nauman, and Dr. Suruz Miah
+\thanks{This paper was submitted for review on 5/3/22.
+This project was supported by Hexagon's AutonomouStuff with special thanks to Joe Buckner, Erik Guetz, Sai Chittemsetty, Matt Goben, and Travis Catton.}
+\thanks{Hannah Grady is an electrical engineering student at Bradley University, Peoria, IL 61625 USA (e-mail: hgrady@mail.bradley.edu).}
+\thanks{Nicholas Nauman is an electrical engineering student at Bradley University, Peoria, IL 61625 USA (e-mail: nnauman@mail.bradley.edu).}
+\thanks{Dr. Suruz Miah is a professor for the Electrical Engineering Department, Bradley University, Peoria, IL 
+61625 USA, (e-mail: smiah@bradley.edu).}
 }
@@
 (Add section about testing and results).
-
-%These instructions give you guidelines for preparing papers for 
-%IEEE Transactions and Journals. Use this document as a template if you are 
-%using \LaTeX. Otherwise, use this document as an 
-%instruction set. The electronic file of your paper will be formatted further 
-%at IEEE. Paper titles should be written in uppercase and lowercase letters, 
-%not all uppercase. Avoid writing long formulas with subscripts in the title; 
-%short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
-%not write ``(Invited)'' in the title. Full names of authors are preferred in 
-%the author field, but are not required. Put a space between authors' 
-%initials. The abstract must be a concise yet comprehensive reflection of 
-%what is in your article. In particular, the abstract must be self-contained, 
-%without abbreviations, footnotes, or references. It should be a microcosm of 
-%the full article. The abstract must be between 150--250 words. Be sure that 
-%you adhere to these limits; otherwise, you will need to edit your abstract 
-%accordingly. The abstract must be written as one paragraph, and should not 
-%contain displayed mathematical equations or tabular material. The abstract 
-%should include three or four different keywords or phrases, as this will 
-%help readers to find it. It is important to avoid over-repetition of such 
-%phrases as this can result in a page being rejected by search engines. 
-%Ensure that your abstract reads well and is grammatically correct.
 \end{abstract}
@@
   \centering
-  %  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
     \includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
@@
 	\draw[stealth-,thick]
-    (plant.-130)--node[very near end,above](in1){Input 1}++(-1.9,0);    
+    (plant.145)--node[very near end,above](in1){Input 1}++(-1.9,0);    
     \draw[stealth-,thick]
@@
     \draw[-stealth,thick]
-    (plant.130)--node[very near end,above](inn){Input n}++(1.9,0);
-
-    \draw[-stealth,thick]
-    (plant.-45)--node[very near end,above](out1){Output 1}++(1.9,0);
+    (plant.-145)--node[very near end,above](inn){Input n}++(1.9,0);
+
+    \draw[-stealth,thick]
+    (plant.30)--node[very near end,above](out1){Output 1}++(1.9,0);
     \draw[-stealth,thick]
@@
     \draw[-stealth,thick]
-    (plant.0)--node[very near end,above](outm){Output m}++(1.9,0);
-
+    (plant.-30)--node[very near end,above](outm){Output m}++(1.9,0);
   \end{tikzpicture}
@@
 
-The neural network inputs are mapped to the outputs by being assigned a set of weights. 
+The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}.
 The approximated neural network signal can be written as:
@@
  The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set.
-An acceptable neural network model will meet the desired error requirements.
+An acceptable neural network model will meet the desired error requirements~\footnote{\url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.
 
@@
 
-\todo[inline]{Add subsections for each subsystem on how NNs are used to model each subsystem}
-
-\todo[inline]{For each subsystem you will need to draw different NN structure }
-
 \section{Validation and Testing} \label{sec:simresults}
-
-%To start this project, we first read documentation outlining the uses of
-%MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
-%on how to model systems from data using System Identification and then find the
-%most accurate model. We specifically tried to find examples with Multiple-Input
-%Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
-%most of the vehicle subsystems we will model fall into one of these categories.
-%A literature review was also conducted to see how systems with small
-%non-linearities like our steering subsystem were modeled using System
-%Identification.
 
@@
 
-\todo[inline]{Discuss results using the setup you explained in the previous section. See some IEEE papers}
-
 \subsubsection{Steering Subsystem}
@@
 for this model is 90.27\%.
-
-  % %
-  % \begin{figure}
-  %   \centering
-  %   \begin{subfigure}[b]{0.48\linewidth}
-  %     \centering
-  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsTopViewV3}
-  %     \caption{}
-  %     \label{fig:PowertrainModelCorrectDimsTopViewV3}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.48\linewidth}
-  %     \centering
-  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsFrontViewV4}
-  %     \caption{}
-  %     \label{fig:PowertrainModelCorrectDimsFrontViewV4}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.48\linewidth}
-  %     \centering
-  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsSideViewV4}
-  %     \caption{}
-  %     \label{fig:PowertrainModelCorrectDimsSideViewV4}
-  %   \end{subfigure}
-  %   \caption{\subref{fig:PowertrainModelCorrectDimsTopViewV3} Top view,
-  %     \subref{fig:PowertrainModelCorrectDimsFrontViewV4} front view, and
-  %     \subref{fig:PowertrainModelCorrectDimsSideViewV4} side view of the
-  %     proposed disinfecting robot.}
-  %   \label{fig:2dViewsDisinfectingRobot}
-  % \end{figure}
 
@@
 
-\todo[inline]{Discuss results  NN modeling using the setup you explained in the previous section. See some IEEE papers}
-
 \subsection{Discussion}
@@
 The neural network models, however, track the data more accurately and reduced the error significantly so that all error requirements were met.
+We first proved that the neural network models that we developed were accurate using subsets of data as inputs to a Simulink model.
+Then we visited AutonomouStuff to generate the models on their HIL bench, as shown in Fig.~\ref{fig:hilBench}, using Control Desk to interface.
+Due to time constraints, AutonomouStuff was not able to get the proper hardware for this project connected to the HIL bench but we were able to test our models in an open-loop configuration and measure outputs to show that the correct voltages would be fed to any hardware that would be connected, shown in Fig.~\ref{fig:hilMeasuring}.
 One downside to using neural networks as the plant model is it causes some complexities when trying to include these models into the HIL bench software for use in developing and testing controllers.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.48\linewidth}
+		\centering    		
+    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
+    		\caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\linewidth}
+		\centering    		
+    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+    		\caption{}
+    \end{subfigure}
+    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}}
+    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}}
+    \caption{Verifying voltage measurements on the HIL Bench}
+    \label{fig:hilMeasuring}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.95\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
+	\caption{AutonomouStuff HIL Bench Configuration}
+	\label{fig:hilBench}
+\end{figure}
 
@@
 
-\section*{Acknowledgments}
-The authors would like to thank Erik Guetz, Joe Buckner, Sai Chittemsetty, Matt Goben, and AutonomouStuff for their help and collaboration with this project.
-Without their support this project would never have been possible.
-
 \bibliographystyle{IEEEtran}
@@
 
-% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.eps}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
-% biographies. Biographies are often not included in conference-related
-% papers. This author became a Member (M) of IEEE in 1976, a Senior
-
-%
-% Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
-% contain a place and/or date of birth (list place, then date). Next,
-% the author's educational background is listed. The degrees should be
-% listed with type of degree in what field, which institution, city,
-% state, and country, and year the degree was earned. The author's major
-% field of study should be lower-cased.
-
-% The second paragraph uses the pronoun of the person (he or she) and not the 
-% author's last name. It lists military and work experience, including summer 
-% and fellowship jobs. Job titles are capitalized. The current job must have a 
-% location; previous positions may be listed 
-% without one. Information concerning previous publications may be included. 
-% Try not to list more than three books or published articles. The format for 
-% listing publishers of a book within the biography is: title of book 
-% (publisher name, year) similar to a reference. Current and previous research 
-% interests end the paragraph. The third paragraph begins with the author's 
-% title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
-% List any memberships in professional societies other than the IEEE. Finally, 
-% list any awards and work for IEEE committees and publications. If a 
-% photograph is provided, it should be of good quality, and 
-% professional-looking. Following are two examples of an author's biography.
-% \end{IEEEbiography}
-
-% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.eps}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
-% 1977. He received the B.S. and M.S. degrees in aerospace engineering from 
-% the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
-% mechanical engineering from Drexel University, Philadelphia, PA, in 2008.
-
-% From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
-% Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
-% Mechanical Engineering Department, Texas A{\&}M University, College Station. 
-% He is the author of three books, more than 150 articles, and more than 70 
-% inventions. His research interests include high-pressure and high-density 
-% nonthermal plasma discharge processes and applications, microscale plasma 
-% discharges, discharges in liquids, spectroscopic diagnostics, plasma 
-% propulsion, and innovation plasma applications. He is an Associate Editor of 
-% the journal \emph{Earth, Moon, Planets}, and holds two patents.
-
-% Dr. Author was a recipient of the International Association of Geomagnetism 
-% and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
-% Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
-% \end{IEEEbiography}
-
-% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.eps}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
-% engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
-% and the M.S. degree in mechanical engineering from National Tsing Hua 
-% University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
-% degree in mechanical engineering at Texas A{\&}M University, College 
-% Station, TX, USA.
-
-% From 2008 to 2009, he was a Research Assistant with the Institute of 
-% Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
-% development of surface processing and biological/medical treatment 
-% techniques using nonthermal atmospheric pressure plasmas, fundamental study 
-% of plasma sources, and fabrication of micro- or nanostructured surfaces.
-
-% Mr. Author's awards and honors include the Frew Fellowship (Australian 
-% Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
-% Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
-% Award and the Adolph Lomb Medal (OSA).
-% \end{IEEEbiography}
-
 \end{document}

### 2022-04-13 finalReportPres.tex
Update final report presentation and lab notebook
Update finalReportPres.tex
I added to the Modeling using Neural Networks slide
Updated Final Presentation

@@
 
-\subject{Mobile Robot Localization}
+\subject{Plant Modeling for Autonomous Vehicle}
 % This is only inserted into the PDF information catalog. Can be left
@@
     \begin{Large}
-    		Use neural network modeling techniques to develop models
+    		Use neural network modeling techniques to develop plant models
     \end{Large}
@@
 %----------------------------------
-
-%----------------------------------
-
-%\begin{frame}{Introduction}{Previous Work}
-%  \begin{block}{Existing Solution}
-%        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
-%  \end{block}
-%    % \begin{figure}[b]
-%    %     \centering
-%    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
-%    %     \caption{CompaRob}
-%    %     %\label{fig:sysBlockDiag}
-%    % \end{figure}
-%\end{frame}
-%
-%%----------------------------------
-%
-%\begin{frame}{Introduction}{Previous Work}
-%  \begin{block}{Existing Solution}
-%        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
-%  \end{block}
-%    % \begin{figure}[b]
-%    %     \centering
-%    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
-%    %     \caption{Shopping Support Robot}
-%    %     %\label{fig:sysBlockDiag}
-%    % \end{figure}
-%\end{frame}
 
@@
 \end{frame}
+
 %---------------------------
@@
 
-\begin{frame}{System Identification Preliminaries}{Examples}
-  \begin{block}{}
-    \begin{LARGE}
-
-    \end{LARGE}
-  \end{block}
-  \begin{block}{}
-    \begin{LARGE}
-
-    \end{LARGE}
-  \end{block}
-\end{frame}
 %-------------------------
@@
 \begin{frame}{Modeling using Neural Networks}{}
+	\begin{block}{}
+ \begin{itemize}
+        \item Used MATLAB's Neural Network Time Series App 
+        \item All models generated using the Bayesian Regularization Algorithm 
+        \item Models trained using collected log data 
+\end{itemize}
+  \end{block}
+\end{frame}
 
-\end{frame}
 %-------------------------
 \section{Modeling Vehicle Subsystems}
-
-\begin{frame}{Modeling Vehicle Subsystems}{}
-
-\end{frame}
 
@@
 
+\begin{frame}{Validation and Testing}{Validation Setup}
+
+\end{frame}
+
 \begin{frame}{Transfer Function Modeling}{Steering System}
-	\begin{block}
+	\begin{block}{}
  \begin{itemize}
@@
 \begin{frame}{Transfer Function Modeling}{Acceleration System}
-	\begin{block}
+	\begin{block}{}
  \begin{itemize}
@@
 \begin{frame}{Transfer Function Modeling}{Brake System}
-
+\begin{block}{}
+ \begin{itemize}
+	\item Only manual models were considered 
+	\item There were no transfer function models that could satisfy both the best fit and error requirements 
+ \end{itemize}
+% \begin{figure}
+%    \centering
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+%        \caption{Output of Estimated By-Wire System Model}
+%        \label{fig:byWireSteerModel}
+%    \end{minipage}\hfill
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+%        \caption{Output of Estimated Manual System Model}
+%        \label{fig:manualSteerModel}
+%    \end{minipage}
+%\end{figure}
+  \end{block}
 \end{frame}
@@
 \begin{frame}{Neural Network Modeling}{Steering System}
-	\begin{block}
+	\begin{block}{}
   		\begin{figure}[H]
@@
 \begin{frame}{Neural Network Modeling}{Acceleration System}
-	\begin{block}
+	\begin{block}{}
   		\begin{figure}[H]
@@
 \begin{frame}{Neural Network Modeling}{Brake System}
-	\begin{block}
+	\begin{block}{}
 \begin{figure}[H]

### 2022-04-13 finalReportPres.tex
Updated Final Presentation

@@
 \usepackage{rotating}
+\usepackage{amsmath,amssymb,amsfonts,bm}
 
@@
 	\begin{block}{}
+		\begin{figure}
+			\centering
+      \tikzset{%
+        input neuron/.style={
+          circle,
+          fill=green!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        hidden neuron/.style={
+          circle,
+          fill=blue!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        output neuron/.style={
+          circle,
+          fill=red!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+
+        \foreach \m/\l [count=\y] in {1,2,missing,3}
+        \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
+
+        \foreach \m [count=\y] in {1,2,3,missing,4}
+        \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
+
+        \foreach \m [count=\y] in {1,missing,2}
+        \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*1.2) {};
+
+        \foreach \l [count=\i] in {1,2,n}
+        \draw [<-] (input-\i) -- ++(-1,0)
+        node [above, midway] {$\mathbf{e}_{k,\l}$};
+
+        \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
+        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};
+
+        \foreach \l [count=\i] in {1,m}
+        \draw [->] (output-\i) -- ++(1,0)
+        node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};
+
+        \foreach \i in {1,...,3}
+        \foreach \j in {1,...,4}
+        \draw [->] (input-\i) -- (hidden-\j);
+
+        \foreach \i in {1,...,4}
+        \foreach \j in {1,2}
+        \draw [->] (hidden-\i) -- (output-\j);
+
+        \foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
+        \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
+
+        \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
+        \draw[->,ultra thick](3,-2.5) -- (3,1.6);
+
+      \end{tikzpicture}
+  \caption{Actor neural network structure for approximating control input.}
+  \label{fig:nnActor}
+		\end{figure}
+	\end{block}
+\end{frame}
+
+\begin{frame}
+Therefore, approximated actor signal can be written as:
+\begin{align}
+  \label{eq:approximatePolicyActorWeights}
+    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
+  \end{align}
+%
+where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
+%
+\begin{align*}
+  {\bf W}_a = 
+  \begin{bmatrix}
+    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
+    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
+    \vdots & \ddots & \ldots &\vdots\\
+    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
+  \end{bmatrix}.
+\end{align*}
+%
+
+Now take $\eta$ data points and form the set of linear equations as: %
+%
+\begin{align*}
+&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
+ & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
+                                            &\vdots \\
+ & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
+\end{align*}
+%
+
+\end{frame}
+
+\begin{frame}
+  In compact form:
+  \begin{align*}
+    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
+    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
+  \end{align*}
+  %
+  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
+
+  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
+  \begin{align*}
+    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+  \end{align*}
+
+Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
+%
+\begin{align*}
+  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+\end{align*}
+%
+Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
+%
+\begin{align}
+  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
+  \label{eq:actorWeightsGradient}
+\end{align}
+%
+Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
+\begin{align*}
+  {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+\end{align*}
+
+\end{frame}
+
+\begin{frame}
+$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
+
+\begin{multline}
+  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
+  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
+  \label{eq:actorWeightUpdate}
+\end{multline}
+
+\end{frame}
+
+\begin{frame}{Modeling using Neural Networks}{}
+	\begin{block}{}
  \begin{itemize}
@@
 \begin{frame}{Validation and Testing}{Validation Setup}
-
+	\begin{figure}
+		\centering \includegraphics[width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
+		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
+		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
+		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+	\end{figure}
 \end{frame}
@@
  \begin{itemize}
-	\item Best fit percentage of the by-wire steering estimated model is 85.54
+	\item Best fit percentage of the by-wire steering estimated model is 83.25
 	\item Best fit percentage of the manual steering estimated model is 90.27
@@
  \begin{itemize}
-	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
+	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
 	\item Best fit percentage of the manual acceleration estimated model is 98.3

### 2022-04-15 reportTII-ArticleHIL.tex

@@
 
-The steering subsystem consists of steering, the power steering motors, $\ldots$ The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
+The steering subsystem consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
+The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
 Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
@@
   \subsection{Brake Subsystem}
-  The brake subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
+ The brake subsystem is made up of the master cylinder, brake rotor, brake drum, brake pad, brake caliper, brake shoe, brake booster, brake pedal, wheel speed sensors, ABS module, and brake lines~\footnote{\url{https://oards.com/car-brake-system-components/}}.
+The subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
 Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed.
@@
   \subsection{Acceleration Subsystem}
-  The acceleration subsystem is a multiple-input multiple-output system. 
+  The acceleration subsystem consists of the throttle pedal, engine, and crankshaft~\footnote{\url{https://harrisautomotiverepair.com/car-accelerator/}}.
+It is a multiple-input multiple-output system.
 Acceleration pedal voltages are sent to the subsystem. 
@@
   \subsection{Shift Subsystem}
+ The components that make up the shift subsystem are the friction clutch, bands, spring loaded valve, load sensor, shift valve, torque converter, gear stick, seals, and gasket~\footnote{\url{https://oards.com/car-automatic-transmission-system-components/}}.
 This subsystem can be classified as a single-input single-output system.
@@
   \subsection{Speed Control Subsystem}
-  The speed control subsystem is a straightforward single-input single-output system.
+  The speed control subsystem components include the cruise control switch, vehicle speed sensor, throttle sensor, and brake switch~\footnote{\url{https://www.freeasestudyguides.com/electrical-cruise-control-systems.html}}.
+This subsystem is a straightforward single-input single-output system.
 The desired vehicle speed is set by the user and sent to the speed control subsystem.

### 2022-04-15 reportTII-ArticleHIL.tex
Fixed Fig. 13: MIMO system block diagram

@@
     % place nodes
-    \node[block,text width=1.75cm,text centered](plant){};
+    \node[block,text width=1.75cm,text centered](plant){MIMO system};
 
@@
 	\draw[stealth-,thick]
-    (plant.145)--node[very near end,above](in1){Input 1}++(-1.9,0);    
-    \draw[stealth-,thick]
-    (plant.180)--node[very near end,above](in2){Input 2}++(-1.9,0);
-    %\draw[ultra thick,Dotted] (in2) -- (inn);
-    \draw[-stealth,thick]
-    (plant.-145)--node[very near end,above](inn){Input n}++(1.9,0);
-
-    \draw[-stealth,thick]
-    (plant.30)--node[very near end,above](out1){Output 1}++(1.9,0);
-    \draw[-stealth,thick]
-    (plant.0)--node[very near end,above](out2){Output 2}++(1.9,0);
-    %\draw[ultra thick,Dotted] (out2) -- (outm);
-    \draw[-stealth,thick]
-    (plant.-30)--node[very near end,above](outm){Output m}++(1.9,0);
+  (plant.150)--++(-1.2,0)node[left](in1){$x_1$};    
+    \draw[stealth-,thick]
+    (plant.170)--++(-1.2,0)node[left](in2){$x_2$};
+    \draw
+    ($(plant.180)+(-0.5,0)$)node[yshift=-0.9mm]{$\vdots$};
+    \draw[stealth-,thick]
+    (plant.-150)--++(-1.2,0)node[left](inn){$x_n$};
+
+    \draw[-stealth,thick]
+    (plant.30)--++(1.2,0)node[right](out1){$y_1$};
+    \draw[-stealth,thick]
+    (plant.10)--++(1.2,0)node[right](out2){$y_2$};
+    \draw
+    ($(plant.0)+(0.5,0)$)node[yshift=-0.9mm]{$\vdots$};
+    \draw[-stealth,thick]
+    (plant.-30)--++(1.2,0)node[right](outm){$y_m$};
   \end{tikzpicture}

### 2022-04-15 poster.tex
Poster, presentation, and report edits
Updated Poster

@@
 \vskip -1cm
-\begin{itemize}
-    %\item Reinforcement learning based approach
-    \item Uses neural network based on difference between desired and actual orientation to determine optimal gain
-    %\item Unlike LQR, ADP operates only in discrete-time and calculates new gains as the system is running
-%    \begin{subequations}
-%        \small
-%        \begin{align}
-%            & some eq = x\\
-%            & some eq = y\\
-%            & some eq = z
-%        \end{align}
-%    \label{eq:ADP_EQ}
-%    \end{subequations}
-\end{itemize} 
-%\begin{enumerate}
-%    \item Apply input to the system and calculate error e(k) at time k
-%    \item Use Euler's method to convert the error model into discrete-time and record data every $\tau \sec$
-%    \begin{center}
-%        $e_{k+1}=f(e_k)+G(e_k)u_k$
-%    \end{center}
-%    \item 
-%    %\item Minimize the cost function
-%    %\begin{center}
-%        $J(u)=\sum_{k=0}^{\infty} e_k^TQe_k+u_k^TRu_k$
-%    %\end{center}
-%    %\item Define value function
-%    %\begin{center}
-%        $V(e_k)=$
-%    %\end{center}    
-%    \item Solve for gain, K
-%    \begin{center}
-%        $K=0.5R^{-1}B^TP$
-%    \end{center}
-%\end{enumerate}
 
@@
 \vskip 1.5cm
-%(1) t = kτ where τ is given
-%(2)Advance the system by applying determined inputs to the system and measure system states
-%(3)Calculate state error as e[k] = xref[k] − x[k], save state error
-%(4) If t 6= T, increment k and start at (1)
-%(5) If t = T, update K using collected error data
-%(5a)Use error states since last update of K as inputs to the neural network
-%(5b)Recursively determine wc values for each of the instances
-%(5c)Approximate new wc value using regression analysis of the individually calculated wc values
-%(6)Calculate new K using wc values
-%(7) Increment k and start at (1)
+
+The neural network inputs are mapped to the outputs by being assigned a set of weights. 
+The approximated neural network signal can be written as:
+\begin{align}
+  \label{eq:approximatePolicyActorWeights}
+    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
+  \end{align}
+%
+where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
+%
+\begin{align*}
+  {\bf W}_a = 
+  \begin{bmatrix}
+    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
+    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
+    \vdots & \ddots & \ldots &\vdots\\
+    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
+  \end{bmatrix}.
+\end{align*}
+%
+In compact form:
+  \begin{align*}
+    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
+    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
+  \end{align*}
+  %
+  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
+
+  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
+  \begin{align*}
+    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+  \end{align*}
+
+Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
+%
+\begin{align*}
+  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+\end{align*}
+%
+Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
+%
+\begin{align}
+  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
+  \label{eq:actorWeightsGradient}
+\end{align}
+%
+Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
+\begin{align*}
+  {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+\end{align*}
+
+ The neural network is trained by altering the weights to minimize the least square error by utilizing the gradient descent approach which is defined as:
+ \begin{multline}
+  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
+  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
+  \label{eq:actorWeightUpdate}
+\end{multline}
 
@@
     \item Preliminary model testing conducted before sending models to AutonomouStuff 
-    \item Official testing conducted at AutonomouStuff using...
+    \item Official testing conducted using dSPACE software and HIL Bench 
 \end{itemize}
@@
     \caption{Verifying voltage measurements on the HIL Bench}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/img/aStuffValidationBrakeModel.jpg}}
+    \caption{Model validation setup}
+    \label{fig:Setup}
 \end{figure}

### 2022-04-15 poster.tex
Updated poster
Formatting Fixes and correcting neural network algorithm block

@@
 \usepackage{siunitx} % for units like degree, ...
-\sisetup{unitsep=\cdot,binary-units=true}
+%\sisetup{unitsep=\cdot,binary-units=true}
 \usepackage{mathtools}
@@
 \textbf{Objective}
-\vskip -0.75cm
+%\vskip -0.75cm
 \begin{itemize}
@@
 %
-\vskip -1cm
+%\vskip -1cm
 \textbf{Contribution}
-\vskip -0.75cm
+%\vskip -0.75cm
 \begin{itemize}
@@
 \end{itemize}
-\vskip -0.75cm
+%\vskip -0.75cm
 \textbf{Applications}
-\vskip -0.75cm
+%\vskip -0.75cm
 \begin{itemize}
@@
 %-----------------------------------------------------------
-\vskip -1cm
-\begin{block}{Problem Setup}
+%\vskip -1cm
+\begin{alertblock}{Problem Setup}
 %\vskip -1cm
@@
 \vskip -1cm
-\end{block}
+\end{alertblock}
 
@@
 
-\begin{block}{Transfer Function Modeling}
-\vskip -1cm
+\begin{alertblock}{Transfer Function Modeling}
+\vskip 0.5cm
 \begin{itemize}
@@
 %\vskip -2.5cm
-\end{block}
+\end{alertblock}
 
@@
 
-\begin{block}{Neural Network Modeling}
-\vskip -1cm
+\begin{alertblock}{Neural Network Modeling}
+\vskip 0.5cm
 \begin{itemize}
@@
 
-\begin{block}{Neural Network Algorithm}
-\vskip -1cm
+\begin{alertblock}{Neural Network Algorithm}
+\vskip 0.5cm
 
@@
 
-      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+      \begin{tikzpicture}[x=3cm, y=3cm]
 
@@
 
-\vskip 1.5cm
+\vskip .5cm
 
-The neural network inputs are mapped to the outputs by being assigned a set of weights. 
-The approximated neural network signal can be written as:
-\begin{align}
-  \label{eq:approximatePolicyActorWeights}
+\begin{enumerate}
+	\item Approximate neural network signal
+	\begin{align*}
   		\hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
-  \end{align}
-%
-where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
-%
+  	\end{align*}
+  	\item Define the weight matrix
   	\begin{align*}
@@
 	\end{align*}
-%
-In compact form:
+	\item Compute the sum-of-squared error
 	\begin{align*}
@@
   	\end{align*}	
-  %
-  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
-
-  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
+  	\begin{align*}
+  		\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}}
+  	\end{align*}
 	\begin{align*}
@@
   	\end{align*}
-
-Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
-%
+  	\item Find the actor weight by minimizing the sum-of-square error
   	\begin{align*}
-  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+  	\delta_a = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
 	\end{align*}
-%
-Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
-%
-\begin{align}
+	\item Take the derivative of $\delta_a$ with respect to ${\bf W}_a$ and set $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero
+	\begin{align*}
   		\frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T 					\bm{\Sigma}\mathbf{W}_a
-  \label{eq:actorWeightsGradient}
-\end{align}
-%
-Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
+	\end{align*}
 	\begin{align*}
@@
 	\end{align*}
-
- The neural network is trained by altering the weights to minimize the least square error by utilizing the gradient descent approach which is defined as:
- \begin{multline}
-  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
+	\item Use the gradient descent approach to minimize the least square order alter weights when training the neural network
+	\begin{multline*}
+  		\mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}\\
+  		=\mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}				_a^{(r)}\right)\\
   		= \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
-  \label{eq:actorWeightUpdate}
-\end{multline}
+	\end{multline*}
+\end{enumerate}
 
 \vskip -2.5cm
-\end{block}
+\end{alertblock}
 %-----------------------------------------------------------
@@
 
-\begin{block}{Experimental Results}
-\vskip -1cm
+\begin{alertblock}{Experimental Results}
+\vskip 1cm
 \begin{itemize}
@@
     \centering
-    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilBenchAstuff.jpg}}
+    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.2\textheight,width=.95\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilBenchAstuff.jpg}}
     \caption{Experimental Setup}
@@
     \subfigure[][]{
-    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
+    \includegraphics[angle=270,width=.4\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
     }
     \subfigure[][]{
-    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+    \includegraphics[angle=270,width=.4\textwidth,keepaspectratio=true]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
     }
@@
 
-\vskip -.5cm
-
-\vskip -2cm
-\end{block}
+\vskip 2cm
+\end{alertblock}
 
@@
 \end{itemize}
-
 \end{alertblock}

### 2022-04-17 finalReportPres.tex
A few comments on final presentation and the report. More to come

@@
 \usepackage{media9}
-\usepackage{subfigure}
+% \usepackage{subfigure}
 \usepackage{booktabs,array}
@@
   \begin{block}{Problem Statement}
-    \begin{Large}
-    		Model autonomous vehicle subsystems for a Lexus platform
-    \end{Large}
+    Given input-output data of different subsystems, such as steering, acceleration, brake, shift, speed, and speed control, of an autonomous (self-driving) vehicle:
+    \begin{itemize}
+    \item Develop mathematical and/or block diagram models of these subsystems
+
+    \item Develop machine learning-based models for the major subsystems of Lexus self-driving vehicle
+    \end{itemize}
   \end{block}
@@
   \begin{block}{Proposed Solution}
-    \begin{Large}
-    		Use neural network modeling techniques to develop plant models
-    \end{Large}
+    \begin{itemize}
+    \item Use state-space modeling techniques based on input and output data
+
+    \item Use system identification modeling techniques
+
+    \item Use machine learning (neural network) based modeling techniques
+    \end{itemize}
   \end{block}
@@
 \begin{frame}{System Architecture}{}
+  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
 	\begin{block}{System Architecture}
-    \begin{large}
     The overall system architecture of this project consists of six subsystems: 
@@
       \end{itemize} 
-    \end{large}
   \end{block}
@@
 \begin{frame}{Modeling using Neural Networks}{}
-	\begin{block}{}
   \begin{figure}
@@
 
-      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+    \begin{tikzpicture}[x=1.5cm, y=1.3cm,transform shape]
 
@@
       \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
-        \draw[->,ultra thick](3,-2.5) -- (3,1.6);
+      \draw[->,ultra thick](3,-2.5) to[bend left] (3,1.6);
 
@@
 		\end{figure}
-	\end{block}
 \end{frame}
@@
 \begin{frame}
+
+\todo[inline]{Use generic input and output symbols instead of my own symbols that I used to inputs (error) and outputs (control inputs) }
   Therefore, approximated actor signal can be written as:
@@
 %
-
 \end{frame}
@@
 %
+
+\end{frame}
+
+\begin{frame}
+
   Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
@@
 
-\end{frame}
-
-\begin{frame}
 $\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
@@
 \end{multline}
+
+\todo[inline]{In your case, there is no actor neural network, I implemented generic reinforcement learning structures using actor critic neural network structure}
 
@@
 
+\begin{frame}
+
+  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
+\end{frame}
+
 \begin{frame}{Validation and Testing}{Validation Setup}
@@
 		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Validation and Testing}{Model Validation}
+	\begin{figure}
+		\centering \includegraphics[width=.45\linewidth]{figs/img/aStuffValidationBrakeModel}\quad%
+		\caption{Model Validation Setup}
+    			\label{fig:validationSetup}
+		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item Testing data points using Control Desk software  \end{itemize} \end{minipage}\\[1em]
 	\end{figure}

### 2022-04-18 finalReportPres.tex
Final project presentation tex file updated

@@
 
-\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
+\author[H.~Grady, N.~Nauman]{Hannah~Grady and Nicholas~Nauman 
 \linebreak Advisor:~Dr.~Suruz~Miah}
@@
 {
-  Department of Electrical and Computer Engineering\\
+  \inst{~}Department of Electrical and Computer Engineering\\
   Bradley University\\
@@
   Peoria, IL, 61625, USA
+  \and
+  \inst{~}\textbf{Sponsor:}~AutonomouStuff $|$~https://autonomoustuff.com/\\
+  306 Erie Avenue, Morton, IL 61550\\
+  Telephone:~309-291-0966, email:info.as.ap@hexagon.com
 }
@@
 
-\date[April~29,~2022]{Tuesday, April~29,~2022}
+\date[April~21,~2022]{Thursday, April~21,~2022}
 

### 2022-04-18 finalReportPres.tex
Updated NN Algorithm Section of Presentation

@@
       \draw [<-] (input-\i) -- ++(-1,0)
-      node [above, midway] {$\mathbf{e}_{k,\l}$};
+      node [above, midway] {$\mathbf{x}_{\l}$};
 
-      \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
+      \foreach \l [count=\i] in {1,2,3,p}
       \node [above] at (hidden-\i.north) {$\sigma_{\l}$};
@@
       \draw [->] (output-\i) -- ++(1,0)
-      node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};
+      node [above, midway] {${y}_{\l}$};
 
@@
 
-      \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
+      \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}$};
       \draw[->,ultra thick](3,-2.5) to[bend left] (3,1.6);
@@
     \end{tikzpicture}
-    \caption{Actor neural network structure for approximating control input.}
+    \caption{Neural network structure for approximating system behavior}
     \label{fig:nnActor}
@@
 
-\todo[inline]{Use generic input and output symbols instead of my own symbols that I used to inputs (error) and outputs (control inputs) }
-  Therefore, approximated actor signal can be written as:
+  Therefore, approximated output signal can be written as:
 \begin{align}
   \label{eq:approximatePolicyActorWeights}
-    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
+    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
   \end{align}
 %
-where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
+where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
 %
 \begin{align*}
-  {\bf W}_a = 
+  {\bf W} = 
   \begin{bmatrix}
-    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
-    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
+    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
+    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
     \vdots & \ddots & \ldots &\vdots\\
-    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
+    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
   \end{bmatrix}.
@@
 \begin{align*}
-&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
- & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
+&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
+ & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
                                             &\vdots \\
- & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
+ & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
 \end{align*}
@@
   \begin{align*}
-    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
+    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
     % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
@@
   %
-  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
+  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
 
-  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
+  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
   \begin{align*}
-    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
   \end{align*}
 
-Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
+Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
 %
 \begin{align*}
-  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
 \end{align*}
 %
-Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
+Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
 %
 \begin{align}
-  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
+  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
   \label{eq:actorWeightsGradient}
@@
 
-  Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
+  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yeilds
   \begin{align*}
-    {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
   \end{align*}
 
-$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
+$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
 
 \begin{multline}
-  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
-  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
+  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
+  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
   \label{eq:actorWeightUpdate}
 \end{multline}
-
-\todo[inline]{In your case, there is no actor neural network, I implemented generic reinforcement learning structures using actor critic neural network structure}
 

### 2022-04-18 finalReportPres.tex
Update finalReportPres.tex

--- 2022-04-18 finalReportPres.tex
@@
 \begin{frame}{System Architecture}{}
-  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
+%  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
+\begin{figure}
+				\centering
+				\includegraphics[height=3.5cm]{figs/inkscape/carSystemModelOutline}
+				%\caption{}
+				\label{fig:carSystemSubsystem}
+        \end{figure}
+%	\begin{block}{System Architecture}
+%    The overall system architecture of this project consists of six subsystems: 
+%    \begin{itemize}
+%        \item Steering
+%        \item Acceleration
+%        \item Brake %Model
+%        \item Shift %Model
+%        \item Speed %Model
+%        \item Speed control %Model
+%      \end{itemize} 
+%  \end{block}
+\end{frame}
+
+\begin{frame}{System Architecture}{}
 	\begin{block}{System Architecture}
@@
 %-------------------------
+\begin{frame}{Transfer Function Modeling}{Steering System Simulation}
+	\begin{block}{}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire steering estimated model is 83.25
+	\item Best fit percentage of the manual steering estimated model is 90.27
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireSteerModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualSteerModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
+\end{frame}
+%-------------------------
+\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation}
+	\begin{block}{}
+ \begin{itemize}
+	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
+	\item Best fit percentage of the manual acceleration estimated model is 98.3
+ \end{itemize}
+ \begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+        \caption{Output of Estimated By-Wire System Model}
+        \label{fig:byWireAccelModel}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
+        \caption{Output of Estimated Manual System Model}
+        \label{fig:manualAccelModel}
+    \end{minipage}
+\end{figure}
+  \end{block}
+\end{frame}
+%-------------------------
+\begin{frame}{Transfer Function Modeling}{Brake System Simulation}
+\begin{block}{}
+ \begin{itemize}
+	\item Only manual models were considered 
+	\item There were no transfer function models that could satisfy both the best fit and error requirements 
+ \end{itemize}
+% \begin{figure}
+%    \centering
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+%        \caption{Output of Estimated By-Wire System Model}
+%        \label{fig:byWireSteerModel}
+%    \end{minipage}\hfill
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+%        \caption{Output of Estimated Manual System Model}
+%        \label{fig:manualSteerModel}
+%    \end{minipage}
+%\end{figure}
+  \end{block}
+\end{frame}
+%-------------------------
+\begin{frame}{Neural Network Modeling}{Steering System Simulation}
+	\begin{block}{}
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item Only a few samples are just outside of the accuracy requirements
+			\item Transfer function model did not meet the accuracy requirements
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
+	\end{block}
+\end{frame}
+%-------------------------
+\begin{frame}{Neural Network Modeling}{Acceleration System Simulation}
+	\begin{block}{}
+  		\begin{figure}[H]
+  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item All samples within 2\% of the actual output
+			\item Transfer function model did not have the same accuracy bounds
+			\item Fewer concerns about connections in Simulink
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
+  		\end{figure}
+	\end{block}
+\end{frame}
+%-------------------------
+\begin{frame}{Neural Network Modeling}{Brake System Simulation}
+	\begin{block}{}
+\begin{figure}[H]
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
+			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+			\item With this model, the error is kept below 5\%
+			\item Able to easily track model performance
+			\item Provides better results than the transfer function model
+			\end{itemize} \end{minipage}\\[1em]
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
+			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
+  		\end{figure}
+
+  \end{block}
+\end{frame}
+%-------------------------
 \section{Validation and Testing}
@@
 
-\begin{frame}{Transfer Function Modeling}{Steering System}
-	\begin{block}{}
- \begin{itemize}
-	\item Best fit percentage of the by-wire steering estimated model is 83.25
-	\item Best fit percentage of the manual steering estimated model is 90.27
- \end{itemize}
- \begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-        \caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireSteerModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
-        \caption{Output of Estimated Manual System Model}
-        \label{fig:manualSteerModel}
-    \end{minipage}
-\end{figure}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Transfer Function Modeling}{Acceleration System}
-	\begin{block}{}
- \begin{itemize}
-	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
-	\item Best fit percentage of the manual acceleration estimated model is 98.3
- \end{itemize}
- \begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
-        \caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireAccelModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
-        \caption{Output of Estimated Manual System Model}
-        \label{fig:manualAccelModel}
-    \end{minipage}
-\end{figure}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Transfer Function Modeling}{Brake System}
-\begin{block}{}
- \begin{itemize}
-	\item Only manual models were considered 
-	\item There were no transfer function models that could satisfy both the best fit and error requirements 
- \end{itemize}
+%\begin{frame}{Transfer Function Modeling}{Steering System}
+%	\begin{block}{}
+% \begin{itemize}
+%	\item Best fit percentage of the by-wire steering estimated model is 83.25
+%	\item Best fit percentage of the manual steering estimated model is 90.27
+% \end{itemize}
 % \begin{figure}
@@
 %\end{figure}
-  \end{block}
-\end{frame}
+%  \end{block}
+%\end{frame}
 
-\begin{frame}{Neural Network Modeling}{Steering System}
-	\begin{block}{}
-  		\begin{figure}[H]
-  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
-			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item Only a few samples are just outside of the accuracy requirements
-			\item Transfer function model did not meet the accuracy requirements
-			\end{itemize} \end{minipage}\\[1em]
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
-  		\end{figure}
-	\end{block}
-\end{frame}
+%\begin{frame}{Transfer Function Modeling}{Acceleration System}
+%	\begin{block}{}
+% \begin{itemize}
+%	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
+%	\item Best fit percentage of the manual acceleration estimated model is 98.3
+% \end{itemize}
+% \begin{figure}
+%    \centering
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+%        \caption{Output of Estimated By-Wire System Model}
+%        \label{fig:byWireAccelModel}
+%    \end{minipage}\hfill
+%    \begin{minipage}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
+%        \caption{Output of Estimated Manual System Model}
+%        \label{fig:manualAccelModel}
+%    \end{minipage}
+%\end{figure}
+%  \end{block}
+%\end{frame}
 
-\begin{frame}{Neural Network Modeling}{Acceleration System}
-	\begin{block}{}
-  		\begin{figure}[H]
-  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
-			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item All samples within 2\% of the actual output
-			\item Transfer function model did not have the same accuracy bounds
-			\item Fewer concerns about connections in Simulink
-			\end{itemize} \end{minipage}\\[1em]
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
-  		\end{figure}
-	\end{block}
-\end{frame}
+%\begin{frame}{Transfer Function Modeling}{Brake System}
+%\begin{block}{}
+% \begin{itemize}
+%	\item Only manual models were considered 
+%	\item There were no transfer function models that could satisfy both the best fit and error requirements 
+% \end{itemize}
+%% \begin{figure}
+%%    \centering
+%%    \begin{minipage}{0.45\textwidth}
+%%        \centering
+%%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
+%%        \caption{Output of Estimated By-Wire System Model}
+%%        \label{fig:byWireSteerModel}
+%%    \end{minipage}\hfill
+%%    \begin{minipage}{0.45\textwidth}
+%%        \centering
+%%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+%%        \caption{Output of Estimated Manual System Model}
+%%        \label{fig:manualSteerModel}
+%%    \end{minipage}
+%%\end{figure}
+%  \end{block}
+%\end{frame}
 
-\begin{frame}{Neural Network Modeling}{Brake System}
-	\begin{block}{}
-\begin{figure}[H]
-  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
-			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item With this model, the error is kept below 5\%
-			\item Able to easily track model performance
-			\item Provides better results than the transfer function model
-			\end{itemize} \end{minipage}\\[1em]
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
-			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
-  		\end{figure}
+%\begin{frame}{Neural Network Modeling}{Steering System}
+%	\begin{block}{}
+%  		\begin{figure}[H]
+%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
+%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+%			\item Only a few samples are just outside of the accuracy requirements
+%			\item Transfer function model did not meet the accuracy requirements
+%			\end{itemize} \end{minipage}\\[1em]
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
+%  		\end{figure}
+%	\end{block}
+%\end{frame}
 
-  \end{block}
-\end{frame}
+%\begin{frame}{Neural Network Modeling}{Acceleration System}
+%	\begin{block}{}
+%  		\begin{figure}[H]
+%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
+%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+%			\item All samples within 2\% of the actual output
+%			\item Transfer function model did not have the same accuracy bounds
+%			\item Fewer concerns about connections in Simulink
+%			\end{itemize} \end{minipage}\\[1em]
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
+%  		\end{figure}
+%	\end{block}
+%\end{frame}
+
+%\begin{frame}{Neural Network Modeling}{Brake System}
+%	\begin{block}{}
+%\begin{figure}[H]
+%  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
+%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
+%			\item With this model, the error is kept below 5\%
+%			\item Able to easily track model performance
+%			\item Provides better results than the transfer function model
+%			\end{itemize} \end{minipage}\\[1em]
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
+%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
+%  		\end{figure}
+%	
+%  \end{block}
+%\end{frame}
 
@@
 \begin{frame}{Conclusions and Future Work}
-  \begin{block}{Conclusions}
+  \begin{block}{Conclusions and Challenges}
     \begin{itemize}
-      \item Transfer Function to Neural Network models
-      \item Neural Network modeling worked best 
+      \item Conclusions
+      \begin{itemize}
+      	\item Switch from transfer function to neural network models
+      	\item Neural network modeling worked best 
+      \end{itemize}
+      \item Challenges
+        \begin{itemize}
+      	\item Time constraints 
+      	\item Hardware constraints 
+      \end{itemize}
     \end{itemize}

### 2022-04-18 finalReportPres.tex
Added detailed NN Simulink blocks for steering and accel
Updated Final Presentation

--- 2022-04-18 finalReportPres.tex
@@
 	\begin{figure}
-		\centering \includegraphics[width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
-		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
-		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
-		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+		\centering \includegraphics[width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
+		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
+		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
+		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
 	\end{figure}

### 2022-04-19 finalReportPres.tex
finalReportPres.tex updates
I added pictures of the simulink neural network models to the presentation
Presentation and Poster Updates
I added the new subsystem block diagrams to the presentation and made some edits to the poster

@@
 \usepackage{amsmath,amssymb,amsfonts,bm}
+\usepackage{tikz}
 
@@
 				\includegraphics[height=3.5cm]{figs/inkscape/carSystemModelOutline}
-				%\caption{}
 				\label{fig:carSystemSubsystem}
+				\caption{Lexus Vehicle with Subsystems}
         \end{figure}
@@
 \begin{frame}{System Architecture}{Subsystems}
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
-	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System 			\item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
+    \tikzstyle{sum} = [draw, circle,fill=orange!15]
+    % place nodes
+    \node[sum](sum){$\sum$};
+    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
+    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
+    \draw[-stealth,thick]
+    (sum.east)--node[midway,above]{Error}(steeringController);
+    \draw[-stealth,thick]
+    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
+    \draw[-stealth,thick]
+    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
+    \draw[-stealth,thick]
+    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
+    \fill
+    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
+    \draw[-stealth,thick]
+    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
+
+  \end{tikzpicture}
+  % \captionsetup{justification=centering, margin=3cm}
+
+  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
+  \caption{Steering subsystem block diagram.}
+  \label{fig:steeringModelBlockDiagram}
+\end{figure}
+
+\begin{figure}
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-2.0,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-2.0,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-2.0,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(2.2,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(2.2,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Brake subsystem block diagram}
+    \label{fig:brakeModelArchitecture}
+\end{figure}
+
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
+%	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System 			\item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
+\end{frame}
+%
+\begin{frame}{System Architecture}{Subsystems}
+
+\begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
+    % Connections
+    \draw[stealth-,thick]
+    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.5,0);
+    \draw[-stealth,thick]
+    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.5,0);
+  \end{tikzpicture}
+    \caption{Acceleration subsystem block diagram}
+    \label{fig:accelModelArchitecture}
+ \end{figure}
+
+ \begin{figure}
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
+    \draw[-stealth,thick]
+    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Shift subsystem block diagram}
+    \label{fig:shiftModelArchitecture}
+ \end{figure}
+
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
+%	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
+%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
 \end{frame}
@@
 \begin{frame}{System Architecture}{Subsystems}
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
-	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
-	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
+\begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-2.5,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-2.5,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-2.5,0);
+    \draw[-stealth,thick]
+    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Speed subsystem block diagram}
+    \label{fig:speedModelArchitecture}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Speed Control subsystem block diagram}
+    \label{fig:speedControlModelArchitecture}
+ \end{figure}
+
 \end{frame}
@@
 
-  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
+%  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
+	\begin{figure}
+		\centering \includegraphics[width=.35\linewidth]{figs/img/steeringNeuralNetworkDetailedSystem}\quad%
+		\caption{Steering Neural Network Simulink Model Subsystem}
+		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} 
+%		\begin{itemize} \item HIL Bench 						
+%		\item Measuring output voltages to confirm results \end{itemize} 
+		\end{minipage}\\[1em]
+		\centering \includegraphics[width=.35\linewidth]{figs/img/accelNeuralNetworkDetailedSystem}\quad%
+		\caption{Acceleration Neural Network Simulink Model Subsystem}
+		\centering \includegraphics[,width=.35\linewidth]{figs/img/brakeNeuralNetworkDetailedSystem}
+		\caption{Brake Neural Network Simulink Model Subsystem}
+	\end{figure}
 \end{frame}

### 2022-04-19 poster.tex
Presentation and Poster Updates
I added the new subsystem block diagrams to the presentation and made some edits to the poster

@@
 
+%\begin{figure}
+%    \centering
+%        \begin{tikzpicture}
+%    \tikzstyle{every node} = [font=\footnotesize]
+%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
+%    % place nodes
+%    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+%
+%    % Connections
+%    \draw[stealth-,thick]
+%    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
+%    \draw[-stealth,thick]
+%    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
+%    
+%  \end{tikzpicture}
+%    \caption{Speed Control subsystem block diagram}
+%    \label{fig:speedControlModelArchitecture}
+%
+%\end{figure}
+%
+%
+%\begin{figure}
+%    \centering
+%  \begin{tikzpicture}
+%    \tikzstyle{every node} = [font=\footnotesize]
+%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
+%    % place nodes
+%    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+%
+%    % Connections
+%    \draw[stealth-,thick]
+%    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
+%    \draw[stealth-,thick]
+%    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
+%    \draw[stealth-,thick]
+%    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
+%    \draw[-stealth,thick]
+%    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
+%    
+%  \end{tikzpicture}
+%    % \captionsetup{justification=centering, margin=3cm}
+%    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%    \caption{ Speed subsystem block diagram}
+%    \label{fig:speedModelArchitecture}
+%\end{figure}
+
+%\begin{figure}
+%    \centering
+%\begin{tikzpicture}
+%    \tikzstyle{every node} = [font=\footnotesize]
+%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
+%    % place nodes
+%    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+%
+%    % Connections
+%    \draw[stealth-,thick]
+%    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
+%    \draw[-stealth,thick]
+%    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
+%    
+%  \end{tikzpicture}
+%    \caption{Shift subsystem block diagram}
+%    \label{fig:shiftModelArchitecture}
+%\end{figure}
+
+$\bullet$ Collected data using a Lexus RX450H vehicle platform
+
 \begin{figure}
 	\centering
-        \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
-    \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
-
-  \end{tikzpicture}
-    \caption{Speed Control subsystem block diagram}
-    \label{fig:speedControlModelArchitecture}
-
+	\includegraphics[width=0.48\linewidth]{figs/inkscape/carSystemModelOutline}
+	\caption{Lexus vehicle with subsystems}
 \end{figure}
@@
 	\centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
-    % place nodes
-    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
-    \draw[-stealth,thick]
-    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
-
-  \end{tikzpicture}
-    % \captionsetup{justification=centering, margin=3cm}
-    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-    \caption{ Speed subsystem block diagram}
-    \label{fig:speedModelArchitecture}
+	\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\caption{AutonomouStuff Lexus RX450H vehicle}
 \end{figure}
-
-\begin{figure}
-    \centering
-\begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
-    \draw[-stealth,thick]
-    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
-
-  \end{tikzpicture}
-    \caption{Shift subsystem block diagram}
-    \label{fig:shiftModelArchitecture}
-\end{figure}
-
-$\bullet$ Collected data using a Lexus RX450H vehicle platform
 

### 2022-04-20 finalReportPres.tex
Updated Final Presentation

@@
 %-------------------------
+
+\section{Simulation Results}
+
 \begin{frame}{Transfer Function Modeling}{Steering System Simulation}
@@
 \begin{figure}[H]
-  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeNeuralNetworkDetailedSystem}\quad%
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
@@
 
+\begin{frame}{Validation and Testing}{Validation Setup}
+	\begin{figure}
+		\centering	
+		\begin{minipage}{.5\textwidth}
+	  		\centering
+	  		\includegraphics[width=.85\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
+	  		%\captionof{figure}{A figure}
+	  		\label{fig:test1}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+	  		\centering
+	  		\begin{itemize} 
+	  			\item HIL Bench
+	  			\item Measuring output voltages to confirm results 
+	  		\end{itemize}
+		\end{minipage}
+	\end{figure}
+\end{frame}
+
 \begin{frame}
-
-%  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
-	\begin{figure}
-		\centering \includegraphics[width=.35\linewidth]{figs/img/steeringNeuralNetworkDetailedSystem}\quad%
-		\caption{Steering Neural Network Simulink Model Subsystem}
-		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} 
-%		\begin{itemize} \item HIL Bench 						
-%		\item Measuring output voltages to confirm results \end{itemize} 
-		\end{minipage}\\[1em]
-		\centering \includegraphics[width=.35\linewidth]{figs/img/accelNeuralNetworkDetailedSystem}\quad%
-		\caption{Acceleration Neural Network Simulink Model Subsystem}
-		\centering \includegraphics[,width=.35\linewidth]{figs/img/brakeNeuralNetworkDetailedSystem}
-		\caption{Brake Neural Network Simulink Model Subsystem}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Validation and Testing}{Validation Setup}
-	\begin{figure}
-		\centering \includegraphics[width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
-		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
-		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
-		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+	\begin{figure}
+		\centering	
+		\begin{minipage}{.5\textwidth}
+	  		\centering
+	  		\includegraphics[angle=270,width=.85\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
+	  		%\captionof{figure}{A figure}
+	  		\label{fig:test1}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+	  		\centering
+	  		\includegraphics[angle=270,width=.85\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+	  		%\captionof{figure}{Another figure}
+	  		\label{fig:test2}
+		\end{minipage}
 	\end{figure}
@@
 \begin{frame}{Validation and Testing}{Model Validation}
-	\begin{figure}
-		\centering \includegraphics[width=.45\linewidth]{figs/img/aStuffValidationBrakeModel}\quad%
+	\begin{block}{}	
+		\begin{itemize}
+			\item Testing data points using Control Desk software  
+		\end{itemize}		
+		\begin{figure}
+			\centering \includegraphics[width=.9\linewidth]{figs/img/aStuffValidationBrakeModel}
 			\caption{Model Validation Setup}
     				\label{fig:validationSetup}
-		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item Testing data points using Control Desk software  \end{itemize} \end{minipage}\\[1em]
-	\end{figure}
-\end{frame}
-
-%\begin{frame}{Transfer Function Modeling}{Steering System}
-%	\begin{block}{}
-% \begin{itemize}
-%	\item Best fit percentage of the by-wire steering estimated model is 83.25
-%	\item Best fit percentage of the manual steering estimated model is 90.27
-% \end{itemize}
-% \begin{figure}
-%    \centering
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-%        \caption{Output of Estimated By-Wire System Model}
-%        \label{fig:byWireSteerModel}
-%    \end{minipage}\hfill
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
-%        \caption{Output of Estimated Manual System Model}
-%        \label{fig:manualSteerModel}
-%    \end{minipage}
-%\end{figure}
-%  \end{block}
-%\end{frame}
-
-%\begin{frame}{Transfer Function Modeling}{Acceleration System}
-%	\begin{block}{}
-% \begin{itemize}
-%	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
-%	\item Best fit percentage of the manual acceleration estimated model is 98.3
-% \end{itemize}
-% \begin{figure}
-%    \centering
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
-%        \caption{Output of Estimated By-Wire System Model}
-%        \label{fig:byWireAccelModel}
-%    \end{minipage}\hfill
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
-%        \caption{Output of Estimated Manual System Model}
-%        \label{fig:manualAccelModel}
-%    \end{minipage}
-%\end{figure}
-%  \end{block}
-%\end{frame}
-
-%\begin{frame}{Transfer Function Modeling}{Brake System}
-%\begin{block}{}
-% \begin{itemize}
-%	\item Only manual models were considered 
-%	\item There were no transfer function models that could satisfy both the best fit and error requirements 
-% \end{itemize}
-%% \begin{figure}
-%%    \centering
-%%    \begin{minipage}{0.45\textwidth}
-%%        \centering
-%%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-%%        \caption{Output of Estimated By-Wire System Model}
-%%        \label{fig:byWireSteerModel}
-%%    \end{minipage}\hfill
-%%    \begin{minipage}{0.45\textwidth}
-%%        \centering
-%%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
-%%        \caption{Output of Estimated Manual System Model}
-%%        \label{fig:manualSteerModel}
-%%    \end{minipage}
-%%\end{figure}
-%  \end{block}
-%\end{frame}
-
-%\begin{frame}{Neural Network Modeling}{Steering System}
-%	\begin{block}{}
-%  		\begin{figure}[H]
-%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
-%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-%			\item Only a few samples are just outside of the accuracy requirements
-%			\item Transfer function model did not meet the accuracy requirements
-%			\end{itemize} \end{minipage}\\[1em]
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
-%  		\end{figure}
-%	\end{block}
-%\end{frame}
-
-%\begin{frame}{Neural Network Modeling}{Acceleration System}
-%	\begin{block}{}
-%  		\begin{figure}[H]
-%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
-%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-%			\item All samples within 2\% of the actual output
-%			\item Transfer function model did not have the same accuracy bounds
-%			\item Fewer concerns about connections in Simulink
-%			\end{itemize} \end{minipage}\\[1em]
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
-%  		\end{figure}
-%	\end{block}
-%\end{frame}
-
-%\begin{frame}{Neural Network Modeling}{Brake System}
-%	\begin{block}{}
-%\begin{figure}[H]
-%  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
-%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-%			\item With this model, the error is kept below 5\%
-%			\item Able to easily track model performance
-%			\item Provides better results than the transfer function model
-%			\end{itemize} \end{minipage}\\[1em]
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
-%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
-%  		\end{figure}
-%	
-%  \end{block}
-%\end{frame}
+		\end{figure}
+	\end{block}
+\end{frame}
 
@@
 
-\begin{frame}{References}
+\begin{frame}[allowframebreaks]{References}
   \bibliographystyle{IEEEtran}

### 2022-04-20 finalReportPres.tex
Updated Final Presentation

@@
 \begin{frame}{Transfer Function Modeling}{Steering System Simulation}
-	\begin{block}{}
- \begin{itemize}
-	\item Best fit percentage of the by-wire steering estimated model is 83.25
-	\item Best fit percentage of the manual steering estimated model is 90.27
- \end{itemize}
+	\begin{block}{Manual Mode}
  		\begin{figure}
 		    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-        \caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireSteerModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
+		    \includegraphics[width=0.4\textwidth]{figs/img/byWireSteeringTransferFunctionModel}
 		    \caption{Output of Estimated Manual System Model}
 		        \label{fig:manualSteerModel}
-    \end{minipage}
  		\end{figure}
@@
 \end{frame}
-%-------------------------
-\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation}
-	\begin{block}{}
- \begin{itemize}
-	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
-	\item Best fit percentage of the manual acceleration estimated model is 98.3
- \end{itemize}
+
+\begin{frame}{Transfer Function Modeling}{Steering System Simulation (Cont.)}
+	\begin{block}{By-Wire Mode}
 		\begin{figure}
     			\centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
+    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
     			\caption{Output of Estimated By-Wire System Model}
-        \label{fig:byWireAccelModel}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
-        \caption{Output of Estimated Manual System Model}
-        \label{fig:manualAccelModel}
-    \end{minipage}
+        		\label{fig:byWireSteerModel}
  		\end{figure}
@@
 \end{frame}
+
+%-------------------------
+\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation}
+	\begin{block}{Manual Mode}
+ 		\begin{figure}
+	    		\centering
+	    		\includegraphics[width=0.4\textwidth]{figs/img/manualAccelTransferFunctionModel}
+	        \caption{Output of Estimated Manual System Model}
+	        \label{fig:manualAccelModel}
+		\end{figure}
+  	\end{block}
+\end{frame}
+
+\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation (Cont.)}
+	\begin{block}{By-Wire Mode}
+		\begin{figure}
+    			\centering
+    			\includegraphics[width=0.4\textwidth]{figs/img/byWireAccelArxModel}
+    			\caption{Output of Estimated By-Wire System Model}
+        		\label{fig:byWireSteerModel}
+ 		\end{figure}
+	\end{block}
+\end{frame}
+
 %-------------------------
@@
  		\end{itemize}
-% \begin{figure}
-%    \centering
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
-%        \caption{Output of Estimated By-Wire System Model}
-%        \label{fig:byWireSteerModel}
-%    \end{minipage}\hfill
-%    \begin{minipage}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
-%        \caption{Output of Estimated Manual System Model}
-%        \label{fig:manualSteerModel}
-%    \end{minipage}
-%\end{figure}
   	\end{block}
 \end{frame}
+
 %-------------------------
@@
 	        \item MATLAB's System Identification Toolbox
+	        \item MATLAB's Neural Network Time Series Toolbox
+	        \item DSpace/Control Desk
 	        \item Vector CANAlyzer

### 2022-04-20 poster.tex

@@
 \begin{alertblock}{Problem Setup}
-%\vskip -1cm
-%\begin{enumerate}
-%    \item Develop and linearize system model
-%    \item Simulate algorithms in MATLAB
-%    \item Test algorithms on desktop computer using USB connection 
-%    \item Test algorithms on Raspberry Pi microcontroller
-%    \item Test algorithms on mobile device
-%\end{enumerate}
 
 %\vskip -1cm
-$\bullet$ Conducted a literature review to look for existing solutions
-$\bullet$ System Architecture 
+\begin{itemize}
+	\item Conducted a literature review to look for existing solutions
+	\item System Architecture 
+\end{itemize}
+
 \begin{figure}
 	\centering
-	\begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=0.75 cm]
-    \tikzstyle{sum} = [draw, circle,fill=orange!15]
-    % place nodes
-    \node[sum](sum){$\sum$};
-    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
-    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
-    \draw[-stealth,thick]
-    (sum.east)--node[midway,above]{Error}(steeringController);
-    \draw[-stealth,thick]
-    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
-    \draw[-stealth,thick]
-    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
-    \draw[-stealth,thick]
-    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
-    \fill
-    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
-    \draw[-stealth,thick]
-    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
-
-  \end{tikzpicture}
-  % \captionsetup{justification=centering, margin=3cm}
-
-  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
-  \caption{Steering subsystem block diagram.}
-  \label{fig:steeringModelBlockDiagram}
+	\includegraphics[width=1.0\linewidth]{figs/inkscape/steeringModelBlockDiagram}
+	\caption{Steering subsystem block diagram}
 \end{figure}
@@
 	\centering
-	 \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width= 5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
-    % Connections
-    \draw[stealth-,thick]
-    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-5.0,0);
-    \draw[-stealth,thick]
-    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(5.0,0);
-  \end{tikzpicture}
+	\includegraphics[width=0.48\linewidth]{figs/inkscape/accelerationModelArchitecture}
 	\caption{Acceleration subsystem block diagram}
-    \label{fig:accelModelArchitecture}
 \end{figure}
@@
 	\centering
-	  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2.0 cm]
-    % place nodes
-    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};
-
-    % Connections
-    \draw[stealth-,thick]
-    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-4.5,0);
-    \draw[stealth-,thick]
-    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-4.5,0);
-    \draw[stealth-,thick]
-    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-4.5,0);
-    \draw[-stealth,thick]
-    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(4.5,0);
-    \draw[-stealth,thick]
-    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(4.5,0);
-
-  \end{tikzpicture}
-    % \captionsetup{justification=centering, margin=3cm}
-    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+	\includegraphics[width=0.48\linewidth]{figs/inkscape/brakeModelArchitecture}
 	\caption{Brake subsystem block diagram}
-    \label{fig:brakeModelArchitecture}
 \end{figure}
-
-%\begin{figure}
-%    \centering
-%        \begin{tikzpicture}
-%    \tikzstyle{every node} = [font=\footnotesize]
-%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
-%    % place nodes
-%    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
-%
-%    % Connections
-%    \draw[stealth-,thick]
-%    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
-%    \draw[-stealth,thick]
-%    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
-%    
-%  \end{tikzpicture}
-%    \caption{Speed Control subsystem block diagram}
-%    \label{fig:speedControlModelArchitecture}
-%
-%\end{figure}
-%
-%
-%\begin{figure}
-%    \centering
-%  \begin{tikzpicture}
-%    \tikzstyle{every node} = [font=\footnotesize]
-%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
-%    % place nodes
-%    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
-%
-%    % Connections
-%    \draw[stealth-,thick]
-%    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
-%    \draw[stealth-,thick]
-%    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
-%    \draw[stealth-,thick]
-%    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
-%    \draw[-stealth,thick]
-%    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
-%    
-%  \end{tikzpicture}
-%    % \captionsetup{justification=centering, margin=3cm}
-%    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-%    \caption{ Speed subsystem block diagram}
-%    \label{fig:speedModelArchitecture}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%\begin{tikzpicture}
-%    \tikzstyle{every node} = [font=\footnotesize]
-%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
-%    % place nodes
-%    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
-%
-%    % Connections
-%    \draw[stealth-,thick]
-%    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
-%    \draw[-stealth,thick]
-%    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
-%    
-%  \end{tikzpicture}
-%    \caption{Shift subsystem block diagram}
-%    \label{fig:shiftModelArchitecture}
-%\end{figure}
 
@@
 		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
-	\caption{Steering System Training Plots}
+	\caption{ Steering System Training Plots}
     \label{fig:SteeringSysNeuralNetwork}
@@
 
-\begin{figure}
-    \centering
-		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
-	\caption{Acceleration System Training Plots}
-    \label{fig:AccelerationSysNeuralNetwork}
-\end{figure}
+%\begin{figure}
+%    \centering
+%		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
+%		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
+%	\caption{Acceleration System Training Plots}
+%    \label{fig:AccelerationSysNeuralNetwork}
+%\end{figure}
 
@@
 		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
-	\caption{Brake System Training Plots}
+	\caption{ Brake System Training Plots}
     \label{fig:BrakeSysNeuralNetwork}
@@
 
-\begin{enumerate}
-	\item Approximate neural network signal
-	\begin{align*}
-  		\hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
-  	\end{align*}
-  	\item Define the weight matrix
-  	\begin{align*}
-  		{\bf W}_a = 
-  		\begin{bmatrix}
-    		w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
-    		w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
-    		\vdots & \ddots & \ldots &\vdots\\
-    		w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
-  		\end{bmatrix}.
-	\end{align*}
-	\item Compute the sum-of-squared error
-	\begin{align*}
-    		\bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
-    		% \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
-  	\end{align*}	
-  	\begin{align*}
-  		\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}}
-  	\end{align*}
-	\begin{align*}
-    		\delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
-  	\end{align*}
-  	\item Find the actor weight by minimizing the sum-of-square error
-  	\begin{align*}
-  	\delta_a = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
-	\end{align*}
-	\item Take the derivative of $\delta_a$ with respect to ${\bf W}_a$ and set $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero
-	\begin{align*}
-  		\frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T 					\bm{\Sigma}\mathbf{W}_a
-	\end{align*}
-	\begin{align*}
-  		{\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
-	\end{align*}
-	\item Use the gradient descent approach to minimize the least square order alter weights when training the neural network
-	\begin{multline*}
-  		\mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}\\
-  		=\mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}				_a^{(r)}\right)\\
-  		= \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
-	\end{multline*}
-\end{enumerate}
+%\begin{enumerate}
+%	\item Approximate neural network signal
+%	\begin{align*}
+%  		\hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
+%  	\end{align*}
+%  	\item Define the weight matrix
+%  	\begin{align*}
+%  		{\bf W}_a = 
+%  		\begin{bmatrix}
+%    		w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
+%    		w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
+%    		\vdots & \ddots & \ldots &\vdots\\
+%    		w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
+%  		\end{bmatrix}.
+%	\end{align*}
+%	\item Compute the sum-of-squared error
+%	\begin{align*}
+%    		\bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
+%    		% \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
+%  	\end{align*}	
+%  	\begin{align*}
+%  		\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}}
+%  	\end{align*}
+%	\begin{align*}
+%    		\delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+%  	\end{align*}
+%  	\item Find the actor weight by minimizing the sum-of-square error
+%  	\begin{align*}
+%  	\delta_a = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
+%	\end{align*}
+%	\item Take the derivative of $\delta_a$ with respect to ${\bf W}_a$ and set $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero
+%	\begin{align*}
+%  		\frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T 					\bm{\Sigma}\mathbf{W}_a
+%	\end{align*}
+%	\begin{align*}
+%  		{\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+%	\end{align*}
+%	\item Use the gradient descent approach to minimize the least square order alter weights when training the neural network
+%	\begin{multline*}
+%  		\mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}\\
+%  		=\mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}				_a^{(r)}\right)\\
+%  		= \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
+%	\end{multline*}
+%\end{enumerate}
+
+\begin{figure}
+    \centering
+		\includegraphics[width=0.80\linewidth]{figs/img/steeringSimulinkBlock}
+	\caption{Steering Neural Network Simulink Model}
+    \label{fig:steeringNeuralNetwork}
+\end{figure}
+
+\begin{figure}
+    \centering
+		\includegraphics[width=0.80\linewidth]{figs/img/accelerationSimulinkBlock}
+	\caption{Acceleration Neural Network Simulink Model}
+    \label{fig:accelNeuralNetwork}
+\end{figure}
+
+\begin{figure}
+    \centering
+		\includegraphics[width=0.80\linewidth]{figs/img/brakeSimulinkBlock}
+	\caption{Brake Neural Network Simulink Model}
+    \label{fig:brakeNeuralNetwork}
+\end{figure}
 

### 2022-04-27 reportTII-ArticleHIL.tex
A few comments on final presentation and the report. More to come
Report Updates

@@
 \begin{abstract}
-This report presents the results of modeling vehicle systems and testing them using Hardware-in-the-Loop (HIL).
+This report presents the results of modeling vehicle systems and testing them using open-loop.
 First, data was collected for each system using a Lexus RX450H vehicle.
@@
 These models gave much more accurate results when compared to the transfer function models developed using the System Identification Toolbox.
-(Add section about testing and results).
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Hardware-in-the-Loop, Neural Network, System Identification
+Deep Learning, Hardware-in-the-Loop, Neural Network, Plant Modeling, System Identification
 \end{IEEEkeywords}
@@
 	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
 	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
 	\caption{Steering System Training Plots}
@@
 	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
 	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
 	\caption{Acceleration System Training Plots}
@@
 The results from that test, shown in \autoref{testedBrakeModel}, also show that the model can accurately predict the output values and do this within the accepted error bound of 5\%.
+The graphs show how the model tracks the data log and the error between the model output and the data log output.
+The y-axis for both graphs, “Output and Target” represents the Actual and Desired Brake Pedal Position as a percentage.
+The x-axis for both graphs represents the Time Steps, with $T_s$ equal to 33ms.
+The graph  \autoref{initalBrakeModel} represents the initial training of the model and the further training of the graph is represented in \autoref{testedBrakeModel}.
+
 \begin{figure}[h]
@@
 	\subcaptionbox{Model Output Tracking and Error Plots \label{initalBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/brake_new_neuralNetworkFig}}
 	\subcaptionbox{Model Output Tracking and Error Plots for Log Two Data \label{testedBrakeModel}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
 	\caption{Brake System Training Plots}
@@
 
-Once the model was created, it was exported to Simulink and tested again.
+%Once the model was created, it was exported to Simulink and tested again.
 One test involved using To Workspace blocks to access the pressure voltages, position voltages, and desired pedal position values in the first brake log.
@@
 
-\begin{figure}[h]
-	\centering
-	\subcaptionbox{Actual Pedal Position \label{brakeWorkspacePedalPosition}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
-	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeWorkspacePedalError}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
-	\caption{Actual Pedal Position and Error Plots Using the From Workspace Blocks}
-\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\subcaptionbox{Actual Pedal Position \label{brakeWorkspacePedalPosition}}
+%		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
+%	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeWorkspacePedalError}}
+%		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
+%	\caption{Actual Pedal Position and Error Plots Using the From Workspace Blocks}
+%\end{figure}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\subcaptionbox{Actual Pedal Position \label{brakeConstantsPedalPosition}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionConstantBlocks}}
-	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeConstantsPedalError}}
-		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorConstantBlocks}}
-	\caption{Actual Pedal Position and Error Plots Using the Constant Blocks}
-\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\subcaptionbox{Actual Pedal Position \label{brakeConstantsPedalPosition}}
+%		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionConstantBlocks}}
+%	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeConstantsPedalError}}
+%		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorConstantBlocks}}
+%	\caption{Actual Pedal Position and Error Plots Using the Constant Blocks}
+%\end{figure}
 
@@
 
+\todo[inline]{Need annotation of each of the pictures. Like that, we show what
+  each of the equipment are}
 \begin{figure}
@@
   \centering
-	\includegraphics[width=0.95\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
+    \includegraphics[width=0.95\linewidth]{figs/inkscape/hilBenchAstuffAnnotated}
   \caption{AutonomouStuff HIL Bench Configuration}
@@
 \end{figure}
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.95\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
+%	\caption{AutonomouStuff HIL Bench Configuration}
+%	\label{fig:hilBench}
+%\end{figure}
 

### 2022-04-29 reportTII-ArticleHIL.tex
Updated report

--- 2022-04-15 reportTII-ArticleHIL.tex
@@
 
-      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+      \begin{tikzpicture}[x=1.25cm, y=1.25cm]
 
@@
 
-The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}.
+The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\tiny \hsize=0.45\textwidth \url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}.
 The approximated neural network signal can be written as:
@@
  The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set.
-An acceptable neural network model will meet the desired error requirements~\footnote{\url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.
+An acceptable neural network model will meet the desired error requirements~\footnote{\hsize=0.9\textwidth \url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.
 

### 2022-05-03 deliverables/simulationFiles/neuralNetworkAccel.m
Added deliverables folder and files

@@ -1,0 +1,48 @@
+%%% ECE499 Senior Project
+%%% Load and Prepare Data Script
+%%% 1/26/22
+%%% Nick Nauman and Hannah Grady
+
+clear all; close all; clc
+
+%% Load Data into Workspace
+accel1 = load('dataLogs\accelDataLogs\accellogs1.mat');
+accel2by = load('dataLogs\accelDataLogs\accellogs2_bywire.mat');
+accel2m = load('dataLogs\accelDataLogs\accellogs2_manual.mat');
+accel3m = load('dataLogs\accelDataLogs\accellogs3_manual.mat');
+accel3by = load('dataLogs\accelDataLogs\accellogs3_bywire.mat');
+
+%% Save Data to Workspace for Simulink and Simulate Model
+accel2_inputs = [accel2m.accel2_manual.Input_VoltageA accel2m.accel2_manual.Input_VoltageB]';
+accel2_target = [accel2m.accel2_manual.Output_Position]';
+accellog.time = accel2m.accel2_manual.Time_s_;
+accellog.signals.dimensions = 2;
+accellog.signals.values = accel2_inputs';
+accelout.time = accel2m.accel2_manual.Time_s_;
+accelout.signals.values = accel2_target';
+accelout.signals.dimensioins = 1;
+tstop = (length(accel2_target)-1)*0.033;
+accellog2sim = sim('accelSystemNeuralNetworkSimulink19b', tstop);
+
+figure();
+plot(accellog2sim.tout, accellog2sim.actualpedal.Data)
+hold on;
+plot(accellog2sim.tout, accel2_target)
+hold off;
+
+accel3_inputs = [accel3m.accel3_manual.Input_VoltageA accel3m.accel3_manual.Input_VoltageB]';
+accel3_target = [accel3m.accel3_manual.Output_Position]';
+accellog.time = accel3m.accel3_manual.Time_s_;
+accellog.signals.dimensions = 2;
+accellog.signals.values = accel3_inputs';
+accelout.time = accel3m.accel3_manual.Time_s_;
+accelout.signals.values = accel3_target';
+accelout.signals.dimensioins = 1;
+tstop = (length(accel3_target)-1)*0.033;
+accellog3sim = sim('accelSystemNeuralNetworkSimulink19b', tstop);
+
+figure();
+plot(accellog3sim.tout, accellog3sim.actualpedal.Data)
+hold on;
+plot(accellog3sim.tout, accel3_target)
+hold off;

### 2022-05-03 deliverables/simulationFiles/neuralNetworkBrake.m

@@ -1,0 +1,53 @@
+%Using the Neural Network Timeseries app 
+
+%Read the brake logs 
+brakeLog1 = readtable('dataLogs\brakeDataLogs\brake_test_log_T001.csv'); 
+brakeLog2 = readtable('dataLogs\brakeDataLogs\brake_test_log_T002.csv'); 
+brakeLog3 = readtable('dataLogs\brakeDataLogs\brake_test_log_T003.csv'); 
+
+brakeLog1Manual1 = brakeLog1(1:4132,:);
+brakeLog2_Manual = brakeLog2; 
+brakeLog2ManualLogs = brakeLog2_Manual(1:1141,:); 
+
+
+%Get needed inputs and outputs from each log 
+outputValLog1 = brakeLog1Manual1.as_pacmod__BRAKE_RPT__OUTPUT_VALUE___;
+pressureVoltage1Log1 = brakeLog1Manual1.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_1_IN_VOLTAGE;
+pressureVoltage2Log1 = brakeLog1Manual1.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_2_IN_VOLTAGE;
+positionVoltage1Log1 = brakeLog1Manual1.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT_2__BRAKE_1_IN_VOLTAGE_2;
+positionVoltage2Log1 = brakeLog1Manual1.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT_2__BRAKE_2_IN_VOLTAGE_2;
+
+outputValLog2 = brakeLog2ManualLogs.as_pacmod__BRAKE_RPT__OUTPUT_VALUE___;
+pressureVoltage1Log2 = brakeLog2ManualLogs.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_1_IN_VOLTAGE;
+pressureVoltage2Log2 = brakeLog2ManualLogs.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_2_IN_VOLTAGE;
+positionVoltage1Log2 = brakeLog2ManualLogs.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT_2__BRAKE_1_IN_VOLTAGE_2;
[…]

### 2022-05-03 deliverables/simulationFiles/neuralNetworkSteering.m

@@ -1,0 +1,47 @@
+%%% ECE499 Senior Project
+%%% Load and Prepare Data Script
+%%% 1/26/22
+%%% Nick Nauman and Hannah Grady
+
+clear all; close all; clc
+
+%% Load Data into Workspace
+steer1 = load('dataLogs\steeringDataLogs\steerlogs1_clean.mat');
+steer2 = load('dataLogs\steeringDataLogs\steerlogs2_clean.mat');
+steer3 = load('dataLogs\steeringDataLogs\steerlogs3_clean.mat');
+
+%% Save Data to Workspace for Simulink and Simulate Model
+steering1 = steer1.steering1;
+steering1_inputs = [steering1.In_VoltageA steering1.In_VoltageB]';
+steering1_target = [steering1.Out_SWAngle]';
+steeringlog.time = steering1.Time_s_;
+steeringlog.signals.dimensions = 2;
+steeringlog.signals.values = steering1_inputs';
+steeringout.time = steering1.Time_s_;
+steeringout.signals.values = steering1_target';
+steeringout.signals.dimensioins = 1;
+tstop = (length(steering1_target)-1)*0.033;
+steeringlog1sim = sim('steeringSystemNeuralNetworkSimulink19b', tstop);
+figure();
+plot(steeringlog1sim.tout, steeringlog1sim.actualsteering.Data)
+hold on;
+plot(steeringlog1sim.tout, steering1_target)
+hold off;
+
+steering3 = steer3.steering3;
+steering3_inputs = [steering3.In_VoltageA steering3.In_VoltageB]';
+steering3_target = [steering3.Out_SWAngle]';
+steeringlog.time = steering3.Time_s_;
+steeringlog.signals.dimensions = 2;
+steeringlog.signals.values = steering3_inputs';
+steeringout.time = steering3.Time_s_;
+steeringout.signals.values = steering3_target';
+steeringout.signals.dimensioins = 1;
+tstop = (length(steering3_target)-1)*0.033;
+steeringlog3sim = sim('steeringSystemNeuralNetworkSimulink19b', tstop);
+
+figure();
+plot(steeringlog3sim.tout, steeringlog3sim.actualsteering.Data)
+hold on;
+plot(steeringlog3sim.tout, steering3_target)
+hold off;

### 2022-05-03 deliverables/simulationFiles/transferFunctionAccel.m

@@ -1,0 +1,38 @@
+%%% AStuff Senior Project
+%%% Create Transfer Function Plots for Acceleration System
+%%% Based on Models Created in the System Identification Toolbox
+
+%%% Nick Nauman & Hannah Grady
+%%% Bradley University
+%%% ECE499
+%%% 4/26/22
+
+clear all; close all; clc;
+
+%% Load Data into Workspace
+accel1 = load('dataLogs\accelDataLogs\accellogs1.mat');
+accel2by = load('dataLogs\accelDataLogs\accellogs2_bywire.mat');
+accel2m = load('dataLogs\accelDataLogs\accellogs2_manual.mat');
+accel3m = load('dataLogs\accelDataLogs\accellogs3_manual.mat');
+accel3by = load('dataLogs\accelDataLogs\accellogs3_bywire.mat');
+
+%% Save Data as IDDATA object
+accellog1 = iddata(accel1.accel1.Output_Position, [accel1.accel1.Output_VoltageA accel1.accel1.Output_VoltageB], 0.033);
+accellog2by = iddata(accel2by.accel2_bywire.Output_Position, [accel2by.accel2_bywire.Output_VoltageA accel2by.accel2_bywire.Output_VoltageB], 0.033);
+accellog2m = iddata(accel2m.accel2_manual.Output_Position, [accel2m.accel2_manual.Output_VoltageA accel2m.accel2_manual.Output_VoltageB], 0.033);
+accellog3by = iddata(accel3by.accel3_bywire.Output_Position, [accel3by.accel3_bywire.Output_VoltageA accel3by.accel3_bywire.Output_VoltageB], 0.033);
+accellog3m = iddata(accel3m.accel3_manual.Output_Position, [accel3m.accel3_manual.Output_VoltageA accel3m.accel3_manual.Output_VoltageB], 0.033);
+
+%%% Create models from iddata logs using System ID Toolbox
+%%% See online documentation for further instruction
+
+%% Load Saved Models
+manualAccelTFModel = load('TFModels_SysID\manualAccelTFModel.mat');
+bywireAccelArxModel = load('TFModels_SysID\bywireAccelArxModel.mat');
+
+%% Plot Figures
+figure;
+compare(accellog3m, manualAccelTFModel.manualAccelTFModel1)
+
+figure;
+compare(accellog3by, bywireAccelArxModel.bywireAccelArxModel)

### 2022-05-03 deliverables/simulationFiles/transferFunctionSteering.m

@@ -1,0 +1,34 @@
+%%% AStuff Senior Project
+%%% Create Transfer Function Plots for Steering System
+%%% Based on Models Created in the System Identification Toolbox
+
+%%% Nick Nauman & Hannah Grady
+%%% Bradley University
+%%% ECE499
+%%% 4/26/22
+
+clear all; close all; clc;
+
+%% Load Data into Workspace
+steer1 = load('dataLogs\steeringDataLogs\steerlogs1_clean.mat');
+steer2 = load('dataLogs\steeringDataLogs\steerlogs2_clean.mat');
+steer3 = load('dataLogs\steeringDataLogs\steerlogs3_clean.mat');
+
+%% Save Data as IDDATA object
+steerlog1 = iddata(steer1.steering1.Out_SWAngle, [steer1.steering1.Out_VoltageA steer1.steering1.Out_VoltageB], 0.033);
+steerlog2 = iddata(steer2.steering2.Out_SWAngle, [steer2.steering2.Out_VoltageA steer2.steering2.Out_VoltageB], 0.033);
+steerlog3 = iddata(steer3.steering3.Out_SWAngle, [steer3.steering3.Out_VoltageA steer3.steering3.Out_VoltageB], 0.033);
+
+%%% Create models from iddata logs using System ID Toolbox
+%%% See online documentation for further instruction
+
+%% Load Saved Models
+manualSteeringTFModel = load('TFModels_SysID\manualSteeringTFModel.mat');
+bywireSteeringTFModel = load('TFModels_SysID\bywireSteeringTFModel.mat');
+
+%% Plot Figures
+figure;
+compare(steerlog1, manualSteeringTFModel.manualSteeringTfModel);
+
+figure;
+compare(steerlog2, bywireSteeringTFModel.bywireSteeringTFModel)

### 2022-05-03 reportTII-ArticleHIL.tex

@@
 The x-axis for both graphs represents the Time Steps, with $T_s$ equal to 33ms.
-The graph  \autoref{initalBrakeModel} represents the initial training of the model and the further training of the graph is represented in \autoref{testedBrakeModel}.
 
@@
 
-The second test used constant blocks to represent the voltages and desired pedal position at a specific time instant in the first brake log.
-The error and the actual pedal position were then plotted again.
-The pedal position plot is shown in \autoref{brakeConstantsPedalPosition}, and the error plot is represented by \autoref{brakeConstantsPedalError}.
-As the plots show, the model is able to produce the desired pedal position and the error falls to 0\% after a spike at the start.
+The second test used constant blocks and To Workspace blocks to represent the voltages and desired pedal position in the first brake log.
+The results from this test also showed that the model was able to accurately track the data.
 

### 2022-05-04 deliverables/simulationFiles/neuralNetworkBrake.m
Added Time Series Data, Edited TF Figures

@@ -28,8 +28,6 @@ pressureVoltage1Log3 = brakeLog3.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_
 pressureVoltage2Log3 = brakeLog3.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT__BRAKE_2_IN_VOLTAGE;
 positionVoltage1Log3 = brakeLog3.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT_2__BRAKE_1_IN_VOLTAGE_2;
 positionVoltage2Log3 = brakeLog3.as_pacmod__BRAKE_VOLTAGE_DIAGNOSTIC_RPT_2__BRAKE_2_IN_VOLTAGE_2;
- 
-
 
 %Group together the inputs and outputs 
 inputsLog1 = [pressureVoltage1Log1,pressureVoltage2Log1,positionVoltage1Log1, positionVoltage2Log1]';
@@ -51,3 +49,12 @@ sysBrakeLog1Pedal.signals.values = outputLog1';
 sysBrakeLog1Pedal.sampleTime = 0.033;
 sysBrakeLog1Pedal.dimensions = 1; 
 sysBrakeLog1Pedal.time = brakeLog1Manual1.Time_s_;
+
+tstop = (length(outputLog1)-1)*0.033;
+brakelog1sim = sim('brakeSystemNeuralNetworkSimulink19b', tstop);
+
+figure();
+plot(brakelog1sim.tout, brakelog1sim.actualpedal.Data)
+hold on;
+plot(brakelog1sim.tout, outputLog1)
+hold off;

### 2022-05-04 deliverables/timeSeriesData/drawPlots.m

@@ -1,0 +1,100 @@
+%%% AStuff Senior Project 
+%%% Redraw Plots from Final Report
+%%% Nick Nauman & Hannah Grady
+
+clear all; close all; clc;
+
+%% Load Data
+accelNeuralNetworkLog2 = readmatrix('accelNeuralNetworkTimeSeriesDataLog2.dat');
+accelNeuralNetworkLog3 = readmatrix('accelNeuralNetworkTimeSeriesDataLog3.dat');
+brakeNeuralNetwork = readmatrix('brakeNeuralNetworkTimeSeriesData.dat');
+steeringNeuralNetworkLog1 = readmatrix('steeringNeuralNetworkTimeSeriesDataLog1.dat');
+steeringNeuralNetworkLog3 = readmatrix('steeringNeuralNetworkTimeSeriesDataLog3.dat');
+bywireAccelArx = readmatrix('bywireAccelArxTimeSeriesData.dat');
+manualAccelTf = readmatrix('manualAccelTfTimeSeriesData.dat');
+bywireSteeringTf = readmatrix('bywireSteeringTfTimeSeriesData.dat');
+manualSteeringTf = readmatrix('manualSteeringTfTimeSeriesData.dat');
+
+%% Generate Steering Neural Network Plot
+figure();
+plot(steeringNeuralNetworkLog1(1,:), steeringNeuralNetworkLog1(2,:), 'r:', 'LineWidth', 2)
+xlabel('Time (s)', 'FontSize', 14);
+ylabel('Steering Angle [rad]', 'FontSize', 14);
+grid on;
+grid minor;
+
+figure();
+plot(steeringNeuralNetworkLog3(1,:), steeringNeuralNetworkLog3(2,:), 'r:', 'LineWidth', 2)
+xlabel('Time (s)', 'FontSize', 14);
+ylabel('Steering Angle [rad]', 'FontSize', 14);
+grid on;
+grid minor;
+
+%% Generate Acceleration Neural Network Plot
+figure();
+plot(accelNeuralNetworkLog2(1,:), accelNeuralNetworkLog2(2,:), 'r:', 'LineWidth', 2)
+xlabel('Time (s)', 'FontSize', 14);
+ylabel('Normalized Acceleration Pedal Position', 'FontSize', 14);
+grid on;
+grid minor;
+
+figure();
+plot(accelNeuralNetworkLog3(1,:), accelNeuralNetworkLog3(2,:), 'r:', 'LineWidth', 2)
[…]

### 2022-05-10 reportTII-ArticleHIL.tex
Updated Readme files and Final Report
Feedback on the final report

@@
 
-\usepackage{hyperref}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage{soul}
+\usepackage{soul,xcolor}
+% \usepackage{todonotes}
 \usepackage{easyReview}
@@
 \usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
-
 \usepackage{siunitx}
+\usepackage{hyperref}
 % \sisetup{unitsep=\cdot}
@@
 \begin{document}
-\title{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}
+\title{Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles}
 \author{Hannah Grady, Nicholas Nauman, and Dr. Suruz Miah
@@
 \begin{abstract}
-This report presents the results of modeling vehicle systems and testing them using open-loop.
-First, data was collected for each system using a Lexus RX450H vehicle.
-After data collection, models were developed in order to accurately simulate the physical vehicle system.
-MATLAB’s System Identification Toolbox was initially used to create these models.
-However, the transfer function models it provided weren’t able to accurately represent these systems and their non-linear behaviors.
-After this was established, modeling was done using MATLAB’s Neural Network Time Series application.
-Once a Neural Network model was created, it was then exported to Simulink and modified to be able to run without the use of the Deep Learning toolbox.
-These models gave much more accurate results when compared to the transfer function models developed using the System Identification Toolbox.
+
+\highlight{This report presents the results of modeling vehicle systems and testing them
+  using open-loop. First, data was collected for each system using a Lexus
+  RX450H vehicle. After data collection, models were developed in order to
+  accurately simulate the physical vehicle system. MATLAB's System
+  Identification Toolbox was initially used to create these models. However,
+the transfer function models it provided w
+these systems and their non-linear behaviors. After this was established,
+modeling was done using MATLAB's Neural Network Time Series application. Once a
+Neural Network model was created, it was then exported to Simulink and modified
+to be able to run without the use of the Deep Learning toolbox. These models
+gave much more accurate results when compared to the transfer function models
+developed using the System Identification Toolbox.}
+
+\alert{SM: I'll rewrite the abstract}
+
 \end{abstract}
@@
 \label{sec:introduction}
+
+\todo[inline]{NN/HG: Add 2/3 sentences on what motivated the company to model
+  subsystems of autonomous vehicles, Hint: Erik mentioned already that employees
+can perform testing without the physical vehicle. You just need to extend his statement to write the motivational paragraph behind this project}
+
 \IEEEPARstart{A}{utonomous} vehicles are being developed by many companies for commercial and
@@
 modern world, a large body of research in the field of autonomous vehicles is
-being conducted in recent decades \cite{Liu2017} \cite{Prasad2020}.
+being conducted in recent decades \cite{Liu2017,Prasad2020}.
 Therefore, it is apparent that researchers of the autonomous vehicle community
@@
 
-\item speed control (cruise) subsystems.
+\item speed control (cruise). 
 \end{enumerate}
@@
 Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+
 The first subsystem we will model is the steering model, and then we will move onto
 the other subsystems. There are already controllers in place for the Lexus
-vehicle platform, but their reliability is lower than expected due to non-linear
+vehicle platform, but their \comment{reliability}{Need to define what do you mean by reliability, be very specific} is lower than expected due to non-linear
 behaviors of the torque voltages required to control each subsystem. The scope
-of this project includes developing mathematical models for each subsystem so
-AutonomouStuff can implement control systems that improve the reliability of the
+of this project includes developing mathematical \add{and/or data-driven} models for each subsystem so \add{that one} \remove{AutonomouStuff} can \add{easily} implement control systems that improve the reliability of the
 autonomous vehicle platform.
 These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
-Once these models are developed, they will be tested using AutonomouStuff's Hardware-in-the-Loop (HIL) bench.
-Once there is confidence in each model, AutonomouStuff can use these models on their HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-There are two operating modes of the Lexus vehicle platform used in this project: Manual-drive and by-wire or autonomous.
+Once these models are developed, they will be tested using \remove{AutonomouStuff's} Hardware-in-the-Loop (HIL) bench.
+Once there is confidence in each model, \remove{AutonomouStuff can use} these models \add{can be used} on \add{the}  \remove{their}  HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
+
+There are two operating modes of the Lexus vehicle platform used in this project: %
+%
+\begin{itemize}
+  \item Manual-drive and
+  \item by-wire or autonomous. 
+\end{itemize}
+%
+\todo[inline]{NN/HG: Add a sentence on what does manual-drive operating mode mean? You mentioned this in your presentation already. Then you pass on to autonomous mode. }
 Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
@@
 motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
-turn the pinion arms which would change the steering angle of the vehicle. This
-principle is applied to all other subsystems.
+turn the pinion arms which would change the steering angle of the vehicle. \comment{This
+principle is applied to all other subsystems.}{Does this mean that this principle will be applicable to acceleration subsystem as well? If not, you will need to modify this statement.}
 
@@
  this system, Matlab’s System Identification Toolbox was used. In order to
- create different models, they collected and used data from an energy center in
- Malaysia. After generating different models, the authors ended up going with a
+ create different models, \remove{they}\add{raw data} collected \remove{and used data} from an energy center in
+ Malaysia \add{was used}. After generating different models, the authors ended up going with a
  fourth order ARX (also known as ARXQS) model because it was the most accurate,
@@
 $y(t)$ is the system output at time $t,$ while $u(t)$ is the input.
-The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.
+The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system's number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system's output.
 
@@
 
-The example given in~\cite{example1} shows how to create an iddata object from a
+The example given in~\cite{example1} shows how to create an \comment{iddata}{What do you mean? Could you please define this term from high-level perspective?} object from a
 dataset in order to get the inputs and the outputs. The next step was to look at
 the impulse and step responses in order to learn more about how the inputs and
-outputs act. From there the state space model was estimated using the first part
+outputs act. From there, the state space model was estimated using the first part
 of the given data. This model was compared to the step responses and with the
@@
 percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\%
-
-for the speed data. The frequency response of the model was estimated with
-spectral analysis and bode plots were also created. The tutorial explained that
-if the data doesn’t give nice models, then it is best to try out submodels for
+for the speed data.
+
+The frequency response of the model was estimated with
+spectral analysis and bode \replace{plots}{diagrams} were also created. The tutorial explained that
+if the data \replace{doesn't}{does not} give \replace{nice}{acceptable} models, then it is best to try out submodels for
 the different channels. Two single-input single-output (SISO) models were
@@
 model that more accurately reflected the generated voltage data. By creating
-this model and comparing it to the validation data and previous models, we saw a
+this model and comparing it to the validation data and previous models, \replace{we saw}{it is observed} a
 best fit percentage of 90.18\%. The last thing the example showed was how to
-merge the two SISO models we created earlier.
-
+merge the two SISO models we created earlier. %
+%
+\todo[inline]{Fig.~\mbox{\ref{fig:exMIMO}} was not referred in the previous paragraph.
+At least you should say, Fig...
+shows $\ldots$.
+A figure cannot be placed without explaining what the figure is about in the section.}
 \begin{figure}[htbp]
@@
 \label{sec:sysID-Example2}
-This example~\cite{Matlab2} discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example~\cite{Matlab2} discusses solutions for modeling both MISO \add{multiple-input single-output} and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
 The other channels should be able to closely relate to the model for the output channel you selected.
-
+%
+%
 \begin{figure}[htbp]
@@
 \end{figure}
+%
+\todo[inline]{Same thing happened here. A figure (Fig. 3) is placed without explaining what this figure is about in the text. }
 
@@
 was the most accurate, with a best fit percentage of 85.83\%.
+%
 \begin{figure}[htbp]
@@
 \end{figure}
+% 
+\todo[inline]{Same thing happened here. A figure (Fig. 4) is placed without explaining what this figure is about in the text. }
 
@@
 The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
+\add{Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus self-driving vehicle provided by company (Hexagon $|$ AutonomouStuff).} %
+% 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
+  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
+  \label{fig:highLevelSystemArchitecture}
+\end{figure}
+%
+\add{However, actual vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
+A team of the project members visited the site to collect raw data for steering, brake, and acceleration subsystems of the vehicle.} %
+% 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\caption{AutonomouStuff Lexus RX450H vehicle.}
+	\label{fig:lexusvehicle}
+\end{figure}
+%
+
 Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
@@
 The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based on the other output's behavior.
-%
-\begin{figure}[htbp]
-  \centering
-    \includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
-  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
-  \label{fig:highLevelSystemArchitecture}
-\end{figure}
-
-% 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
-	\caption{AutonomouStuff Lexus RX450H vehicle.}
-	\label{fig:lexusvehicle}
-\end{figure}
 
@@
 
-The steering subsystem consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
+The steering subsystem \add{of a generic self-driving vehicle} consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
 The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
 Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
-The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}
-
-\begin{figure}[h]
+The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}\add{, where the target and the actual orientations of the vehicle are denoted by $\theta^{\text{ref}}$ and $\theta(t)$ at time $t\ge 0,$ respectively.} %
+%
+\begin{figure}[htbp]
   \centering
@@
     (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
-
   \end{tikzpicture}
   % \captionsetup{justification=centering, margin=3cm}
-
   % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
@@
 \end{figure}
+%
+\add{The error signal, which is the difference between the target and the actual directions of the vehicle, is passed on to the steering controller.
+The outputs of the steering controller are the torque voltages that are applied to the power steering motors of the steering subsystems of the vehicle.}
 
@@
   The brake subsystem is made up of the master cylinder, brake rotor, brake drum, brake pad, brake caliper, brake shoe, brake booster, brake pedal, wheel speed sensors, ABS module, and brake lines~\footnote{\url{https://oards.com/car-brake-system-components/}}.
-The subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
-Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed.
-This boolean value indicates to the user whether or not the brake pedal is being pressed.
-The brake subsystem is another example of a multiple-input multiple-output system.
+\add{A high-level block diagrams showing the inputs and puts of a conventional brake subsystem of a self-driving vehicle is shown in Fig.~\ref{fig:brakeModelArchitecture}.} %
+%  
  \begin{figure}[htbp]
@@
     (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
-
   \end{tikzpicture}
@@
 \end{figure}
+%
+The subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs.
+Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed.
+This boolean value indicates to the user whether or not the brake pedal is being pressed.
+The brake subsystem is another example of a multiple-input multiple-output system.
 
@@
  \end{figure}
-
+ %
+\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
   \subsection{Shift Subsystem}
@@
 
+ % 
+ \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
   \subsection{Speed Subsystem}
@@
 \end{figure}
+% 
+\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
 
@@
  \end{figure}
+ % 
+ \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
 
@@
 \end{figure}
-
+%
+\todo[inline]{SM: I'll rewrite the following paragraph since the description herein is valid for specific architecture of an actor neural network. } 
 The neural network inputs are mapped to the outputs by being assigned a set of weights~\footnote{\tiny \hsize=0.45\textwidth \url{https://towardsdatascience.com/machine-learning-for-beginners-an-introduction-to-neural-networks-d49f22d238f9}}.
@@
 The neural network is validated by passing another subset of data that was not used for training purposes and comparing the output results of the neural network with the expected output results from the data set.
-An acceptable neural network model will meet the desired error requirements~\footnote{\hsize=0.9\textwidth \url{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}}.
+An acceptable neural network model will meet the desired error requirements\footnote{\href{https://medium.com/autonomous-agents/bayesian-regularization-for-neuralnetworks-2f2d34f03adc}{Bayesian regularization}}.
 
@@
 The first method that we tried was developing different system types using Mathworks' MATLAB System Identification Toolbox.
-Using data we collected from the Lexus vehcile platform at AutonomouStuff,this toolbox allowed us to add input and output data for each vehicle subsystem.
+Using data we collected from the Lexus vehcile platform at AutonomouStuff, this toolbox allowed us to add input and output data for each vehicle subsystem.
 With this data, we used one subset to train the system and another subset for validation.
@@
 
-In order to accurately model each vehicle subsystem so that safe, reliable controllers can be developed for autonomous control, the following criteria will be met:
+\replace{In order t}{T}o accurately model each vehicle subsystem so that safe, reliable controllers can be developed for autonomous control, the following criteria will be met:
 \begin{itemize}
-\item Each vehicle subsystem will be able to track nonlinearities depicted in Fig.~\ref{fig:nonlinGraph} associated with small changes in the output of each subsystem
-\item Each vehicle subsystem plant model will track any desired inputs within the specified error bounds
+\item Each vehicle subsystem will be able to track nonlinearities depicted in Fig.~\ref{fig:nonlinGraph} associated with small changes in the output of each subsystem. %
+  %
+  \begin{figure}[htbp]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
+    \caption{Steering Non-linear Behavior}
+    \label{fig:nonlinGraph}
+  \end{figure}
+
+\item Each vehicle subsystem plant model will track any desired inputs within the specified error bounds\add{:}
 	\begin{itemize}
-		\item Steering Angle within 5 degrees
-		\item Pedal Positions within 5\%
+		\item Steering \replace{A}{a}ngle within 5 degrees
+		\item Pedal \replace{P}{p}ositions within 5\%
 	\end{itemize}
@@
 \end{itemize}
-
+%
 The vehicle plant model will fulfill the requirements listed below:
@@
 \end{itemize}
+%
 
@@
 The steering subsystem, for example, should behave in a smooth, continuous manner.
-However, AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+However, \add{a team of researchers from }AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
 This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
-These models will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
-
-\begin{figure}[htbp]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
-    \caption{Steering Non-linear Behavior}
-    \label{fig:nonlinGraph}
-\end{figure}
+\replace{These}{The plant models developed in this work}\remove{ models} will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
 
@@
 \subsection{Acceleration System Modeling}
+\todo[inline]{The text of the following paragraph is very similar to the above section except that the word ``steering'' was replaced by ``acceleration''.
+You paraphrase the sentences and there should some differences in the input and output data.
+What are the input data, the output data, units of those data, for example}
 To develop a model of the acceleration system, we employed multiple methods.
@@
 
-We traveled to AutonomouStuff in order to collect
+We \replace{traveled to}{visited the workplace of} AutonomouStuff in order to collect
 data from the steering, acceleration, and braking subsystems in an autonomous
@@
 
-\noindent The laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+\noindent The \add{interfacing software,} \todo[fancyline]{name of the software}, \add{installed in the} laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
 This data is sent or received using the CANCase and CAN bus.
@@
 The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
-This is how we were able to collect logs of data that we would use to develop models of the autonomous vehicle subsystems.
-\\
+This is how we were able to collect logs of data that we would use to develop \add{plant} models of the autonomous vehicle subsystems.
 
@@
 In Fig.~\ref{fig:vehicleSetup}, the experimental setup for data collection is shown.
-The laptop is used to collect the data from the desired vehicle subsystem by the use of Vector's CANAlyzer software.
-The CAN Case collects data from the PAC Mod and ECU and sends the data using a CAN bus to the laptop which is then parsed and displayed through the use of CANAlyzer.
-The ECU and PAC Mod are not shown in Fig.~\ref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
-\\
-
+%
+% 
 \begin{figure}[htbp]
@@
 \end{figure}
+% 
+The laptop is used to collect the data from the desired vehicle subsystem by the use of Vector's CANAlyzer software.
+The CAN Case collects data from the PAC Mod and ECU and sends the data using a CAN bus to the laptop which is then parsed and displayed through the use of CANAlyzer.
+The ECU and PAC Mod are not shown in Fig.~\ref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
+%
 
@@
 As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
-For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems.
+For reference, the differences in the models created for by-wire and manual mode are \comment{depicted in \mbox{\ref{sec:simresults}}}{I do not understand what do you mean by in VII, is it a section, figure, or table?
+The sentence does not read well} for the steering and acceleration subsystems.
 For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
@@
 \vspace{12pt}
-\noindent The model of the by-wire steering system is a twentieth order transfer function.
-The twentieth order transfer function is the best proposed estimation considering the system costs associated with a higher order transfer function while also obtaining an acceptable best fit percentage.
-Table~\ref{tab:byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.%
+\noindent The model of the by-wire steering system is a twentieth order transfer
+function. The twentieth order transfer function is the best proposed estimation
+considering the system costs associated with a higher-order transfer function
+while also obtaining an acceptable best fit percentage. %
 %
 \begin{table}[hbtp]
-	\label{tab:byWireSteerCoeffA}
-	\caption{By-Wire Mode Steering Transfer Function Torque Voltage A Coefficient Table}
   \centering
@@
 
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage A Coefficient Table}
+	\label{tab:byWireSteerCoeffA}
+\end{table}
+%
+Table~\ref{tab:byWireSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal.%
+% 
+\add{The second set of coefficients for the torque voltage A is given below:} %
+%
 \begin{center}
@@
 \end{center}
-\end{table}
-%
 
@@
 %
-\begin{table}[hbtp]
-	\label{tab:byWireSteerCoeffB}
-	\caption{By-Wire Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+\begin{table}[htbp]
   \centering
@@
     \end{tabular}}
+	\caption{By-Wire Mode Steering Transfer Function Torque Voltage B Coefficient Table}
+	\label{tab:byWireSteerCoeffB}
+\end{table}
+%
+\add{Similar to the torque voltage A, the second set of coefficients for the torque voltage B signal is shown below:} %
+%
 \begin{center}
@@
 \end{center}
-\end{table}
 %
@@
     \end{tabular}}
+\end{table}
+%
+\add{This is followed by the $b$-coefficients given below:} %
+%
 \begin{center}
@@
 \end{center}	
-\end{table}
 %
@@
 
+\todo[inline]{Figures of both steering and acceleration subsystem models are placed without referring them in the paragraph.
+Each of the figures needs to be explained.
+Also, the following paragraph and the paragraph for the acceleration system are alike except that the word ``steering'' is replaced with the word ``acceleration''.
+This should not be the case in a professional report.}
+
 To develop the model of the steering system using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked.
@@
 
-\todo[inline]{Need annotation of each of the pictures. Like that, we show what
-  each of the equipment are}
 \begin{figure}

### 2022-05-12 reportTII-ArticleHIL.tex
Final Report Updates

@@
 
-\todo[inline]{NN/HG: Add 2/3 sentences on what motivated the company to model
-  subsystems of autonomous vehicles, Hint: Erik mentioned already that employees
-can perform testing without the physical vehicle. You just need to extend his statement to write the motivational paragraph behind this project}
+%\todo[inline]{NN/HG: Add 2/3 sentences on what motivated the company to model
+%  subsystems of autonomous vehicles, Hint: Erik mentioned already that employees
+%can perform testing without the physical vehicle. You just need to extend his statement to write the motivational paragraph behind this project}
 
@@
 Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+By creating these software models, the company can run tests using them without needing the physical vehicle.
+As a result, these models could potentially allow the company to get more testing done.
 
@@
 the other subsystems. There are already controllers in place for the Lexus
-vehicle platform, but their \comment{reliability}{Need to define what do you mean by reliability, be very specific} is lower than expected due to non-linear
+vehicle platform, but their ability to match the desired input specified by the vehicle operator
+%\comment{reliability}{Need to define what do you mean by reliability, be very specific} 
+is lower than expected due to non-linear
 behaviors of the torque voltages required to control each subsystem. The scope
-of this project includes developing mathematical \add{and/or data-driven} models for each subsystem so \add{that one} \remove{AutonomouStuff} can \add{easily} implement control systems that improve the reliability of the
+of this project includes developing mathematical and/or data-driven models for each subsystem so that one can easily implement control systems that improve the reliability of the
 autonomous vehicle platform.
 These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
-Once these models are developed, they will be tested using \remove{AutonomouStuff's} Hardware-in-the-Loop (HIL) bench.
-Once there is confidence in each model, \remove{AutonomouStuff can use} these models \add{can be used} on \add{the}  \remove{their}  HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
+Once these models are developed, they will be tested using Hardware-in-the-Loop (HIL) bench.
+Once there is confidence in each model, these models can be used on the   HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
 
@@
  this system, Matlab’s System Identification Toolbox was used. In order to
- create different models, \remove{they}\add{raw data} collected \remove{and used data} from an energy center in
- Malaysia \add{was used}. After generating different models, the authors ended up going with a
+ create different models, raw data collected from an energy center in
+ Malaysia was used. After generating different models, the authors ended up going with a
  fourth order ARX (also known as ARXQS) model because it was the most accurate,
@@
 The frequency response of the model was estimated with
-spectral analysis and bode \replace{plots}{diagrams} were also created. The tutorial explained that
-if the data \replace{doesn't}{does not} give \replace{nice}{acceptable} models, then it is best to try out submodels for
+spectral analysis and bode diagrams were also created. The tutorial explained that
+if the data does not give acceptable models, then it is best to try out submodels for
 the different channels. Two single-input single-output (SISO) models were
@@
 model that more accurately reflected the generated voltage data. By creating
-this model and comparing it to the validation data and previous models, \replace{we saw}{it is observed} a
+this model and comparing it to the validation data and previous models, it is observed a
 best fit percentage of 90.18\%. The last thing the example showed was how to
-merge the two SISO models we created earlier. %
-%
-\todo[inline]{Fig.~\mbox{\ref{fig:exMIMO}} was not referred in the previous paragraph.
-At least you should say, Fig...
-shows $\ldots$.
-A figure cannot be placed without explaining what the figure is about in the section.}
+merge the two SISO models we created earlier. Fig.~\ref{fig:exMIMO} shows the results of comparing the estimated state space model along with the merged SISO models to the given validation data. 
+%
+
 \begin{figure}[htbp]
@@
 \label{sec:sysID-Example2}
-This example~\cite{Matlab2} discusses solutions for modeling both MISO \add{multiple-input single-output} and MIMO models using Mathworks' Matlab System Identification Toolbox.
+This example~\cite{Matlab2} discusses solutions for modeling both MISO multiple-input single-output and MIMO models using Mathworks' Matlab System Identification Toolbox.
 As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs.
@@
 The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
-\add{Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus self-driving vehicle provided by company (Hexagon $|$ AutonomouStuff).} %
+Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus self-driving vehicle provided by company (Hexagon $|$ AutonomouStuff).
+%
 % 
@@
 %
-\add{However, actual vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
-A team of the project members visited the site to collect raw data for steering, brake, and acceleration subsystems of the vehicle.} %
+However, actual vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
+A team of the project members visited the site to collect raw data for steering, brake, and acceleration subsystems of the vehicle.
+%
 % 
@@
 
-The steering subsystem \add{of a generic self-driving vehicle} consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
+The steering subsystem of a generic self-driving vehicle consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
 The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
 Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
-The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}\add{, where the target and the actual orientations of the vehicle are denoted by $\theta^{\text{ref}}$ and $\theta(t)$ at time $t\ge 0,$ respectively.} %
+The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}, where the target and the actual orientations of the vehicle are denoted by $\theta^{\text{ref}}$ and $\theta(t)$ at time $t\ge 0,$ respectively.
+%
 %
@@
 %
-\add{The error signal, which is the difference between the target and the actual directions of the vehicle, is passed on to the steering controller.
-The outputs of the steering controller are the torque voltages that are applied to the power steering motors of the steering subsystems of the vehicle.}
+The error signal, which is the difference between the target and the actual directions of the vehicle, is passed on to the steering controller.
+The outputs of the steering controller are the torque voltages that are applied to the power steering motors of the steering subsystems of the vehicle.
 
@@
   The brake subsystem is made up of the master cylinder, brake rotor, brake drum, brake pad, brake caliper, brake shoe, brake booster, brake pedal, wheel speed sensors, ABS module, and brake lines~\footnote{\url{https://oards.com/car-brake-system-components/}}.
-\add{A high-level block diagrams showing the inputs and puts of a conventional brake subsystem of a self-driving vehicle is shown in Fig.~\ref{fig:brakeModelArchitecture}.} %
+A high-level block diagrams showing the inputs and puts of a conventional brake subsystem of a self-driving vehicle is shown in Fig.~\ref{fig:brakeModelArchitecture}.
+%
 %  
@@
   The acceleration subsystem consists of the throttle pedal, engine, and crankshaft~\footnote{\url{https://harrisautomotiverepair.com/car-accelerator/}}.
-It is a multiple-input multiple-output system.
-Acceleration pedal voltages are sent to the subsystem. 
-A new acceleration pedal position value is generated to better match 
-the real-time pedal position. This is then the output 
-of the acceleration subsystem. %
+It is a multiple-input multiple-output system, whose block diagram is depicted in Fig.~\ref{fig:accelModelArchitecture}.
+Taking the Acceleration Pedal Voltages as the input, the subsystem then produces the Acceleration Pedal Position as the output. The output represents how much the pedal is pressed as a percentage.
+
+%Acceleration pedal voltages are sent to the subsystem. 
+%A new acceleration pedal position value is generated to better match 
+%the real-time pedal position. This is then the output 
+%of the acceleration subsystem. %
 %
@@
  \end{figure}
- %
-\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+% %
+%\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
 Use the same format for explaining all the subsystems.
@@
 This subsystem can be classified as a single-input single-output system.
-The subsystem takes the desired shifter gear value from the user.
-Within the subsystem, the actual shifter gear changes to better reflect the desired gear.
-This actual shifter gear value is then the output of the shift subsystem.
+A block diagram of the shift subsystem is seen in Fig.~\ref{fig:shiftModelArchitecture}.
+The subsystem takes the Desired Shifter Gear value from the user as the input.
+Within the subsystem, the Actual Shifter Gear is changed to better reflect the desired gear.
+This Actual Shifter Gear value is then the output of the shift subsystem.
  \begin{figure}[htbp]
@@
  % 
- \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+% \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
 Use the same format for explaining all the subsystems.
@@
 This speed subsystem would fall under the multiple-input single-output system.
-There are four inputs, the position of the acceleration pedal and the brake pedal, along with the shifter actual gear.
-Taking these inputs, the speed subsystem finds the vehicle speed.
-This vehicle speed is then the output of the system.
+A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}.
+The subsystem has four inputs, the Acceleration Pedal Position, Brake Pedal Position, and Shifter Gear.
+Using these inputs, the speed subsystem finds the Vehicle Speed.
+This Vehicle Speed is then the output of the system.
  \begin{figure}[htbp]
@@
 % 
-\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+%\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
 Use the same format for explaining all the subsystems.
@@
   The speed control subsystem components include the cruise control switch, vehicle speed sensor, throttle sensor, and brake switch~\footnote{\url{https://www.freeasestudyguides.com/electrical-cruise-control-systems.html}}.
-This subsystem is a straightforward single-input single-output system.
-The desired vehicle speed is set by the user and sent to the speed control subsystem.
-Taking this input, the subsystem calculates the new vehicle speed.
+This subsystem is a straightforward single-input single-output system, shown in Fig.~\ref{fig:speedControlModelArchitecture}.
+The Desired Vehicle Speed input is set by the user and sent to the speed control subsystem.
+Taking this input, the subsystem calculates the Actual Vehicle Speed.
 This value is then sent out to the rest of the vehicle system.
@@
     \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
-    \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);
+    (speedControlSubsystem.180)--node[very near end,above]{Desired Vehicle Speed}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedControlSubsystem.0)--node[very near end,above]{Actual Vehicle Speed}++(1.9,0);
 
@@
 
-\replace{In order t}{T}o accurately model each vehicle subsystem so that safe, reliable controllers can be developed for autonomous control, the following criteria will be met:
+To accurately model each vehicle subsystem so that safe, reliable controllers can be developed for autonomous control, the following criteria will be met:
 \begin{itemize}
@@
 	\begin{itemize}
-		\item Steering \replace{A}{a}ngle within 5 degrees
-		\item Pedal \replace{P}{p}ositions within 5\%
+		\item Steering angle within 5 degrees
+		\item Pedal positions within 5\%
 	\end{itemize}
@@
 The steering subsystem, for example, should behave in a smooth, continuous manner.
-However, \add{a team of researchers from }AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+However, a team of researchers from AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
 This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
-\replace{These}{The plant models developed in this work}\remove{ models} will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
+The plant models developed in this work will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
 
@@
 
-We \replace{traveled to}{visited the workplace of} AutonomouStuff in order to collect
+We visited the workplace of AutonomouStuff in order to collect
 data from the steering, acceleration, and braking subsystems in an autonomous
@@
 
-\noindent The \add{interfacing software,} \todo[fancyline]{name of the software}, \add{installed in the} laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+\noindent The interfacing software, \todo[fancyline]{name of the software}, installed in the laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
 This data is sent or received using the CANCase and CAN bus.
@@
 The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
-This is how we were able to collect logs of data that we would use to develop \add{plant} models of the autonomous vehicle subsystems.
+This is how we were able to collect logs of data that we would use to develop plant models of the autonomous vehicle subsystems.
 
@@
 % 
-\add{The second set of coefficients for the torque voltage A is given below:} %
+The second set of coefficients for the torque voltage A is given below: %
 %
@@
 %
-\add{Similar to the torque voltage A, the second set of coefficients for the torque voltage B signal is shown below:} %
+Similar to the torque voltage A, the second set of coefficients for the torque voltage B signal is shown below: %
 %
@@
 %
-\add{This is followed by the $b$-coefficients given below:} %
+This is followed by the $b$-coefficients given below: %
 %
@@
   \centering
-    \includegraphics[width=0.95\linewidth]{figs/inkscape/hilBenchAstuffAnnotated}
+    \includegraphics[width=0.95\linewidth]{figs/inkscape/hilBenchAstuffAnnotatedNew}
   \caption{AutonomouStuff HIL Bench Configuration}

### 2022-05-12 reportTII-ArticleHIL.tex
Edited final report

@@
 %
-\todo[inline]{NN/HG: Add a sentence on what does manual-drive operating mode mean? You mentioned this in your presentation already. Then you pass on to autonomous mode. }
+Manual-drive operation occurs when the driver has complete control over the vehicle, including controlling the steering, speed, acceleration, and braking of the vehicle.
+Autonomous operation occurs where the vehicle is controlled by a computer under driver supervision.
+%
 Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
@@
 motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
-turn the pinion arms which would change the steering angle of the vehicle. \comment{This
-principle is applied to all other subsystems.}{Does this mean that this principle will be applicable to acceleration subsystem as well? If not, you will need to modify this statement.}
+turn the pinion arms which would change the steering angle of the vehicle.
+The idea of by-wire mode for other vehicle subsystems is controlled in a similar manner with torque voltages being applied to a motor that controls the vehicle subsystem.
 
@@
 
-The example given in~\cite{example1} shows how to create an \comment{iddata}{What do you mean? Could you please define this term from high-level perspective?} object from a
-dataset in order to get the inputs and the outputs. The next step was to look at
+The example given in~\cite{example1} shows how to create an iddata object from a
+dataset in order to get the inputs and the outputs. An iddata object is a way to format input and output time-series data for the manipulation of data that MATLAB employs. The next step was to look at
 the impulse and step responses in order to learn more about how the inputs and
@@
 The command line can be used by using the function associated with the model structure name and then using the compare function to get the best fit percentage.
+In Fig.~\ref{fig:ex2fig1}, the plot shows the output of the compare function for the simulated output of a generated model.
+In Fig.~\ref{fig:ex2fig2}, the plot shows the output of the compare function for the simulated output of two generated models.
+These figures were generated using the compare function.
 For MIMO systems, there are not model structures built into the System Identification Toolbox and they must be imported instead.
@@
 %
-\todo[inline]{Same thing happened here. A figure (Fig. 3) is placed without explaining what this figure is about in the text. }
 
@@
 experimental data. The state-space model with the five-step response prediction
-was the most accurate, with a best fit percentage of 85.83\%.
+was the most accurate, with a best fit percentage of 85.83\% as depicted in Fig.~\ref{fig:exIO}.
+The plot shows the effects of the two inputs, consumption rate and current, as well as the simulated output of the production.
 %
@@
 %
-\todo[inline]{Same thing happened here. A figure (Fig. 4) is placed without explaining what this figure is about in the text. }
 
@@
   \subsection{Acceleration Subsystem}
+
   The acceleration subsystem consists of the throttle pedal, engine, and crankshaft~\footnote{\url{https://harrisautomotiverepair.com/car-accelerator/}}.
@@
 \subsection{Acceleration System Modeling}
-\todo[inline]{The text of the following paragraph is very similar to the above section except that the word ``steering'' was replaced by ``acceleration''.
-You paraphrase the sentences and there should some differences in the input and output data.
-What are the input data, the output data, units of those data, for example}
 To develop a model of the acceleration system, we employed multiple methods.
 The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB.
-The NARX model we developed was not accurate and did not track the output of the acceleration system data.
-The transfer function model we developed was more reliable tracking the output of the acceleration system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
+The NARX model we developed was accurate for the by-wire model and tracked the output of the acceleration system data, but did not meet the error requirements.
+The transfer function model we developed was more reliable tracking the output of the acceleration system data for the manual mode operation, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
 Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
@@
 
-\noindent The interfacing software, \todo[fancyline]{name of the software}, installed in the laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+\noindent The interfacing software, Vector CANAlyzer, installed in the laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
 This data is sent or received using the CANCase and CAN bus.
@@
 As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
-For reference, the differences in the models created for by-wire and manual mode are \comment{depicted in \mbox{\ref{sec:simresults}}}{I do not understand what do you mean by in VII, is it a section, figure, or table?
-The sentence does not read well} for the steering and acceleration subsystems.
+For reference, the differences in the models created for by-wire and manual mode are depicted in Section \ref{subsec:SteeringTF} and \ref{subsec:AccelTF} for the steering and acceleration subsystems.
 For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
@@
 \subsubsection{Steering Subsystem}
+\label{subsec:SteeringTF}
 In Fig.~\ref{byWireSteerModel}, the output steering angle is plotted versus time
@@
 \subsubsection{Acceleration System}
+\label{subsec:AccelTF}
 In \autoref{byWireAccelModel}, the output acceleration pedal position is plotted versus time when the vehicle is in by-wire mode.
@@
 \subsubsection{Steering System}
-
-\todo[inline]{Figures of both steering and acceleration subsystem models are placed without referring them in the paragraph.
-Each of the figures needs to be explained.
-Also, the following paragraph and the paragraph for the acceleration system are alike except that the word ``steering'' is replaced with the word ``acceleration''.
-This should not be the case in a professional report.}
-
 To develop the model of the steering system using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked.
@@
 The model was also trained with twelve delay units to achieve the required accuracy, meaning that the first twelve output samples of the model should be ignored.
-
-\begin{figure}[htbp]
-	\centering
-	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
+%
+In Fig.~\ref{initalSteeringModel}, the top plot shows the simulated output of the neural network when the input torque voltages and desired steering angle from data subset 1 are fed into the model.
+The bottom plot shows the error between the desired steering angle and the output of the neural network.
+For the steering model, the error should be less than 5 degrees or approximatley 0.1 radians.
+Fig.~\ref{testedSteeringModel} shows the same plots except data subset 2 was used instead.
+
+\begin{figure}[htbp]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalSteeringModel}}
 		{\includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
-	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedSteeringModel}}
 		{\includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
@@
 The model was also trained with three delay units to achieve the required accuracy, meaning that the first three output samples of the model should be ignored.
-
-\begin{figure}[htbp]
-	\centering
-	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalBrakeModel}}
+%
+In Fig.~\ref{initalAccelModel}, the top plot shows the simulated output of the neural network when the input torque voltages and desired acceleration pedal position from data subset 1 are fed into the model.
+The bottom plot shows the error between the acceleration pedal position and the output of the neural network.
+For the acceleration model, the error should be less than 5\% or 0.05.
+Fig.~\ref{testedAccelModel} shows the same plots except data subset 2 was used instead.
+
+\begin{figure}[htbp]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 1 \label{initalAccelModel}}
 		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
-	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedBrakeModel}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedAccelModel}}
 		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}

### 2022-08-10 paperIEEE-ROSE2022.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{soul,xcolor}
\usepackage{easyReview}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles\\
\thanks{This work was partially supported by AutonomouStuff (https://autonomoustuff.com/)}
}

\author{\IEEEauthorblockN{Hannah Grady, Nicholas Nauman, and Md Suruz Miah}
\IEEEauthorblockA{\textit{Department of Electrical and Computer Engineering} \\
\textit{Bradley University}\\
Peoria, Illinois, 61615, USA \\
E-mail: \{hgrady,nnauman\}@mail.bradley.edu, smiah@bradley.edu }
}

\maketitle

\begin{abstract}
\highlight{This report presents the results of modeling vehicle systems and testing them
  using open-loop. First, data was collected for each system using a Lexus
  RX450H vehicle. After data collection, models were developed in order to
  accurately simulate the physical vehicle system. MATLAB's System
  Identification Toolbox was initially used to create these models. However,
the transfer function models it provided w
these systems and their non-linear behaviors. After this was established,
modeling was done using MATLAB's Neural Network Time Series application. Once a
Neural Network model was created, it was then exported to Simulink and modified
to be able to run without the use of the Deep Learning toolbox. These models
gave much more accurate results when compared to the transfer function models
developed using the System Identification Toolbox}

\hl{SM:I'll modify}
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

% \begin{figure}[htbp]
% \centerline{\includegraphics{fig1.png}}
% \caption{Example of a figure caption.}
% \label{fig}
% \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2022-08-10 paperIEEE-ROSE2022.tex
Updated introduction

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
+\usepackage{cite,url}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{easyReview}
+
+\usepackage[format=default,justification=centerlast]{caption} % Figure caption text customization
+
+\usepackage[list=true,labelformat=simple]{subcaption}
+\renewcommand\thesubfigure{(\alph{subfigure})}
+\graphicspath{%
+  {figs/matlab/}
+}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+\label{sec:introduction}
 
-\section{Ease of Use}
+%\todo[inline]{NN/HG: Add 2/3 sentences on what motivated the company to model
+%  subsystems of autonomous vehicles, Hint: Erik mentioned already that employees
+%can perform testing without the physical vehicle. You just need to extend his statement to write the motivational paragraph behind this project}
 
-\subsection{Maintaining the Integrity of the Specifications}
+Self-driving vehicles have attracted a significant interest in the past decades due to the advent of new technologies in the field of robotics and autonomous systems.
+Such vehicles are being developed by companies for commercial and personal use as they mainly aim to reduce crashes, energy consumption, pollution, and congestion.
+As it is apparent each self-driving vehicle is composed of varaious subsystems that researchers of autonomous vehicle community analyze, design, develop, and test.
+Intuitively, self-driving vehcles require thorough testing at the factory level before their demonstrations for  the commerical purpose.
+Such a testing procedure each physical vehicle is inefficient and costly as it involves testing of different subsystems, such as steering, brake, shift, to name a few, of a vehicle.
+In this work, we model different modules of a self-driving vehicle using machine learning techniques, where a physical self-driving vehicle is not required for testing.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+It is important to note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for these vehicles to be managed in the era of modern transportation systems in general.
+In particular, modeling different subsystems are conducted for a self-driving vehicle from the vehicle fleet shown in Fig.~\ref{fig:fleet}.
+would allow companies to continue crucial deliveries
+or transports of their products even if there is a shortage of drivers. In
+addition, autonomous vehicles have the ability to make roads safer for drivers
+and pedestrians alike. To develop a reliable and safe transportation system for
+modern world, a large body of research in the field of autonomous vehicles is
+being conducted in recent decades \cite{Liu2017,Prasad2020}.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+% \vspace*{12pt}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\noindent Usually, there are six main subsystems of a self-driving vehicle: %
+%
+\begin{enumerate}
+\item  Steering,
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\item acceleration,
 
-\subsection{Units}
+\item brake,
+
+\item shift,
+
+\item speed, and
+
+\item speed control (cruise).
+\end{enumerate}
+%
+These subsystems are to be modeled to get an accurate representation of how
+the vehicle should be controlled.
+Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+By creating these software models, the company can run tests using them without needing the physical vehicle.
+As a result, these models could potentially allow the company to get more testing done.
+
+The first subsystem we will model is the steering model, and then we will move onto
+the other subsystems. There are already controllers in place for the Lexus
+vehicle platform, but their ability to match the desired input specified by the vehicle operator
+%\comment{reliability}{Need to define what do you mean by reliability, be very specific}
+is lower than expected due to non-linear
+behaviors of the torque voltages required to control each subsystem. The scope
+of this project includes developing mathematical and/or data-driven models for each subsystem so that one can easily implement control systems that improve the reliability of the
+autonomous vehicle platform.
+These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
+Once these models are developed, they will be tested using Hardware-in-the-Loop (HIL) bench.
+Once there is confidence in each model, these models can be used on the   HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
+
+There are two operating modes of the Lexus vehicle platform used in this project: %
+%
 \begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+  \item Manual-drive and
+  \item by-wire or autonomous.
 \end{itemize}
+%
+Manual-drive operation occurs when the driver has complete control over the vehicle, including controlling the steering, speed, acceleration, and braking of the vehicle.
+Autonomous operation occurs where the vehicle is controlled by a computer under driver supervision.
+%
+Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
+subsystem, like the steering system in this example, sends torque voltages to a
+motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
+turn the pinion arms which would change the steering angle of the vehicle.
+The idea of by-wire mode for other vehicle subsystems is controlled in a similar manner with torque voltages being applied to a motor that controls the vehicle subsystem.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\vspace*{12pt}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=3cm]{figs/img/autonomousVehiclesAStuff}    \caption{}
+    \label{fig:fleet}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.48\linewidth}
+    \centering
+    \includegraphics[height=3cm]{figs/img/autonomousVehiclesSteering}
+    \caption{}
+    \label{fig:steerOverview}
+  \end{subfigure}
+  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerOverview} steering model setup (courtesy of AutonomouStuff). }
+  \label{fig:AstuffFleetSteeringSetup}
+\end{figure}
 
-\subsection{\LaTeX-Specific Advice}
+\section{Conclusion and Future Work}
+\label{sec:conclustionAndFutureWork}
+Our initial approach was to model the subsystems using the System Identification Toolbox from MATLAB, but it produced unsatisfactory results.
+Switching to the Neural Network Time Series app allowed us to train models using the data we collected.
+These models that were developed met the predefined accuracy requirements, and so were tested using an open loop setup.
+In the future if AutonomouStuff would like to model other vehicle subsystems, we would recommend modeling them using Neural Networks.
+Creating the Neural Networks and exporting the models to Simulink was easy to do and produced accurate results.
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+For this project, further testing should be completed for these subsystem models.
+Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop, this would be a good place to start.
+Further testing is important to make sure the developed models are accurate and compatible with testing using hardware.
+Depending on what AutonomouStuff decides, future engineers working on this project could start developing controllers based off of these models.
+Currently, AutonomouStuff develops their own controllers for their vehicle subsystems, but they could allow students to design some as part of this senior project.
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-% \begin{figure}[htbp]
-% \centerline{\includegraphics{fig1.png}}
-% \caption{Example of a figure caption.}
-% \label{fig}
-% \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{IEEEtran}
+\bibliography{bib/references.bib}
 

### 2022-08-17 paperIEEE-ROSE2022.tex
Self-driving vehicle overview

@@
 
-\title{Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles\\
+\title{Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles\\
 \thanks{This work was partially supported by AutonomouStuff (https://autonomoustuff.com/)}
@@
 
-Self-driving vehicles have attracted a significant interest in the past decades due to the advent of new technologies in the field of robotics and autonomous systems.
-Such vehicles are being developed by companies for commercial and personal use as they mainly aim to reduce crashes, energy consumption, pollution, and congestion.
-As it is apparent each self-driving vehicle is composed of varaious subsystems that researchers of autonomous vehicle community analyze, design, develop, and test.
+Due to escalating demand of self-driving vehicles, automotive industry is gradually shifting its attention in  manufacturing a variety of autonomous vehicles.
+The advancement of new technologies led the automotive industry to develop such vehicles for commercial and personal use as they mainly aim to reduce crashes, energy consumption, pollution, and congestion.
+However, the development of process of autonomous vehicles still faces signifant challenges to overcome.
+As it is apparent, each self-driving vehicle is composed of varaious subsystems that researchers of autonomous vehicle community analyze, design, develop, and test.
 Intuitively, self-driving vehcles require thorough testing at the factory level before their demonstrations for  the commerical purpose.
-Such a testing procedure each physical vehicle is inefficient and costly as it involves testing of different subsystems, such as steering, brake, shift, to name a few, of a vehicle.
-In this work, we model different modules of a self-driving vehicle using machine learning techniques, where a physical self-driving vehicle is not required for testing.
+Such a testing procedure for each physical vehicle is inefficient and costly as it involves testing of different subsystems, such as steering, brake, shift, to name a few, of a vehicle.
+In this work, we model different modules/subsystems of a self-driving vehicle using machine learning techniques, where a physical self-driving vehicle is not required for testing.
+Note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for autonomous vehicles to be managed in the era of modern transportation systems in general.
+In particular, modeling different subsystems is conducted for a self-driving vehicle from the vehicle fleet shown in Fig.~\ref{fig:fleet}.
+%
+%
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.15]{figs/img/autonomousVehiclesAStuff}
+  \caption{Autonomous vehicle fleet (courtesy of AutonomouStuff Inc., https://autonomoustuff.com)}
+  \label{fig:fleet}
+\end{figure}
+%
+Such modeling process would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. %
 
-It is important to note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for these vehicles to be managed in the era of modern transportation systems in general.
-In particular, modeling different subsystems are conducted for a self-driving vehicle from the vehicle fleet shown in Fig.~\ref{fig:fleet}.
-would allow companies to continue crucial deliveries
-or transports of their products even if there is a shortage of drivers. In
-addition, autonomous vehicles have the ability to make roads safer for drivers
+% \begin{figure}[htbp]
+%   \centering
+%   \begin{subfigure}[b]{0.48\linewidth}
+%     \centering
+%        \caption{}
+%     \label{fig:fleet}
+%   \end{subfigure}
+%   \begin{subfigure}[b]{0.48\linewidth}
+%     \centering
+%
+%     \caption{}
+%     \label{fig:steerOverview}
+%   \end{subfigure}
+%   \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerOverview} steering model setup (courtesy of AutonomouStuff). }
+%   \label{fig:AstuffFleetSteeringSetup}
+% \end{figure}
+
+Autonomous vehicles have the ability to make roads safer for drivers
 and pedestrians alike. To develop a reliable and safe transportation system for
 modern world, a large body of research in the field of autonomous vehicles is
-being conducted in recent decades \cite{Liu2017,Prasad2020}.
+being conducted in recent decades~\cite{Liu2017,Prasad2020}.
 
-% \vspace*{12pt}
-
-\noindent Usually, there are six main subsystems of a self-driving vehicle: %
+Usually, there are six main subsystems of a self-driving vehicle: %
 %
@@
 Once there is confidence in each model, these models can be used on the   HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
+\section{Self-Driving Vehicle Overview}
+\label{sec:selfDrivingVehicleOverview}
+In this section, we present an overview of the self-driving vehicle pertaining to the hardware-in-the-loop modeling process conducted in the work.
 
@@
 subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. In Fig.~\ref{fig:steerOverview}, the motor would
+motor that will control the subsystem. %
+%
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{figs/img/autonomousVehiclesSteering}
+  \caption{Steering subsystem in autonomous mode (courtesy of Autonomoustuff.com).}
+  \label{fig:steerOverview}
+\end{figure}
+%
+In Fig.~\ref{fig:steerOverview}, the motor would
 turn the pinion arms which would change the steering angle of the vehicle.
@@
 \vspace*{12pt}
-
-\begin{figure}[htbp]
-  \centering
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=3cm]{figs/img/autonomousVehiclesAStuff}    \caption{}
-    \label{fig:fleet}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.48\linewidth}
-    \centering
-    \includegraphics[height=3cm]{figs/img/autonomousVehiclesSteering}
-    \caption{}
-    \label{fig:steerOverview}
-  \end{subfigure}
-  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerOverview} steering model setup (courtesy of AutonomouStuff). }
-  \label{fig:AstuffFleetSteeringSetup}
-\end{figure}
 

### 2022-08-22 paperIEEE-ROSE2022.tex
Submitted version of IEEE ROSE 2022

@@
 
+\usepackage{booktabs,array} % Packages for tables
+\usepackage[inline]{enumitem}
+
 \usepackage[format=default,justification=centerlast]{caption} % Figure caption text customization
@@
 \renewcommand\thesubfigure{(\alph{subfigure})}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows, positioning, quotes}
+\usetikzlibrary{arrows.meta, positioning, decorations.markings}
+\usetikzlibrary{calc,tikzmark}
+\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
+\usepackage{siunitx}
+
 \graphicspath{%
@@
 \begin{abstract}
-\highlight{This report presents the results of modeling vehicle systems and testing them
-  using open-loop. First, data was collected for each system using a Lexus
-  RX450H vehicle. After data collection, models were developed in order to
-  accurately simulate the physical vehicle system. MATLAB's System
-  Identification Toolbox was initially used to create these models. However,
-the transfer function models it provided w
-these systems and their non-linear behaviors. After this was established,
-modeling was done using MATLAB's Neural Network Time Series application. Once a
-Neural Network model was created, it was then exported to Simulink and modified
-to be able to run without the use of the Deep Learning toolbox. These models
-gave much more accurate results when compared to the transfer function models
-developed using the System Identification Toolbox}
 
-\hl{SM:I'll modify}
+  In this paper, we present data-driven hardware-in-the-loop (HIL) plant models of different subsystems of a self-driving vehicle.
+Despite numerous concerns, automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market.
+Among numerous challenges in the development process of such vehicles are the validation and testing process of various subsystems.
+Here we provide data-driven models of different subsystems so that automotive industries can validate and test autonomous vehicles without the need of a physical vehicle, which indeed reduces the considerable amount of cost for automotive industries.
+The vehicle subsystems considered in this work steering, acceleration, brake, shift, speed, and speed control.
+However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Data-driven modeling, deep learning, hardware-in-the-loop, self-driving vehicle, vehicle subsystems
 \end{IEEEkeywords}
@@
 In this work, we model different modules/subsystems of a self-driving vehicle using machine learning techniques, where a physical self-driving vehicle is not required for testing.
+
 Note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for autonomous vehicles to be managed in the era of modern transportation systems in general.
-In particular, modeling different subsystems is conducted for a self-driving vehicle from the vehicle fleet shown in Fig.~\ref{fig:fleet}.
+In particular, this work models different subsystems for a self-driving vehicle of the vehicle fleet shown in Fig.~\ref{fig:fleet}.
 %
@@
 Such modeling process would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. %
-
+%
 % \begin{figure}[htbp]
@@
 being conducted in recent decades~\cite{Liu2017,Prasad2020}.
-
+In fact, the research on this topic has been conducted from a variety of perspectives, such as the application of connected and autonomous vehicle technology~\cite{DoT2017}, navigation and path control of self-driving vehicles~\cite{Duong2018,Chajan2021}.
+Authors in~\cite{Saruchi2015} worked on active front steering for steer-by-wire vehicle.
+Steering system of high speed intelligent vehicles has been modeled using system identification~\cite{Li1999}.
+Therefore, it is clear that numerous research pertainting to self-driving vehicles has been pursued, especially, in the past two decades.
+There are two operating modes considered for the autonomous vehicle employed in this work: %
+%
+\begin{itemize}
+  \item Manual-drive and
+  \item by-wire or autonomous~\cite{Saruchi2015}.
+\end{itemize}
+%
+Manual-drive operation occurs when the driver has complete control over the vehicle, including controlling the steering, speed, acceleration, and braking of the vehicle.
+Autonomous operation occurs where the vehicle is controlled by a computer under driver supervision.
+%
 Usually, there are six main subsystems of a self-driving vehicle: %
 %
-\begin{enumerate}
+\begin{enumerate*}
 \item  Steering,
@@
 \item speed control (cruise).
-\end{enumerate}
+\end{enumerate*}
 %
 These subsystems are to be modeled to get an accurate representation of how
-the vehicle should be controlled.
-Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
+the vehicle is to be controlled. %
+%Within the scope of this project and to expedite the modeling process, commercially available modeling tools in Mathworks' MATLAB, System Identification app in the System Identification Toolbox and Neural Network Time Series app in the Deep Learning toolbox, were used to model six subsystems for a Lexus vehicle platform, which is an experimental autonomous vehicle platform that belongs to AutonomouStuff Solutions~\footnote{\url{https://autonomoustuff.com/}}.
 By creating these software models, the company can run tests using them without needing the physical vehicle.
 As a result, these models could potentially allow the company to get more testing done.
-
-The first subsystem we will model is the steering model, and then we will move onto
+%
+The first subsystem we shall model is the steering model, and then we will move onto
 the other subsystems. There are already controllers in place for the Lexus
@@
 Once there is confidence in each model, these models can be used on the   HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
-\section{Self-Driving Vehicle Overview}
+
+\section{Self-Driving Vehicle Subsystems}
 \label{sec:selfDrivingVehicleOverview}
-In this section, we present an overview of the self-driving vehicle pertaining to the hardware-in-the-loop modeling process conducted in the work.
 
-There are two operating modes of the Lexus vehicle platform used in this project: %
+In this section, we illustrate subsystems of the self-driving vehicle highlighting  the hardware-in-the-loop modeling process conducted in the work. %
+As mentioned, we focus on  six  main subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
+Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus self-driving vehicle provided by the company, Hexagon $|$ AutonomouStuff (www.autonomoustuff.com).
 %
-\begin{itemize}
-  \item Manual-drive and
-  \item by-wire or autonomous.
-\end{itemize}
 %
-Manual-drive operation occurs when the driver has complete control over the vehicle, including controlling the steering, speed, acceleration, and braking of the vehicle.
-Autonomous operation occurs where the vehicle is controlled by a computer under driver supervision.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
+  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
+  \label{fig:highLevelSystemArchitecture}
+\end{figure}
 %
-Fig.~\ref{fig:steerOverview} depicts how the by-wire mode controls the vehicle. Each
-subsystem, like the steering system in this example, sends torque voltages to a
-motor that will control the subsystem. %
+However, actual self-driving vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
+A team of the project members visited the site to collect raw data for modeling  steering, brake, and acceleration subsystems of the vehicle.
+%
+%
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
+	\caption{AutonomouStuff Lexus RX450H vehicle.}
+	\label{fig:lexusvehicle}
+\end{figure}
+%
+
+Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
+For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus can not be treated as a single input.
+Also, each subsystem will be treated as a single output system.
+The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based on the other output's behavior.
+In the following we give a brief description of each of the subsystems of the self-driving vehicle modeled in this work.
+Each subsystem sends torque voltages to a motor that will control the subsystem.
+
+\subsection{Steering Subsystem}
+\label{sec:steeringSubsystem}
+
+The steering subsystem of a generic self-driving vehicle consists of the steering arm, knuckle, rods, drag link, steering gear box, drop arm, cross shaft, steering column, steering shaft, and steering wheel~\footnote{\url{https://www.theengineerspost.com/car-steering-system-in-automobile/}}.
+Fig.~\ref{fig:steerOverview} depicts steering subsystems in the by-wire (autonomous) mode.
+%
 %
@@
 
-\vspace*{12pt}
+The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading.
+Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction.
+The block diagram of the control system designed for this subsystem is shown in Fig.~\ref{fig:steeringModelBlockDiagram}, where the target and the actual orientations of the vehicle are denoted by $\theta^{\text{ref}}$ and $\theta(t)$ at time $t\ge 0,$ respectively.
+%
+%
+\begin{figure}[htbp]
+  \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
+    \tikzstyle{sum} = [draw, circle,fill=orange!15]
+    % place nodes
+    \node[sum](sum){$\sum$};
+    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
+    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
+    \draw[-stealth,thick]
+    (sum.east)--node[midway,above]{Error}(steeringController);
+    \draw[-stealth,thick]
+    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
+    \draw[-stealth,thick]
+    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
+    \draw[-stealth,thick]
+    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
+    \fill
+    (tt) circle [radius=2pt];
+    \draw[-stealth,thick]
+    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};
+  \end{tikzpicture}
+  % \captionsetup{justification=centering, margin=3cm}
+  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
+  \caption{Steering subsystem block diagram.}
+  \label{fig:steeringModelBlockDiagram}
+\end{figure}
+%
+The torque voltages applied to the power steering motor are denoted by $v_{A}$ and $v_{B},$ respectively.
+The error signal, which is the difference between the target and the actual directions of the vehicle, is passed on to the steering controller.
+The outputs of the steering controller are the torque voltages that are applied to the power steering motors of the steering subsystems of the vehicle.
+
+  \subsection{Brake Subsystem}
+  The brake subsystem is made up of the master cylinder, brake rotor, brake drum, brake pad, brake caliper, brake shoe, brake booster, brake pedal, wheel speed sensors, ABS module, and brake lines~\footnote{\url{https://oards.com/car-brake-system-components/}}.
+A high-level block diagrams showing the inputs and outputs of a conventional brake subsystem of a self-driving vehicle is shown in Fig.~\ref{fig:brakeModelArchitecture}.
+%
+%
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
+    \draw[stealth-,thick]
+    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(1.7,0);
+    \draw[-stealth,thick]
+    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Brake subsystem block diagram}
+    \label{fig:brakeModelArchitecture}
+\end{figure}
+%
+The subsystem takes the brake pedal pressure voltages, brake pedal stroke voltages, and the brake pedal on/off switch values as inputs.
+Using these values, it generates a new brake pedal position (in percentage) and a boolean value called brake pressed.
+This boolean value indicates to the user whether or not the brake pedal is being pressed.
+
+\subsection{Acceleration Subsystem}
+
+  The acceleration subsystem consists of the throttle pedal, engine, and crankshaft~\footnote{\url{https://harrisautomotiverepair.com/car-accelerator/}}.
+It is a multiple-input multiple-output system, whose block diagram is depicted in Fig.~\ref{fig:accelModelArchitecture}.
+Taking the acceleration pedal voltages as the input, the subsystem then produces the acceleration pedal position as the output. The output represents how much the pedal is pressed as a percentage. %
+%of the acceleration subsystem. %
+%
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
+    % Connections
+    \draw[stealth-,thick]
+    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.0,0);
+    \draw[-stealth,thick]
+    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.0,0);
+  \end{tikzpicture}
+    \caption{Acceleration subsystem block diagram}
+    \label{fig:accelModelArchitecture}
+ \end{figure}
+% %
+%\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
+  \subsection{Shift Subsystem}
+ The components that make up the shift subsystem are the friction clutch, bands, spring loaded valve, load sensor, shift valve, torque converter, gear stick, seals, and gasket~\footnote{\url{https://oards.com/car-automatic-transmission-system-components/}}.
+This subsystem can be classified as a single-input single-output system.
+A block diagram of the shift subsystem is seen in Fig.~\ref{fig:shiftModelArchitecture}.
+The subsystem takes the desired shifter gear value from the user as the input.
+Within the subsystem, the actual shifter gear is changed to better reflect the desired gear.
+This actual shifter gear value is then the output of the shift subsystem.
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
+    \draw[-stealth,thick]
+    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Shift subsystem block diagram}
+    \label{fig:shiftModelArchitecture}
+ \end{figure}
+
+ %
+% \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
+  \subsection{Speed Subsystem}
+This speed subsystem would fall under the multiple-input single-output system.
+A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}.
+The subsystem has four inputs, the acceleration pedal position, brake pedal position, and shifter gear.
+Using these inputs, the speed subsystem finds the vehicle speed.
+This vehicle speed is then the output of the system.
+
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
+    % place nodes
+    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
+    \draw[stealth-,thick]
+    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
+
+  \end{tikzpicture}
+    % \captionsetup{justification=centering, margin=3cm}
+    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+    \caption{Speed subsystem block diagram}
+    \label{fig:speedModelArchitecture}
+\end{figure}
+%
+%\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
+
+  \subsection{Speed Control Subsystem}
+  The speed control subsystem components include the cruise control switch, vehicle speed sensor, throttle sensor, and brake switch~\footnote{\url{https://www.freeasestudyguides.com/electrical-cruise-control-systems.html}}.
+This subsystem is a straightforward single-input single-output system, shown in Fig.~\ref{fig:speedControlModelArchitecture}.
+The Desired Vehicle Speed input is set by the user and sent to the speed control subsystem.
+Taking this input, the subsystem calculates the Actual Vehicle Speed.
+This value is then sent out to the rest of the vehicle system.
+ \begin{figure}[htbp]
+    \centering
+  \begin{tikzpicture}
+    \tikzstyle{every node} = [font=\footnotesize]
+    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+    % place nodes
+    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+
+    % Connections
+    \draw[stealth-,thick]
+    (speedControlSubsystem.180)--node[very near end,above]{Desired Vehicle Speed}++(-1.9,0);
+    \draw[-stealth,thick]
+    (speedControlSubsystem.0)--node[very near end,above]{Actual Vehicle Speed}++(1.9,0);
+
+  \end{tikzpicture}
+    \caption{Speed Control subsystem block diagram}
+    \label{fig:speedControlModelArchitecture}
+ \end{figure}
+ %
+% % \todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
+Use the same format for explaining all the subsystems.
+You cannot just place a figure without referring and explaining the figure in the text.}
+
+\section{Modeling Vehicle Subsystems}
+
+To start the modeling process, we first collected raw data of the subsystems illustrated in the previous section.
+The input-output data are then used to model different subsystems of the self-driving vehicle using deep learning toolbox available in a commercial modeling software SIMULINK\footnote{\url{https://www.mathworks.com/products/simulink.html}}.
+To demonstrate the modeling accuracy, to evaluate the effectiveness of our models, and to develop safe and reliable controllers for each subsystem, the following system requirements are to be met:
+
+\begin{itemize}
+\item Each vehicle subsystem will be able to track nonlinearities depicted in Fig.~\ref{fig:nonlinGraph} associated with small changes in the output of each subsystem. %
+  %
+  \begin{figure}[htbp]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
+    \caption{Nonlinear behavior of steering subsystem.}
+    \label{fig:nonlinGraph}
+  \end{figure}
+
+\item Each vehicle subsystem plant model will track any desired inputs within the specified error bounds\add{:}
+	\begin{itemize}
+		\item Steering angle within 5 degrees
+		\item Pedal positions within 5\%
+	\end{itemize}
+\item Each vehicle subsystem will be modeled independently from other vehicle subsystems
+\end{itemize}
+%
+The vehicle plant models will satisfy the requirements listed below:
+\begin{itemize}
+    \item The resulting plant model will consist of accurate subsystem models, as defined above
+    \item The subsystems can be used to create a hardware-in-the-loop (HIL) testbench
+    \item The subsystems can handle very small changes in their output accurately
+\end{itemize}
+%
+
+All of the subsystems have nonlinear behaviors when there are small changes in the output of the subsystem.
+The steering subsystem, for example, should behave in a smooth, continuous manner.
+However, a team of researchers from AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
+The plant models developed in this work will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
+
+\subsection{Steering System Modeling}
+To develop a model of the steering system, we employed multiple methods.
+The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB.
+The NARX model we developed was not accurate and did not track the output of the steering system data.
+The transfer function model we developed was more reliable tracking the output of the steering system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
+Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
+With the neural network model, the model was able to reliably and accurately track the output of the steering system data and stayed within the error requirements.
+
+\subsection{Acceleration System Modeling}
+To develop a model of the acceleration system, we employed multiple methods.
+The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB.
+The NARX model we developed was accurate for the by-wire model and tracked the output of the acceleration system data, but did not meet the error requirements.
+The transfer function model we developed was more reliable tracking the output of the acceleration system data for the manual mode operation, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
+Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
+With the neural network model, the model was able to reliably and accurately track the output of the acceleration system data and stayed within the error requirements.
+
+\subsection{Brake System Modeling}
+To create a brake system model, we first tried generating transfer function models using MATLAB’s System Identification Toolbox.
+After generating multiple transfer function models and trying many different data log combinations, we still couldn’t find a model that was completely accurate across all combinations and that was below the error bound of 5\% for all combinations.
+Once this became clear Neural Network models were created using the Neural Network Time Series Toolbox provided by MATLAB to see if they could create accurate brake models.
+Using this we were able to create a model that accurately tracked the data we collected from the brake system and that stayed within the 5\% error bound.
+
+\section{Validation and Testing} \label{sec:simresults}
+
+\subsection{Experimental Setup}
+\label{sec:experimentalSetup}
+
+We visited the workplace of AutonomouStuff in order to collect
+data from the steering, acceleration, and braking subsystems in an autonomous
+vehicle. The data we collected will be used to generate and then verify our
+models. We collected data on the Lexus RX450H vehicle platform shown in
+Fig.~\ref{fig:lexusvehicle}. %
+The following  the hardware components required to collect the data:
+	\begin{itemize}
+    		\item Laptop
+    		\item PACMod ECU
+    		\item CANCase
+    		\item CAN bus
+ 	\end{itemize}
+  %
+The interfacing software, Vector CANAlyzer, installed in the laptop is used to pass commands or log data, such as steering angle or acceleration or brake pedal position.
+This data is sent or received using the CANCase and CAN bus.
+These are connected to the AutonomouStuff designed PACMod ECU, which sends torque voltages to the desired vehicle subsystem allowing the laptop to either control the desired vehicle system or log data.
+The Vector CANAlyzer software is installed on the laptop and is used to parse the collected data that is sent from the CANCase.
+This is how we were able to collect logs of data that we would use to develop plant models of the autonomous vehicle subsystems.
+
+Each subsystem that we are modeling is set up in a similar manner.
+In manual mode, the torque voltages that control each subsystem are sent by the vehicle's electronic control unit (ECU).
+In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode.
+In by-wire mode, the torque voltages from the vehicle's ECU are discarded by open-circuiting the motors that control each subsystem.
+Instead, the PACMod ECU built by AutonomouStuff sends the torque voltages to the motor using relays.
+In Fig.~\ref{fig:vehicleSetup}, the experimental setup for data collection is shown.
+%
+%
+\begin{figure}[htbp]
+	\centering
+  % \captionsetup{justification=centering, margin=3cm}
+  \includegraphics[width=.48\textwidth]{figs/img/picturesVisitToAStuff/dataColletionSetup1-20211007}
+  \caption{Setup for collecting data in the Lexus RX450H self-driving vehicle.}
+  \label{fig:vehicleSetup}
+\end{figure}
+%
+The laptop is used to collect the data from the desired vehicle subsystem by the use of Vector's CANAlyzer software.
+The CAN Case collects data from the PAC Mod and ECU and sends the data using a CAN bus to the laptop which is then parsed and displayed through the use of CANAlyzer.
+The ECU and PAC Mod are not shown in Fig.~\ref{fig:vehicleSetup} as they are fixed behind panels of the vehicle.
+%
+
+Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually.
+This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in.
+After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models.
+When the vehicle subsystem is in by-wire mode, the controller generates the torque voltages that are applied to each subsystem motor.
+As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode.
+% For reference, the differences in the models created for by-wire and manual mode are depicted in Section \ref{subsec:SteeringTF} and \ref{subsec:AccelTF} for the steering and acceleration subsystems.
+For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
+
+To develop the model of the steering, acceleration, and brake subsystems using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked.
+The neural network model used a feedforward network that had one hidden layer containing three neurons.
+The model was also trained with twelve delay units to achieve the required accuracy, meaning that the first twelve output samples of the model should be ignored.
+\subsection{Neural Network Modeling}
+\label{sec:NN-Modeling}
+
+\subsubsection{Steering System}
+%
+In Fig.~\ref{fig:InitialSteeringModel}, the top plot shows the simulated output of the neural network when the input torque voltages and desired steering angle from a subset of data (subset~\#1) collected offline is fed into the model.
+The bottom plot shows the error between the desired steering angle and the output of the neural network.
+For the steering model, the error should be less than 5 degrees or approximately 0.1 radians.
+%Fig.~\ref{testedSteeringModel} shows the same plots except data subset 2 was used instead.
+%
+%
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}
+  \caption{Steering model performance in tracking desired steering angle and the error based on the data (subset 1).}
+  \label{fig:InitialSteeringModel}
+\end{figure}
+%
+% \begin{figure}[htbp]
+% 	\centering
+% 	\subcaptionbox{. \label{initalSteeringModel}}
+% 		{}
+% 	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedSteeringModel}}
+% 		{\includegraphics[width=0.90\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
+% 	\caption{Steering System Training Plots}
+% \end{figure}
+
+\subsubsection{Acceleration System}
+%
+In Fig.~\ref{initalAccelModel}, the top plot shows the simulated output of the neural network when the input torque voltages and desired acceleration pedal position from data subset 1 are fed into the model.
+The bottom plot shows the error between the acceleration pedal position and the output of the neural network.
+For the acceleration model, the error should be less than 5\% or 0.05.
+Fig.~\ref{testedAccelModel} shows the same plots except data subset 2 was used instead.
+
+\begin{figure}[htbp]
+	\centering
+	\subcaptionbox{Model output tracking and Error Plots for Data Subset 1 \label{initalAccelModel}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Data Subset 2 \label{testedAccelModel}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
+	\caption{Acceleration System Training Plots}
+\end{figure}
+
+\subsubsection{Brake System}
+
+The brake system was modeled using only the manual log data.
+It was trained using the data from the first brake log, and the result and error plots can be seen in Fig.~\ref{initalBrakeModel}.
+The plots show that the model is able to predict the outputs relatively accurately, along with keeping the error below 5\%.
+In order to further verify the accuracy of the model, it was tested using data from the second brake log.
+The results from that test, shown in Fig.~\ref{testedBrakeModel}, also show that the model can accurately predict the output values and do this within the accepted error bound of 5\%.
+The graphs show how the model tracks the data log and the error between the model output and the data log output.
+The y-axis for both graphs, “Output and Target” represents the Actual and Desired Brake Pedal Position as a percentage.
+The x-axis for both graphs represents the Time Steps, with $T_s$ equal to 33ms.
+
+\begin{figure}[h]
+	\centering
+	\subcaptionbox{Model Output Tracking and Error Plots \label{initalBrakeModel}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/brake_new_neuralNetworkFig}}
+	\subcaptionbox{Model Output Tracking and Error Plots for Log Two Data \label{testedBrakeModel}}
+		{\includegraphics[width=0.90\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
+	\caption{Brake System Training Plots}
+\end{figure}
+
+% The second test used constant blocks and To Workspace blocks to represent the voltages and desired pedal position in the first brake log.
+The results from this test also showed that the model was able to accurately track the data.
+
+\subsection{Discussion}
+\label{sec:discussion}
+
+For each vehicle subsystem, the results show that the neural network models were the most accurate models.
+Other models that we developed, such as the transfer function models, were relatively accurate when tracking the data, but those models were consistently falling outside of the error bounds that were defined at the start of the project.
+The neural network models, however, track the data more accurately and reduced the error significantly so that all error requirements were met.
+We first proved that the neural network models that we developed were accurate using subsets of data as inputs to a Simulink model.
+Then we visited AutonomouStuff to generate the models on their HIL bench, as shown in Fig.~\ref{fig:hilBench}, using Control Desk to interface.
+Due to time constraints, AutonomouStuff was not able to get the proper hardware for this project connected to the HIL bench but we were able to test our models in an open-loop configuration and measure outputs to show that the correct voltages would be fed to any hardware that would be connected, shown in Fig.~\ref{fig:hilMeasuring}.
+One downside to using neural networks as the plant model is it causes some complexities when trying to include these models into the HIL bench software for use in developing and testing controllers.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.48\linewidth}
+		\centering
+    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
+    		\caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\linewidth}
+		\centering
+    		\includegraphics[angle=270,width=0.9\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
+    		\caption{}
+    \end{subfigure}
+    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}}
+    %\subfigure[b]{\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}}
+    \caption{Verifying voltage measurements on the HIL bench.}
+    \label{fig:hilMeasuring}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.95\linewidth]{figs/inkscape/hilBenchAstuffAnnotatedNew}
+  \caption{AutonomouStuff HIL bench configuration}
+  \label{fig:hilBench}
+\end{figure}
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.95\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
+%	\caption{AutonomouStuff HIL Bench Configuration}
+%	\label{fig:hilBench}
+%\end{figure}
 
@@
 \label{sec:conclustionAndFutureWork}
-Our initial approach was to model the subsystems using the System Identification Toolbox from MATLAB, but it produced unsatisfactory results.
-Switching to the Neural Network Time Series app allowed us to train models using the data we collected.
+
+In this paper, we presented the effectiveness of the data-driven hardware-in-the-loop plant modeling process using deep learning.
+The neural network time series modeling method  allowed us to train models using the data we collected.
 These models that were developed met the predefined accuracy requirements, and so were tested using an open loop setup.
-In the future if AutonomouStuff would like to model other vehicle subsystems, we would recommend modeling them using Neural Networks.
-Creating the Neural Networks and exporting the models to Simulink was easy to do and produced accurate results.
-
-For this project, further testing should be completed for these subsystem models.
-Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop, this would be a good place to start.
+For the conciseness, we  presented HIL plant modeling for three subsystems, which are steering, brake, and acceleration subsystems of the Lexus vehicle available at AutonomouStuff (the company who sponsored the project).
+Further testing should be completed for these subsystem models.
+Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop.
 Further testing is important to make sure the developed models are accurate and compatible with testing using hardware.
-Depending on what AutonomouStuff decides, future engineers working on this project could start developing controllers based off of these models.
-Currently, AutonomouStuff develops their own controllers for their vehicle subsystems, but they could allow students to design some as part of this senior project.
+Future work  could be to start developing controllers based off of these models.
 

### 2022-08-22 paperIEEE-ROSE2022.tex
Paper submitted to IEEE ROSE2022 conference

@@
 The vehicle subsystems considered in this work steering, acceleration, brake, shift, speed, and speed control.
+Each of these subsystems is either multi-input single output or single-input single output system.
+Lexus RX450H self-driving vehicle is employed to collect raw data (inputs and outputs data for different subsystems) offline.
+We used deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems.
+Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle.
+As such, the proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing.
 However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose.
@@
 As it is apparent, each self-driving vehicle is composed of varaious subsystems that researchers of autonomous vehicle community analyze, design, develop, and test.
-Intuitively, self-driving vehcles require thorough testing at the factory level before their demonstrations for  the commerical purpose.
+Intuitively, self-driving vehicles require thorough testing at the factory level before their demonstrations for  the commercial purpose.
 Such a testing procedure for each physical vehicle is inefficient and costly as it involves testing of different subsystems, such as steering, brake, shift, to name a few, of a vehicle.
@@
 This subsystem can be classified as a single-input single-output system.
-A block diagram of the shift subsystem is seen in Fig.~\ref{fig:shiftModelArchitecture}.
+%
+%
+  % A block diagram of the shift subsystem is seen in Fig.~\ref{fig:shiftModelArchitecture}.
   The subsystem takes the desired shifter gear value from the user as the input.
@@
 This actual shifter gear value is then the output of the shift subsystem.
- \begin{figure}[htbp]
-    \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
+ % \begin{figure}[htbp]
+ %    \centering
+ %  \begin{tikzpicture}
+ %    \tikzstyle{every node} = [font=\footnotesize]
+ %    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+ %    % place nodes
+ %    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
 
-    % Connections
-    \draw[stealth-,thick]
-    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
-    \draw[-stealth,thick]
-    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
+ %    % Connections
+ %    \draw[stealth-,thick]
+ %    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
+ %    \draw[-stealth,thick]
+ %    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);
 
-  \end{tikzpicture}
-    \caption{Shift subsystem block diagram}
-    \label{fig:shiftModelArchitecture}
- \end{figure}
+ %  \end{tikzpicture}
+ %    \caption{Shift subsystem block diagram}
+ %    \label{fig:shiftModelArchitecture}
+ % \end{figure}
 
@@
   \subsection{Speed Subsystem}
-This speed subsystem would fall under the multiple-input single-output system.
-A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}.
+  This speed subsystem would fall under the multiple-input single-output system. %A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}. %
   The subsystem has four inputs, the acceleration pedal position, brake pedal position, and shifter gear.
@@
 
- \begin{figure}[htbp]
-    \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
-    % place nodes
-    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
+%  \begin{figure}[htbp]
+%     \centering
+%   \begin{tikzpicture}
+%     \tikzstyle{every node} = [font=\footnotesize]
+%     \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
+%     % place nodes
+%     \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
 
-    % Connections
-    \draw[stealth-,thick]
-    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
-    \draw[stealth-,thick]
-    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
-    \draw[-stealth,thick]
-    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
+%     % Connections
+%     \draw[stealth-,thick]
+%     (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
+%     \draw[stealth-,thick]
+%     (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
+%     \draw[stealth-,thick]
+%     (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
+%     \draw[-stealth,thick]
+%     (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);
 
-  \end{tikzpicture}
-    % \captionsetup{justification=centering, margin=3cm}
-    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
-    \caption{Speed subsystem block diagram}
-    \label{fig:speedModelArchitecture}
-\end{figure}
-%
+%   \end{tikzpicture}
+%     % \captionsetup{justification=centering, margin=3cm}
+%     % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
+%     \caption{Speed subsystem block diagram}
+%     \label{fig:speedModelArchitecture}
+% \end{figure}
+% %
 %\todo[inline]{Please see how I described block diagrams for steering, and brake subsystems.
@@
   The speed control subsystem components include the cruise control switch, vehicle speed sensor, throttle sensor, and brake switch~\footnote{\url{https://www.freeasestudyguides.com/electrical-cruise-control-systems.html}}.
-This subsystem is a straightforward single-input single-output system, shown in Fig.~\ref{fig:speedControlModelArchitecture}.
+%This subsystem is a straightforward single-input single-output system, shown in Fig.~\ref{fig:speedControlModelArchitecture}.
+%
   The Desired Vehicle Speed input is set by the user and sent to the speed control subsystem.
@@
 This value is then sent out to the rest of the vehicle system.
- \begin{figure}[htbp]
-    \centering
-  \begin{tikzpicture}
-    \tikzstyle{every node} = [font=\footnotesize]
-    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
-    % place nodes
-    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
+ % \begin{figure}[htbp]
+ %    \centering
+ %  \begin{tikzpicture}
+ %    \tikzstyle{every node} = [font=\footnotesize]
+ %    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
+ %    % place nodes
+ %    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
 
-    % Connections
-    \draw[stealth-,thick]
-    (speedControlSubsystem.180)--node[very near end,above]{Desired Vehicle Speed}++(-1.9,0);
-    \draw[-stealth,thick]
-    (speedControlSubsystem.0)--node[very near end,above]{Actual Vehicle Speed}++(1.9,0);
+ %    % Connections
+ %    \draw[stealth-,thick]
+ %    (speedControlSubsystem.180)--node[very near end,above]{Desired Vehicle Speed}++(-1.9,0);
+ %    \draw[-stealth,thick]
+ %    (speedControlSubsystem.0)--node[very near end,above]{Actual Vehicle Speed}++(1.9,0);
 
-  \end{tikzpicture}
-    \caption{Speed Control subsystem block diagram}
-    \label{fig:speedControlModelArchitecture}
- \end{figure}
+ %  \end{tikzpicture}
+ %    \caption{Speed Control subsystem block diagram}
+ %    \label{fig:speedControlModelArchitecture}
+ % \end{figure}
  %
@@
 \begin{itemize}
-\item Each vehicle subsystem will be able to track nonlinearities depicted in Fig.~\ref{fig:nonlinGraph} associated with small changes in the output of each subsystem. %
+  \item Each vehicle subsystem will be able to track nonlinearities %depicted in Fig.~\ref{fig:nonlinGraph} %
+        associated with small changes in the output of each subsystem. %
   %
-  \begin{figure}[htbp]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
-    \caption{Nonlinear behavior of steering subsystem.}
-    \label{fig:nonlinGraph}
-  \end{figure}
+  % \begin{figure}[htbp]
+  %   \centering
+  %   \captionsetup{justification=centering}
+  %   \includegraphics[width=2.5in]{figs/inkscape/nonlinearBehavior}
+  %   \caption{Nonlinear behavior of steering subsystem.}
+  %   \label{fig:nonlinGraph}
+  % \end{figure}
 
@@
 However, a team of researchers from AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
-This behavior, depicted in Fig.~\ref{fig:nonlinGraph}, made it very challenging to complete features like lane tracking.
+This behavior %, depicted in Fig.~\ref{fig:nonlinGraph}, %
+made it very challenging to complete features like lane tracking.
 The plant models developed in this work will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
@@
 		{\includegraphics[width=0.90\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
-	\caption{Brake System Training Plots}
+	\caption{Performance of the brake system modeling.}
 \end{figure}
@@
 
+\clearpage
 \bibliographystyle{IEEEtran}

### 2022-10-05 paperIEEE-ROSE2022-Pres.tex
Uploaded presentation  paperIEEE-ROSE2022-Pres.tex

--- 2022-04-20 finalReportPres.tex
@@
 %==============================================================================
-\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}
+\title[HIL Plant Modeling]{Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles}
 
-\author[H.~Grady, N.~Nauman]{Hannah~Grady and Nicholas~Nauman 
-\linebreak Advisor:~Dr.~Suruz~Miah}
+\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
 % - Give the names in the same order as the appear in the paper.
@@
   \inst{~}Department of Electrical and Computer Engineering\\
-  Bradley University\\
-  1501 W. Bradley Avenue\\
-  Peoria, IL, 61625, USA
+  Bradley University, Peoria, Illinois, 61625, USA
   \and
@@
 % - Keep it simple, no one is interested in your street address.
+%
 
-\date[April~21,~2022]{Thursday, April~21,~2022}
+\date[IEEE ROSE,~2022]{IEEE International Symposium on Robotics and Sensors Environments $|$ Nov. 14-15,~2022 $|$ Hybrid $|$ Khalifa University, Abu Dhabi UAE}
 
@@
 \begin{figure}[H]
-  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeNeuralNetworkDetailedSystem}\quad%
+  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock}\quad%
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
@@
     \begin{itemize}
+    	  \item Model shift, speed, and speed control subsystems
       \item Test models using Hardware-in-the-Loop

### 2022-10-05 paperIEEE-ROSE2022.tex
IEEE ROSE Presentation and Paper Work
I made some slight changes to the presentation and added to the paper abstract

@@
   In this paper, we present data-driven hardware-in-the-loop (HIL) plant models of different subsystems of a self-driving vehicle.
-Despite numerous concerns, automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market.
+Despite numerous concerns, the automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market.
 Among numerous challenges in the development process of such vehicles are the validation and testing process of various subsystems.
 Here we provide data-driven models of different subsystems so that automotive industries can validate and test autonomous vehicles without the need of a physical vehicle, which indeed reduces the considerable amount of cost for automotive industries.
-The vehicle subsystems considered in this work steering, acceleration, brake, shift, speed, and speed control.
-Each of these subsystems is either multi-input single output or single-input single output system.
-Lexus RX450H self-driving vehicle is employed to collect raw data (inputs and outputs data for different subsystems) offline.
-We used deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems.
+The vehicle subsystems considered in this work include steering, acceleration, brake, shift, speed, and speed control subsystems.
+Each of these subsystems is either a multi-input single output or single-input single output system.
+A Lexus RX450H self-driving vehicle is employed to collect raw data (inputs and outputs data for different subsystems) offline.
+We used the deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems.
 Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle.
@@
 However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose.
+The contribution of this project is twofold.
+The first part is that we were able to take real time raw data collected from a Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems.
+The second portion of our contribution is that we took the models that we created and tested them using Hardware-in-the-Loop.
 

### 2022-10-06 paperIEEE-ROSE2022.tex
Modified the contrb. statements in the abstract

@@
 We used the deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems.
+The contribution of this paper is twofold.
+First, collecting real time raw data from a physical Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems.
+Second, subsystem models created using machine learning tools for the Lexus vehicle are tested using Hardware-in-the-Loop.
 Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle.
-As such, the proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing.
+The proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing.
 However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose.
-The contribution of this project is twofold.
-The first part is that we were able to take real time raw data collected from a Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems.
-The second portion of our contribution is that we took the models that we created and tested them using Hardware-in-the-Loop.
+.
 

### 2022-10-10 paperIEEE-ROSE2022.tex
Paper and presentation push

@@
   In this paper, we present data-driven hardware-in-the-loop (HIL) plant models of different subsystems of a self-driving vehicle.
-Despite numerous concerns, the automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market.
-Among numerous challenges in the development process of such vehicles are the validation and testing process of various subsystems.
-Here we provide data-driven models of different subsystems so that automotive industries can validate and test autonomous vehicles without the need of a physical vehicle, which indeed reduces the considerable amount of cost for automotive industries.
-The vehicle subsystems considered in this work include steering, acceleration, brake, shift, speed, and speed control subsystems.
+Despite numerous concerns, the automotive industry is still investing remarkable resources into the production of self-driving vehicles.
+Among the challenges in the development process of such vehicles are the validation and testing process of various subsystems.
+Here we provide data-driven models of different subsystems so that the  automotive industry can validate and test autonomous vehicles without the need of a physical vehicle, which would reduce the considerable amount of cost to the automotive industry.
+The vehicle subsystems considered in this work include the steering, acceleration, brake, shift, speed, and speed control subsystems.
 Each of these subsystems is either a multi-input single output or single-input single output system.
@@
 The contribution of this paper is twofold.
-First, collecting real time raw data from a physical Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems.
+First, collecting real time raw data from a physical Lexus RX450H vehicle and using it to develop machine learning models to represent the vehicle subsystems.
 Second, subsystem models created using machine learning tools for the Lexus vehicle are tested using Hardware-in-the-Loop.
-Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle.
-The proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing.
-However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose.
-.
+Therefore, the results of such modeling could be used for validation and testing without the need for a physical self-driving vehicle.
+The proposed modeling results could be useful for reducing the cost of the vehicle development process, since a physical vehicle is not required for validation and testing.
+
+  %However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose. .
 
@@
 
-Due to escalating demand of self-driving vehicles, automotive industry is gradually shifting its attention in  manufacturing a variety of autonomous vehicles.
-The advancement of new technologies led the automotive industry to develop such vehicles for commercial and personal use as they mainly aim to reduce crashes, energy consumption, pollution, and congestion.
-However, the development of process of autonomous vehicles still faces signifant challenges to overcome.
-As it is apparent, each self-driving vehicle is composed of varaious subsystems that researchers of autonomous vehicle community analyze, design, develop, and test.
-Intuitively, self-driving vehicles require thorough testing at the factory level before their demonstrations for  the commercial purpose.
-Such a testing procedure for each physical vehicle is inefficient and costly as it involves testing of different subsystems, such as steering, brake, shift, to name a few, of a vehicle.
+Due to the escalating demand for self-driving vehicles, the automotive industry is gradually shifting its attention toward manufacturing a variety of autonomous vehicles.
+The advancement of new technologies has led the automotive industry to develop such vehicles for commercial and personal use, with the aim to reduce crashes, energy consumption, pollution and congestion.
+However, the development process for autonomous vehicles still faces significant challenges.
+Each self-driving vehicle is composed of various subsystems that researchers of the autonomous vehicle community analyze, design, develop, and test.
+Intuitively, self-driving vehicles require thorough testing at the factory level before they can be used by the public.
+Such a testing procedure for each physical vehicle is inefficient and costly, as it involves the testing of different vehicle subsystems, such as the steering, brake and shift subsystems.
 In this work, we model different modules/subsystems of a self-driving vehicle using machine learning techniques, where a physical self-driving vehicle is not required for testing.
 
-Note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for autonomous vehicles to be managed in the era of modern transportation systems in general.
+Note that modeling vehicle subsystems is a pre-requisite for the development of reliable controllers for autonomous vehicles to be managed in the era of modern transportation systems.
 In particular, this work models different subsystems for a self-driving vehicle of the vehicle fleet shown in Fig.~\ref{fig:fleet}.
@@
 %
-Such modeling process would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. %
+%Such modeling process would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. %
 %
@@
 Autonomous vehicles have the ability to make roads safer for drivers
-and pedestrians alike. To develop a reliable and safe transportation system for
-modern world, a large body of research in the field of autonomous vehicles is
-being conducted in recent decades~\cite{Liu2017,Prasad2020}.
-In fact, the research on this topic has been conducted from a variety of perspectives, such as the application of connected and autonomous vehicle technology~\cite{DoT2017}, navigation and path control of self-driving vehicles~\cite{Duong2018,Chajan2021}.
-Authors in~\cite{Saruchi2015} worked on active front steering for steer-by-wire vehicle.
-Steering system of high speed intelligent vehicles has been modeled using system identification~\cite{Li1999}.
-Therefore, it is clear that numerous research pertainting to self-driving vehicles has been pursued, especially, in the past two decades.
+and pedestrians alike. To develop a reliable and safe transportation system for the 
+modern world, a large body of research in the field of autonomous vehicles has
+been generated~\cite{Liu2017,Prasad2020}.
+In fact, the research on this topic has been conducted from a variety of perspectives, such as the application of connected and autonomous vehicle technology~\cite{DoT2017}, and the navigation and path control of self-driving vehicles~\cite{Duong2018,Chajan2021}.
+Authors in~\cite{Saruchi2015} worked on active front steering for a steer-by-wire vehicle.
+The steering system of high speed intelligent vehicles has been modeled using system identification~\cite{Li1999}.
+Therefore, it is clear that a large amount of research pertaining to self-driving vehicles has been pursued, especially in the past two decades.
 There are two operating modes considered for the autonomous vehicle employed in this work: %
@@
 %
-Manual-drive operation occurs when the driver has complete control over the vehicle, including controlling the steering, speed, acceleration, and braking of the vehicle.
-Autonomous operation occurs where the vehicle is controlled by a computer under driver supervision.
+Manual-drive operation occurs when the driver has complete control over the vehicle; including controlling the steering, speed, acceleration and braking of the vehicle.
+Autonomous operation occurs when the vehicle is controlled by a computer under driver supervision.
 %
@@
 %
-These subsystems are to be modeled to get an accurate representation of how
+These subsystems are modeled in order to get an accurate representation of how
 the vehicle is to be controlled. %
@@
 %\comment{reliability}{Need to define what do you mean by reliability, be very specific}
-is lower than expected due to non-linear
+is lower than expected due to the non-linear
 behaviors of the torque voltages required to control each subsystem. The scope
@@
 These models will be considered reliable if they can track actual vehicle subsystem behaviors with a minimum best fit percentage between 85 to 95 percent and fall within the error bounds defined for each subsystem.
-Once these models are developed, they will be tested using Hardware-in-the-Loop (HIL) bench.
+Once these models are developed, they will be tested using a Hardware-in-the-Loop (HIL) bench.
 Once there is confidence in each model, these models can be used on the HIL bench to develop controllers that will remove the non-linear behaviors of each vehicle subsystem.
@@
 
-In this section, we illustrate subsystems of the self-driving vehicle highlighting  the hardware-in-the-loop modeling process conducted in the work. %
+In this section, we illustrate subsystems of the self-driving vehicle; highlighting the hardware-in-the-loop modeling process conducted in the work. %
 As mentioned, we focus on  six  main subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems.
-Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus self-driving vehicle provided by the company, Hexagon $|$ AutonomouStuff (www.autonomoustuff.com).
+Fig.~\ref{fig:highLevelSystemArchitecture} outlines these six subsystems in a Lexus vehicle similar to the one provided by the company, Hexagon $|$ AutonomouStuff (www.autonomoustuff.com).
 %
@@
 %
-However, actual self-driving vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
-A team of the project members visited the site to collect raw data for modeling  steering, brake, and acceleration subsystems of the vehicle.
+However, the actual self-driving vehicle (Lexus RX450H) that is used for collecting input-output data for all of these subsystems is shown in the picture of Fig.~\ref{fig:lexusvehicle}.
+A team of the project members visited the site to collect raw data for modeling the steering, brake, and acceleration subsystems of the vehicle.
 %
@@
 Each of the six subsystems will be treated as a multiple-input single-output (MISO) system.
-For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus can not be treated as a single input.
-Also, each subsystem will be treated as a single output system.
-The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based on the other output's behavior.
-In the following we give a brief description of each of the subsystems of the self-driving vehicle modeled in this work.
+For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus cannot be treated as a single input.
+The brake subsystem is shown to have two outputs, but the behaviors of one of the outputs is already known, so it will be modeled based on the other output's behavior.
+In the following sections we give a brief description of each of the subsystems of the self-driving vehicle modeled in this work.
 Each subsystem sends torque voltages to a motor that will control the subsystem.
@@
 The torque voltages applied to the power steering motor are denoted by $v_{A}$ and $v_{B},$ respectively.
-The error signal, which is the difference between the target and the actual directions of the vehicle, is passed on to the steering controller.
+These voltages are taken from a torque sensor located on the vehicle's steering column.
+The error signal, which is the difference between the target and the actual steering angles of the vehicle, is passed on to the steering controller.
 The outputs of the steering controller are the torque voltages that are applied to the power steering motors of the steering subsystems of the vehicle.
@@
 The subsystem takes the brake pedal pressure voltages, brake pedal stroke voltages, and the brake pedal on/off switch values as inputs.
-Using these values, it generates a new brake pedal position (in percentage) and a boolean value called brake pressed.
+Using these values, it generates a new brake pedal position (as a percentage) and a boolean value called brake pressed.
 This boolean value indicates to the user whether or not the brake pedal is being pressed.
@@
 Within the subsystem, the actual shifter gear is changed to better reflect the desired gear.
-This actual shifter gear value is then the output of the shift subsystem.
+This actual shifter gear value is then the output of the subsystem.
  % \begin{figure}[htbp]
@@
   \subsection{Speed Subsystem}
-  This speed subsystem would fall under the multiple-input single-output system. %A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}. %
+  The speed subsystem would fall under the multiple-input single-output system category. %A block diagram representation can be found in Fig.~\ref{fig:speedModelArchitecture}. %
   The subsystem has four inputs, the acceleration pedal position, brake pedal position, and shifter gear.
@@
   The Desired Vehicle Speed input is set by the user and sent to the speed control subsystem.
-Taking this input, the subsystem calculates the Actual Vehicle Speed.
+Taking this input, the subsystem updates the Actual Vehicle Speed to better reflect the desired value.
 This value is then sent out to the rest of the vehicle system.
@@
 To start the modeling process, we first collected raw data of the subsystems illustrated in the previous section.
-The input-output data are then used to model different subsystems of the self-driving vehicle using deep learning toolbox available in a commercial modeling software SIMULINK\footnote{\url{https://www.mathworks.com/products/simulink.html}}.
+The input-output data were then used to model different subsystems of the self-driving vehicle using the deep learning toolbox available in the commercial modeling software SIMULINK\footnote{\url{https://www.mathworks.com/products/simulink.html}}.
 To demonstrate the modeling accuracy, to evaluate the effectiveness of our models, and to develop safe and reliable controllers for each subsystem, the following system requirements are to be met:
@@
 The steering subsystem, for example, should behave in a smooth, continuous manner.
-However, a team of researchers from AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform, that when small changes in the steering angle (less than five degrees) occurred, the torque voltages would momentarily stall and then suddenly change causing a more drastic change.
+However, a team of researchers from AutonomouStuff observed that when trying to implement features such as lane tracking for the Lexus vehicle platform,  the torque voltages would momentarily stall and then suddenly change when small changes in the steering angle (less than five degrees) occurred.
 This behavior %, depicted in Fig.~\ref{fig:nonlinGraph}, %
 made it very challenging to complete features like lane tracking.
-The plant models developed in this work will aid in the development of controllers that will remove the nonlinearities allowing features like lane tracking to be implemented in a safer, smoother manner.
+The plant models developed in this work will aid in the development of controllers that will remove the nonlinearities, allowing features like lane tracking to be implemented in a safer, smoother manner.
 
@@
 The NARX model we developed was accurate for the by-wire model and tracked the output of the acceleration system data, but did not meet the error requirements.
-The transfer function model we developed was more reliable tracking the output of the acceleration system data for the manual mode operation, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks.
-Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB.
-With the neural network model, the model was able to reliably and accurately track the output of the acceleration system data and stayed within the error requirements.
+The transfer function model we developed was more reliable tracking the output of the acceleration system data for the manual mode operation, but was unable to meet the error requirements, due to sudden changes that caused high error peaks.
+We then tried using a neural network model, using the Neural Network Time Series Toolbox in MATLAB.
+The neural network model reliably and accurately tracked the output of the acceleration system data while staying within the error requirements.
 
@@
 After generating multiple transfer function models and trying many different data log combinations, we still couldn’t find a model that was completely accurate across all combinations and that was below the error bound of 5\% for all combinations.
-Once this became clear Neural Network models were created using the Neural Network Time Series Toolbox provided by MATLAB to see if they could create accurate brake models.
+Once this became clear, neural network models were created using the Neural Network Time Series Toolbox provided by MATLAB to see if they could create accurate brake models.
 Using this we were able to create a model that accurately tracked the data we collected from the brake system and that stayed within the 5\% error bound.
@@
 Fig.~\ref{fig:lexusvehicle}. %
-The following  the hardware components required to collect the data:
+The following hardware components that were used to collect the data:
 	\begin{itemize}
@@
 %
-In Fig.~\ref{fig:InitialSteeringModel}, the top plot shows the simulated output of the neural network when the input torque voltages and desired steering angle from a subset of data (subset~\#1) collected offline is fed into the model.
+In Fig.~\ref{fig:InitialSteeringModel}, the top plot shows the simulated output of the neural network (Actual Output and Desired Output) when the input torque voltages and desired steering angle from a subset of data (subset~\#1) collected offline is fed into the model.
 The bottom plot shows the error between the desired steering angle and the output of the neural network.
@@
 Fig.~\ref{testedAccelModel} shows the same plots except data subset 2 was used instead.
+The model generated was able to follow the data from the logs very closely, and so met the accuracy requirements we had set.
 
@@
 The y-axis for both graphs, “Output and Target” represents the Actual and Desired Brake Pedal Position as a percentage.
+Target represents the pedal position values from the brake data log we fed into our model.
+Output represents the pedal position values that the model produced.
 The x-axis for both graphs represents the Time Steps, with $T_s$ equal to 33ms.
+The brake subsystem neural network model was able to meet both the best fit and error requirements that had been set earlier, making it an accurate model.
 
@@
 These models that were developed met the predefined accuracy requirements, and so were tested using an open loop setup.
-For the conciseness, we  presented HIL plant modeling for three subsystems, which are steering, brake, and acceleration subsystems of the Lexus vehicle available at AutonomouStuff (the company who sponsored the project).
+For conciseness, we presented HIL plant modeling for three subsystems, which are the steering, brake, and acceleration subsystems of the Lexus vehicle available at AutonomouStuff (the company who sponsored the project).
 Further testing should be completed for these subsystem models.
-Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop.
-Further testing is important to make sure the developed models are accurate and compatible with testing using hardware.
+Since time and availability constraints prevented us from testing the models using Hardware-in-the-Loop, further testing is important to make sure the developed models are accurate and compatible with testing using hardware.
 Future work  could be to start developing controllers based off of these models.

### 2022-10-12 paperIEEE-ROSE2022-Pres.tex
IEEE ROSE Presentation and Paper Work
I made some slight changes to the presentation and added to the paper abstract

@@
 
-\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
+\author[H.~Grady, N.~Nauman, Md Suruz~Miah]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
 % - Give the names in the same order as the appear in the paper.
@@
 
-\begin{frame}
+%\begin{frame}
+%
+%  Therefore, approximated output signal can be written as:
+%\begin{align}
+%  \label{eq:approximatePolicyActorWeights}
+%    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
+%  \end{align}
+%%
+%where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
+%%
+%\begin{align*}
+%  {\bf W} = 
+%  \begin{bmatrix}
+%    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
+%    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
+%    \vdots & \ddots & \ldots &\vdots\\
+%    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
+%  \end{bmatrix}.
+%\end{align*}
+%%
+%
+%Now take $\eta$ data points and form the set of linear equations as: %
+%%
+%\begin{align*}
+%&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
+% & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
+%                                            &\vdots \\
+% & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
+%\end{align*}
+%%
+%\end{frame}
 
-  Therefore, approximated output signal can be written as:
-\begin{align}
-  \label{eq:approximatePolicyActorWeights}
-    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
-  \end{align}
+%\begin{frame}
+%  In compact form:
+%  \begin{align*}
+%    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
+%    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
+%  \end{align*}
+%  %
+%  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
 %
-where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
+%  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
+%  \begin{align*}
+%    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
+%  \end{align*}
 %
-\begin{align*}
-  {\bf W} = 
-  \begin{bmatrix}
-    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
-    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
-    \vdots & \ddots & \ldots &\vdots\\
-    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
-  \end{bmatrix}.
-\end{align*}
+%Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
+%%
+%\begin{align*}
+%  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
+%\end{align*}
+%%
+%Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
+%%
+%\begin{align}
+%  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
+%  \label{eq:actorWeightsGradient}
+%\end{align}
+%%
 %
+%\end{frame}
 
-Now take $\eta$ data points and form the set of linear equations as: %
+%\begin{frame}
 %
-\begin{align*}
-&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
- & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
-                                            &\vdots \\
- & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
-\end{align*}
 %
-\end{frame}
-
-\begin{frame}
-  In compact form:
-  \begin{align*}
-    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
-    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
-  \end{align*}
+%  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yields
+%  \begin{align*}
+%    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
+%  \end{align*}
 %  
-  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
-
-  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
-  \begin{align*}
-    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
-  \end{align*}
-
-Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
+%$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
 %
-\begin{align*}
-  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
-\end{align*}
+%\begin{multline}
+%  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
+%  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
+%  \label{eq:actorWeightUpdate}
+%\end{multline}
 %
-Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
-%
-\begin{align}
-  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
-  \label{eq:actorWeightsGradient}
-\end{align}
-%
-
-\end{frame}
-
-\begin{frame}
-
-  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yeilds
-  \begin{align*}
-    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
-  \end{align*}
-
-$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
-
-\begin{multline}
-  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
-  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
-  \label{eq:actorWeightUpdate}
-\end{multline}
-
-\end{frame}
+%\end{frame}
 

### 2022-11-07 paperIEEE-ROSE2022-Pres.tex
Made changes to IEEE Presentation
I changed the graphs for the steering transfer function models and added some text to different slides.

@@
 	\begin{minipage}[t]{0.62\linewidth}    
-    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
+    Proposed vehicle subsystem models are expected to fulfill requirements listed below'
+    :
 	\begin{itemize}
     		\item Resulting plant model will consist of reasonably accurate subsystem models
-    		\item Subsystems can be used to create a HIL testbench
+    		\item Subsystem models must reach an accuracy level of at least 95\% 
+    		%\item Subsystems can be used to create a HIL testbench
     		\item Steering model can handle very small changes in steering angles
@@
 	\begin{block}{Manual Mode}
+	\begin{itemize}
+			\item x-axis represents time in seconds 
+			\item y-axis represents the steering angle in radians
+			\item Model was able to achieve a best fit percentage of 83.25\% 
+ 		\end{itemize}
+ 		\begin{figure}
+    			\centering
+    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
+    			\caption{Output of Estimated By-Wire System Model}
+        		\label{fig:byWireSteerModel}
+ 		\end{figure}
+% 		\begin{figure}
+%		    \centering
+%		    \includegraphics[width=0.4\textwidth]{figs/img/byWireSteeringTransferFunctionModel}
+%		    \caption{Output of Estimated Manual System Model}
+%		        \label{fig:manualSteerModel}
+% 		\end{figure}
+  	\end{block}
+\end{frame}
+
+\begin{frame}{Transfer Function Modeling}{Steering System Simulation (Cont.)}
+	\begin{block}{By-Wire Mode}
+		\begin{itemize}
+			\item x-axis represents time in seconds 
+			\item y-axis represents the steering angle in radians
+			\item Model was able to achieve a best fit percentage of 86.87\% 
+ 		\end{itemize}
  		\begin{figure}
@@
  		\end{figure}
-  	\end{block}
-\end{frame}
-
-\begin{frame}{Transfer Function Modeling}{Steering System Simulation (Cont.)}
-	\begin{block}{By-Wire Mode}
-		\begin{figure}
-    			\centering
-    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
-    			\caption{Output of Estimated By-Wire System Model}
-        		\label{fig:byWireSteerModel}
- 		\end{figure}
+%		\begin{figure}
+%    			\centering
+%    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
+%    			\caption{Output of Estimated By-Wire System Model}
+%        		\label{fig:byWireSteerModel}
+% 		\end{figure}
 	\end{block}
@@
 	\begin{block}{Manual Mode}
+		\begin{itemize}
+			\item x-axis represents time in seconds 
+			\item y-axis represents the acceleration pedal position as a percentage 
+			\item Model was able to achieve a best fit percentage of 98.3\% 
+ 		\end{itemize}
  		\begin{figure}
@@
 	\begin{block}{By-Wire Mode}
+			\begin{itemize}
+			\item x-axis represents time in seconds 
+			\item y-axis represents the acceleration pedal position as a percentage 
+			\item Model was able to achieve a best fit percentage of 97.69\% 
+ 		\end{itemize}
 		\begin{figure}
@@
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item Only a few samples are just outside of the accuracy requirements
-			\item Transfer function model did not meet the accuracy requirements
+			\item \begin{small} Only a few samples are just outside of the accuracy requirements \end{small}
+			%\item \begin{small} Transfer function model did not meet the accuracy requirements \end{small} 
+			\item \begin{small} y-axis of top graph represents the actual and desired steering angle in radians \end{small} 
 			\end{itemize} \end{minipage}\\[1em]
@@
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item All samples within 2\% of the actual output
-			\item Transfer function model did not have the same accuracy bounds
-			\item Fewer concerns about connections in Simulink
+			\item \begin{small} All samples within 2\% of the actual output \end{small}
+			\item \begin{small} y-axis of top graph represents the actual and desired acceleration pedal position as a percentage \end{small} 
+			\item \begin{small} Fewer concerns about connections in Simulink \end{small} 
 			\end{itemize} \end{minipage}\\[1em]
@@
 			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
-			\item With this model, the error is kept below 5\%
-			\item Able to easily track model performance
-			\item Provides better results than the transfer function model
+			\item \begin{small} With this model, the error is kept below 5\% \end{small} 
+			\item \begin{small} y-axis of top graph represents the actual and desired brake pedal position as a percentage \end{small}
+			\item \begin{small} Provides better results than the transfer function model \end{small} 
 			\end{itemize} \end{minipage}\\[1em]

### 2022-11-13 paperIEEE-ROSE2022-Pres.tex
Added y-axis range to tf slides
Made changes to deep learning slides
I edited the bullet point containing the y-axis descriptions for the deep learning slides.

@@
 	\begin{itemize}
-			\item x-axis represents time in seconds 
-			\item y-axis represents the steering angle in radians
+%			\item x-axis represents time in seconds 
+			\item y-axis represents the steering angle in radians; range of -10 to 10
 			\item Model was able to achieve a best fit percentage of 83.25\%
+
  		\end{itemize}
@@
 		\begin{itemize}
-			\item x-axis represents time in seconds 
-			\item y-axis represents the steering angle in radians
+%			\item x-axis represents time in seconds 
+			\item y-axis represents the steering angle in radians; range of -10 to 10
 			\item Model was able to achieve a best fit percentage of 86.87\% 
@@
 		\begin{itemize}
-			\item x-axis represents time in seconds 
-			\item y-axis represents the acceleration pedal position as a percentage 
+%			\item x-axis represents time in seconds 
+			\item y-axis represents the acceleration pedal position as a percentage; range of -0.2 to 1.2 
 			\item Model was able to achieve a best fit percentage of 98.3\% 
@@
 			\begin{itemize}
-			\item x-axis represents time in seconds 
-			\item y-axis represents the acceleration pedal position as a percentage 
+%			\item x-axis represents time in seconds  
+			\item  y-axis represents the acceleration pedal position as a percentage; range of -0.2 to 1.2 
 			\item  Model was able to achieve a best fit percentage of 97.69\% 
@@
 			%\item \begin{small} Transfer function model did not meet the accuracy requirements \end{small} 
-			\item \begin{small} y-axis of top graph represents the actual and desired steering angle in radians \end{small} 
+			\item \begin{small} y-axis of the top graphs represents the steering angle in radians \end{small} 
 			\end{itemize} \end{minipage}\\[1em]
@@
 			\item \begin{small} All samples within 2\% of the actual output \end{small}
-			\item \begin{small} y-axis of top graph represents the actual and desired acceleration pedal position as a percentage \end{small} 
+			\item \begin{small} y-axis of the top graphs represents the acceleration pedal position as a percentage \end{small} 
 			\item \begin{small} Fewer concerns about connections in Simulink \end{small} 
@@
 			\item \begin{small} With this model, the error is kept below 5\% \end{small} 
-			\item \begin{small} y-axis of top graph represents the actual and desired brake pedal position as a percentage \end{small}
+			\item \begin{small} y-axis of the top graphs represents the brake pedal position as a percentage \end{small}
 			\item \begin{small} Provides better results than the transfer function model \end{small} 
